### 2022-10-05 paper.qmd
bunch of updates

---
title: "paper"
format: pdf
editor: visual
author:
  - name: Lindsay Katz
  - name: Rohan Alexander
---

# Introduction
- Mention the available formats of Hansard

# Existing Datasets
- What already exists, and how has it been used
- How are these existing data sets lacking?
- How do we account for this in our data set?
    - WhoGov article has good summary table offering comparison to other existing data sets

# Description of the Dataset
- I figure this would be a good spot to highlight everything within the dataset, as well as descriptive statistics

# Creation of the Dataset

## Interjections

## Question time

# Validation
- Might also mention strengths and weaknesses of our dataset

# Applications

# Conclusion

# References

### 2022-10-05 scripts/00-scrape_files.R

@@ -1,0 +1,59 @@
+### scraping Hansards
+library(heapsofpapers)
+library(tidyverse)
+library(here)
+
+# 2010-2022
+# read in excel sheet with URLs
+urls_df <- read.csv(here("hansard-urls-2010-2022.csv"))
+
+# define tibble with URLs and file names
+urls <- tibble(locations_are = urls_df$URL, 
+                      save_here = urls_df$file_name)
+
+# get and save files
+heapsofpapers::get_and_save(data=urls,
+                            links = "locations_are",
+                            save_names = "save_here",
+                            dir = "/Volumes/Verbatim/input",
+                            dupe_strategy = "overwrite")
+
+# 2000-2009
+# read in excel sheet with URLs
+urls_df <- read.csv(here("hansard-urls-2000-2009.csv"))
+
+# two dates are missing XMLs so I left the url blank, filter those out
+urls_df <- urls_df %>% filter(URL!="")
+
+# define tibble with URLs and file names
+urls <- tibble(locations_are = urls_df$URL, 
+               save_here = urls_df$file_name)
+
+# get and save files
+heapsofpapers::get_and_save(data=urls,
+                            links = "locations_are",
+                            save_names = "save_here",
+                            dir = "/Volumes/Verbatim/input",
+                            dupe_strategy = "overwrite")
+
+# issue with link from 2022 had to fix
+urls2 <- tibble(locations_are = "https://parlinfo.aph.gov.au/parlInfo/download/chamber/hansardr/25917/toc_unixml/House%20of%20Representatives_2022_07_26_Official.xml;fileType=text%2Fxml",
+       save_here = "2022-07-26.xml")
+heapsofpapers::get_and_save(data=urls2,
+                            links = "locations_are",
+                            save_names = "save_here",
+                            dir = "/Volumes/Verbatim/input",
+                            dupe_strategy = "overwrite")
+
+# issue with link from 2017 had to fix
+urls2 <- tibble(locations_are = "https://parlinfo.aph.gov.au/parlInfo/download/chamber/hansardr/7acf60a0-3455-43aa-bfd0-083a6b4252db/toc_unixml/House%20of%20Representatives_2017_06_14_5147_Official.xml;fileType=text%2Fxml",
+                save_here = "2017-06-14.xml")
+heapsofpapers::get_and_save(data=urls2,
+                            links = "locations_are",
+                            save_names = "save_here",
+                            dir = "/Volumes/Verbatim/input",
+                            dupe_strategy = "overwrite")
+
+
+
+

### 2022-10-05 scripts/01-session_info.R

@@ -10,7 +10,7 @@ library(tidyverse)
 parse_session_info <- function(filename){
   
   # parse XML file
-  hansard_xml <- xmlParse(here("input", filename))
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
   
   # store session information in tibble, correct class of variables
   session_info <- xmlToDataFrame(node=getNodeSet(hansard_xml, "//session.header")) %>% 
@@ -26,5 +26,5 @@ parse_session_info <- function(filename){
 }
 
 # call function, pass file name
-parse_session_info("2022_08_01.xml")
+parse_session_info("2018-08-23.xml")
 

### 2022-10-05 scripts/02-debate_info.R

@@ -10,7 +10,7 @@ library(tidyverse)
 parse_debate_info <- function(filename){
   
   # parse XML file
-  hansard_xml <- xmlParse(here("input", filename))
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
   
   #################### CHAMBER ####################
   ######### BUSINESS START #########
@@ -31,6 +31,15 @@ parse_debate_info <- function(filename){
            fedchamb_flag = 0,
            sub1_flag = 0,
            sub2_flag = 0)
+  
+  ######### DEBATE SPEECH #########
+  debate_speech_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/speech/talk.start/talker")),
+                             xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/speech/talk.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+           time.stamp = {if ("body" %in% names(.)) str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d") else NULL},
+           party = {if("party" %in% names(.)) as.factor(party) else NULL},
+           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
   
   #################### FEDERATION CHAMBER ####################
   # use if-else statement to ensure code works for Hansard with and without federation chamber
@@ -63,6 +72,19 @@ parse_debate_info <- function(filename){
     # merge chamber & federation chamber tibbles into single debate information tibble
     debate_info <- rbind(debate_info_chamb, debate_info_fed)
     
+    ######### DEBATE SPEECH #########
+    # store debate speech that aren't part of sub-debates
+    debate_speech_fed <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//fedchamb.xscript/debate/speech/talk.start/talker")),
+                                 xmlToDataFrame(node=getNodeSet(hansard_xml, "//fedchamb.xscript/debate/speech/talk.text"))) %>% 
+      as_tibble() %>% 
+      mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+             time.stamp = {if ("body" %in% names(.)) str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d") else NULL},
[…]

### 2022-10-05 scripts/03-subdebate_1.R

@@ -5,11 +5,13 @@ library(XML)
 library(here)
 library(tidyverse)
 
+######## TUESDAY 6:00 NEED TO ADD IF-ELSE TO SUBDEBATE 1 CHAMBER.
+
 # define function
 parse_sub1 <- function(filename){
   
   # parse XML
-  hansard_xml <- xmlParse(here("input", filename))
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
 
   # # define interjection words - commenting this out b/c found better way to do so after everything is split (see 99-everything script)
   # interject_words <- c("Order!", "Order.", "interjecting", "Interjecting", "interjected", "Interjected", "interjections", "interjection", "Interjections", 
@@ -25,17 +27,17 @@ parse_sub1 <- function(filename){
   sub1_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebateinfo")),
                            xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.text"))) %>%
     as_tibble() %>% 
-    mutate(page.no = as.numeric(page.no),
-           fedchamb_flag = 0)
+    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
   
   # store sub-debate 1 talker info & speech in tibble, correct variable class, add flag for federation chamber, extract time
   sub1_speech_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
                              xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
     as_tibble() %>% 
-    mutate(page.no = as.numeric(page.no),
-           time.stamp = str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d"),
-           party = as.factor(party),
-           fedchamb_flag = 0)
+    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
[…]

### 2022-10-05 scripts/04-subdebate_2.R

@@ -9,17 +9,8 @@ library(tidyverse)
 parse_sub2 <- function(filename){
   
   # parse XML
-  hansard_xml <- xmlParse(here("input", filename))
-  
-  # # define interjection words
-  # interject_words <- c("Order!", "Order.", "interjecting", "Interjecting", "interjected", "Interjected", "interjections", "interjection", "Interjections", 
-  #                      "Interjection", "interject", "Interject", "The time for the discussion has concluded", "I thank the honourable member for", 
-  #                      "I thank the member for", "should withdraw that remark", "In accordance with standing order 193 the time for constituency statements has concluded", 
-  #                      "There being no further grievances, the debate is adjourned","the time for members' statements has concluded", 
-  #                      "The original question was that this bill be now read a second time", "Is the amendment seconded?",
-  #                      "Do you want to seek the call again?", "The question is that the amendment be disagreed to", "The question now is that the bill be agreed to", 
-  #                      "will resume his seat", "will resume her seat", "will resume their seat")
-  
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+
   #### CHAMBER ####
   # store sub-debate 2 information & text in tibble, correct variable class, add flag for federation chamber
   # include if-else statements in case sub-debate 2 does not exist
@@ -29,6 +20,19 @@ parse_sub2 <- function(filename){
     mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
            fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
   
+  # sometimes sub-debate 2 isn't nested in sub-debate 1 (most recent date where this is the case is 2021-10-21)
+  # if the number of rows of this is > 1, let's bind that onto what we already have to ensure we aren't missing anything
+  if (nrow(as_tibble(cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebateinfo")),
[…]

### 2022-10-05 scripts/05-debate_interjections.R

@@ -8,7 +8,7 @@ library(tidyverse)
 parse_interject <- function(filename){
   
   # parse XML
-  hansard_xml <- xmlParse(here("input", filename))
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
   
   #### CHAMBER ####
   # sub-debate 1 speech interjections in tibble, correct variable class, add flag for federation chamber

### 2022-10-05 scripts/06-q_and_a.R

@@ -9,15 +9,7 @@ library(tidyverse)
 parse_q_and_a <- function(filename){
   
   # parse XML
-  hansard_xml <- xmlParse(here("input", filename))
-  
-  # define interjection words
-  # interject_words <- c("Order!", "Order.", "interjecting", "Interjecting", "interjected", "Interjected", "interjections", "interjection", "Interjections", 
-  #                      "Interjection", "interject", "Interject", "The time for the discussion has concluded", "I thank the honourable member for", "I thank the member for", "should withdraw that remark", 
-  #                      "In accordance with standing order 193 the time for constituency statements has concluded", "There being no further grievances, the debate is adjourned",
-  #                      "the time for members' statements has concluded", "The original question was that this bill be now read a second time", "Is the amendment seconded?",
-  #                      "Do you want to seek the call again?", "The question is that the amendment be disagreed to", "The question now is that the bill be agreed to", "will resume his seat", "will resume her seat",
-  #                      "will resume their seat") 
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
   
   #### QUESTION AND ANSWER INFO AND TEXT ####
   # store questions in tibble, correct variable class, add flag for question/answer, extract time

### 2022-10-05 scripts/99-everything2.R

@@ -1,5 +1,6 @@
 # script to parse everything from Hansard
-# WORKS FOR 2011-05-10 TO PRESENT - BUT LOTS OF FORMATTING ISSUES TO DEAL WITH
+# TRYING TO FIX PARSING ISSUE WHICH STOPS AFTER 2011-03-24
+# issue is with debate info parsing
 
 # read in necessary packages
 library(XML)
@@ -100,7 +101,7 @@ split_interjections <- function(main, interject, bus_start){
   } else {
     all_names <- c()
   }
-
+  
   
   # now, add to all_names list using names of speakers from main data frame
   all_names <-  main_orig %>% 
@@ -457,7 +458,7 @@ split_interjections <- function(main, interject, bus_start){
   } else {
     name_info <- c()
   }
-
+  
   if ("SPEAKER" %in% name_info$last_name) {
     name_info <- main %>% filter(str_detect(name, "The SPEAKER") & !is.na(party)) %>% 
       select(c(name.id, electorate, party, name)) %>% unique() %>% 
@@ -507,7 +508,7 @@ split_interjections <- function(main, interject, bus_start){
       select(-name) %>% 
       rbind(., name_info)
   }
-
+  
   # get names of all speakers from main data frame (MPs)
   name_info <- main_orig %>% 
     select(c(name, name.id, electorate, party)) %>% 
@@ -637,7 +638,7 @@ split_interjections <- function(main, interject, bus_start){
 
 # define script as function with filename argument
 parse_hansard <- function(filename){
-
+  
   # parse XML
   hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
   
@@ -655,37 +656,32 @@ parse_hansard <- function(filename){
   #################### CHAMBER ####################
   ######### BUSINESS START #########
   # store business start in tibble, add flag for federation chamber, extract date, body, and start time
-  # in rare cases (ex. 2016-08-30, there is no business start, so add if-else in case of this)
   if (nrow(tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"))))>0) {
-    bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start")), 
-                              fedchamb_flag = 0)
-    
[…]

### 2022-10-17 paper/paper.qmd
adding paper docs

---
title: "Digitization of the Australian Parliamentary Debates (1901-2022)"
number-sections: true
format: pdf
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - name: Lindsay Katz
  - name: Rohan Alexander
abstract: "Parliamentary dialogue is critical for political science research. In Australia, following the UK tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality to be credibly analysed with statistical models. Following the lead of the Lipad project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard. Our dataset will be publicly available and linked to other datasets such as election results. The creation of this dataset will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers. This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications."
---

# Introduction {#sec-intro}

------ need better intro bit here ------ The official written record of parliamentary debates, formally known as Hansard, play a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of these reports became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history]. Given the contents and sheer magnitude of these records, their value cannot be overstated - particularly in the context of political science research. In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavor called the Linked Parliamentary Data (LiPaD) project [@lipad]. Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling. Inspired by the LiPaD project, in this paper we introduce a novel database for Australian Hansard. This is composed of individual datasets for each sitting day in the House of Representatives, containing details on everything said in parliament in a form which can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve has a valuable resource for studying and exploring political behaviour in Australia over time.

The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. Sittings of the House in the follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber includes debates on government business, 90 second member statements, Question Time, document presentation, matters of public importance, ministerial statements, and an adjournment debate [@australia2018house, ch. 8]. In contrast to the Chamber, sittings in the Federation Chamber are quite different in terms of their order of business and scope of discussion. The Federation Chamber was created in 1994 as a subordinate debate venue, to allow for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bills, and the business of private Members [@australia2018house, ch. 21]. It is the compilation of these proceedings upon which Hansard is based.

On each sitting day, a transcript is available for download from the official Parliament of Australia website in both scanned PDF and extensible markup language (XML) form. The scanned PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt2016]. This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions. Our database has been developed solely using the XML formatted files. The choice to create this database using the potentially incomplete or flawed XML format of Hansard as opposed to the scanned PDF is ---- mention previous work on this using the PDF and this motivated us to try to parse things from the XML side this time ------ .

The end goal for this work is to create a publicly available database of parsed Hansard transcripts from 1901 to present in a form which can be readily analyzed. More specifically, each transcript is presented in an ordered form with details on each speaker such as their political affiliation, the time stamp of their statement, and whether they interjected (i.e. spoke out of turn). Thus far, this has been completed from 2011 to present. Due to the extensive variation in structural formatting of these transcripts, additional work is needed to parse transcripts from further in the past.

We begin this paper with a description of what datasets for Australian Hansard already exist will be provided (@sec-existing). Next will be a detailed description of the contents of our database (@sec-description), followed by a thorough discussion of how this database was created (@sec-create). Finally, @sec-apps provides a description of some applications of our database.

# Existing Datasets {#sec-existing}

-   What already exists, and how has it been used
-   How are these existing data sets lacking?
-   How do we account for this in our data set?
    -   WhoGov article has good summary table offering comparison to other existing data sets

# Description of the Database {#sec-description}

Our database thus far contains 1388 CSV files, one for each sitting day of the House of Representatives from 10 May 2011 to 08 September 2022. Each CSV is produced from the same script, so all files in our database are formatted and processed in the exact same way. @fig-main_ex_15rows provides a snapshot of one of these files.

![First 15 rows of CSV file for Hansard on 25 February 2020](main_ex15.png){#fig-main_ex_15rows}

```{r}
#| warning: false
#| echo: false

library(readr)
library(tidyverse)
library(here)
library(XML)
library(lubridate)

##### re-run this after fixing things up in case names changed etc.
main_ex <- read_csv("/Volumes/Verbatim/output/main/2020-02-25-main.csv", show_col_types = F)

main_ex_vars <- tibble("Variable" = names(main_ex),
       "Description" = c("Name of speaker",
                         "Row number",
                         "Speech number, to keep track of which separated text belonged to which original speech",
                         "Page number statement can be found on in official Hansard",
                         "Time of statement",
                         "Unique member identification code",
                         "Speaking member's electorate",
                         "Speaking member's party",
                         "Statement text",
                         "Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)",
                         "Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)",
                         "Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)",
                         "Flag for question (1 if question, 0 otherwise)",
                         "Flag for answer (1 if answer, 0 otherwise)",
                         "Flag for interjection (1 if statement is an interjection, 0 otherwise)"))

knitr::kable(main_ex_vars, booktabs=T)
```
-   number missing (so far two days in 2014)
-   number unique speakers
-   avg number of rows per day
-   number of interjections (graph over time?)

```{r}
#| warning: false
#| echo: false

# grab list of all file names
all_files <- list.files("/Volumes/Verbatim/input")

# extract year month and day
all_files <- all_files %>% 
  str_remove(".xml") %>% 
  as_tibble() %>% 
  mutate(year = as.numeric(str_extract(value, "^[[:digit:]]{4}")),
         month = as.numeric(str_extract(value, "(?<=\\-)[[:digit:]]{2}(?=\\-)")),
         day = as.numeric(str_extract(value, "(?<=\\-)[[:digit:]]{2}$")))

# plot of total number of sitting days per year
all_files %>% 
  filter(year!=2022) %>% 
  group_by(year) %>% 
  summarise(tot_days = sum(unique(day))) %>% 
  ggplot(aes(x=year, y=tot_days)) + 
  geom_point() +
  geom_line() + 
  theme_bw() +
  labs(x = "Year", 
       y = "Count", 
       title = "Total number of sitting days per year (2000-2021)")

# plot of average number of sitting days per month
# adding rows for January and July which are always zero (no sitting days in these months)
# not sure if I should incldue for visual purposes or leave out
# all_files %>% 
#   filter(year==2020) %>%
#   add_row(year=2020, month=1) %>% 
#   add_row(year=2020, month=7) %>% 
#   mutate(month_abb = month.abb[month]) %>% 
#   group_by(month, month_abb) %>% 
#   summarise(avg_days = mean(unique(day))) %>% 
#   ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
#   geom_col() + 
#   theme_bw() + 
#   labs(x = "Month", 
#        y="Average sitting days", 
#        title = "Average number of sitting days per month (2020)")

all_files %>% 
  filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
  mutate(month_abb = month.abb[month]) %>% 
  group_by(year, month_abb) %>% 
  summarise(avg_days = mean(unique(day))) %>% 
  ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
  geom_col() + 
  facet_wrap(~year) +
  theme_bw() + 
  labs(x = "Month", 
       y="Average sitting days", 
       title = "Average number of sitting days per month (2015-2020)") +
  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
```

# Creation of the Database {#sec-create}

The approach to parsing contents of an XML document is heavily dependent on its tree structure. As such, to create this database, we started by looking at a single Hansard transcript in XML form. Doing so enabled us to understand the various components of interest in the document, and how each one can be parsed according to its corresponding structural form. For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them. Extracting and correctly organizing these nested sub-elements required careful consideration. ---- this sentence feels incomplete / out of place -------. Parsing was performed in `R` using the `XML` package. Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible. Further, since we are looking at such a wide time span of these documents, there are expectedly a number of changes in the way they are formatted. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting. As mentioned in section @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.

----- should I add little example of the XML to give the reader a visual?? it's hard to put into words clearly -----

The XML structure begins with a root or parent element "hansard", followed by a child element "session header" with sub-child elements with information such as the date, and parliament number. Next there is a child element containing everything that takes place in the Chamber, "chamber.xscript". On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too. This allows for the distinction of proceedings of the Chamber and Federation Chamber. Each proceeding begins with a business start, naming the speaker and what time they took the chair. Next comes the debates and nested sub-debates. Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it. That said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of these three elements as well as their respective sub-elements contain important information on the title of the debate or sub-debate, who is speaking, and what is being said. As mentioned, in many cases speeches are interrupted by interjections, which are embedded in these sub-elements as well. The final key distinct component of Hansard is Question Time, in which question and answer elements are classified differently than general debate text. Sometimes questions and answers are nested within debate or sub-debate child nodes, and other times they have their own child node. More detail on the processing of Question Time will follow in @sec-qa.

Once code was written to parse all components, it was organized into individual scripts. The first script includes everything from the session header element, the second contains everything from the debate element, and the third and fourth contain everything from the sub-debate 1 and 2 elements, respectively. The fifth script contains debate interjection information, and the sixth contains content from Question Time. The final script is a compilation of everything. The next step was to further develop these scripts to produce tidy data sets from each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order. This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2. The next key task revolved around the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by the Speaker and Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person who's turn it was to speak. Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort. @sec-interject will provide further details on the intricacies of this task.

When running these scripts on transcripts from other sitting days, it became clear that not every sitting day contains every possible XML element. For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file. Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. Specifically, the earliest date for which it works is 10 May 2011. Before writing a new script for parsing earlier Hansard, we decided to prioritize cleaning and finalizing what we have been able to parse. As such we continued building our scripts, fixing any issues we noticed in the resulting datasets, and separating any additional sections of the parsed text where necessary. Specifically, we added a section of our script to separate on general stage directions. More information on this separation will be provided in @sec-stage.

## Question Time {#sec-qa}

A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions with notice (often referred to as questions in writing), which are written in advance, or questions without notice, which are asked verbally in the Chamber and are responded to in real time [@house2021]. Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document. Sometimes, questions in writing are included directly in the "chamber.xscript" child node, with sub-child nodes called "question" and "answer" to differentiate the two. However, in other times, questions in writing are embedded in their own child node called "answers.to.questions" outside of "chamber.xscript". Difficulty arose when trying to order these questions and answers correctly within the rest of the debate text, because unlike all other statements made which have both an associated page number and time stamp, these generally only have associated page numbers. Time stamps have been a key variable for which we have arranged parsed text in chronological order, especially since many statements tend to be on the same page number, meaning we cannot rely solely on page number to capture correct ordering. To approach this issue, we merged all parsed questions to be in a single dataframe, and all parsed answers in another dataframe. We then arranged each dataframe by page number, and merged the two dataframes in such a way that each question would be followed by it's corresponding answer.

## Interjections {#sec-interject}

-   First thought was to use a number of phrases, but it would be really difficult to create an exhaustive list manually

-   Once all the text were split to have a different row for each interjection/continuation etc, we could just flag for interjections automatically b/c i kept the original row number that the speech started on so I could flag if the original speaker or speaker/deputy speaker wasnt speaking, it was an interjection

-   Had to consider a ton of different names and possible formatting of the names
    -   Ex: last name only, two first names, last names with two words or hyphen or apostrophe, people with the same last name
    -   had to also find a way to match these various formats to the name id, electorate, party info

-   Also had to consider general interjections that are not directly named, such as "an opposition member" or "government members", or "Mr Smith interjecting-"

-   Some people have no first name so couldn't manually extract their info (i.e. electorate, party etc.)

Tons of variation in how names are formatted (Capitalization makes it super difficult with regex) - also pre 2021 the speaker is not fully identified the same way as in 2021 2022 - just lots of small changes to account for

## Stage Directions {#sec-stage}

As mentioned, one of the final components added to our script was to separate general stage directions out from statements made by members. Stage directions are general statements included in the transcript to document happenings in the Chamber. Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned". It is unclear from the XML and PDF who exactly these statements are attributed to, or in other words, who are making these statements. For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time - but this is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". It is important to note that these stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually build a list of stage directions to separate out. We have been building this list of stage directions as we work backwards in parsing Hansard.

# Applications {#sec-apps}

# Conclusion {#sec-conclusion}

# References

### 2022-10-17 scripts/99-everything.R
updated everything script

@@ -33,11 +33,23 @@ split_interjections <- function(main, interject, bus_start){
       summarise(form1 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
                 form2 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)"),
                 form3 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
-                form4 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)")) %>%
-      pivot_longer(form1:form4, names_to = "type", values_to = "form") %>%
+                form4 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)"),
+                form5 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", str_sub(first_name, end=1), "[[:space:]]", last_name, "\\)"),
+                form6 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", str_sub(first_name, end=1), "[[:space:]]", last_name, "\\)")) %>%
+      pivot_longer(form1:form6, names_to = "type", values_to = "form") %>%
       select(form) %>% 
       unique() %>% 
       pull()
+    
+    # sometimes the names of all deputy speakers aren't captured in main or interject, so let's also manually grab these to avoid missing any
+    interject_names <- str_extract_all(main$body, paste0("The DEPUTY SPEAKER \\((Dr|Mr|Mrs|Ms|Hon.)[[:space:]].{0,50}\\)(?=\\:)")) %>% 
+      na.omit() %>% 
+      unlist() %>% 
+      unique() %>% 
+      as_tibble() %>% 
+      mutate(value = ifelse(str_detect(value, "\\("), str_replace(value, "\\(", "\\\\("), value),
+             value = ifelse(str_detect(value, "\\)"), str_replace(value, "\\)", "\\\\)"), value)) %>% 
+      pull() %>% c(., interject_names)
     
     # next add the ones in form like "Ms Ryan interjecting-"
     interject_names <- interject %>% 
[…]

### 2022-10-17 paper/paper.qmd
fixed graphs

@@
 
+cases where unsure how to proceed w xml always deferred to pdf
+
 The end goal for this work is to create a publicly available database of parsed Hansard transcripts from 1901 to present in a form which can be readily analyzed.
@@
     -   WhoGov article has good summary table offering comparison to other existing data sets
+
+to this point various researchers have had to create
+
+- tim sherrett (historic hansard) - 
+- patrick leslie has also created a dataset as have others
+rework paragrpah about how these have been used
+
+no comprehensive dataset based on xml that goes from 1901-today
+1930s and before - ocr ruins accuracy (earlier decades)
 
@@
 # plot of total number of sitting days per year
+# numbers are wrong
 all_files %>% 
@@
   group_by(year) %>% 
-  summarise(tot_days = sum(unique(day))) %>% 
+  summarise(tot_days = n()) %>% 
   ggplot(aes(x=year, y=tot_days)) + 
@@
   group_by(year, month_abb) %>% 
-  summarise(avg_days = mean(unique(day))) %>% 
+  summarise(avg_days = n()) %>% 
   ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
@@
   labs(x = "Month", 
-       y="Average sitting days", 
-       title = "Average number of sitting days per month (2015-2020)") +
+       y="Count", 
+       title = "Number of sitting days per month (2015-2020)") +
   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
@@
 For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them.
-Extracting and correctly organizing these nested sub-elements required careful consideration.
----- this sentence feels incomplete / out of place -------.
 Parsing was performed in `R` using the `XML` package.
 Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible.
-Further, since we are looking at such a wide time span of these documents, there are expectedly a number of changes in the way they are formatted.
+Further, since we are looking at such a wide time span of documents, there are expectedly a number of changes in the way they are formatted.
 Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure.
 Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting.
-As mentioned in section @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.
+As mentioned in @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.
 
@@
 
-The XML structure begins with a root or parent element "hansard", followed by a child element "session header" with sub-child elements with information such as the date, and parliament number.
-Next there is a child element containing everything that takes place in the Chamber, "chamber.xscript".
+The XML structure begins with a root or parent element `"hansard"`, followed by a child element `"session.header"` with sub-child elements with information such as the date, and parliament number.
+Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`.
 On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too.

### 2022-10-25 paper/paper.qmd
lots of paper updates

@@
 author:
-  - name: Lindsay Katz
-  - name: Rohan Alexander
+  - Lindsay Katz
+  - Rohan Alexander
 abstract: "Parliamentary dialogue is critical for political science research.
@@
 While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality to be credibly analysed with statistical models.
-Following the lead of the Lipad project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard.
+Following the lead of the LiPaD project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard.
 Our dataset will be publicly available and linked to other datasets such as election results.
@@
 
------- need better intro bit here ------ The official written record of parliamentary debates, formally known as Hansard, play a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
-Originating in the British parliament, the production of these reports became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
-Given the contents and sheer magnitude of these records, their value cannot be overstated - particularly in the context of political science research.
+The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
+Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
+Given the contents and sheer magnitude of these records, their value cannot be overstated, particularly in the context of political science research.
 In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavor called the Linked Parliamentary Data (LiPaD) project [@lipad].
 Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling.
-Inspired by the LiPaD project, in this paper we introduce a novel database for Australian Hansard.
+Following the lead of the LiPaD project, in this paper we introduce a novel database for Australian Hansard.
 This is composed of individual datasets for each sitting day in the House of Representatives, containing details on everything said in parliament in a form which can be readily used by researchers.
-With the development of tools for large-scale text analysis, this database will serve has a valuable resource for studying and exploring political behaviour in Australia over time.
+With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.
 
@@
 1].
-Sittings of the House in the follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch.
+Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch.
 8].
-A typical sitting day in the Chamber includes debates on government business, 90 second member statements, Question Time, document presentation, matters of public importance, ministerial statements, and an adjournment debate [@australia2018house, ch.
+A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch.
 8].
-In contrast to the Chamber, sittings in the Federation Chamber are quite different in terms of their order of business and scope of discussion.
-The Federation Chamber was created in 1994 as a subordinate debate venue, to allow for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch.
+In contrast, the Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber.
+This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch.
 21].
-Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bills, and the business of private Members [@australia2018house, ch.
+Sittings in the Federation Chamber are quite different than those of the Chamber in terms of their order of business and scope of discussion.
+Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch.
 21].
-It is the compilation of these proceedings upon which Hansard is based.
+It is the recording and compilation of all of these proceedings upon which Hansard is based.
 
-On each sitting day, a transcript is available for download from the official Parliament of Australia website in both scanned PDF and extensible markup language (XML) form.
-The scanned PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt2016].
-This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions.
-Our database has been developed solely using the XML formatted files.
-The choice to create this database using the potentially incomplete or flawed XML format of Hansard as opposed to the scanned PDF is ---- mention previous work on this using the PDF and this motivated us to try to parse things from the XML side this time ------ .
-
-cases where unsure how to proceed w xml always deferred to pdf
+On each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form.
+The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt].
+This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt].
+The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility.
+The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files.
+In cases where we were unsure on how to proceed with processing the XML, we always deferred first to the PDF, and then to the video recording of the proceeding if necessary.
 
 The end goal for this work is to create a publicly available database of parsed Hansard transcripts from 1901 to present in a form which can be readily analyzed.
-More specifically, each transcript is presented in an ordered form with details on each speaker such as their political affiliation, the time stamp of their statement, and whether they interjected (i.e.
+More specifically, we aim to present each transcript in an ordered form with details on each speaker such as their political affiliation, the time stamp of their statement (where available), and whether they interjected (i.e.
 spoke out of turn).
-Thus far, this has been completed from 2011 to present.
+Thus far, this has been done for Hansard from mid-2011 to present.
 Due to the extensive variation in structural formatting of these transcripts, additional work is needed to parse transcripts from further in the past.
 
-We begin this paper with a description of what datasets for Australian Hansard already exist will be provided (@sec-existing).
+We begin this paper with a description of what datasets for Australian Hansard already exist (@sec-existing).
 Next will be a detailed description of the contents of our database (@sec-description), followed by a thorough discussion of how this database was created (@sec-create).
-Finally, @sec-apps provides a description of some applications of our database.
 
@@
 
--   What already exists, and how has it been used
--   How are these existing data sets lacking?
--   How do we account for this in our data set?
-    -   WhoGov article has good summary table offering comparison to other existing data sets
+At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis.
+To this point, various researchers have had to create their own databases in an attempt to produce usable, complete Hansard data.
+For instance, @sherratt created an online, easy to read [database](http://historichansard.net) of Hansard from 1901 to 1980 using the XML files.
+These data can be navigated by year, parliament, people, and bills [@sherratt].
+As well, @Leslie_2021_HoR_Aus has released data on all Members of the Australian House of Representatives from 1945 to 2019, and is developing an `R` package for these data.
 
-to this point various researchers have had to create
+A number of papers exist which utilize components of Australian Hansard to explore various research topics.
+For example, @salisbury2011 used online Hansard records to explore the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark.
+@rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
+In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
+Finally, the work of @alexander2021 offers the most complete database for Australian Hansard we have encountered thus far, along with a thorough analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
+@alexander2021 created this database with the static PDF versions Hansard, using OCR to digitize these files into text which is suitable for analysis.
 
-- tim sherrett (historic hansard) - 
-- patrick leslie has also created a dataset as have others
-rework paragrpah about how these have been used
-
-no comprehensive dataset based on xml that goes from 1901-today
-1930s and before - ocr ruins accuracy (earlier decades)
+While there is evidently a growing body of literature on this topic, there is still no comprehensive database for Australian Hansard based on XML that spans from 1901 to the present day.
+Our work serves to bridge this gap.
 
@@
 
-Our database thus far contains 1388 CSV files, one for each sitting day of the House of Representatives from 10 May 2011 to 08 September 2022.
-Each CSV is produced from the same script, so all files in our database are formatted and processed in the exact same way.
-@fig-main_ex_15rows provides a snapshot of one of these files.
+Our current database contains 670 comma-separated values (CSV) files, one for each sitting day of the House of Representatives from 10 May 2011 to 08 September 2022.
+We used two scripts to produce these files, which only have one subtle difference.
+Since the Federation Chamber was renamed in mid-2012 from the original title of Main Committee, the element under which all the Federation Chamber contents are nested in the XML was renamed as well [@australia2018house, ch.
+21].
+This difference in element name means that our original code for parsing Federation Chamber contents would not work, as the specified node path would be incorrect.
+We accounted for this by creating a separate script with this name change.
+Our first script parses Hansard from 14 August 2012 to 08 September 2022, that being everything after the Federation Chamber name change, and the second script parses Hansard from 10 May 2011 to 28 June 2012.
+All output files in our database are formatted and processed in the exact same way.
+@fig-main15rows provides a snapshot of one of these files.
 
-![First 15 rows of CSV file for Hansard on 25 February 2020](main_ex15.png){#fig-main_ex_15rows}
+![First 15 rows of CSV file for Hansard on 25 February 2020](main_ex15.png){#fig-main15rows}
+
+Evidently, each row of the CSV file contains an individual statement, with the unique name ID, electorate, and party information of the speaker.
+Of course, for general statements such as "Honourable members", these variables cannot be specified.
+Each proceeding in the Chamber begins with the business start, where the time that The Speaker took the chair is documented, as well as the acknowledgment of the country and reading of the prayers as governed by the standing orders of the House [@standingorders, ch.
+6].
+Federation Chamber also begins with a business start, where it is stated at what time The Deputy Speaker takes the chair.
+For further clarification on each variable in the resulting CSV, @tbl-vars provides an overview of each variable in the database.
 
@@
 #| warning: false
+#| message: false
 #| echo: false
+#| label: tbl-vars
+#| tbl-cap: "Summary and description of variables in our database"
 
+# read in packages
 library(readr)
@@
 library(lubridate)
+library(kableExtra)
 
-##### re-run this after fixing things up in case names changed etc.
+# read in example csv
 main_ex <- read_csv("/Volumes/Verbatim/output/main/2020-02-25-main.csv", show_col_types = F)
 
+# create tibble with var names and descriptions
 main_ex_vars <- tibble("Variable" = names(main_ex),
@@
                          "Row number",
-                         "Speech number, to keep track of which separated text belonged to which original speech",
+                         "Speech number",
                          "Page number statement can be found on in official Hansard",
@@
                          "Flag for answer (1 if answer, 0 otherwise)",
+                         "Flag for question in writing (1 if question in writing, 0 otherwise)",
                          "Flag for interjection (1 if statement is an interjection, 0 otherwise)"))
 
-knitr::kable(main_ex_vars, booktabs=T)
+# print tibble using kable
+knitr::kable(main_ex_vars, booktabs=T) %>% 
+  kable_styling(full_width = F, latex_options = "HOLD_position")
 ```
--   number missing (so far two days in 2014)
--   number unique speakers
--   avg number of rows per day
--   number of interjections (graph over time?)
+
+The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, and `body` variables all came directly from the XML contents.
+In addition to these variables, we added a number of flags to enable easy filtering of statements.
+For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber.
+As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document.
+Further details on this XML structure will follow in @sec-create.
+The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.[^1] We also added a flag for interjections, which are defined as statements made during one members speech by another member who is not The Speaker or Deputy Speaker.
+Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.
+For example, in @fig-main15rows, statements belonging to speech number 3 spans five rows, including two interjections.
+Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest.
+Finally, the `order` variable was added to keep track of the order in which everything was said, and was created after all statements and interjections were separated onto their own rows.
+
+[^1]: More on this in @sec-qa
+
+## Descriptive Statistics {#sec-stats}
+
+A visual exploration of our database offers interesting insight into general characteristics of Hansard.
+First, we looked at the total number of sitting days in the House of Representatives for each year from 2000 to 2021.
+@fig-plot1 illustrates that the number of House sitting days tends to fluctuate over time, where within this time span the years 2013 and 2019 had the fewest sitting days (45), and 2014 had the most sitting days (76).
 
@@
 # plot of total number of sitting days per year
-# numbers are wrong
-all_files %>% 
+plot1 <- all_files %>% 
   filter(year!=2022) %>% 
@@
   labs(x = "Year", 
-       y = "Count", 
-       title = "Total number of sitting days per year (2000-2021)")
+       y = "Count")
 
-# plot of average number of sitting days per month
-# adding rows for January and July which are always zero (no sitting days in these months)
-# not sure if I should incldue for visual purposes or leave out
+# plot of number of sitting days per month from 2015-2020
 # all_files %>% 
-#   filter(year==2020) %>%
-#   add_row(year=2020, month=1) %>% 
-#   add_row(year=2020, month=7) %>% 
+#   filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
 #   mutate(month_abb = month.abb[month]) %>% 
-#   group_by(month, month_abb) %>% 
-#   summarise(avg_days = mean(unique(day))) %>% 
+#   group_by(year, month_abb) %>% 
+#   summarise(avg_days = n()) %>% 
 #   ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
 #   geom_col() + 
+#   facet_wrap(~year) +
 #   theme_bw() + 
 #   labs(x = "Month", 
-#        y="Average sitting days", 
-#        title = "Average number of sitting days per month (2020)")
+#        y="Count", 
+#        title = "Number of sitting days per month (2015-2020)") +
+#   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
+```
 
-all_files %>% 
-  filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
-  mutate(month_abb = month.abb[month]) %>% 
-  group_by(year, month_abb) %>% 
-  summarise(avg_days = n()) %>% 
-  ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
-  geom_col() + 
-  facet_wrap(~year) +
+```{r, out.width="80%"}
+#| echo: false
+#| message: false
+#| fig-cap: "Total number of sitting days per year (2000-2021)"
+#| label: fig-plot1
+
+plot1
+```
+
+```{r}
+#| echo: false
+#| eval: false
+# generating some descriptive statistics
+
+# first grab list of all main CSVs
+all_dfs <- list.files("/Volumes/Verbatim/output/main")
+
+# define empty tibbles to store things in
+interject_data <- tibble()
+fedchamb_rows <- tibble()
+unique_data <- tibble()
+
+for(i in 1:length(all_dfs)){
+  # define df
+  this_df <- read_csv(paste0("/Volumes/Verbatim/output/main/", all_dfs[i]), show_col_types = F)
+
+  # number of interjections
+  this_interject_data <- this_df %>% group_by(interject) %>%
+    summarise(n_interject=n()) %>%
+    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
+    select(date, interject, n_interject)
+
+  # number of rows in chamb and fedchamb
+  this_fedchamb_rows <- this_df %>% group_by(fedchamb_flag) %>% 
+    summarise(n_rows = n()) %>% 
+    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
+    select(date, fedchamb_flag, n_rows)
+
+  # number of unique things (NAs omitted) - need to fix a tiny bit more but better for now
+  this_unique_data <- tibble(this_df %>% select(electorate) %>% unique() %>% na.omit() %>% summarise(n_electorate = n()),
+                           this_df %>% select(party) %>% unique() %>% na.omit() %>% summarise(n_party = n()),
+                           this_df %>% select(name.id) %>% unique() %>% na.omit() %>% summarise(n_name.id = n()),
+                           this_df %>% select(name) %>% unique() %>% filter(name!="business start" & name!="stage direction" & 
+                                                                              !str_detect(name, "member") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
+                             na.omit() %>% 
+                             mutate(name = str_remove(name, "^Mrs[[:space:]]|^Mr[[:space:]]|^Ms[[:space:]]|^Dr[[:space:]]"),
+                                    surname = str_extract(name, "^.{1,20}(?=\\,[[:space:]][[:upper:]][[:lower:]])"),
+                                    surname = ifelse(is.na(surname), name, surname),
+                                    surname = str_to_title(surname),
+                                    first_name = str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=\\,[[:space:]]MP)|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP)"),
+                                    first_name = ifelse(is.na(first_name) & str_detect(name, "\\(The"), str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]\\(The)"), first_name)) %>%
+                             group_by(surname) %>% 
+                             fill(first_name, .direction = "updown") %>% select(-name) %>% 
+                             unique() %>% ungroup() %>% summarise(n_names=n())) %>% 
+    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
+    select(date, n_names, n_name.id, n_electorate, n_party)
+
+  # bind new stuff onto existing tibble
+  interject_data <- rbind(interject_data, this_interject_data)
+  fedchamb_rows <- rbind(fedchamb_rows, this_fedchamb_rows)
+  unique_data <- rbind(unique_data, this_unique_data)
+}
+
+main_ex %>% select(name) %>% 
+  unique() %>% 
+  filter(name!="business start" & name!="stage direction" & !str_detect(name, "member") & 
+           !str_detect(name, "^Mrs[[:space:]]|^Mr[[:space:]]|^Ms[[:space:]]|^Dr[[:space:]]") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
+  na.omit() %>% 
+  summarise(name_use = str_remove(name, "\\,[[:space:]]MP[[:space:]]\\(The SPEAKER\\)$|[[:space:]]\\(The DEPUTY SPEAKER\\)$|\\,[[:space:]]MP$|[[:space:]]MP$")) %>% 
+  unique() %>% summarise(n_names=n())
+
+write.csv(interject_data, paste0("~/Desktop/RA/hansard-proj/paper/interject_data.csv"), row.names = FALSE)
+write.csv(fedchamb_rows, paste0("~/Desktop/RA/hansard-proj/paper/fedchamb_rows.csv"), row.names = FALSE)
+write.csv(unique_data, paste0("~/Desktop/RA/hansard-proj/paper/unique_data.csv"), row.names = FALSE)
+```
+
+```{r}
+#| echo: false
+#| message: false
+
+# read in descriptive statistics data
+interject_data <- read_csv("interject_data.csv", show_col_types = FALSE)
+fedchamb_rows <- read_csv("fedchamb_rows.csv", show_col_types = FALSE)
+unique_data <- read_csv("unique_data.csv", show_col_types = FALSE)
+
+# average number of rows per day by year, broken down by chamber and federation chamber
+fedchamb_rows$fedchamb_flag <- factor(fedchamb_rows$fedchamb_flag, levels=c(0, 1), labels=c("Chamber", "Federation Chamber"))
+
+plot2 <- fedchamb_rows %>% 
+  mutate(year = as.numeric(str_extract(date, "\\d\\d\\d\\d(?=-)"))) %>% 
+  filter(year!=2022) %>% 
+  group_by(year, fedchamb_flag) %>% 
+  summarise(avg_rows = mean(n_rows)) %>% 
+  ggplot(aes(y = avg_rows, x = as.factor(year), fill = fedchamb_flag)) + 
+  geom_bar(position = "stack", stat = "identity") +
   theme_bw() +
-  labs(x = "Month", 
-       y="Count", 
-       title = "Number of sitting days per month (2015-2020)") +
+  labs(x = "Year", y = "Average number of rows", fill = "") +
   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
+
+# plot pct rows that are interjections
+plot3 <- interject_data %>% 
+  group_by(date) %>% 
+  summarise(pct_interject = 100*(n_interject[interject==1]/sum(n_interject))) %>% 
+  ggplot(aes(x = date, y = pct_interject)) +
+  geom_smooth() +
+  geom_point()+
+  theme_bw() +
+  labs(x = "Date", y = "Percent interjections")
+```
+
+In @fig-plot2, we plotted the average number of rows per sitting day per year, disaggregated by Chamber and Federation Chamber proceedings.
+We can see that 2014 has the highest average number of rows per day, and 2021 has the lowest average number of rows per day.
+There appears to be less fluctuation in the average number of rows per day in the Federation Chamber than there is in that of the Chamber.
+
+```{r, out.width="80%"}
+#| fig-cap: "Average number of rows in Hansard per year,\nby Chamber and Federation Chamber"
+#| label: fig-plot2
+#| echo: false
+#| message: false
+
+plot2
+```
+
+Next we were interested in the percentage of rows in each Hansard which are flagged as interjections, using our definition of interjections mentioned above.
+We found that on average, approximately 18.4% of rows are characterized as interjections.
+Further, of all sitting days in our database, 25 June 2014 had the greatest percentage of rows being interjections, which was approximately 33.1%.
+The day with the smallest percentage of interjections was 23 March 2015, at approximately 2.8%.
+Based on @fig-plot3, there do not appear to be any significant fluctuations or patterns in the percentage of rows that are interjections across our time span.
+
+```{r, out.width="80%"}
+#| fig-cap: "Percentage of rows in Hansard that are interjections, 10 May 2011 - 08 September 2022"
+#| label: fig-plot3
+#| echo: false
+#| message: false
+
+plot3
+```
+
+Finally, we created a @tbl-descrip to summarize the average number of unique speakers, electorates, and parties found in Hansard per year.
+For each of these variables the numbers do not fluctuate much over the years, and across all years, there are on average approximately 94 unique speakers, 89 unique electorates, and 6 unique parties.
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-descrip
+#| tbl-cap: "Average number of unique names, electorates, and parties in Hansard per year"
+
+# create table of averages by year
+unique_table <- unique_data %>% 
+  mutate(year = str_extract(date, "^\\d\\d\\d\\d")) %>% 
+  filter(year!=2022) %>% 
+  group_by(year) %>% 
+  summarise(mean_name = round(mean(n_names), 2),
+            mean_elec = round(mean(n_electorate), 2),
+            mean_party = round(mean(n_party), 2)) %>% 
+  rename("Names" = mean_name,
+         "Electorates" = mean_elec,
+         "Parties" = mean_party,
+         "Year" = year)
+
+# overall averages all years
+unique_avgs <- unique_data %>% 
+  mutate(year = str_extract(date, "^\\d\\d\\d\\d")) %>% 
+  filter(year!=2022) %>% 
+  summarise(mean_name = round(mean(n_names), 2),
+            mean_elec = round(mean(n_electorate), 2),
+            mean_party = round(mean(n_party), 2))
+
+# print table
+knitr::kable(unique_table, booktabs=T) %>% 
+  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
 ```
@@
 The approach to parsing contents of an XML document is heavily dependent on its tree structure.
-As such, to create this database, we started by looking at a single Hansard transcript in XML form.
-Doing so enabled us to understand the various components of interest in the document, and how each one can be parsed according to its corresponding structural form.
+As such, to create this database, we started by looking at a single Hansard XML transcript.
+Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form.
 For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them.
@@
 
------ should I add little example of the XML to give the reader a visual?? it's hard to put into words clearly -----
-
-The XML structure begins with a root or parent element `"hansard"`, followed by a child element `"session.header"` with sub-child elements with information such as the date, and parliament number.
-Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`.
+@fig-xml1 provides an example of the beginning of an XML file for Hansard.
+The XML structure begins with a root or parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements with information such as the date, and parliament number, which are all highlighted in pink.
+Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1.
 On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too.
 This allows for the distinction of proceedings of the Chamber and Federation Chamber.
-Each proceeding begins with a business start, naming the speaker and what time they took the chair.
-Next comes the debates and nested sub-debates.
+As mentioned in @sec-description, each proceeding begins with the business start.
+The structure of this business start can be seen between the nodes highlighted in green in @fig-xml1.
+The content we parse from the business start are shown highlighted in orange in @fig-xml1.
+Next comes the debates and nested sub-debates, which follow the business start.
 Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it.
@@
 
+![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
+
 Once code was written to parse all components, it was organized into individual scripts.
@@
 This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
-The next key task revolved around the fact that the raw text data were not separated by each statement when parsed.
-In other words, any interjections, comments made by the Speaker and Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
+The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
+In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
 As such, the name, name ID, electorate and party details were only provided for the person who's turn it was to speak.
@@
 
-When running these scripts on transcripts from other sitting days, it became clear that not every sitting day contains every possible XML element.
+When beginning to run these scripts on transcripts from other sitting days, it became clear that not every sitting day contains every possible XML element.
 For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding.
@@
 Before writing a new script for parsing earlier Hansard, we decided to prioritize cleaning and finalizing what we have been able to parse.
-As such we continued building our scripts, fixing any issues we noticed in the resulting datasets, and separating any additional sections of the parsed text where necessary.
-Specifically, we added a section of our script to separate on general stage directions.
+As such we continued building our scripts, fixing any issues we noticed in the resulting datasets, and splitting up any additional sections of the parsed text onto separate rows where necessary.
+Specifically, we added a section of our script to separate out general stage directions.
 More information on this separation will be provided in @sec-stage.
+
+After completing the scripts, they were formatted as functions which take a file name argument.
+The final script which parses everything from Hansard produces two CSV files: one table of contents dataset with the title of each debate and sub-debate topic, and one dataset with the data on all proceedings (example shown in @fig-main15rows).
+Emphasis is placed on the latter as this contains the vast majority of information of interest, and required much more work to produce.
 
@@
 One core mechanism by which this is achieved is called Question Time.
-This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions with notice (often referred to as questions in writing), which are written in advance, or questions without notice, which are asked verbally in the Chamber and are responded to in real time [@house2021].
+This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
 Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
-Sometimes, questions in writing are included directly in the "chamber.xscript" child node, with sub-child nodes called "question" and "answer" to differentiate the two.
-However, in other times, questions in writing are embedded in their own child node called "answers.to.questions" outside of "chamber.xscript".
-Difficulty arose when trying to order these questions and answers correctly within the rest of the debate text, because unlike all other statements made which have both an associated page number and time stamp, these generally only have associated page numbers.
-Time stamps have been a key variable for which we have arranged parsed text in chronological order, especially since many statements tend to be on the same page number, meaning we cannot rely solely on page number to capture correct ordering.
+Sometimes, questions in writing are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
+However, in other times, questions in writing are embedded in their own child node called `"answers.to.questions"` outside of `"chamber.xscript"`.
+Difficulty arose when trying to order these questions and answers correctly within the rest of the debate text, because unlike all other statements made which have both an associated page number and time stamp, these generally only have a page number.
+Time stamps have been a key variable for which we have arranged parsed text in chronological order, especially since many statements tend to be on the same page, meaning we cannot rely solely on page number to capture correct ordering.
 To approach this issue, we merged all parsed questions to be in a single dataframe, and all parsed answers in another dataframe.
-We then arranged each dataframe by page number, and merged the two dataframes in such a way that each question would be followed by it's corresponding answer.
+We then arranged each dataframe by page number, and merged the two dataframes in such a way that each question would be followed by its corresponding answer.
 
@@
 
--   First thought was to use a number of phrases, but it would be really difficult to create an exhaustive list manually
+As mentioned, the text was structured and parsed in such a way that various interjections and comments which happened during a speech were not separated onto individual rows.
+Below is a simple example extracted from Hansard on 30 November 2021, where Mr.
+van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.
 
--   Once all the text were split to have a different row for each interjection/continuation etc, we could just flag for interjections automatically b/c i kept the original row number that the speech started on so I could flag if the original speaker or speaker/deputy speaker wasnt speaking, it was an interjection
+> ```{r}
+> #| warning: false
+> #| echo: false
+> #| message: false
+> #| results: asis
+> >
+> # read in XML file
+> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
+> >
+> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
+> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
+>                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
+>   as_tibble() %>% 
+>   slice(25) %>% 
+>   pull(body)
+> >
+> # print example of text in quotations
+> cat(paste0('"', interject_text_ex, '"'))
+> ```
 
--   Had to consider a ton of different names and possible formatting of the names
-    -   Ex: last name only, two first names, last names with two words or hyphen or apostrophe, people with the same last name
-    -   had to also find a way to match these various formats to the name id, electorate, party info
+As previously discussed, we wanted to have each statement on its own row, with the correct name, name ID, electorate and party information on the individual speaking.
+We approached this task in a number of steps.
+Once all parsed text from the XML was merged into one dataframe called `main`, we added a `"speech_no"` variable.
+As noted in @sec-description, this was done to keep track of which speech each interjection, comment, or continuation belonged to as we separated these components onto their own rows.
 
--   Also had to consider general interjections that are not directly named, such as "an opposition member" or "government members", or "Mr Smith interjecting-"
+The next step was to extract all the names and titles preceding these interjections, comments and continuations.
+This would enable us to then separate the speeches in the correct places using these names and titles in combination with regular expressions, which are patterns of characters that can be used to search bodies of text.
+We completed this extraction process with a few intermediate steps, due to the large number of name styles and interjection types that had to be accounted for, each requiring their own unique regular expression format.
 
--   Some people have no first name so couldn't manually extract their info (i.e. electorate, party etc.)
+In many of the XML files, below the full speech including all interjections and continuations, there is a series of child-nodes which exist to capture the structure of interruptions in that speech.
+@fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
+Looking at the elements highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation.
+As mentioned, this text is embedded within the speech above it.
+However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on.
+Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
+We stored this as a dataframe called `"interject"`.[^2]
 
-Tons of variation in how names are formatted (Capitalization makes it super difficult with regex) - also pre 2021 the speaker is not fully identified the same way as in 2021 2022 - just lots of small changes to account for
+[^2]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.
+
+![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
+
+We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
+We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
+When a Member interjects or continues a speech, the usual form of their name is a prefix followed by their first name or first initial and/or last name.
+There is also variation in the capitalization of these names.^[Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
+Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
+This variation demands careful consideration when writing regular expression patterns to search for in the text.
+In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
+
+Having these lists enabled us to extract the names of Members and their associated prefixes as they exist in the text, by searching for exact matches with regular expression patterns.
+We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds.
+A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
+These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.
+
+Once all interjections, comments and continuations were successfully split onto their own rows, we added a general order variable to the dataset based on row number, to keep track of the order in which everything was said.
+The next step was to fill the name, name ID, electorate and party variables with the correct data for each row.
+To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, and party for that individual [@fig-lookup].
+We used the main dataset from the `AustralianPoliticians` package in the creation of this lookup table [@auspol].
+
+![First 10 rows of lookup table from 10 May 2018 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
+
+Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps in the table with available name ID, electorate and party information.
+Finally, we were able to add a flag for interjections.
+Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak.
+@fig-interject provides an example of a Federation Chamber proceeding with interjections.
+Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
+
+![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
 
@@
 As mentioned, one of the final components added to our script was to separate general stage directions out from statements made by members.
-Stage directions are general statements included in the transcript to document happenings in the Chamber.
+Stage directions are general statements included in the transcript to document happenings in parliament.
 Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned".
-It is unclear from the XML and PDF who exactly these statements are attributed to, or in other words, who are making these statements.
+It was unclear to us from the XML and PDF who exactly these statements were attributed to.
 For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament.
-For example, when the Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time - but this is not explicitly transcribed, rather what is written is: "Question agreed to.
+For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
+This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
 Bill read a second time".
 For this reason, we filled the name variable for these statements with "stage direction".
-It is important to note that these stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually build a list of stage directions to separate out.
-We have been building this list of stage directions as we work backwards in parsing Hansard.
-
-# Applications {#sec-apps}
+Note that stage directions were not flagged as interjections.
+These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches.
+We have been building upon this list of stage directions as we work backwards in parsing Hansard.
 
@@
 
+Using a number of computational tools, we have created a novel database for Australian Hansard entirely based on XML data.
+Despite the public availability of Hansard, it is not functional in its current form for analysis at scale.
+Our work will enable individuals from various disciplines to perform broad spectrum research on Australian parliamentary proceedings without requiring a strong computational background.
+
+Our database provides a CSV file for each sitting day of Hansard from 10 May 2011 to 08 September 2022.
+In our work, we have embedded a number of additional variables to the resulting datasets and accounted for variation in the way that proceedings were initially transcribed.
+This ensured that users of our database can easily filter through transcripts as needed to achieve their distinct research goal.
+
+The vastness of our database and the significance of the content within it enables the exploration of an endless variety of research questions.
+For example, one might be interested in investigating the frequency of certain words or phrases, such as those relating to Covid-19.
+Another area of interest would be frequency of interjections, and the gender of individuals both being interrupted and doing the interrupting.
+This database would also act as a valuable resource for research using Natural Language Processing tools.
+
 # References

### 2022-10-25 scripts/00-scrape_files.R

@@ -36,24 +36,6 @@ heapsofpapers::get_and_save(data=urls,
                             dir = "/Volumes/Verbatim/input",
                             dupe_strategy = "overwrite")
 
-# issue with link from 2022 had to fix
-urls2 <- tibble(locations_are = "https://parlinfo.aph.gov.au/parlInfo/download/chamber/hansardr/25917/toc_unixml/House%20of%20Representatives_2022_07_26_Official.xml;fileType=text%2Fxml",
-       save_here = "2022-07-26.xml")
-heapsofpapers::get_and_save(data=urls2,
-                            links = "locations_are",
-                            save_names = "save_here",
-                            dir = "/Volumes/Verbatim/input",
-                            dupe_strategy = "overwrite")
-
-# issue with link from 2017 had to fix
-urls2 <- tibble(locations_are = "https://parlinfo.aph.gov.au/parlInfo/download/chamber/hansardr/7acf60a0-3455-43aa-bfd0-083a6b4252db/toc_unixml/House%20of%20Representatives_2017_06_14_5147_Official.xml;fileType=text%2Fxml",
-                save_here = "2017-06-14.xml")
-heapsofpapers::get_and_save(data=urls2,
-                            links = "locations_are",
-                            save_names = "save_here",
-                            dir = "/Volumes/Verbatim/input",
-                            dupe_strategy = "overwrite")
-
 
 
 

### 2022-10-25 scripts/01-session_info.R

@@ -25,6 +25,20 @@ parse_session_info <- function(filename){
   return(session_info)
 }
 
-# call function, pass file name
+# ex: call function, pass file name
 parse_session_info("2018-08-23.xml")
 
+# grab list of all file names
+files_all <- list.files("/Volumes/Verbatim/input/")
+
+# define empty tibble
+session_info_all <- tibble()
+
+# loop through all files, parse session info, store in tibble
+for(i in 1:length(files_all)){
+  this_session_info <- parse_session_info(files_all[i])
+  session_info_all <- rbind(session_info_all, this_session_info)
+}
+
+# export all session info
+write.csv(session_info_all, paste0("/Volumes/Verbatim/output/session_info/session_info_all.csv"), row.names = FALSE)

### 2022-10-25 scripts/99-everything.R

@@ -1,5 +1,5 @@
 # script to parse everything from Hansard
-# WORKS FOR 2011-05-10 TO PRESENT - BUT LOTS OF FORMATTING ISSUES TO DEAL WITH
+# WORKS FOR 2012-08-14 TO PRESENT (that day is when the federation chamber was renamed)
 
 # read in necessary packages
 library(XML)
@@ -10,8 +10,8 @@ library(tidyverse)
 
 split_interjections <- function(main, interject, bus_start){
   
-  #### step 1: add index to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "index")
+  #### step 1: add speech_no to make it easier to see where interjections happened 
+  main <- rowid_to_column(main, "speech_no")
   
   # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
   main_orig <- main
@@ -67,7 +67,7 @@ split_interjections <- function(main, interject, bus_start){
   interject_names <- c(interject_names, "Opposition members interjecting—", "Government members interjecting—", 
                        "Opposition members", "Honourable members interjecting—", "An opposition member", 
                        "An honourable member", "The SPEAKER", "The DEPUTY SPEAKER", "A government member interjecting—",
-                       "The Clerk", "A government member", "Honourable members", "Honourable members and senators",
+                       "The Clerk", "A government member", "Government members", "Honourable members", "Honourable members and senators",
                        "Honourable member and senators")
   
   #### step 3: we need another list of names that we haven't grabbed yet to separate speech based on ("all_names")
@@ -156,14 +156,22 @@ split_interjections <- function(main, interject, bus_start){
   
   #### step 5: split rows
   
-  # use interject_names list to separate rows
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_names, ")(?!", interject_names, "[[:space:]]on[[:space:]]my)(?!", interject_names, "[[:space:]]having)", collapse="|"))
+  # need to separate out general interjections (e.g. Opposition members, A government member, etc.) because these sometimes are followed by "on my left" or "having stood in their places"
+  # and don't want to split on those so need specific negative lookaheads
+  # can't paste all interject_names b/c regex too long error
[…]

### 2022-10-25 scripts/99-everything2.R

@@ -1,6 +1,6 @@
+# main committee
 # script to parse everything from Hansard
-# TRYING TO FIX PARSING ISSUE WHICH STOPS AFTER 2011-03-24
-# issue is with debate info parsing
+#### good for everything up to 2012-06-28 (last day before main committee was renamed to federation chamber)
 
 # read in necessary packages
 library(XML)
@@ -9,10 +9,10 @@ library(tidyverse)
 
 # define function for splitting interjections, which will be referenced in parse_hansard function
 
-split_interjections <- function(main, interject, bus_start){
+split_interjections_maincomm <- function(main, interject, bus_start){
   
-  #### step 1: add index to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "index")
+  #### step 1: add speech_no to make it easier to see where interjections happened 
+  main <- rowid_to_column(main, "speech_no")
   
   # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
   main_orig <- main
@@ -34,11 +34,23 @@ split_interjections <- function(main, interject, bus_start){
       summarise(form1 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
                 form2 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)"),
                 form3 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
-                form4 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)")) %>%
-      pivot_longer(form1:form4, names_to = "type", values_to = "form") %>%
+                form4 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)"),
+                form5 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", str_sub(first_name, end=1), "[[:space:]]", last_name, "\\)"),
+                form6 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", str_sub(first_name, end=1), "[[:space:]]", last_name, "\\)")) %>%
[…]

### 2022-11-01 paper/paper.qmd
paper files

@@
 ---
-title: "Digitization of the Australian Parliamentary Debates (1901-2022)"
+title: "Digitization of the Australian Parliamentary Debates (1901-2022)^[Code is available at: https://github.com/lindsaykatz/hansard-proj]"
 number-sections: true
-format: pdf
+format: 
+  pdf:
+    keep-tex: true
 bibliography: references.bib
@@
 author:
-  - Lindsay Katz
-  - Rohan Alexander
-abstract: "Parliamentary dialogue is critical for political science research.
+  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
+  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
+abstract: "Public knowledge of what is said in parliament is a key tenet of democracy.
+Parliamentary dialogue is also critical for political science research.
 In Australia, following the UK tradition, the written record of what is said in parliament is known as Hansard.
@@
 The creation of this dataset will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers.
-This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications."
+This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications.
+To this point, we have completed this for 2011 to 2022."
 ---
@@
 Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
-Given the contents and sheer magnitude of these records, their value cannot be overstated, particularly in the context of political science research.
+Given the content and magnitude of these records, they have significance, particularly in the context of political science research.
 In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavor called the Linked Parliamentary Data (LiPaD) project [@lipad].
 Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling.
-Following the lead of the LiPaD project, in this paper we introduce a novel database for Australian Hansard.
+Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard.
 This is composed of individual datasets for each sitting day in the House of Representatives, containing details on everything said in parliament in a form which can be readily used by researchers.
@@
 8].
-In contrast, the Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber.
+The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber.
 This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch.
 21].
-Sittings in the Federation Chamber are quite different than those of the Chamber in terms of their order of business and scope of discussion.
+Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion.
 Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch.
 21].
-It is the recording and compilation of all of these proceedings upon which Hansard is based.
+It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.
 
-On each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form.
+A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form.
 The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt].
@@
 The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files.
-In cases where we were unsure on how to proceed with processing the XML, we always deferred first to the PDF, and then to the video recording of the proceeding if necessary.
+In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.
 
@@
 Thus far, this has been done for Hansard from mid-2011 to present.
-Due to the extensive variation in structural formatting of these transcripts, additional work is needed to parse transcripts from further in the past.
 
@@
 As well, @Leslie_2021_HoR_Aus has released data on all Members of the Australian House of Representatives from 1945 to 2019, and is developing an `R` package for these data.
+Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
 
@@
 In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
-Finally, the work of @alexander2021 offers the most complete database for Australian Hansard we have encountered thus far, along with a thorough analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
+Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
 @alexander2021 created this database with the static PDF versions Hansard, using OCR to digitize these files into text which is suitable for analysis.
+This means there are considerable digitization errors especially in the first half of the dataset.
 
@@
 21].
-This difference in element name means that our original code for parsing Federation Chamber contents would not work, as the specified node path would be incorrect.
+This difference in element name means that our original code for parsing Federation Chamber content would not work, as the specified node path would be incorrect.
 We accounted for this by creating a separate script with this name change.
@@
 
-Evidently, each row of the CSV file contains an individual statement, with the unique name ID, electorate, and party information of the speaker.
+Each row of the CSV file contains an individual statement, with the unique name ID, electorate, and party information of the speaker.
 Of course, for general statements such as "Honourable members", these variables cannot be specified.
-Each proceeding in the Chamber begins with the business start, where the time that The Speaker took the chair is documented, as well as the acknowledgment of the country and reading of the prayers as governed by the standing orders of the House [@standingorders, ch.
+Each proceeding in the Chamber begins with the business start, where the time that the Speaker took the chair is documented, as well as the acknowledgment of the country and reading of the prayers as governed by the standing orders of the House [@standingorders, ch.
 6].
-Federation Chamber also begins with a business start, where it is stated at what time The Deputy Speaker takes the chair.
+The Federation Chamber also begins with a business start, where it is stated at what time 5he Deputy Speaker takes the chair.
 For further clarification on each variable in the resulting CSV, @tbl-vars provides an overview of each variable in the database.
@@
 main_ex <- read_csv("/Volumes/Verbatim/output/main/2020-02-25-main.csv", show_col_types = F)
+
+main_ex <- main_ex %>% select(-c(gender, uniqueID))
 
@@
 Further details on this XML structure will follow in @sec-create.
-The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.[^1] We also added a flag for interjections, which are defined as statements made during one members speech by another member who is not The Speaker or Deputy Speaker.
+The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.[^1] We also added a flag for interjections, which are defined as statements made during one members speech by another member who is not the Speaker or Deputy Speaker.
 Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.
@@
   # number of unique things (NAs omitted) - need to fix a tiny bit more but better for now
-  this_unique_data <- tibble(this_df %>% select(electorate) %>% unique() %>% na.omit() %>% summarise(n_electorate = n()),
-                           this_df %>% select(party) %>% unique() %>% na.omit() %>% summarise(n_party = n()),
-                           this_df %>% select(name.id) %>% unique() %>% na.omit() %>% summarise(n_name.id = n()),
-                           this_df %>% select(name) %>% unique() %>% filter(name!="business start" & name!="stage direction" & 
-                                                                              !str_detect(name, "member") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
+  this_nameid <- this_df %>% select(name.id, fedchamb_flag) %>% 
+    group_by(fedchamb_flag) %>% 
+    unique() %>% 
+    na.omit() %>% 
+    summarise(n_name.id = n())
+
+  this_electorate <- this_df %>% select(electorate, fedchamb_flag) %>% 
+    group_by(fedchamb_flag) %>% 
+    unique() %>% 
+    na.omit() %>% 
+    summarise(n_electorate = n())
+
+  this_party <- this_df %>% select(party, fedchamb_flag) %>% 
+    group_by(fedchamb_flag) %>% 
+    unique() %>% 
+    na.omit() %>% 
+    summarise(n_party = n())
+
+  this_name <- this_df %>% select(name, fedchamb_flag) %>% 
+    group_by(fedchamb_flag) %>% 
+    unique() %>% 
+    filter(name!="business start" & name!="stage direction" & !str_detect(name, "member") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
     na.omit() %>% 
@@
            surname = str_extract(name, "^.{1,20}(?=\\,[[:space:]][[:upper:]][[:lower:]])"),
-                                    surname = ifelse(is.na(surname), name, surname),
+           surname = ifelse(is.na(surname) & !str_detect(name, "^The DEPUTY SPEAKER"), name, surname),
+           surname = ifelse(is.na(surname) & str_detect(name, "^The DEPUTY SPEAKER"), str_extract(name, "(?<=\\(Mrs[[:space:]]|\\(Mr[[:space:]]|\\(Ms[[:space:]]|\\(Dr[[:space:]]).{1,20}(?=\\))"), surname),
            surname = str_to_title(surname),
-                                    first_name = str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=\\,[[:space:]]MP)|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP)"),
+           first_name = str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=\\,[[:space:]]MP)|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP \\(The DEPUTY SPEAKER\\))|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP)"),
            first_name = ifelse(is.na(first_name) & str_detect(name, "\\(The"), str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]\\(The)"), first_name)) %>%
@@
     fill(first_name, .direction = "updown") %>% select(-name) %>% 
-                             unique() %>% ungroup() %>% summarise(n_names=n())) %>% 
-    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
-    select(date, n_names, n_name.id, n_electorate, n_party)
+    unique() %>% 
+    ungroup() %>% 
+    group_by(fedchamb_flag) %>% 
+    summarise(n_names=n())
+
+this_unique_data <- merge(this_nameid, this_electorate, by="fedchamb_flag") %>% 
+  merge(., this_party, by="fedchamb_flag") %>% 
+  merge(., this_name, by="fedchamb_flag") %>% 
+  as_tibble() %>% 
+  mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d")))
+
+# this_unique_data <- tibble(this_df %>% select(electorate) %>% unique() %>% na.omit() %>% summarise(n_electorate = n()),
+#                            this_df %>% select(party) %>% unique() %>% na.omit() %>% summarise(n_party = n()),
+#                            this_df %>% select(name.id) %>% unique() %>% na.omit() %>% summarise(n_name.id = n()),
+#                            this_df %>% select(name) %>% unique() %>% filter(name!="business start" & name!="stage direction" & 
+#                                                                               !str_detect(name, "member") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
+#                              na.omit() %>% 
+#                              mutate(name = str_remove(name, "^Mrs[[:space:]]|^Mr[[:space:]]|^Ms[[:space:]]|^Dr[[:space:]]"),
+#                                     surname = str_extract(name, "^.{1,20}(?=\\,[[:space:]][[:upper:]][[:lower:]])"),
+#                                     surname = ifelse(is.na(surname), name, surname),
+#                                     surname = str_to_title(surname),
+#                                     first_name = str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=\\,[[:space:]]MP)|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP)"),
+#                                     first_name = ifelse(is.na(first_name) & str_detect(name, "\\(The"), str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]\\(The)"), first_name)) %>%
+#                              group_by(surname) %>% 
+#                              fill(first_name, .direction = "updown") %>% select(-name) %>% 
+#                              unique() %>% ungroup() %>% summarise(n_names=n())) %>% 
+#     mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
+#     select(date, n_names, n_name.id, n_electorate, n_party)
 
@@
 }
-
-main_ex %>% select(name) %>% 
-  unique() %>% 
-  filter(name!="business start" & name!="stage direction" & !str_detect(name, "member") & 
-           !str_detect(name, "^Mrs[[:space:]]|^Mr[[:space:]]|^Ms[[:space:]]|^Dr[[:space:]]") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
-  na.omit() %>% 
-  summarise(name_use = str_remove(name, "\\,[[:space:]]MP[[:space:]]\\(The SPEAKER\\)$|[[:space:]]\\(The DEPUTY SPEAKER\\)$|\\,[[:space:]]MP$|[[:space:]]MP$")) %>% 
-  unique() %>% summarise(n_names=n())
 
@@
 
+# checking meeting of fed chamb on fridays, only happened once in our database on 12 June 2020
+# library(lubridate)
+# fedchamb_rows$day_of_week <- wday(fedchamb_rows$date, label=T)
+# fedchamb_rows %>% filter(day_of_week=="Fri")
+
 # average number of rows per day by year, broken down by chamber and federation chamber
-fedchamb_rows$fedchamb_flag <- factor(fedchamb_rows$fedchamb_flag, levels=c(0, 1), labels=c("Chamber", "Federation Chamber"))
+fedchamb_rows$fedchamb_flag <- factor(fedchamb_rows$fedchamb_flag, levels=c(0, 1), labels=c("House of Representatives", "Federation Chamber"))
 
@@
   geom_smooth() +
-  geom_point()+
+  geom_point(alpha = 0.4)+
   theme_bw() +
@@
 
-In @fig-plot2, we plotted the average number of rows per sitting day per year, disaggregated by Chamber and Federation Chamber proceedings.
+In @fig-plot2, we consider the average number of rows per sitting day per year, disaggregated by Chamber and Federation Chamber proceedings.
 We can see that 2014 has the highest average number of rows per day, and 2021 has the lowest average number of rows per day.
@@
 Next we were interested in the percentage of rows in each Hansard which are flagged as interjections, using our definition of interjections mentioned above.
-We found that on average, approximately 18.4% of rows are characterized as interjections.
-Further, of all sitting days in our database, 25 June 2014 had the greatest percentage of rows being interjections, which was approximately 33.1%.
-The day with the smallest percentage of interjections was 23 March 2015, at approximately 2.8%.
+We found that on average, approximately 18% of rows are characterized as interjections.
+Further, of all sitting days in our database, 25 June 2014 had the greatest percentage of rows being interjections, which was approximately 33%.
+The day with the smallest percentage of interjections was 23 March 2015, at approximately 3%.
 Based on @fig-plot3, there do not appear to be any significant fluctuations or patterns in the percentage of rows that are interjections across our time span.
@@
 
-Finally, we created a @tbl-descrip to summarize the average number of unique speakers, electorates, and parties found in Hansard per year.
-For each of these variables the numbers do not fluctuate much over the years, and across all years, there are on average approximately 94 unique speakers, 89 unique electorates, and 6 unique parties.
+Finally, @fig-unique_plots summarizes the number of unique speakers, electorates, and parties found in Hansard over time.
+In all three panels, the data exhibit the same general pattern over time for both the House of Representatives and the Federation Chamber, where the magnitude for the House data is consistently greater than that of the Federation Chamber.
+Panels A and B in @fig-unique_plots illustrate that the number of unique names and electorates follow a very consistent trend across the entire time frame.
+Panel C shows that the number of unique parties has increased slightly since 2018.
+
+![Number of unique names (A), electorates (B), and parties (C) found on each sitting day.](unique_plots.png){#fig-unique_plots}
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| eval: false
+
+unique_data$fedchamb_flag <- factor(unique_data$fedchamb_flag, levels=c(0, 1), labels=c("House of Representatives", "Federation Chamber"))
+
+unique_plot1 <- ggplot(unique_data, aes(x = date, y = n_names, color = fedchamb_flag)) + 
+  geom_point(alpha = 0.5)+
+  geom_smooth() +
+  theme_bw() +
+  labs(y = "# unique names", x = "Date", color = "")
+
+unique_plot2 <- ggplot(unique_data, aes(x = date, y = n_electorate, color = fedchamb_flag)) + 
+  geom_point(alpha = 0.5) +
+  geom_smooth() +
+  theme_bw() +
+  labs(y = "# unique electorates", x = "Date", color = "")
+
+unique_plot3 <- ggplot(unique_data, aes(x = date, y = n_party, color = fedchamb_flag)) + 
+  geom_point(position = "jitter", alpha = 0.5) +
+  geom_smooth() +
+  theme_bw() +
+  labs(y = "# unique parties", x = "Date", color = "")
+
+# unique_data %>% group_by(fedchamb_flag) %>% summarise(mean_name = mean(n_names),
+#                                                       mean_nameID = mean(n_name.id),
+#                                                       mean_elecs = mean(n_electorate),
+#                                                       mean_party = mean(n_party))
+
+# ggsave("unique_plot1.png", unique_plot1)
+# ggsave("unique_plot2.png", unique_plot2)
+# ggsave("unique_plot3.png", unique_plot3)
+
+ggpubr::ggarrange(unique_plot1, unique_plot2, unique_plot3, ncol=2, nrow=2, common.legend = T, legend = "top", labels = "AUTO")
+```
 
@@
 #| tbl-cap: "Average number of unique names, electorates, and parties in Hansard per year"
+#| eval: false
+
+######## not using this
 
@@
   group_by(year) %>% 
-  summarise(mean_name = round(mean(n_names), 2),
-            mean_elec = round(mean(n_electorate), 2),
-            mean_party = round(mean(n_party), 2)) %>% 
+  summarise(mean_name = round(mean(n_names), 0),
+            mean_elec = round(mean(n_electorate), 0),
+            mean_party = round(mean(n_party), 0)) %>% 
   rename("Names" = mean_name,
@@
   filter(year!=2022) %>% 
-  summarise(mean_name = round(mean(n_names), 2),
-            mean_elec = round(mean(n_electorate), 2),
-            mean_party = round(mean(n_party), 2))
+  summarise(mean_name = round(mean(n_names), 0),
+            mean_elec = round(mean(n_electorate), 0),
+            mean_party = round(mean(n_party), 0))
 
@@
 After completing the scripts, they were formatted as functions which take a file name argument.
-The final script which parses everything from Hansard produces two CSV files: one table of contents dataset with the title of each debate and sub-debate topic, and one dataset with the data on all proceedings (example shown in @fig-main15rows).
-Emphasis is placed on the latter as this contains the vast majority of information of interest, and required much more work to produce.
+The final script which parses everything from Hansard produces one CSV file with the data on all proceedings for each sitting day (example shown in @fig-main15rows).
 
@@
 When a Member interjects or continues a speech, the usual form of their name is a prefix followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.^[Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
+There is also variation in the capitalization of these names.[^3] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
 Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
@@
 In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
+
+[^3]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
 

### 2022-11-01 paper/paper.tex
paper files

--- 2022-11-01 paper/paper.qmd
@@
----
-title: "Digitization of the Australian Parliamentary Debates (1901-2022)^[Code is available at: https://github.com/lindsaykatz/hansard-proj]"
-number-sections: true
-format: 
-  pdf:
-    keep-tex: true
-bibliography: references.bib
-editor: visual
-date: "now"
-date-format: long
-author:
-  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
-  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
-abstract: "Public knowledge of what is said in parliament is a key tenet of democracy.
-Parliamentary dialogue is also critical for political science research.
-In Australia, following the UK tradition, the written record of what is said in parliament is known as Hansard.
-While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality to be credibly analysed with statistical models.
-Following the lead of the LiPaD project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard.
-Our dataset will be publicly available and linked to other datasets such as election results.
-The creation of this dataset will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers.
-This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications.
-To this point, we have completed this for 2011 to 2022."
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-# Introduction {#sec-intro}
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
-Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
-Given the content and magnitude of these records, they have significance, particularly in the context of political science research.
-In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavor called the Linked Parliamentary Data (LiPaD) project [@lipad].
-Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling.
-Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard.
-This is composed of individual datasets for each sitting day in the House of Representatives, containing details on everything said in parliament in a form which can be readily used by researchers.
-With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
-1].
-Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch.
-8].
-A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch.
-8].
-The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber.
-This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch.
-21].
-Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion.
-Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch.
-21].
-It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Digitization of the Australian Parliamentary Debates (1901-2022)},
+  pdfauthor={Lindsay Katz; Rohan Alexander},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form.
-The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt].
-This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt].
-The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility.
-The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files.
-In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.
+\title{Digitization of the Australian Parliamentary Debates
+(1901-2022)\footnote{Code is available at:
+  https://github.com/lindsaykatz/hansard-proj}}
+\author{Lindsay Katz\footnote{University of Toronto,
+  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
+  of Toronto, rohan.alexander@utoronto.ca}}
+\date{October 27, 2022}
 
-The end goal for this work is to create a publicly available database of parsed Hansard transcripts from 1901 to present in a form which can be readily analyzed.
-More specifically, we aim to present each transcript in an ordered form with details on each speaker such as their political affiliation, the time stamp of their statement (where available), and whether they interjected (i.e.
-spoke out of turn).
-Thus far, this has been done for Hansard from mid-2011 to present.
+\begin{document}
+\maketitle
+\begin{abstract}
+Public knowledge of what is said in parliament is a key tenet of
+democracy. Parliamentary dialogue is also critical for political science
+research. In Australia, following the UK tradition, the written record
+of what is said in parliament is known as Hansard. While the Australian
+Hansard has always been publicly available, it has been difficult to use
+it for the purpose of large-scale macro and micro-level text analysis
+because it has not been available as a dataset of sufficient quality to
+be credibly analysed with statistical models. Following the lead of the
+LiPaD project which achieved this for Canada, our project aims to
+provide a new, comprehensive, high-quality database that captures all
+proceedings of the Australian parliamentary debates from 1901 to the
+present day using Hansard. Our dataset will be publicly available and
+linked to other datasets such as election results. The creation of this
+dataset will enable the exploration of questions that are not currently
+possible to explore, serving as a valuable resource for both researchers
+and policymakers. This work will provide a thorough description of the
+creation and computational underpinnings of this database, followed by a
+discussion of some applications. To this point, we have completed this
+for 2011 to 2022.
+\end{abstract}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, sharp corners, breakable, frame hidden, enhanced, boxrule=0pt]}{\end{tcolorbox}}\fi
 
-We begin this paper with a description of what datasets for Australian Hansard already exist (@sec-existing).
-Next will be a detailed description of the contents of our database (@sec-description), followed by a thorough discussion of how this database was created (@sec-create).
+\hypertarget{sec-intro}{%
+\section{Introduction}\label{sec-intro}}
 
-# Existing Datasets {#sec-existing}
+The official written record of parliamentary debates, formally known as
+Hansard, plays a fundamental role in capturing the history of political
+proceedings and facilitating the exploration of valuable research
+questions. Originating in the British parliament, the production of
+Hansard became tradition in a number of Commonwealth countries such as
+Canada, the United Kingdom, and Australia (Vice and Farrell 2017). Given
+the content and magnitude of these records, they have significance,
+particularly in the context of political science research. In the case
+of Canada, a team of researchers at the University of Toronto have
+digitized Hansard from 1901 to 2019, an endeavor called the Linked
+Parliamentary Data (LiPaD) project (Beelen et al. 2017). Having a
+digitized version of Hansard enables researchers to perform advanced
+analyses on these records using text analysis tools and statistical
+modelling. Following the lead of the LiPaD project, in this paper we
+introduce a novel database for the Australian Hansard. This is composed
+of individual datasets for each sitting day in the House of
+Representatives, containing details on everything said in parliament in
+a form which can be readily used by researchers. With the development of
+tools for large-scale text analysis, this database will serve as a
+valuable resource for efficiently studying and exploring political
+behaviour in Australia over time.
 
-At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis.
-To this point, various researchers have had to create their own databases in an attempt to produce usable, complete Hansard data.
-For instance, @sherratt created an online, easy to read [database](http://historichansard.net) of Hansard from 1901 to 1980 using the XML files.
-These data can be navigated by year, parliament, people, and bills [@sherratt].
-As well, @Leslie_2021_HoR_Aus has released data on all Members of the Australian House of Representatives from 1945 to 2019, and is developing an `R` package for these data.
-Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
+The House of Representatives performs a number of crucial governmental
+functions, such as creating new laws and overseeing government
+expenditure (House of Representatives 2018, ch.~1). Sittings of the
+House follow a predefined order of business, regulated by procedural
+rules called standing orders (House of Representatives 2018, ch.~8). A
+typical sitting day in the Chamber has a number of scheduled proceedings
+including debates on government business, 90 second member statements,
+and Question Time (House of Representatives 2018, ch.~8). The Federation
+Chamber was created in 1994 as a subordinate debate venue of the
+Chamber. This allows for better time management of House business as its
+proceedings occur simultaneously with those of the Chamber (House of
+Representatives 2018, ch.~21). Sittings in the Federation Chamber are
+quite different to those of the Chamber in terms of their order of
+business and scope of discussion. Business matters discussed in the
+Federation Chamber are limited largely to intermediate stages of bill
+development, and the business of private Members (House of
+Representatives 2018, ch.~21). It is the recording and compilation of
+all of these proceedings on which Hansard is based, and it is
+essentially, but not entirely, verbatim.
 
-A number of papers exist which utilize components of Australian Hansard to explore various research topics.
-For example, @salisbury2011 used online Hansard records to explore the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark.
-@rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
-In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
-Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
-@alexander2021 created this database with the static PDF versions Hansard, using OCR to digitize these files into text which is suitable for analysis.
-This means there are considerable digitization errors especially in the first half of the dataset.
+A week or so after each sitting day, a transcript is available for
+download from the official Parliament of Australia website in both
+static PDF and extensible markup language (XML) form. The PDF is the
+official release, which is converted to typed text using Optical
+Character Recognition (OCR) technology (Sherratt 2016). This conversion
+allows for the production of the XML formatted transcript, though these
+are not always perfect conversions and are particularly flawed in the
+early decades of Hansard (Sherratt 2016). The PDF imposes formatting
+designed for humans to read with ease, whereas XML is designed for
+consistency and machine legibility. The nature of XML enables us to more
+easily use code to manipulate these records at scale, motivating our
+choice to develop our database solely using the XML formatted files. In
+cases where we were unsure on how to proceed with processing the XML, we
+defer first to the PDF, and then to the video recording of the
+proceeding if available.
 
-While there is evidently a growing body of literature on this topic, there is still no comprehensive database for Australian Hansard based on XML that spans from 1901 to the present day.
-Our work serves to bridge this gap.
+The end goal for this work is to create a publicly available database of
+parsed Hansard transcripts from 1901 to present in a form which can be
+readily analyzed. More specifically, we aim to present each transcript
+in an ordered form with details on each speaker such as their political
+affiliation, the time stamp of their statement (where available), and
+whether they interjected (i.e.~spoke out of turn). Thus far, this has
+been done for Hansard from mid-2011 to present.
 
-# Description of the Database {#sec-description}
+We begin this paper with a description of what datasets for Australian
+Hansard already exist (Section~\ref{sec-existing}). Next will be a
+detailed description of the contents of our database
+(Section~\ref{sec-description}), followed by a thorough discussion of
+how this database was created (Section~\ref{sec-create}).
 
-Our current database contains 670 comma-separated values (CSV) files, one for each sitting day of the House of Representatives from 10 May 2011 to 08 September 2022.
-We used two scripts to produce these files, which only have one subtle difference.
-Since the Federation Chamber was renamed in mid-2012 from the original title of Main Committee, the element under which all the Federation Chamber contents are nested in the XML was renamed as well [@australia2018house, ch.
-21].
-This difference in element name means that our original code for parsing Federation Chamber content would not work, as the specified node path would be incorrect.
-We accounted for this by creating a separate script with this name change.
-Our first script parses Hansard from 14 August 2012 to 08 September 2022, that being everything after the Federation Chamber name change, and the second script parses Hansard from 10 May 2011 to 28 June 2012.
-All output files in our database are formatted and processed in the exact same way.
-@fig-main15rows provides a snapshot of one of these files.
+\hypertarget{sec-existing}{%
+\section{Existing Datasets}\label{sec-existing}}
 
-![First 15 rows of CSV file for Hansard on 25 February 2020](main_ex15.png){#fig-main15rows}
+At present, the Hansard format that is available on the Parliament of
+Australia website is not accessible for large scale analysis. To this
+point, various researchers have had to create their own databases in an
+attempt to produce usable, complete Hansard data. For instance, Sherratt
+(2016) created an online, easy to read
+\href{http://historichansard.net}{database} of Hansard from 1901 to 1980
+using the XML files. These data can be navigated by year, parliament,
+people, and bills (Sherratt 2016). As well, Leslie (2021) has released
+data on all Members of the Australian House of Representatives from 1945
+to 2019, and is developing an \texttt{R} package for these data.
+Further, Alexander and Hodgetts (2021) created the
+\texttt{AustralianPoliticians} \texttt{R} package, which contains a
+number of datasets related to the political and biographical information
+of Australian federal politicians who were active between 1901 and 2021.
 
-Each row of the CSV file contains an individual statement, with the unique name ID, electorate, and party information of the speaker.
-Of course, for general statements such as "Honourable members", these variables cannot be specified.
-Each proceeding in the Chamber begins with the business start, where the time that the Speaker took the chair is documented, as well as the acknowledgment of the country and reading of the prayers as governed by the standing orders of the House [@standingorders, ch.
-6].
-The Federation Chamber also begins with a business start, where it is stated at what time 5he Deputy Speaker takes the chair.
-For further clarification on each variable in the resulting CSV, @tbl-vars provides an overview of each variable in the database.
+A number of papers exist which utilize components of Australian Hansard
+to explore various research topics. For example, Salisbury (2011) used
+online Hansard records to explore the occurrences of unparliamentary
+comments by members of the House, where The Speaker tells that member to
+withdraw their remark. Rasiah (2010) worked with Question Time data from
+Hansard transcripts during February and March of 2003, to investigate
+resistance of politicians in answering questions about Iraq. In their
+work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
+political prominence by investigating strategic mentions of interest
+groups by elected officials. Finally, the work of Alexander and
+Alexander (2021) offers a dataset of the Australian Hansard, along with
+an analysis of the effect of elections and changes in Prime Ministers
+upon topics mentioned in parliament. Alexander and Alexander (2021)
+created this database with the static PDF versions Hansard, using OCR to
+digitize these files into text which is suitable for analysis. This
+means there are considerable digitization errors especially in the first
+half of the dataset.
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-vars
-#| tbl-cap: "Summary and description of variables in our database"
+While there is evidently a growing body of literature on this topic,
+there is still no comprehensive database for Australian Hansard based on
+XML that spans from 1901 to the present day. Our work serves to bridge
+this gap.
 
-# read in packages
-library(readr)
-library(tidyverse)
-library(here)
-library(XML)
-library(lubridate)
-library(kableExtra)
+\hypertarget{sec-description}{%
+\section{Description of the Database}\label{sec-description}}
 
-# read in example csv
-main_ex <- read_csv("/Volumes/Verbatim/output/main/2020-02-25-main.csv", show_col_types = F)
+Our current database contains 670 comma-separated values (CSV) files,
+one for each sitting day of the House of Representatives from 10 May
+2011 to 08 September 2022. We used two scripts to produce these files,
+which only have one subtle difference. Since the Federation Chamber was
+renamed in mid-2012 from the original title of Main Committee, the
+element under which all the Federation Chamber contents are nested in
+the XML was renamed as well (House of Representatives 2018, ch.~21).
+This difference in element name means that our original code for parsing
+Federation Chamber content would not work, as the specified node path
+would be incorrect. We accounted for this by creating a separate script
+with this name change. Our first script parses Hansard from 14 August
+2012 to 08 September 2022, that being everything after the Federation
+Chamber name change, and the second script parses Hansard from 10 May
+2011 to 28 June 2012. All output files in our database are formatted and
+processed in the exact same way. Figure~\ref{fig-main15rows} provides a
+snapshot of one of these files.
 
-main_ex <- main_ex %>% select(-c(gender, uniqueID))
+\begin{figure}
 
-# create tibble with var names and descriptions
-main_ex_vars <- tibble("Variable" = names(main_ex),
-       "Description" = c("Name of speaker",
-                         "Row number",
-                         "Speech number",
-                         "Page number statement can be found on in official Hansard",
-                         "Time of statement",
-                         "Unique member identification code",
-                         "Speaking member's electorate",
-                         "Speaking member's party",
-                         "Statement text",
-                         "Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)",
-                         "Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)",
-                         "Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)",
-                         "Flag for question (1 if question, 0 otherwise)",
-                         "Flag for answer (1 if answer, 0 otherwise)",
-                         "Flag for question in writing (1 if question in writing, 0 otherwise)",
-                         "Flag for interjection (1 if statement is an interjection, 0 otherwise)"))
+{\centering \includegraphics{main_ex15.png}
 
-# print tibble using kable
-knitr::kable(main_ex_vars, booktabs=T) %>% 
-  kable_styling(full_width = F, latex_options = "HOLD_position")
-```
-
-The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, and `body` variables all came directly from the XML contents.
-In addition to these variables, we added a number of flags to enable easy filtering of statements.
-For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber.
-As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document.
-Further details on this XML structure will follow in @sec-create.
-The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.[^1] We also added a flag for interjections, which are defined as statements made during one members speech by another member who is not the Speaker or Deputy Speaker.
-Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.
-For example, in @fig-main15rows, statements belonging to speech number 3 spans five rows, including two interjections.
-Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest.
-Finally, the `order` variable was added to keep track of the order in which everything was said, and was created after all statements and interjections were separated onto their own rows.
-
-[^1]: More on this in @sec-qa
-
-## Descriptive Statistics {#sec-stats}
-
-A visual exploration of our database offers interesting insight into general characteristics of Hansard.
-First, we looked at the total number of sitting days in the House of Representatives for each year from 2000 to 2021.
-@fig-plot1 illustrates that the number of House sitting days tends to fluctuate over time, where within this time span the years 2013 and 2019 had the fewest sitting days (45), and 2014 had the most sitting days (76).
-
-```{r}
-#| warning: false
-#| echo: false
-
-# grab list of all file names
-all_files <- list.files("/Volumes/Verbatim/input")
-
-# extract year month and day
-all_files <- all_files %>% 
-  str_remove(".xml") %>% 
-  as_tibble() %>% 
-  mutate(year = as.numeric(str_extract(value, "^[[:digit:]]{4}")),
-         month = as.numeric(str_extract(value, "(?<=\\-)[[:digit:]]{2}(?=\\-)")),
-         day = as.numeric(str_extract(value, "(?<=\\-)[[:digit:]]{2}$")))
-
-# plot of total number of sitting days per year
-plot1 <- all_files %>% 
-  filter(year!=2022) %>% 
-  group_by(year) %>% 
-  summarise(tot_days = n()) %>% 
-  ggplot(aes(x=year, y=tot_days)) + 
-  geom_point() +
-  geom_line() + 
-  theme_bw() +
-  labs(x = "Year", 
-       y = "Count")
-
-# plot of number of sitting days per month from 2015-2020
-# all_files %>% 
-#   filter(year==2015|year==2016|year==2017|year==2018|year==2019|year==2020) %>%
-#   mutate(month_abb = month.abb[month]) %>% 
-#   group_by(year, month_abb) %>% 
-#   summarise(avg_days = n()) %>% 
-#   ggplot(aes(x=factor(month_abb, levels=month.abb), y=avg_days)) +
-#   geom_col() + 
-#   facet_wrap(~year) +
-#   theme_bw() + 
-#   labs(x = "Month", 
-#        y="Count", 
-#        title = "Number of sitting days per month (2015-2020)") +
-#   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
-```
-
-```{r, out.width="80%"}
-#| echo: false
-#| message: false
-#| fig-cap: "Total number of sitting days per year (2000-2021)"
-#| label: fig-plot1
-
-plot1
-```
-
-```{r}
-#| echo: false
-#| eval: false
-# generating some descriptive statistics
-
-# first grab list of all main CSVs
-all_dfs <- list.files("/Volumes/Verbatim/output/main")
-
-# define empty tibbles to store things in
-interject_data <- tibble()
-fedchamb_rows <- tibble()
-unique_data <- tibble()
-
-for(i in 1:length(all_dfs)){
-  # define df
-  this_df <- read_csv(paste0("/Volumes/Verbatim/output/main/", all_dfs[i]), show_col_types = F)
-
-  # number of interjections
-  this_interject_data <- this_df %>% group_by(interject) %>%
-    summarise(n_interject=n()) %>%
-    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
-    select(date, interject, n_interject)
-
-  # number of rows in chamb and fedchamb
-  this_fedchamb_rows <- this_df %>% group_by(fedchamb_flag) %>% 
-    summarise(n_rows = n()) %>% 
-    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
-    select(date, fedchamb_flag, n_rows)
-
-  # number of unique things (NAs omitted) - need to fix a tiny bit more but better for now
-  this_nameid <- this_df %>% select(name.id, fedchamb_flag) %>% 
-    group_by(fedchamb_flag) %>% 
-    unique() %>% 
-    na.omit() %>% 
-    summarise(n_name.id = n())
-
-  this_electorate <- this_df %>% select(electorate, fedchamb_flag) %>% 
-    group_by(fedchamb_flag) %>% 
-    unique() %>% 
-    na.omit() %>% 
-    summarise(n_electorate = n())
-
-  this_party <- this_df %>% select(party, fedchamb_flag) %>% 
-    group_by(fedchamb_flag) %>% 
-    unique() %>% 
-    na.omit() %>% 
-    summarise(n_party = n())
-
-  this_name <- this_df %>% select(name, fedchamb_flag) %>% 
-    group_by(fedchamb_flag) %>% 
-    unique() %>% 
-    filter(name!="business start" & name!="stage direction" & !str_detect(name, "member") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
-    na.omit() %>% 
-    mutate(name = str_remove(name, "^Mrs[[:space:]]|^Mr[[:space:]]|^Ms[[:space:]]|^Dr[[:space:]]"),
-           surname = str_extract(name, "^.{1,20}(?=\\,[[:space:]][[:upper:]][[:lower:]])"),
-           surname = ifelse(is.na(surname) & !str_detect(name, "^The DEPUTY SPEAKER"), name, surname),
-           surname = ifelse(is.na(surname) & str_detect(name, "^The DEPUTY SPEAKER"), str_extract(name, "(?<=\\(Mrs[[:space:]]|\\(Mr[[:space:]]|\\(Ms[[:space:]]|\\(Dr[[:space:]]).{1,20}(?=\\))"), surname),
-           surname = str_to_title(surname),
-           first_name = str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=\\,[[:space:]]MP)|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP \\(The DEPUTY SPEAKER\\))|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP)"),
-           first_name = ifelse(is.na(first_name) & str_detect(name, "\\(The"), str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]\\(The)"), first_name)) %>%
-    group_by(surname) %>% 
-    fill(first_name, .direction = "updown") %>% select(-name) %>% 
-    unique() %>% 
-    ungroup() %>% 
-    group_by(fedchamb_flag) %>% 
-    summarise(n_names=n())
-
-this_unique_data <- merge(this_nameid, this_electorate, by="fedchamb_flag") %>% 
-  merge(., this_party, by="fedchamb_flag") %>% 
-  merge(., this_name, by="fedchamb_flag") %>% 
-  as_tibble() %>% 
-  mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d")))
-
-# this_unique_data <- tibble(this_df %>% select(electorate) %>% unique() %>% na.omit() %>% summarise(n_electorate = n()),
-#                            this_df %>% select(party) %>% unique() %>% na.omit() %>% summarise(n_party = n()),
-#                            this_df %>% select(name.id) %>% unique() %>% na.omit() %>% summarise(n_name.id = n()),
-#                            this_df %>% select(name) %>% unique() %>% filter(name!="business start" & name!="stage direction" & 
-#                                                                               !str_detect(name, "member") & name!="The DEPUTY SPEAKER" & name!="The SPEAKER") %>% 
-#                              na.omit() %>% 
-#                              mutate(name = str_remove(name, "^Mrs[[:space:]]|^Mr[[:space:]]|^Ms[[:space:]]|^Dr[[:space:]]"),
-#                                     surname = str_extract(name, "^.{1,20}(?=\\,[[:space:]][[:upper:]][[:lower:]])"),
-#                                     surname = ifelse(is.na(surname), name, surname),
-#                                     surname = str_to_title(surname),
-#                                     first_name = str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=\\,[[:space:]]MP)|(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]MP)"),
-#                                     first_name = ifelse(is.na(first_name) & str_detect(name, "\\(The"), str_extract(name, "(?<=\\,[[:space:]]).{1,20}(?=[[:space:]]\\(The)"), first_name)) %>%
-#                              group_by(surname) %>% 
-#                              fill(first_name, .direction = "updown") %>% select(-name) %>% 
-#                              unique() %>% ungroup() %>% summarise(n_names=n())) %>% 
-#     mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
-#     select(date, n_names, n_name.id, n_electorate, n_party)
-
-  # bind new stuff onto existing tibble
-  interject_data <- rbind(interject_data, this_interject_data)
-  fedchamb_rows <- rbind(fedchamb_rows, this_fedchamb_rows)
-  unique_data <- rbind(unique_data, this_unique_data)
 }
 
-write.csv(interject_data, paste0("~/Desktop/RA/hansard-proj/paper/interject_data.csv"), row.names = FALSE)
-write.csv(fedchamb_rows, paste0("~/Desktop/RA/hansard-proj/paper/fedchamb_rows.csv"), row.names = FALSE)
-write.csv(unique_data, paste0("~/Desktop/RA/hansard-proj/paper/unique_data.csv"), row.names = FALSE)
-```
+\caption{\label{fig-main15rows}First 15 rows of CSV file for Hansard on
+25 February 2020}
 
-```{r}
-#| echo: false
-#| message: false
+\end{figure}
 
-# read in descriptive statistics data
-interject_data <- read_csv("interject_data.csv", show_col_types = FALSE)
-fedchamb_rows <- read_csv("fedchamb_rows.csv", show_col_types = FALSE)
-unique_data <- read_csv("unique_data.csv", show_col_types = FALSE)
+Each row of the CSV file contains an individual statement, with the
+unique name ID, electorate, and party information of the speaker. Of
+course, for general statements such as ``Honourable members'', these
+variables cannot be specified. Each proceeding in the Chamber begins
+with the business start, where the time that the Speaker took the chair
+is documented, as well as the acknowledgment of the country and reading
+of the prayers as governed by the standing orders of the House
+(Department of the House of Representatives 2019, ch.~6). The Federation
+Chamber also begins with a business start, where it is stated at what
+time 5he Deputy Speaker takes the chair. For further clarification on
+each variable in the resulting CSV, Table~\ref{tbl-vars} provides an
+overview of each variable in the database.
 
-# checking meeting of fed chamb on fridays, only happened once in our database on 12 June 2020
-# library(lubridate)
-# fedchamb_rows$day_of_week <- wday(fedchamb_rows$date, label=T)
-# fedchamb_rows %>% filter(day_of_week=="Fri")
+\hypertarget{tbl-vars}{}
+\begin{table}[H]
+\caption{\label{tbl-vars}Summary and description of variables in our database }\tabularnewline
 
-# average number of rows per day by year, broken down by chamber and federation chamber
-fedchamb_rows$fedchamb_flag <- factor(fedchamb_rows$fedchamb_flag, levels=c(0, 1), labels=c("House of Representatives", "Federation Chamber"))
+\centering
+\begin{tabular}{ll}
+\toprule
+Variable & Description\\
+\midrule
+name & Name of speaker\\
+order & Row number\\
+speech\_no & Speech number\\
+page.no & Page number statement can be found on in official Hansard\\
+time.stamp & Time of statement\\
+\addlinespace
+name.id & Unique member identification code\\
+electorate & Speaking member's electorate\\
+party & Speaking member's party\\
+body & Statement text\\
+fedchamb\_flag & Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)\\
+\addlinespace
+sub1\_flag & Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)\\
+sub2\_flag & Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)\\
+question & Flag for question (1 if question, 0 otherwise)\\
+answer & Flag for answer (1 if answer, 0 otherwise)\\
+q\_in\_writing & Flag for question in writing (1 if question in writing, 0 otherwise)\\
+\addlinespace
+interject & Flag for interjection (1 if statement is an interjection, 0 otherwise)\\
+\bottomrule
+\end{tabular}
+\end{table}
 
-plot2 <- fedchamb_rows %>% 
-  mutate(year = as.numeric(str_extract(date, "\\d\\d\\d\\d(?=-)"))) %>% 
-  filter(year!=2022) %>% 
-  group_by(year, fedchamb_flag) %>% 
-  summarise(avg_rows = mean(n_rows)) %>% 
-  ggplot(aes(y = avg_rows, x = as.factor(year), fill = fedchamb_flag)) + 
-  geom_bar(position = "stack", stat = "identity") +
-  theme_bw() +
-  labs(x = "Year", y = "Average number of rows", fill = "") +
-  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
+The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
+\texttt{name.id}, \texttt{electorate}, \texttt{party}, and \texttt{body}
+variables all came directly from the XML contents. In addition to these
+variables, we added a number of flags to enable easy filtering of
+statements. For example, adding the \texttt{fedchamb\_flag} provides a
+clear distinction between the proceedings of the Chamber with those of
+the Federation Chamber. As well, the \texttt{sub1\_flag} and
+\texttt{sub2\_flag} variables allow us to keep track of where various
+statements are being parsed from in the XML document. Further details on
+this XML structure will follow in Section~\ref{sec-create}. The
+\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
+were added to identify statements belonging to Question Time, and the
+nature of these statements.\footnote{More on this in
+  Section~\ref{sec-qa}} We also added a flag for interjections, which
+are defined as statements made during one members speech by another
+member who is not the Speaker or Deputy Speaker. Further, the
+\texttt{speech\_no} variable allows us to keep track of the speech
+number that each statement and interjection belongs to. For example, in
+Figure~\ref{fig-main15rows}, statements belonging to speech number 3
+spans five rows, including two interjections. Having the speech number
+variable offers an easy way to group statements by speech or isolate
+specific speeches of interest. Finally, the \texttt{order} variable was
+added to keep track of the order in which everything was said, and was
+created after all statements and interjections were separated onto their
+own rows.
 
-# plot pct rows that are interjections
-plot3 <- interject_data %>% 
-  group_by(date) %>% 
-  summarise(pct_interject = 100*(n_interject[interject==1]/sum(n_interject))) %>% 
-  ggplot(aes(x = date, y = pct_interject)) +
-  geom_smooth() +
-  geom_point(alpha = 0.4)+
-  theme_bw() +
-  labs(x = "Date", y = "Percent interjections")
-```
+\hypertarget{sec-stats}{%
+\subsection{Descriptive Statistics}\label{sec-stats}}
 
-In @fig-plot2, we consider the average number of rows per sitting day per year, disaggregated by Chamber and Federation Chamber proceedings.
-We can see that 2014 has the highest average number of rows per day, and 2021 has the lowest average number of rows per day.
-There appears to be less fluctuation in the average number of rows per day in the Federation Chamber than there is in that of the Chamber.
+A visual exploration of our database offers interesting insight into
+general characteristics of Hansard. First, we looked at the total number
+of sitting days in the House of Representatives for each year from 2000
+to 2021. Figure~\ref{fig-plot1} illustrates that the number of House
+sitting days tends to fluctuate over time, where within this time span
+the years 2013 and 2019 had the fewest sitting days (45), and 2014 had
+the most sitting days (76).
 
-```{r, out.width="80%"}
-#| fig-cap: "Average number of rows in Hansard per year,\nby Chamber and Federation Chamber"
-#| label: fig-plot2
-#| echo: false
-#| message: false
+\begin{figure}
 
-plot2
-```
+{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-plot1-1.pdf}
 
-Next we were interested in the percentage of rows in each Hansard which are flagged as interjections, using our definition of interjections mentioned above.
-We found that on average, approximately 18% of rows are characterized as interjections.
-Further, of all sitting days in our database, 25 June 2014 had the greatest percentage of rows being interjections, which was approximately 33%.
-The day with the smallest percentage of interjections was 23 March 2015, at approximately 3%.
-Based on @fig-plot3, there do not appear to be any significant fluctuations or patterns in the percentage of rows that are interjections across our time span.
+}
 
-```{r, out.width="80%"}
-#| fig-cap: "Percentage of rows in Hansard that are interjections, 10 May 2011 - 08 September 2022"
-#| label: fig-plot3
-#| echo: false
-#| message: false
+\caption{\label{fig-plot1}Total number of sitting days per year
+(2000-2021)}
 
-plot3
-```
+\end{figure}
 
-Finally, @fig-unique_plots summarizes the number of unique speakers, electorates, and parties found in Hansard over time.
-In all three panels, the data exhibit the same general pattern over time for both the House of Representatives and the Federation Chamber, where the magnitude for the House data is consistently greater than that of the Federation Chamber.
-Panels A and B in @fig-unique_plots illustrate that the number of unique names and electorates follow a very consistent trend across the entire time frame.
-Panel C shows that the number of unique parties has increased slightly since 2018.
+In Figure~\ref{fig-plot2}, we consider the average number of rows per
+sitting day per year, disaggregated by Chamber and Federation Chamber
+proceedings. We can see that 2014 has the highest average number of rows
+per day, and 2021 has the lowest average number of rows per day. There
+appears to be less fluctuation in the average number of rows per day in
+the Federation Chamber than there is in that of the Chamber.
 
-![Number of unique names (A), electorates (B), and parties (C) found on each sitting day.](unique_plots.png){#fig-unique_plots}
+\begin{figure}
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| eval: false
+{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-plot2-1.pdf}
 
-unique_data$fedchamb_flag <- factor(unique_data$fedchamb_flag, levels=c(0, 1), labels=c("House of Representatives", "Federation Chamber"))
+}
 
-unique_plot1 <- ggplot(unique_data, aes(x = date, y = n_names, color = fedchamb_flag)) + 
-  geom_point(alpha = 0.5)+
-  geom_smooth() +
-  theme_bw() +
-  labs(y = "# unique names", x = "Date", color = "")
+\caption{\label{fig-plot2}Average number of rows in Hansard per year, by
+Chamber and Federation Chamber}
 
-unique_plot2 <- ggplot(unique_data, aes(x = date, y = n_electorate, color = fedchamb_flag)) + 
-  geom_point(alpha = 0.5) +
-  geom_smooth() +
-  theme_bw() +
-  labs(y = "# unique electorates", x = "Date", color = "")
+\end{figure}
 
-unique_plot3 <- ggplot(unique_data, aes(x = date, y = n_party, color = fedchamb_flag)) + 
-  geom_point(position = "jitter", alpha = 0.5) +
-  geom_smooth() +
-  theme_bw() +
-  labs(y = "# unique parties", x = "Date", color = "")
+Next we were interested in the percentage of rows in each Hansard which
+are flagged as interjections, using our definition of interjections
+mentioned above. We found that on average, approximately 18\% of rows
+are characterized as interjections. Further, of all sitting days in our
+database, 25 June 2014 had the greatest percentage of rows being
+interjections, which was approximately 33\%. The day with the smallest
+percentage of interjections was 23 March 2015, at approximately 3\%.
+Based on Figure~\ref{fig-plot3}, there do not appear to be any
+significant fluctuations or patterns in the percentage of rows that are
+interjections across our time span.
 
-# unique_data %>% group_by(fedchamb_flag) %>% summarise(mean_name = mean(n_names),
-#                                                       mean_nameID = mean(n_name.id),
-#                                                       mean_elecs = mean(n_electorate),
-#                                                       mean_party = mean(n_party))
+\begin{figure}
 
-# ggsave("unique_plot1.png", unique_plot1)
-# ggsave("unique_plot2.png", unique_plot2)
-# ggsave("unique_plot3.png", unique_plot3)
+{\centering \includegraphics[width=0.8\textwidth,height=\textheight]{paper_files/figure-pdf/fig-plot3-1.pdf}
 
-ggpubr::ggarrange(unique_plot1, unique_plot2, unique_plot3, ncol=2, nrow=2, common.legend = T, legend = "top", labels = "AUTO")
-```
+}
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-descrip
-#| tbl-cap: "Average number of unique names, electorates, and parties in Hansard per year"
-#| eval: false
+\caption{\label{fig-plot3}Percentage of rows in Hansard that are
+interjections, 10 May 2011 - 08 September 2022}
 
-######## not using this
+\end{figure}
 
-# create table of averages by year
-unique_table <- unique_data %>% 
-  mutate(year = str_extract(date, "^\\d\\d\\d\\d")) %>% 
-  filter(year!=2022) %>% 
-  group_by(year) %>% 
-  summarise(mean_name = round(mean(n_names), 0),
-            mean_elec = round(mean(n_electorate), 0),
-            mean_party = round(mean(n_party), 0)) %>% 
-  rename("Names" = mean_name,
-         "Electorates" = mean_elec,
-         "Parties" = mean_party,
-         "Year" = year)
+Finally, Figure~\ref{fig-unique_plots} summarizes the number of unique
+speakers, electorates, and parties found in Hansard over time. In all
+three panels, the data exhibit the same general pattern over time for
+both the House of Representatives and the Federation Chamber, where the
+magnitude for the House data is consistently greater than that of the
+Federation Chamber. Panels A and B in Figure~\ref{fig-unique_plots}
+illustrate that the number of unique names and electorates follow a very
+consistent trend across the entire time frame. Panel C shows that the
+number of unique parties has increased slightly since 2018.
 
-# overall averages all years
-unique_avgs <- unique_data %>% 
-  mutate(year = str_extract(date, "^\\d\\d\\d\\d")) %>% 
-  filter(year!=2022) %>% 
-  summarise(mean_name = round(mean(n_names), 0),
-            mean_elec = round(mean(n_electorate), 0),
-            mean_party = round(mean(n_party), 0))
+\begin{figure}
 
-# print table
-knitr::kable(unique_table, booktabs=T) %>% 
-  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
-```
+{\centering \includegraphics{unique_plots.png}
 
-# Creation of the Database {#sec-create}
+}
 
-The approach to parsing contents of an XML document is heavily dependent on its tree structure.
-As such, to create this database, we started by looking at a single Hansard XML transcript.
-Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form.
-For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them.
-Parsing was performed in `R` using the `XML` package.
-Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible.
-Further, since we are looking at such a wide time span of documents, there are expectedly a number of changes in the way they are formatted.
-Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure.
-Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting.
-As mentioned in @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.
+\caption{\label{fig-unique_plots}Number of unique names (A), electorates
+(B), and parties (C) found on each sitting day.}
 
-@fig-xml1 provides an example of the beginning of an XML file for Hansard.
-The XML structure begins with a root or parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements with information such as the date, and parliament number, which are all highlighted in pink.
-Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1.
-On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too.
-This allows for the distinction of proceedings of the Chamber and Federation Chamber.
-As mentioned in @sec-description, each proceeding begins with the business start.
-The structure of this business start can be seen between the nodes highlighted in green in @fig-xml1.
-The content we parse from the business start are shown highlighted in orange in @fig-xml1.
-Next comes the debates and nested sub-debates, which follow the business start.
-Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it.
-That said, sometimes sub-debate 2 is not nested within sub-debate 1.
-Each of these three elements as well as their respective sub-elements contain important information on the title of the debate or sub-debate, who is speaking, and what is being said.
-As mentioned, in many cases speeches are interrupted by interjections, which are embedded in these sub-elements as well.
-The final key distinct component of Hansard is Question Time, in which question and answer elements are classified differently than general debate text.
-Sometimes questions and answers are nested within debate or sub-debate child nodes, and other times they have their own child node.
-More detail on the processing of Question Time will follow in @sec-qa.
+\end{figure}
 
-![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
+\begin{table}
 
-Once code was written to parse all components, it was organized into individual scripts.
-The first script includes everything from the session header element, the second contains everything from the debate element, and the third and fourth contain everything from the sub-debate 1 and 2 elements, respectively.
-The fifth script contains debate interjection information, and the sixth contains content from Question Time.
-The final script is a compilation of everything.
-The next step was to further develop these scripts to produce tidy data sets from each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order.
-This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
-The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
-In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
-As such, the name, name ID, electorate and party details were only provided for the person who's turn it was to speak.
-Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort.
-@sec-interject will provide further details on the intricacies of this task.
+\end{table}
 
-When beginning to run these scripts on transcripts from other sitting days, it became clear that not every sitting day contains every possible XML element.
-For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding.
-To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
-For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.
-Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files.
-Specifically, the earliest date for which it works is 10 May 2011.
-Before writing a new script for parsing earlier Hansard, we decided to prioritize cleaning and finalizing what we have been able to parse.
-As such we continued building our scripts, fixing any issues we noticed in the resulting datasets, and splitting up any additional sections of the parsed text onto separate rows where necessary.
-Specifically, we added a section of our script to separate out general stage directions.
-More information on this separation will be provided in @sec-stage.
+\hypertarget{sec-create}{%
+\section{Creation of the Database}\label{sec-create}}
 
-After completing the scripts, they were formatted as functions which take a file name argument.
-The final script which parses everything from Hansard produces one CSV file with the data on all proceedings for each sitting day (example shown in @fig-main15rows).
+The approach to parsing contents of an XML document is heavily dependent
+on its tree structure. As such, to create this database, we started by
+looking at a single Hansard XML transcript. Doing so enabled us to
+identify the various components of interest in the document, and how
+each one can be parsed according to its corresponding structural form.
+For example, the beginning of a speech may be followed by various
+interjections and continuations, all of which are structured as unique
+sub-elements containing further nested sub-elements within them. Parsing
+was performed in \texttt{R} using the \texttt{XML} package. Focusing on
+one transcript also allowed us to ensure that all key components of the
+transcript were being parsed and captured with as much detail as
+possible. Further, since we are looking at such a wide time span of
+documents, there are expectedly a number of changes in the way they are
+formatted. Some changes are as subtle as a differently named child-node,
+while others are as extensive as a completely different nesting
+structure. Smaller changes were accounted for as we became aware of
+them, and embedded into the final scripts in a way that would not cause
+issues for parsing more current Hansards with slightly different
+formatting. As mentioned in Section~\ref{sec-intro}, the significant
+changes in XML structure of Hansard preceding 2011 necessitates much
+further development of our current scripts, which we are actively
+working to complete.
 
-## Question Time {#sec-qa}
+Figure~\ref{fig-xml1} provides an example of the beginning of an XML
+file for Hansard. The XML structure begins with a root or parent element
+\texttt{"hansard"} (highlighted in blue), followed by a child element
+\texttt{"session.header"} (highlighted in yellow) with sub-child
+elements with information such as the date, and parliament number, which
+are all highlighted in pink. Next there is a child element containing
+everything that takes place in the Chamber, \texttt{"chamber.xscript"},
+which is also highlighted in yellow in Figure~\ref{fig-xml1}. On sitting
+days where the Federation Chamber met as well, a child element exists
+for the Federation Chamber too. This allows for the distinction of
+proceedings of the Chamber and Federation Chamber. As mentioned in
+Section~\ref{sec-description}, each proceeding begins with the business
+start. The structure of this business start can be seen between the
+nodes highlighted in green in Figure~\ref{fig-xml1}. The content we
+parse from the business start are shown highlighted in orange in
+Figure~\ref{fig-xml1}. Next comes the debates and nested sub-debates,
+which follow the business start. Broadly, the speeches within Hansard
+transcripts are structured with a debate node, containing a sub-debate 1
+child-node which has a sub-debate 2 child-node nested within it. That
+said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of
+these three elements as well as their respective sub-elements contain
+important information on the title of the debate or sub-debate, who is
+speaking, and what is being said. As mentioned, in many cases speeches
+are interrupted by interjections, which are embedded in these
+sub-elements as well. The final key distinct component of Hansard is
+Question Time, in which question and answer elements are classified
+differently than general debate text. Sometimes questions and answers
+are nested within debate or sub-debate child nodes, and other times they
+have their own child node. More detail on the processing of Question
+Time will follow in Section~\ref{sec-qa}.
 
-A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions.
+\begin{figure}
+
+{\centering \includegraphics{xml1.png}
+
+}
+
+\caption{\label{fig-xml1}Snapshot of beginning of XML file for Hansard
+on 25 February 2020}
+
+\end{figure}
+
+Once code was written to parse all components, it was organized into
+individual scripts. The first script includes everything from the
+session header element, the second contains everything from the debate
+element, and the third and fourth contain everything from the sub-debate
+1 and 2 elements, respectively. The fifth script contains debate
+interjection information, and the sixth contains content from Question
+Time. The final script is a compilation of everything. The next step was
+to further develop these scripts to produce tidy data sets from each
+parsed element, where each statement is separated onto its own row with
+details about the speaker, and rows are placed in chronological order.
+This first involved correcting the variable classes and adding a number
+of indicator variables to differentiate where statements came from, such
+as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate
+2. The next key task stemmed from the fact that the raw text data were
+not separated by each statement when parsed. In other words, any
+interjections, comments made by The Speaker or Deputy Speaker and
+continuations within an individual speech were all parsed together as a
+single string. As such, the name, name ID, electorate and party details
+were only provided for the person who's turn it was to speak. Splitting
+up these speeches in a way which would be generalizable across sitting
+days required much thought and effort. Section~\ref{sec-interject} will
+provide further details on the intricacies of this task.
+
+When beginning to run these scripts on transcripts from other sitting
+days, it became clear that not every sitting day contains every possible
+XML element. For example, some days did not have sub-debate 2 content,
+and some days did not have a Federation Chamber proceeding. To improve
+the generalizability of these scripts, if-else statements were embedded
+within the code wherever an error might arise due to a missing element.
+For example, the entire Federation Chamber block of code is wrapped in
+an if-else statement for each script, so that it only executes if what
+the code attempts to parse actually exists in the file. Once the script
+ran without error for a few recent years of Hansard, we continued to
+work backwards until extensive changes in tree structure made our script
+incompatible with parsing earlier XML files. Specifically, the earliest
+date for which it works is 10 May 2011. Before writing a new script for
+parsing earlier Hansard, we decided to prioritize cleaning and
+finalizing what we have been able to parse. As such we continued
+building our scripts, fixing any issues we noticed in the resulting
+datasets, and splitting up any additional sections of the parsed text
+onto separate rows where necessary. Specifically, we added a section of
+our script to separate out general stage directions. More information on
+this separation will be provided in Section~\ref{sec-stage}.
+
+After completing the scripts, they were formatted as functions which
+take a file name argument. The final script which parses everything from
+Hansard produces one CSV file with the data on all proceedings for each
+sitting day (example shown in Figure~\ref{fig-main15rows}).
+
+\hypertarget{sec-qa}{%
+\subsection{Question Time}\label{sec-qa}}
+
+A key characteristic of the Australian parliament system is the ability
+for the executive government to be held accountable for their decisions.
 One core mechanism by which this is achieved is called Question Time.
-This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
-Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
-Sometimes, questions in writing are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
-However, in other times, questions in writing are embedded in their own child node called `"answers.to.questions"` outside of `"chamber.xscript"`.
-Difficulty arose when trying to order these questions and answers correctly within the rest of the debate text, because unlike all other statements made which have both an associated page number and time stamp, these generally only have a page number.
-Time stamps have been a key variable for which we have arranged parsed text in chronological order, especially since many statements tend to be on the same page, meaning we cannot rely solely on page number to capture correct ordering.
-To approach this issue, we merged all parsed questions to be in a single dataframe, and all parsed answers in another dataframe.
-We then arranged each dataframe by page number, and merged the two dataframes in such a way that each question would be followed by its corresponding answer.
+This is a period on each sitting day in the Chamber where members of the
+House can ask ministers two types of questions: questions in writing
+which are written in advance, or questions without notice which are
+asked verbally in the Chamber and are responded to in real time (House
+of Representatives 2021). Parsing the components of Question Time
+required a slightly different approach than that of the debate speech,
+because of its unique structure in the XML document. Sometimes,
+questions in writing are included directly in the
+\texttt{"chamber.xscript"} child node, with sub-child nodes called
+\texttt{"question"} and \texttt{"answer"} to differentiate the two.
+However, in other times, questions in writing are embedded in their own
+child node called \texttt{"answers.to.questions"} outside of
+\texttt{"chamber.xscript"}. Difficulty arose when trying to order these
+questions and answers correctly within the rest of the debate text,
+because unlike all other statements made which have both an associated
+page number and time stamp, these generally only have a page number.
+Time stamps have been a key variable for which we have arranged parsed
+text in chronological order, especially since many statements tend to be
+on the same page, meaning we cannot rely solely on page number to
+capture correct ordering. To approach this issue, we merged all parsed
+questions to be in a single dataframe, and all parsed answers in another
+dataframe. We then arranged each dataframe by page number, and merged
+the two dataframes in such a way that each question would be followed by
+its corresponding answer.
 
-## Interjections {#sec-interject}
+\hypertarget{sec-interject}{%
+\subsection{Interjections}\label{sec-interject}}
 
-As mentioned, the text was structured and parsed in such a way that various interjections and comments which happened during a speech were not separated onto individual rows.
-Below is a simple example extracted from Hansard on 30 November 2021, where Mr.
-van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.
+As mentioned, the text was structured and parsed in such a way that
+various interjections and comments which happened during a speech were
+not separated onto individual rows. Below is a simple example extracted
+from Hansard on 30 November 2021, where Mr.~van Manen is interrupted by
+The Speaker who states that the time for members' statements has
+concluded.
 
-> ```{r}
-> #| warning: false
-> #| echo: false
-> #| message: false
-> #| results: asis
-> >
-> # read in XML file
-> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
-> >
-> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
-> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
->                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
->   as_tibble() %>% 
->   slice(25) %>% 
->   pull(body)
-> >
-> # print example of text in quotations
-> cat(paste0('"', interject_text_ex, '"'))
-> ```
+\begin{quote}
+``Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great
+pleasure to share with the House that Windaroo Valley State High School
+has qualified for the finals of the Australian Space Design Competition,
+to begin in January next year. The competition is regarded as the
+premier STEM competition for high school students and is recognised by
+universities around the country. The students are required to respond to
+industry-level engineering and requests for tender for design and---The
+SPEAKER: Order! In accordance with standing order 43, the time for
+members' statements has concluded.''
+\end{quote}
 
-As previously discussed, we wanted to have each statement on its own row, with the correct name, name ID, electorate and party information on the individual speaking.
-We approached this task in a number of steps.
-Once all parsed text from the XML was merged into one dataframe called `main`, we added a `"speech_no"` variable.
-As noted in @sec-description, this was done to keep track of which speech each interjection, comment, or continuation belonged to as we separated these components onto their own rows.
+As previously discussed, we wanted to have each statement on its own
+row, with the correct name, name ID, electorate and party information on
+the individual speaking. We approached this task in a number of steps.
+Once all parsed text from the XML was merged into one dataframe called
+\texttt{main}, we added a \texttt{"speech\_no"} variable. As noted in
+Section~\ref{sec-description}, this was done to keep track of which
+speech each interjection, comment, or continuation belonged to as we
+separated these components onto their own rows.
 
-The next step was to extract all the names and titles preceding these interjections, comments and continuations.
-This would enable us to then separate the speeches in the correct places using these names and titles in combination with regular expressions, which are patterns of characters that can be used to search bodies of text.
-We completed this extraction process with a few intermediate steps, due to the large number of name styles and interjection types that had to be accounted for, each requiring their own unique regular expression format.
+The next step was to extract all the names and titles preceding these
+interjections, comments and continuations. This would enable us to then
+separate the speeches in the correct places using these names and titles
+in combination with regular expressions, which are patterns of
+characters that can be used to search bodies of text. We completed this
+extraction process with a few intermediate steps, due to the large
+number of name styles and interjection types that had to be accounted
+for, each requiring their own unique regular expression format.
 
-In many of the XML files, below the full speech including all interjections and continuations, there is a series of child-nodes which exist to capture the structure of interruptions in that speech.
-@fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
-Looking at the elements highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation.
-As mentioned, this text is embedded within the speech above it.
-However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on.
-Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
-We stored this as a dataframe called `"interject"`.[^2]
+In many of the XML files, below the full speech including all
+interjections and continuations, there is a series of child-nodes which
+exist to capture the structure of interruptions in that speech.
+Figure~\ref{fig-xml3} provides an example of this, where the speech was
+interrupted by a comment from The Deputy Speaker, and then the member
+continued their speech. Looking at the elements highlighted in blue, it
+is clear that these child-nodes do not contain the actual text for the
+interjection or continuation. As mentioned, this text is embedded within
+the speech above it. However, as shown by the content highlighted in
+pink in Figure~\ref{fig-xml3}, we were able to extract useful details on
+the individual interjecting which we could use later on. Making use of
+this structure, we extracted names and information of all individuals
+that were categorized within the XML as interjections. We stored this as
+a dataframe called \texttt{"interject"}.\footnote{We decided not to
+  include this data in our final database, as it is all embedded in our
+  resulting datasets which have a flag for interjections.}
 
-[^2]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.
+\begin{figure}
 
-![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
+{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}
 
-We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
-We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
-When a Member interjects or continues a speech, the usual form of their name is a prefix followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.[^3] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
-Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
-This variation demands careful consideration when writing regular expression patterns to search for in the text.
-In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
+}
 
-[^3]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
+\caption{\label{fig-xml3}Snapshot of XML structure with interjection and
+continuation from 03 February 2021 Hansard}
 
-Having these lists enabled us to extract the names of Members and their associated prefixes as they exist in the text, by searching for exact matches with regular expression patterns.
-We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds.
-A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
-These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.
+\end{figure}
 
-Once all interjections, comments and continuations were successfully split onto their own rows, we added a general order variable to the dataset based on row number, to keep track of the order in which everything was said.
-The next step was to fill the name, name ID, electorate and party variables with the correct data for each row.
-To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, and party for that individual [@fig-lookup].
-We used the main dataset from the `AustralianPoliticians` package in the creation of this lookup table [@auspol].
+We then created lists using both the \texttt{interject} and
+\texttt{main} dataframes to capture all the names of individuals who
+spoke that day. We added the names of all Members in a number of unique
+formats, due to the frequent variation in how names are transcribed in
+Hansard. When a Member interjects or continues a speech, the usual form
+of their name is a prefix followed by their first name or first initial
+and/or last name. There is also variation in the capitalization of these
+names.\footnote{Sometimes when someones first name is included, only
+  their last name is capitalized, while sometimes their full name is
+  capitalized, or other times neither are capitalized.} Another source
+of variation is in individuals with more than one first name, as
+sometimes only their first first name is written, while other times
+their entire first name is written. Additionally, some surnames have
+punctuation, and some surnames have specific capitalization such as
+``McCormack'', where even in full capitalization, the first ``c''
+remains lower case. This variation demands careful consideration when
+writing regular expression patterns to search for in the text. In these
+lists we also accounted for any general interjection statements
+transcribed that were not attributed to an individual, such as ``An
+opposition member interjecting-''.
 
-![First 10 rows of lookup table from 10 May 2018 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
+Having these lists enabled us to extract the names of Members and their
+associated prefixes as they exist in the text, by searching for exact
+matches with regular expression patterns. We then used these extracted
+names to split all the speeches up, using a number of regular
+expressions with lookarounds. A lookaround can be added to a regular
+expression pattern to enhance the specificity of matches. These were
+used to ensure that the text was not being split in the wrong places,
+such as places where Members were simply being named in the statement of
+another Member.
 
-Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps in the table with available name ID, electorate and party information.
-Finally, we were able to add a flag for interjections.
-Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak.
-@fig-interject provides an example of a Federation Chamber proceeding with interjections.
-Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
+Once all interjections, comments and continuations were successfully
+split onto their own rows, we added a general order variable to the
+dataset based on row number, to keep track of the order in which
+everything was said. The next step was to fill the name, name ID,
+electorate and party variables with the correct data for each row. To do
+so, we created a lookup table, which contained the unique incomplete
+form in which the name was transcribed, and the corresponding full name,
+name ID, electorate, and party for that individual
+Figure~\ref{fig-lookup}. We used the main dataset from the
+\texttt{AustralianPoliticians} package in the creation of this lookup
+table (Alexander and Hodgetts 2021).
 
-![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
+\begin{figure}
 
-## Stage Directions {#sec-stage}
+{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}
 
-As mentioned, one of the final components added to our script was to separate general stage directions out from statements made by members.
-Stage directions are general statements included in the transcript to document happenings in parliament.
-Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned".
-It was unclear to us from the XML and PDF who exactly these statements were attributed to.
-For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament.
-For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
-This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
-Bill read a second time".
-For this reason, we filled the name variable for these statements with "stage direction".
-Note that stage directions were not flagged as interjections.
-These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches.
-We have been building upon this list of stage directions as we work backwards in parsing Hansard.
+}
 
-# Conclusion {#sec-conclusion}
+\caption{\label{fig-lookup}First 10 rows of lookup table from 10 May
+2018 Hansard processing}
 
-Using a number of computational tools, we have created a novel database for Australian Hansard entirely based on XML data.
-Despite the public availability of Hansard, it is not functional in its current form for analysis at scale.
-Our work will enable individuals from various disciplines to perform broad spectrum research on Australian parliamentary proceedings without requiring a strong computational background.
+\end{figure}
 
-Our database provides a CSV file for each sitting day of Hansard from 10 May 2011 to 08 September 2022.
-In our work, we have embedded a number of additional variables to the resulting datasets and accounted for variation in the way that proceedings were initially transcribed.
-This ensured that users of our database can easily filter through transcripts as needed to achieve their distinct research goal.
+Next, we merged our main dataframe with the lookup table to replace any
+incomplete names with their full names, and to fill in any gaps in the
+table with available name ID, electorate and party information. Finally,
+we were able to add a flag for interjections. Grouping our data by the
+speech number, we defined an interjection as a statement made by anyone
+who is not The Speaker, The Deputy Speaker, or the Member whose turn it
+was to speak. Figure~\ref{fig-interject} provides an example of a
+Federation Chamber proceeding with interjections. Evidently, statements
+made by the original speaker Stuart Robert or by The Deputy Speaker
+Maria Vamvakinou are not flagged as interjections.
 
-The vastness of our database and the significance of the content within it enables the exploration of an endless variety of research questions.
-For example, one might be interested in investigating the frequency of certain words or phrases, such as those relating to Covid-19.
-Another area of interest would be frequency of interjections, and the gender of individuals both being interrupted and doing the interrupting.
-This database would also act as a valuable resource for research using Natural Language Processing tools.
+\begin{figure}
 
-# References
+{\centering \includegraphics{interject_ex.png}
+
+}
+
+\caption{\label{fig-interject}Example of speech with interjections from
+21 November 2016 Hansard}
+
+\end{figure}
+
+\hypertarget{sec-stage}{%
+\subsection{Stage Directions}\label{sec-stage}}
+
+As mentioned, one of the final components added to our script was to
+separate general stage directions out from statements made by members.
+Stage directions are general statements included in the transcript to
+document happenings in parliament. Examples of stage directions are
+``Bill read a second time'', ``Question agreed to'' or ``Debate
+adjourned''. It was unclear to us from the XML and PDF who exactly these
+statements were attributed to. For further clarification, we watched
+portions of the video recording for some sitting days, and noticed that
+where these statements are documented in Hansard, they are not
+explicitly stated in parliament. For example, when The Deputy Speaker
+says ``The question is that the bill be now read a second time'',
+members of the House take a vote, and if the majority is in favour, they
+proceed reading the bill the second time. This vote and second reading
+is not explicitly transcribed, rather what is written is: ``Question
+agreed to. Bill read a second time''. For this reason, we filled the
+name variable for these statements with ``stage direction''. Note that
+stage directions were not flagged as interjections. These stage
+directions are not defined differently from the regular debate speech in
+the XML, meaning we had to manually create a list of stage directions to
+separate out of the speeches. We have been building upon this list of
+stage directions as we work backwards in parsing Hansard.
+
+\hypertarget{sec-conclusion}{%
+\section{Conclusion}\label{sec-conclusion}}
+
+Using a number of computational tools, we have created a novel database
+for Australian Hansard entirely based on XML data. Despite the public
+availability of Hansard, it is not functional in its current form for
+analysis at scale. Our work will enable individuals from various
+disciplines to perform broad spectrum research on Australian
+parliamentary proceedings without requiring a strong computational
+background.
+
+Our database provides a CSV file for each sitting day of Hansard from 10
+May 2011 to 08 September 2022. In our work, we have embedded a number of
+additional variables to the resulting datasets and accounted for
+variation in the way that proceedings were initially transcribed. This
+ensured that users of our database can easily filter through transcripts
+as needed to achieve their distinct research goal.
+
+The vastness of our database and the significance of the content within
+it enables the exploration of an endless variety of research questions.
+For example, one might be interested in investigating the frequency of
+certain words or phrases, such as those relating to Covid-19. Another
+area of interest would be frequency of interjections, and the gender of
+individuals both being interrupted and doing the interrupting. This
+database would also act as a valuable resource for research using
+Natural Language Processing tools.
+
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
+Alexander, Rohan, and Monica Alexander. 2021. {``The Increased Effect of
+Elections and Changing Prime Ministers on Topics Discussed in the
+Australian Federal Parliament Between 1901 and 2018.''} \emph{arXiv
+Preprint arXiv:2111.09299}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
+Alexander, Rohan, and Paul A. Hodgetts. 2021.
+\emph{AustralianPoliticians: Provides Datasets about Australian
+Politicians}.
+\url{https://CRAN.R-project.org/package=AustralianPoliticians}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
+Beelen, Kaspar, Timothy Alberdingk Thijm, Christopher Cochrane, Kees
+Halvemaan, Graeme Hirst, Michael Kimmins, Sander Lijbrink, et al. 2017.
+{``Digitization of the Canadian Parliamentary Debates.''} \emph{Canadian
+Journal of Political Science/Revue Canadienne de Science Politique} 50
+(3): 849--64.
+
+\leavevmode\vadjust pre{\hypertarget{ref-standingorders}{}}%
+Department of the House of Representatives. 2019. \emph{Standing Orders
+as at 19 Septmeber 2019}. Commonwealth of Australia.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
+Fraussen, Bert, Timothy Graham, and Darren R Halpin. 2018. {``Assessing
+the Prominence of Interest Groups in Parliament: A Supervised Machine
+Learning Approach.''} \emph{The Journal of Legislative Studies} 24 (4):
+450--74.
+
+\leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
+House of Representatives. 2018. Edited by D. R. Elder and P. E. Fowler.
+\emph{{House of Representatives Practice}}. 7th ed. {Australian
+Government - Department of the House of Representatives}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
+---------. 2021. \emph{{A window on the house: Practices and procedures
+relating to question time}}. {Parliament of Australia}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
+Leslie, Patrick. 2021. \emph{Members of the Australian House of
+Representatives (1945-2019)}.
+\url{https://github.com/palesl/AustralianHouseOfRepresentatives}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
+Rasiah, Parameswary. 2010. {``A Framework for the Systematic Analysis of
+Evasion in Parliamentary Discourse.''} \emph{Journal of Pragmatics} 42
+(3): 664--80.
+
+\leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
+Salisbury, Christopher. 2011. {``'Mr Speaker, i Withdraw...': Standards
+of (Mis) Behaviour in the Queensland, Western Australian and
+Commonwealth Parliaments Compared via Online Hansard.''}
+\emph{Australasian Parliamentary Review} 26 (1): 166--77.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
+Sherratt, Tim. 2016. {``Documentation: Historic Hansard.''}
+\emph{Historic Hansard}.
+\url{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
+Vice, John, and Stephen Farrell. 2017. \emph{The History of Hansard}.
+House of Lords Library; House of Lords Hansard.
+
+\end{CSLReferences}
+
+\end{document}

### 2022-11-01 scripts/99-everything.R

@@ -165,13 +165,17 @@ split_interjections <- function(main, interject, bus_start){
   interject_specific <- as_tibble(interject_names) %>% filter(!(value %in% interject_general)) %>% pull
   
   # now separate rows
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)", collapse="|"))
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_specific, ")", collapse="|"))
+  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)(?!", interject_general, "[[:space:]]standing)(?!", interject_general, "[[:space:]]will )(?!", interject_general, "[[:space:]]can )",
+                                               collapse="|"))
+  main <- separate_rows(main, body, sep=paste0("(?=", interject_specific, ")(?!", interject_specific, "[[:space:]]\\(.{1,30}\\)\\n[[:space:]]{11,22}\\()", collapse="|"))
   
   # separate rows using full names, make sure they aren't preceded by "SPEAKER (" to avoid splitting deputy speaker/speaker titles from name
   # case where there is punctuation right before name (often case with interjections)
   if(length(names_use)>0){
     main <- separate_rows(main, body, sep=paste0("(?<=[[:punct:]])(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
+    main <- separate_rows(main, body, sep=paste0("(?<=\\d\\d\\:\\d\\d)(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
+    main <- separate_rows(main, body, sep=paste0("(?<=[[:punct:]][[:space:]])(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
+    main <- separate_rows(main, body, sep=paste0("(?<=\\d\\d\\:\\d\\d[[:space:]])(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
     
[…]

### 2022-11-01 scripts/99-everything2.R

@@ -166,13 +166,17 @@ split_interjections_maincomm <- function(main, interject, bus_start){
   interject_specific <- as_tibble(interject_names) %>% filter(!(value %in% interject_general)) %>% pull
   
   # now separate rows
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)", collapse="|"))
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_specific, ")", collapse="|"))
-
+  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)(?!", interject_general, "[[:space:]]standing)(?!", interject_general, "[[:space:]]will )",
+                                               collapse="|"))
+  main <- separate_rows(main, body, sep=paste0("(?=", interject_specific, ")(?!", interject_specific, "[[:space:]]\\(.{1,30}\\)\\n[[:space:]]{11,22}\\()", collapse="|"))
+  
   # separate rows using full names, make sure they aren't preceded by "SPEAKER (" to avoid splitting deputy speaker/speaker titles from name
   # case where there is punctuation right before name (often case with interjections)
   if(length(names_use)>0){
     main <- separate_rows(main, body, sep=paste0("(?<=[[:punct:]])(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
+    main <- separate_rows(main, body, sep=paste0("(?<=\\d\\d\\:\\d\\d)(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
+    main <- separate_rows(main, body, sep=paste0("(?<=[[:punct:]][[:space:]])(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
+    main <- separate_rows(main, body, sep=paste0("(?<=\\d\\d\\:\\d\\d[[:space:]])(?<!SPEAKER[[:space:]]\\()(?=", names_use, "\\:)", collapse = "|"))
     
[…]

### 2022-11-28 paper/paper.qmd
new url doc and updated script

@@
 Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
-@alexander2021 created this database with the static PDF versions Hansard, using OCR to digitize these files into text which is suitable for analysis.
+@alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis.
 This means there are considerable digitization errors especially in the first half of the dataset.
@@
 #   theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
+
+#plot1 + ggtitle("Total number of sitting days per year (2000-2021)")
 ```
@@
   theme_bw() +
-  labs(x = "Year", y = "Average number of rows", fill = "") +
-  theme(axis.text.x = element_text(angle=90, vjust=0.5, hjust=0.5))
+  labs(x = "Year", y = "Average number of rows", fill = "")
 

### 2022-11-28 scripts/00-scrape_files.R

@@ -5,7 +5,7 @@ library(here)
 
 # 2010-2022
 # read in excel sheet with URLs
-urls_df <- read.csv(here("hansard-urls-2010-2022.csv"))
+urls_df <- read.csv(here("urls/hansard-urls-1998-1999.csv"))
 
 # define tibble with URLs and file names
 urls <- tibble(locations_are = urls_df$URL, 

### 2022-11-28 scripts/99-everything.R

@@ -1847,8 +1847,8 @@ files_all <- list.files("/Volumes/Verbatim/input/")
 # grab a couple years
 files_get <- files_all %>%
   as_tibble() %>%
-  filter(str_detect(value, "^2022-")) %>%
-  filter(value > "2020-03-05.xml") %>%
+  filter(str_detect(value, "^2013|^2014-|^2015-|^2016-|^2017-|^2018-|^2019-|^2020-|^2021-|^2022-")) %>%
+  #filter(value > "2020-03-05.xml") %>%
   pull(value)
 
 #"^2014-|^2015-|^2016-|^2017-|^2018-|^2019-|^2020-|^2021-|^2022-"

### 2022-11-28 scripts/99-everything-2000_to_2011.R
rename scripts and add new one

@@ -1,0 +1,1791 @@
+# works from 15 February 2000 10 May 2011
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+library(hms)
+
+# code in function below from https://stackoverflow.com/questions/58492429/xml-in-r-multiple-children-with-same-name-without-loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", "1999-02-08.xml"))
+xml_df <- read_xml(here("/Volumes/Verbatim/input/", "1999-02-08.xml"))
+
+filename<-"1999-02-08.xml"
+
+parse_hansard <- function(filename){ 
+ 
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
+  
+  ######### BUSINESS START #########
+  # chamber
+  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F))>0) {
+    bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F), 
[…]

### 2023-02-03 paper/paper-nature_format.qmd
lots of updates

---
title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
number-sections: true
format: 
  pdf:
    keep-tex: true
bibliography: references.bib
editor: visual
date: "now"
date-format: long
author:
  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and a critical resource for political science research. In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard. While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality. Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard. The database is publicly available and can be readily linked to other datasets such as election results. The creation and accessibility of this database will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers."
---

```{r, echo=F, message=F}
library(here)
library(tidyverse)
library(XML)
```

# Background & Summary {#sec-intro}

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavour called the Linked Parliamentary Data (LiPaD) project [@lipad]. Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling. Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form which can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.

The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch. 1]. The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber. Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch. 8]. A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch. 8]. The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber. This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch. 21]. Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion. Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch. 21]. It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.

A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form. The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt]. This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt]. The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility. The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files. In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases in an attempt to produce usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. In an effort to make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

A number of papers exist which utilize components of Australian Hansard to explore various research topics. For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

While there is evidently a growing body of literature on this topic, there is still no comprehensive database for Australian Hansard based on XML that spans from 1901 to the present day. Our work serves to bridge this gap.

# Methods

Our database contains one comma-separated value (CSV) file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022. We developed four scripts to produce all of these files, where each script is designed to parse Hansard documents from a specific portion of the 1998 to 2022 time frame.

This section will be structured as follows. First, we will provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed all four scripts used to create our database. This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure. Next we will explain the specific differences between the four scripts, and outline what structural changes necessitated their separate development. We will then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.

## Overview {#sec-overview}

The approach to parsing contents of an XML document is heavily dependent on its tree structure. As such, to create this database, we started by looking at a single Hansard XML transcript from 2019. Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form. Parsing was performed in `R` using the `XML` and `xml2` packages [@XML_pkg; @xml2_pkg]. Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible. The typical form of a Hansard XML transcript is summarized in the nested list below. Note that this provides a broad overview of the structure, and does not contain every possible nested element that may be found in a Hansard XML.

>          <hansard>
>            1. <session.header>
>            2. <chamber.xscript>
>               a)  <business.start>
>               b)  <debate>
>                   i.  <debateinfo>
>                   ii. <debate.text>
>                   iii. <speech>
>                   iv. <subdebate.1>
>                       (1) <subdebateinfo>
>                       (2) <subdebate.text>
>                       (3) <speech>
>                       (4) <subdebate.2>
>                           (a) <subdebateinfo>
>                           (b) <subdebate.text>
>                           (c) <speech>
>           3. <fedchamb.xscript>
>           4. <answers.to.questions>
>               a)  <question>
>               b)  <answer>

The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document. This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day. Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings. Note that the Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file. The use of separate child nodes allows for the distinction of proceedings of the Chamber and Federation Chamber. The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates. Debate nodes can contain a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it. That said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of these three elements (i.e. `<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said. The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate. A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement. Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations. These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`. The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements. More detail on the purpose and processing of Question Time will follow in @sec-qa.

@fig-xml1 provides an example of the beginning of an XML file for Hansard, which illustrates the structure outlined in the nested list above. As stated, the XML structure begins with a parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements such as the date and parliament number, which are all highlighted in pink. Next there is the child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1. As previously mentioned, the first sub-node of `"chamber.xscript"` is the business start. The structure of the business start can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start are highlighted in orange.

**does this feel a bit repetitive? do you think it's worth keeping?**

![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}

Evidently, the nature of XML formatting means that different pieces of information are categorized under a series of uniquely named and nested nodes. As a result, to parse each piece of information, one must specify the unique hierarchy of nodes in which it is structured. This is known as an XPath expression, and tells the parser how to navigate the XML document to obtain the desired information. For example, the session header date in @fig-xml1 can be accessed using the XPath expression "`hansard/session.header/date`". We began our first script by parsing every piece of information contained in the XML document, using these unique XPath expressions to do so.

The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order. This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2. The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed. In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string. As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak. Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort. @sec-interject will provide further details on the intricacies of this task.

Since we are looking at a wide time span of documents, there are expectedly a number of changes in the way they are formatted over time. These became apparent as we ran our script on XML files from earlier sitting days. Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure. Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting. However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards in time. Further, while working backward in time, it became clear that not every sitting day contains every possible XML element. For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding. To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element. For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.

Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files. The earliest sitting day our first script can successfully parse is 14 August 2012. Before developing new scripts to parse earlier Hansard documents, we decided to prioritize cleaning and finalizing what we have been able to parse. As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary. Specifically, we added a section of our script to separate out general stage directions. More information on this separation will be provided in @sec-stage. After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.

## Script Differences {#sec-diff}

As previously mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents. Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts. While all four scripts use the same general approach to parsing described in @sec-overview and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.

The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee. The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch. 21]. As a result, the child-node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012. Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification. To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`. After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).

While the modifications needed to develop the second script were quite straightforward, this was not the case for our next script. The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology. In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`. The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments and continuations. After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order. For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node. These would contain details on the person who made each statement such as their party and electorate.

In contrast, the speech contents in XMLs from 1998 up to and including 24 March 2011 are nested differently --- there is no `<talk.text>` node. Rather than this single child-node that contains all speech content, statements are categorized in individual child-nodes. This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`debate/speech/talk.text`" or "`debate/subdebate.1/speech/talk.text`" to extract all speeches, in their entirety, at once. This difference in nesting structure made our second script unusable for parsing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.

Since there are numerous speeches in a typical Hansard, each having multiple child-nodes with the same names (i.e. `<continuation>`, `<interjection>`), it is difficult to parse everything while maintaining the correct ordering of statements. We found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly. The reason we did not use its `<speech>` child-node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days.

The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data. For example, the data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:

> `09:31:0010261Costello, Peter, MPMr COSTELLOCT4HigginsLPTreasurer10`

![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}

This was not isolated to just the beginning of speeches --- details on individuals interjecting or commenting during speeches were also captured this way. To separate statements out correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found. After separating statements, we were later able remove these patterns from the body of text. We also used this method of extracting and later removing unwanted patterns for other pieces of data which did not belong to the debate proceedings, such as sub-debate titles.

Once we finalized this new method of processing the data, we proceeded with data cleaning using the same general approach as in the first two scripts to produce the same structure of CSV output. We then worked backwards in time and modified the code as needed for generalizability. Throughout this process we found a number of transcription errors present in the XMLs from earlier years. We fixed these manually, deferring to the official release to ensure the correct information was filled in. Since there were a number of transcription errors specific to the 2000s, we chose to create a fourth script for parsing 1998 and 1999. This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency. As such, our fourth script is essentially the same as the third, the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.

## Question Time {#sec-qa}

A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions. One core mechanism by which this is achieved is called Question Time. This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021]. Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document. Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two. Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.

To parse questions without notice and questions in writing in the first two scripts, we extracted all question and answer elements from the `"chamber.xscript"` and `"answers.to.questions"` child nodes. For the third and fourth scripts, our method of parsing the `"chamber.xscript"` speeches meant that all questions without notice content was already parsed in order. Similar to the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers. Finally, since questions in writing exist in their own child node we were able to use the same parsing method for the third and fourth scripts as we did for the first and second scripts.

We then added binary flags to differentiate between questions and answers, determined by which sub-child node the statement was extracted from, that is, whether it came from a `<question>` node, or an `<answer>` node. Sometimes, questions were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags using the `str_detect` function from the `stringr` package. For instance, our code for parsing questions searches for any statements which include "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer. Once all questions and answers were correctly classified as such, we could then merge all the content back together such that each question was followed by its associated answer. This was straightforward due to the fact that by nature of XML parsing, all questions and answers were parsed in the order in which they appeared in the transcript.

The next step was to merge Question Time contents with all the debate speech. Doing so with the questions without notice content was straightforward. For the first and second scripts, we used the time stamp and page number associated with each question to maintain the correct order of statements. For the third and fourth scripts, our method of parsing meant that everything was already parsed together in order, so we did not have to perform any additional merging. While questions in writing do not contain time stamps, merging this content was also straightforward due to the fact that it is always at the very end of Hansard. This means that we could simply bind question in writing rows to the bottom of the main dataframe. This approach was used for all four scripts.

## Interjections {#sec-interject}

As mentioned, the text was structured and parsed in such a way that various interjections and comments which happened during a speech were not separated onto individual rows. This was the case across the entire time frame of documents. We will first discuss the methodology employed to split interjections in the first and second scripts, as it informed our approach for the third and fourth scripts.

Below is an example of part of a speech we would need to split, extracted from Hansard on 30 November 2021, where Mr. van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.

> ```{r}
> #| warning: false
> #| echo: false
> #| message: false
> #| results: asis
> >
> # read in XML file
> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
> >
> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
>                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
>   as_tibble() %>% 
>   slice(25) %>% 
>   pull(body)
> >
> # print example of text in quotations
> cat(paste0('"', interject_text_ex, '"'))
> ```

We want each statement on its own row with the correct name, name ID, electorate and party information on the individual speaking. We approached this task in a number of steps.

Once all parsed text from the XML was merged into one dataframe called `main`, our first step was to add a `"speech_no"` variable. This was done to keep track of which speech each interjection, comment, or continuation belonged to as we separated these components onto their own rows.

The next step was to extract all the names and titles preceding these interjections, comments and continuations. This would enable us to then separate the speeches in the correct places using these names and titles in combination with regular expressions, which are patterns of characters that can be used to search bodies of text. We completed this extraction process with a few intermediate steps, due to the large number of name styles and interjection types that had to be accounted for, each requiring their own unique regular expression format.

As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech. @fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech. Looking at the element names highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it. However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on. Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections. We stored this as a dataframe called `"interject"`.[^1]

[^1]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.

![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}

We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day. We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard. When a Member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name. There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written. Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case. This variation demands careful consideration when writing regular expression patterns to search for in the text. In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".

[^2]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.

Having these lists enabled us to extract the names of Members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns. We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds. A lookaround can be added to a regular expression pattern to enhance the specificity of matches. These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.

Once all interjections, comments and continuations were successfully split onto their own rows using the lists we created, we did one final check for any additional names that were not captured in these lists. To do so, we searched for any remaining name matches in speech bodies with general regular expressions and lookarounds, and separated text using those matches when found.

We then added an order variable to the dataset based on row number, to keep track of the order in which everything was said. The next step was to fill the name, name ID, electorate and party variables with the correct data for each row. We also wanted to add the gender and unique identifier for each individual as found in the `AustralianPoliticians` package. To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, party, gender and unique ID for that individual. @fig-lookup provides an example of this. We used the main dataset from the `AustralianPoliticians` package in the creation of each lookup table [@auspol].

![First 10 rows of lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}

Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender and unique ID information. Finally, we were able to add a flag for interjections. Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak. @fig-interject provides an example of a Federation Chamber proceeding with interjections. Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.

![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}

Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts. However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology. As discussed in @sec-diff, we used string patterns extracted from `<talk.start>` nodes to separate speeches. As evident in @fig-xml3, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process. In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process. This meant that we did not need to create lists of names and titles to search for in the text as we did before. However, we used the same list of general interjection statements to separate on that was used in the first two scripts. We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^3]

[^3]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.

We then proceeded to clean up speeches and fill in correct speaker details. While we used the same lookup table approach as before, we did so in combination with another means of filling in speaker details. The patterns parsed from `<talk.start>` nodes contain important data on the speaker of each statement. As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `<talk.start/talker>`. We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement. @fig-patterns provides an example of that lookup table. This approach enabled us to fill in missing data on each speaker using data extracted directly from the XML. Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.

![10 rows of pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}

## Stage Directions {#sec-stage}

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by members. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Note that stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We have built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.

# Data Records

Our database contains 1517 CSV files, covering all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022. All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336076 [@katz_2022]. For each CSV file, each row contains an individual statement, with details on the individual speaking. Of course, for general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the database.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-vars
#| tbl-cap: "Summary and description of variables in our database"

# read in packages
library(readr)
library(tidyverse)
library(here)
library(XML)
library(lubridate)
library(kableExtra)

# read in example csv
main_ex <- read_csv("/Volumes/Verbatim/output/main-2000-2011/2003-08-14-main.csv", show_col_types = F)

# create tibble with var names and descriptions
main_ex_vars <- tibble("Variable" = names(main_ex),
       "Description" = c("Name of speaker",
                         "Row number",
                         "Speech number",
                         "Page number statement can be found on in official Hansard",
                         "Time of statement",
                         "Unique member identification code, based on the Parliamentary Handbook",
                         "Speaking member's electorate",
                         "Speaking member's party",
                         "Flag for in government (1 if in government, 0 otherwise)",
                         "Flag for first speech (1 if first speech, 0 otherwise)",
                         "Statement text",
                         "Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)",
                         "Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)",
                         "Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)",
                         "Flag for question (1 if question, 0 otherwise)",
                         "Flag for answer (1 if answer, 0 otherwise)",
                         "Flag for question in writing (1 if question in writing, 0 otherwise)",
                         "Flag for division (1 if division, 0 otherwise)",
                         "Gender of speaker",
                         "Unique identifier of speaker",
                         "Flag for interjection (1 if statement is an interjection, 0 otherwise)"))

# print tibble using kable
knitr::kable(main_ex_vars, booktabs=T) %>% 
  kable_styling(full_width = F, latex_options = "HOLD_position")
```

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first,speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package. Details on the usage of `uniqueID` will be provided in @sec-usage. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. Finally, the `order` variable was added to maintain the order of proceedings.

**this paragraph is a bit repetitive and states everything found in the table, but i also feel like it's valuable to specify which ones we added and elaborate on their meaning. thoughts?**

## Descriptive Statistics {#sec-stats}

# Technical Validation

We developed a script to perform seven automated tests on each file in our database, in an effort to enhance its quality and consistency. Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date. We validated that our file name and date was correct by checking the official PDF release from that sitting day.

[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.

The second test checks that in each file, there is an equal number of flagged questions and answers. This test was motivated by the discrepancies in correct categorization of questions and answers we found when parsing Question Time, and allows us to check for the presence of any of these discrepancies which we have missed.

When a member runs out of allotted time for their speech, Hansard editors transcribe "(Time expired)" after their final word. As a means of checking that we have separated speeches out correctly, our third test checks that when the phrase "(Time expired)" exists in a body of text, it exists at the very end. When this is not the case, we know that we have missed the separation of the next statement onto its own row, and could fix this accordingly.

The remaining tests focus on the members present on each sitting day. Our fourth test checks that there is one unique party and electorate attributed to each individual on each sitting day. As we parsed Hansard further back in time, we found a number of cases where an individual was associated with the wrong electorate or party due to transcription errors. When we found these data errors we corrected them based on the official release. This test provides us with an automated way to catch these errors and correct them at scale.

Next, we test that the unique name identification code attributed to each individual is found in the Australian Parliamentary Handbook. We do so using the `ausPH` package. This test serves as another means to correct for transcription errors, this time in the case of name IDs. We found and corrected for a number of common name ID transcription errors detected by this test, such as a capital letter "O" in place of a zero.

Our sixth test checks that on any given sitting day, the individuals identified are alive. To do so, we utilized the main dataset from the `AustralianPoliticians` package which contains the birth and where applicable death dates for every politician. This test confirmed that all members who are detected to speak on each sitting day are not deceased.

Finally, our seventh test validates that all individuals speaking are active members of parliament on that particular day. We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament. Using these dates, we check that each person speaking on each sitting day is in fact a Member of Parliament on that day.

# Usage Notes {#sec-usage}

To enhance the usability of our database, we added a `uniqueID` variable to each CSV file. This serves as a unique identifier for each speaking Member, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect]. By including this variable, one can readily integrate our data records with those available in these two packages.

Further, the `name.id` variable found in each CSV is another unique identifier for each Member of Parliament. This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook. As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus]. This will allow for convenient extraction of further details on each Member of Parliament in a tidy, ready to analyze format.

# Code Availability

The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj. All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in member details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.

# Acknowledgements

# Author Contributions

# Competing Interests

The authors declare no competing interests.

# References

### 2023-02-03 paper/paper-nature_format.tex
lots of updates

--- 2023-02-03 paper/paper-nature_format.qmd
@@
----
-title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
-number-sections: true
-format: 
-  pdf:
-    keep-tex: true
-bibliography: references.bib
-editor: visual
-date: "now"
-date-format: long
-author:
-  - Lindsay Katz^[University of Toronto, lindsay.katz@mail.utoronto.ca]
-  - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
-abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and a critical resource for political science research.
-In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard.
-While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality.
-Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard.
-The database is publicly available and can be readily linked to other datasets such as election results.
-The creation and accessibility of this database will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers."
----
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
+%
+\documentclass[
+  letterpaper,
+  DIV=11,
+  numbers=noendperiod]{scrartcl}
 
-```{r, echo=F, message=F}
-library(here)
-library(tidyverse)
-library(XML)
-```
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\makeatletter
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
+\makeatother
+\usepackage{xcolor}
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\setcounter{secnumdepth}{5}
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
-# Background & Summary {#sec-intro}
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
-Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
-Given the content and magnitude of these records, they have significance, particularly in the context of political science research.
-In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavour called the Linked Parliamentary Data (LiPaD) project [@lipad].
-Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling.
-Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard.
-This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form which can be readily used by researchers.
-With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
+\KOMAoption{captions}{tableheading}
+\makeatletter
+\makeatother
+\makeatletter
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\AtBeginDocument{%
+\ifdefined\contentsname
+  \renewcommand*\contentsname{Table of contents}
+\else
+  \newcommand\contentsname{Table of contents}
+\fi
+\ifdefined\listfigurename
+  \renewcommand*\listfigurename{List of Figures}
+\else
+  \newcommand\listfigurename{List of Figures}
+\fi
+\ifdefined\listtablename
+  \renewcommand*\listtablename{List of Tables}
+\else
+  \newcommand\listtablename{List of Tables}
+\fi
+\ifdefined\figurename
+  \renewcommand*\figurename{Figure}
+\else
+  \newcommand\figurename{Figure}
+\fi
+\ifdefined\tablename
+  \renewcommand*\tablename{Table}
+\else
+  \newcommand\tablename{Table}
+\fi
+}
+\@ifpackageloaded{float}{}{\usepackage{float}}
+\floatstyle{ruled}
+\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
+\floatname{codelisting}{Listing}
+\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{caption}{}{\usepackage{caption}}
+\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
+\makeatother
+\makeatletter
+\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\makeatother
+\makeatletter
+\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
+\makeatother
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\urlstyle{same} % disable monospaced font for URLs
+\hypersetup{
+  pdftitle={Digitization of the Australian Parliamentary Debates, 1998-2022},
+  pdfauthor={Lindsay Katz; Rohan Alexander},
+  colorlinks=true,
+  linkcolor={blue},
+  filecolor={Maroon},
+  citecolor={Blue},
+  urlcolor={Blue},
+  pdfcreator={LaTeX via pandoc}}
 
-The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
-1].
-The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber.
-Sittings of the House follow a predefined order of business, regulated by procedural rules called standing orders [@australia2018house, ch.
-8].
-A typical sitting day in the Chamber has a number of scheduled proceedings including debates on government business, 90 second member statements, and Question Time [@australia2018house, ch.
-8].
-The Federation Chamber was created in 1994 as a subordinate debate venue of the Chamber.
-This allows for better time management of House business as its proceedings occur simultaneously with those of the Chamber [@australia2018house, ch.
-21].
-Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion.
-Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch.
-21].
-It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.
+\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
+\author{Lindsay Katz\footnote{University of Toronto,
+  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
+  of Toronto, rohan.alexander@utoronto.ca}}
+\date{January 20, 2023}
 
-A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form.
-The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt].
-This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt].
-The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility.
-The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files.
-In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.
+\begin{document}
+\maketitle
+\begin{abstract}
+Public knowledge of what is said in parliament is a key tenet of
+democracy, and a critical resource for political science research. In
+Australia, following the British tradition, the written record of what
+is said in parliament is known as Hansard. While the Australian Hansard
+has always been publicly available, it has been difficult to use it for
+the purpose of large-scale macro and micro-level text analysis because
+it has not been available as a dataset of sufficient quality. Following
+the lead of the Linked Parliamentary Data project which achieved this
+for Canada, we provide a new, comprehensive, high-quality database that
+captures all proceedings of the Australian parliamentary debates from
+1998 to the present using Hansard. The database is publicly available
+and can be readily linked to other datasets such as election results.
+The creation and accessibility of this database will enable the
+exploration of questions that are not currently possible to explore,
+serving as a valuable resource for both researchers and policymakers.
+\end{abstract}
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
 
-At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis.
-To this point, various researchers have had to create their own databases in an attempt to produce usable, complete data based on content from the Australian Parliament website.
-For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files.
-These data can be navigated by year, parliament, people, and bills [@sherratt].
-In an effort to make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019.
-Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
+\hypertarget{sec-intro}{%
+\section{Background \& Summary}\label{sec-intro}}
 
-A number of papers exist which utilize components of Australian Hansard to explore various research topics.
-For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark.
-@rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
-In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
-Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
-@alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis.
-This means there are considerable digitization errors especially in the first half of the dataset.
+The official written record of parliamentary debates, formally known as
+Hansard, plays a fundamental role in capturing the history of political
+proceedings and facilitating the exploration of valuable research
+questions. Originating in the British parliament, the production of
+Hansard became tradition in a number of Commonwealth countries such as
+Canada, the United Kingdom, and Australia (Vice and Farrell 2017). Given
+the content and magnitude of these records, they have significance,
+particularly in the context of political science research. In the case
+of Canada, a team of researchers at the University of Toronto have
+digitized Hansard from 1901 to 2019, an endeavour called the Linked
+Parliamentary Data (LiPaD) project (Beelen et al. 2017). Having a
+digitized version of Hansard enables researchers to perform advanced
+analyses on these records using text analysis tools and statistical
+modelling. Following the lead of the LiPaD project, in this paper we
+introduce a novel database for the Australian Hansard. This is composed
+of individual datasets for each sitting day in the House of
+Representatives from 1998 to 2022, containing details on everything said
+in parliament in a form which can be readily used by researchers. With
+the development of tools for large-scale text analysis, this database
+will serve as a valuable resource for efficiently studying and exploring
+political behaviour in Australia over time.
 
-While there is evidently a growing body of literature on this topic, there is still no comprehensive database for Australian Hansard based on XML that spans from 1901 to the present day.
-Our work serves to bridge this gap.
+The House of Representatives performs a number of crucial governmental
+functions, such as creating new laws and overseeing government
+expenditure (House of Representatives 2018, ch.~1). The House operates
+under a parallel chamber setup, meaning there are two debate venues
+where proceedings take place: the Chamber, and the Federation Chamber.
+Sittings of the House follow a predefined order of business, regulated
+by procedural rules called standing orders (House of Representatives
+2018, ch.~8). A typical sitting day in the Chamber has a number of
+scheduled proceedings including debates on government business, 90
+second member statements, and Question Time (House of Representatives
+2018, ch.~8). The Federation Chamber was created in 1994 as a
+subordinate debate venue of the Chamber. This allows for better time
+management of House business as its proceedings occur simultaneously
+with those of the Chamber (House of Representatives 2018, ch.~21).
+Sittings in the Federation Chamber are quite different to those of the
+Chamber in terms of their order of business and scope of discussion.
+Business matters discussed in the Federation Chamber are limited largely
+to intermediate stages of bill development, and the business of private
+Members (House of Representatives 2018, ch.~21). It is the recording and
+compilation of all of these proceedings on which Hansard is based, and
+it is essentially, but not entirely, verbatim.
 
-# Methods
+A week or so after each sitting day, a transcript is available for
+download from the official Parliament of Australia website in both
+static PDF and extensible markup language (XML) form. The PDF is the
+official release, which is converted to typed text using Optical
+Character Recognition (OCR) technology (Sherratt 2016). This conversion
+allows for the production of the XML formatted transcript, though these
+are not always perfect conversions and are particularly flawed in the
+early decades of Hansard (Sherratt 2016). The PDF imposes formatting
+designed for humans to read with ease, whereas XML is designed for
+consistency and machine legibility. The nature of XML enables us to more
+easily use code to manipulate these records at scale, motivating our
+choice to develop our database solely using the XML formatted files. In
+cases where we were unsure on how to proceed with processing the XML, we
+defer first to the PDF, and then to the video recording of the
+proceeding if available.
 
-Our database contains one comma-separated value (CSV) file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022.
-We developed four scripts to produce all of these files, where each script is designed to parse Hansard documents from a specific portion of the 1998 to 2022 time frame.
+At present, the Hansard format that is available on the Parliament of
+Australia website is not accessible for large scale analysis. To this
+point, various researchers have had to create their own databases in an
+attempt to produce usable, complete data based on content from the
+Australian Parliament website. For instance, Sherratt (2016) created an
+online, easy to read database of Hansard from 1901 to 1980 using the XML
+files. These data can be navigated by year, parliament, people, and
+bills (Sherratt 2016). In an effort to make the Australian Parliamentary
+Handbook more accessible, Leslie (2021) has released an \texttt{R}
+package which includes data on all Members of the Australian House of
+Representatives from 1945 to 2019. Further, Alexander and Hodgetts
+(2021) created the \texttt{AustralianPoliticians} \texttt{R} package,
+which contains a number of datasets related to the political and
+biographical information of Australian federal politicians who were
+active between 1901 and 2021.
 
-This section will be structured as follows.
-First, we will provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed all four scripts used to create our database.
-This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure.
-Next we will explain the specific differences between the four scripts, and outline what structural changes necessitated their separate development.
-We will then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
+A number of papers exist which utilize components of Australian Hansard
+to explore various research topics. For example, Salisbury (2011) used
+online Hansard records to investigate the occurrences of unparliamentary
+comments by members of the House, where The Speaker tells that member to
+withdraw their remark. Rasiah (2010) worked with Question Time data from
+Hansard transcripts during February and March of 2003, to investigate
+resistance of politicians in answering questions about Iraq. In their
+work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
+political prominence by investigating strategic mentions of interest
+groups by elected officials. Finally, the work of Alexander and
+Alexander (2021) offers a dataset of the Australian Hansard, along with
+an analysis of the effect of elections and changes in Prime Ministers
+upon topics mentioned in parliament. Alexander and Alexander (2021)
+created this database with the static PDF versions of Hansard, using OCR
+to digitize these files into text which is suitable for analysis. This
+means there are considerable digitization errors especially in the first
+half of the dataset.
 
-## Overview {#sec-overview}
+While there is evidently a growing body of literature on this topic,
+there is still no comprehensive database for Australian Hansard based on
+XML that spans from 1901 to the present day. Our work serves to bridge
+this gap.
 
-The approach to parsing contents of an XML document is heavily dependent on its tree structure.
-As such, to create this database, we started by looking at a single Hansard XML transcript from 2019.
-Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form.
-Parsing was performed in `R` using the `XML` and `xml2` packages [@XML_pkg; @xml2_pkg].
-Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible.
-The typical form of a Hansard XML transcript is summarized in the nested list below.
-Note that this provides a broad overview of the structure, and does not contain every possible nested element that may be found in a Hansard XML.
+\hypertarget{methods}{%
+\section{Methods}\label{methods}}
 
->          <hansard>
->            1. <session.header>
->            2. <chamber.xscript>
->               a)  <business.start>
->               b)  <debate>
->                   i.  <debateinfo>
->                   ii. <debate.text>
->                   iii. <speech>
->                   iv. <subdebate.1>
->                       (1) <subdebateinfo>
->                       (2) <subdebate.text>
->                       (3) <speech>
->                       (4) <subdebate.2>
->                           (a) <subdebateinfo>
->                           (b) <subdebate.text>
->                           (c) <speech>
->           3. <fedchamb.xscript>
->           4. <answers.to.questions>
->               a)  <question>
->               b)  <answer>
+Our database contains one comma-separated value (CSV) file for each
+sitting day of the House of Representatives from 02 March 1998 to 08
+September 2022. We developed four scripts to produce all of these files,
+where each script is designed to parse Hansard documents from a specific
+portion of the 1998 to 2022 time frame.
 
-The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document.
-This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day.
-Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings.
-Note that the Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file.
-The use of separate child nodes allows for the distinction of proceedings of the Chamber and Federation Chamber.
-The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates.
-Debate nodes can contain a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it.
-That said, sometimes sub-debate 2 is not nested within sub-debate 1.
-Each of these three elements (i.e.
-`<debate>`, `<subdebate.1>`, and `<subdebate.2>`) as well as their respective sub-elements contain important information on the topic of discussion, who is speaking, and what is being said.
-The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate.
-A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement.
-Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations.
-These statements are categorized under different sub-nodes depending on their nature, such as `<interjection>` or `<continuation>`.
-The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements.
-More detail on the purpose and processing of Question Time will follow in @sec-qa.
+This section will be structured as follows. First, we will provide an
+overview of our approach to understanding and parsing an individual
+Hansard XML document, which informed all four scripts used to create our
+database. This will be supplemented with an excerpt from a Hansard XML
+to provide a visual example of its structure. Next we will explain the
+specific differences between the four scripts, and outline what
+structural changes necessitated their separate development. We will then
+provide details on the methodological intricacies of three core
+components of Hansard proceedings: Question Time, interjections, and
+stage directions.
 
-@fig-xml1 provides an example of the beginning of an XML file for Hansard, which illustrates the structure outlined in the nested list above.
-As stated, the XML structure begins with a parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements such as the date and parliament number, which are all highlighted in pink.
-Next there is the child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1.
-As previously mentioned, the first sub-node of `"chamber.xscript"` is the business start.
-The structure of the business start can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start are highlighted in orange.
+\hypertarget{sec-overview}{%
+\subsection{Overview}\label{sec-overview}}
 
-**does this feel a bit repetitive? do you think it's worth keeping?**
+The approach to parsing contents of an XML document is heavily dependent
+on its tree structure. As such, to create this database, we started by
+looking at a single Hansard XML transcript from 2019. Doing so enabled
+us to identify the various components of interest in the document, and
+how each one can be parsed according to its corresponding structural
+form. Parsing was performed in \texttt{R} using the \texttt{XML} and
+\texttt{xml2} packages (Temple Lang 2022; Wickham, Hester, and Ooms
+2021). Focusing on one transcript also allowed us to ensure that all key
+components of the transcript were being parsed and captured with as much
+detail as possible. The typical form of a Hansard XML transcript is
+summarized in the nested list below. Note that this provides a broad
+overview of the structure, and does not contain every possible nested
+element that may be found in a Hansard XML.
 
-![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
+\begin{quote}
+\begin{verbatim}
+     <hansard>
+       1. <session.header>
+       2. <chamber.xscript>
+          a)  <business.start>
+          b)  <debate>
+              i.  <debateinfo>
+              ii. <debate.text>
+              iii. <speech>
+              iv. <subdebate.1>
+                  (1) <subdebateinfo>
+                  (2) <subdebate.text>
+                  (3) <speech>
+                  (4) <subdebate.2>
+                      (a) <subdebateinfo>
+                      (b) <subdebate.text>
+                      (c) <speech>
+      3. <fedchamb.xscript>
+      4. <answers.to.questions>
+          a)  <question>
+          b)  <answer>
+\end{verbatim}
+\end{quote}
 
-Evidently, the nature of XML formatting means that different pieces of information are categorized under a series of uniquely named and nested nodes.
-As a result, to parse each piece of information, one must specify the unique hierarchy of nodes in which it is structured.
-This is known as an XPath expression, and tells the parser how to navigate the XML document to obtain the desired information.
-For example, the session header date in @fig-xml1 can be accessed using the XPath expression "`hansard/session.header/date`".
-We began our first script by parsing every piece of information contained in the XML document, using these unique XPath expressions to do so.
+The outer-most node, also known as the parent node, is denoted
+\texttt{\textless{}hansard\textgreater{}} and serves as a container for
+the entire document. This parent node may have up to four child-nodes,
+where the first child-node contains details on the specific sitting day.
+Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
+proceedings of the Chamber,
+\texttt{\textless{}fedchamb.xscript\textgreater{}} contains all
+proceedings of the Federation Chamber, and
+\texttt{\textless{}answers.to.questions\textgreater{}} contains Question
+Time proceedings. Note that the Federation Chamber does not meet on
+every sitting day, so this child element is not present in every XML
+file. The use of separate child nodes allows for the distinction of
+proceedings of the Chamber and Federation Chamber. The structure of the
+\texttt{\textless{}chamber.xscript\textgreater{}} and
+\texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
+the same, where the proceeding begins with a business start which is
+followed by a series of debates. Debate nodes can contain a sub-debate 1
+child-node which has a sub-debate 2 child-node nested within it. That
+said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of
+these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
+\texttt{\textless{}subdebate.1\textgreater{}}, and
+\texttt{\textless{}subdebate.2\textgreater{}}) as well as their
+respective sub-elements contain important information on the topic of
+discussion, who is speaking, and what is being said. The
+\texttt{\textless{}speech\textgreater{}} node within each one contains
+the bulk of the text associated with that debate or sub-debate. A
+typical \texttt{\textless{}speech\textgreater{}} node begins with a
+\texttt{\textless{}talk.start\textgreater{}} sub-node, providing
+information on the speaker and the time of their first statement.
+Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate
+settings --- they are often composed of a series of interjections and
+continuations. These statements are categorized under different
+sub-nodes depending on their nature, such as
+\texttt{\textless{}interjection\textgreater{}} or
+\texttt{\textless{}continuation\textgreater{}}. The final key component
+of Hansard is Question Time, in which questions and answers are
+classified as unique elements. More detail on the purpose and processing
+of Question Time will follow in Section~\ref{sec-qa}.
 
-The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order.
-This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
-The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
-In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
-As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak.
-Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort.
-@sec-interject will provide further details on the intricacies of this task.
+Figure~\ref{fig-xml1} provides an example of the beginning of an XML
+file for Hansard, which illustrates the structure outlined in the nested
+list above. As stated, the XML structure begins with a parent element
+\texttt{"hansard"} (highlighted in blue), followed by a child element
+\texttt{"session.header"} (highlighted in yellow) with sub-child
+elements such as the date and parliament number, which are all
+highlighted in pink. Next there is the child element containing
+everything that takes place in the Chamber, \texttt{"chamber.xscript"},
+which is also highlighted in yellow in Figure~\ref{fig-xml1}. As
+previously mentioned, the first sub-node of \texttt{"chamber.xscript"}
+is the business start. The structure of the business start can be seen
+between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
+the content we parse from the business start are highlighted in orange.
 
-Since we are looking at a wide time span of documents, there are expectedly a number of changes in the way they are formatted over time.
-These became apparent as we ran our script on XML files from earlier sitting days.
-Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure.
-Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting.
-However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards in time.
-Further, while working backward in time, it became clear that not every sitting day contains every possible XML element.
-For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding.
-To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
-For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.
+\textbf{does this feel a bit repetitive? do you think it's worth
+keeping?}
 
-Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files.
-The earliest sitting day our first script can successfully parse is 14 August 2012.
-Before developing new scripts to parse earlier Hansard documents, we decided to prioritize cleaning and finalizing what we have been able to parse.
-As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary.
-Specifically, we added a section of our script to separate out general stage directions.
-More information on this separation will be provided in @sec-stage.
-After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.
+\begin{figure}
 
-## Script Differences {#sec-diff}
+{\centering \includegraphics{xml1.png}
 
-As previously mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents.
-Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts.
-While all four scripts use the same general approach to parsing described in @sec-overview and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.
+}
 
-The need for a second script stems from the fact that when established in 1994, the Federation Chamber was originally named the Main Committee.
-The Main Committee was renamed to the Federation Chamber in mid-2012 [@australia2018house, ch.
-21].
-As a result, the child-node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012.
-Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification.
-To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`.
-After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).
+\caption{\label{fig-xml1}Snapshot of beginning of XML file for Hansard
+on 25 February 2020}
 
-While the modifications needed to develop the second script were quite straightforward, this was not the case for our next script.
-The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology.
-In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`.
-The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments and continuations.
-After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order.
-For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node.
-These would contain details on the person who made each statement such as their party and electorate.
+\end{figure}
 
-In contrast, the speech contents in XMLs from 1998 up to and including 24 March 2011 are nested differently --- there is no `<talk.text>` node.
-Rather than this single child-node that contains all speech content, statements are categorized in individual child-nodes.
-This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`debate/speech/talk.text`" or "`debate/subdebate.1/speech/talk.text`" to extract all speeches, in their entirety, at once.
-This difference in nesting structure made our second script unusable for parsing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.
+Evidently, the nature of XML formatting means that different pieces of
+information are categorized under a series of uniquely named and nested
+nodes. As a result, to parse each piece of information, one must specify
+the unique hierarchy of nodes in which it is structured. This is known
+as an XPath expression, and tells the parser how to navigate the XML
+document to obtain the desired information. For example, the session
+header date in Figure~\ref{fig-xml1} can be accessed using the XPath
+expression ``\texttt{hansard/session.header/date}''. We began our first
+script by parsing every piece of information contained in the XML
+document, using these unique XPath expressions to do so.
 
-Since there are numerous speeches in a typical Hansard, each having multiple child-nodes with the same names (i.e.
-`<continuation>`, `<interjection>`), it is difficult to parse everything while maintaining the correct ordering of statements.
-We found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly.
-The reason we did not use its `<speech>` child-node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days.
+The next step was to further develop our script to produce tidy data
+sets containing each parsed element, where each statement is separated
+onto its own row with details about the speaker, and rows are placed in
+chronological order. This first involved correcting the variable classes
+and adding a number of indicator variables to differentiate where
+statements came from, such as Chamber versus Federation Chamber or
+sub-debate 1 versus sub-debate 2. The next key task stemmed from the
+fact that the raw text data were not separated by each statement when
+parsed. In other words, any interjections, comments made by The Speaker
+or Deputy Speaker and continuations within an individual speech were all
+parsed together as a single string. As such, the name, name ID,
+electorate and party details were only provided for the person whose
+turn it was to speak. Splitting up these speeches in a way which would
+be generalizable across sitting days required much thought and effort.
+Section~\ref{sec-interject} will provide further details on the
+intricacies of this task.
 
-The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data.
-For example, the data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:
+Since we are looking at a wide time span of documents, there are
+expectedly a number of changes in the way they are formatted over time.
+These became apparent as we ran our script on XML files from earlier
+sitting days. Some changes are as subtle as a differently named
+child-node, while others are as extensive as a completely different
+nesting structure. Smaller changes were accounted for as we became aware
+of them, and embedded into the code in a way that would not cause issues
+for parsing more current Hansards with subtle differences in formatting.
+However, as mentioned, more significant changes in the XML structure of
+Hansard are what necessitated the development of separate scripts as we
+worked backwards in time. Further, while working backward in time, it
+became clear that not every sitting day contains every possible XML
+element. For example, some days did not have sub-debate 2 content, and
+some days did not have a Federation Chamber proceeding. To improve the
+generalizability of these scripts, if-else statements were embedded
+within the code wherever an error might arise due to a missing element.
+For example, the entire Federation Chamber block of code is wrapped in
+an if-else statement for each script, so that it only executes if what
+the code attempts to parse actually exists in the file.
 
-> `09:31:0010261Costello, Peter, MPMr COSTELLOCT4HigginsLPTreasurer10`
+Once the script ran without error for a few recent years of Hansard, we
+continued to work backwards until extensive changes in tree structure
+made our script incompatible with parsing earlier XML files. The
+earliest sitting day our first script can successfully parse is 14
+August 2012. Before developing new scripts to parse earlier Hansard
+documents, we decided to prioritize cleaning and finalizing what we have
+been able to parse. As such we continued building our script, fixing any
+problems we noticed in the resulting datasets such as excess whitespace
+or spacing issues, and splitting up any additional sections of the
+parsed text onto separate rows where necessary. Specifically, we added a
+section of our script to separate out general stage directions. More
+information on this separation will be provided in
+Section~\ref{sec-stage}. After completing our first script, it was
+formatted as a function which takes a single file name argument and
+produces one CSV file containing data on all proceedings from the given
+sitting day.
 
-![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}
+\hypertarget{sec-diff}{%
+\subsection{Script Differences}\label{sec-diff}}
 
-This was not isolated to just the beginning of speeches --- details on individuals interjecting or commenting during speeches were also captured this way.
-To separate statements out correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found.
-After separating statements, we were later able remove these patterns from the body of text.
-We also used this method of extracting and later removing unwanted patterns for other pieces of data which did not belong to the debate proceedings, such as sub-debate titles.
+As previously mentioned, we developed a total of four scripts to parse
+the 1998-2022 time frame of Hansard documents. Two main factors
+motivated us to create four scripts as opposed to just one, the first
+being structural variation in XML over time, and the second being
+improved computational efficiency with separate scripts. While all four
+scripts use the same general approach to parsing described in
+Section~\ref{sec-overview} and produce the same CSV structure, the first
+and second scripts use a different method of data processing than the
+third and fourth scripts.
 
-Once we finalized this new method of processing the data, we proceeded with data cleaning using the same general approach as in the first two scripts to produce the same structure of CSV output.
-We then worked backwards in time and modified the code as needed for generalizability.
-Throughout this process we found a number of transcription errors present in the XMLs from earlier years.
-We fixed these manually, deferring to the official release to ensure the correct information was filled in.
-Since there were a number of transcription errors specific to the 2000s, we chose to create a fourth script for parsing 1998 and 1999.
-This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency.
-As such, our fourth script is essentially the same as the third, the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.
+The need for a second script stems from the fact that when established
+in 1994, the Federation Chamber was originally named the Main Committee.
+The Main Committee was renamed to the Federation Chamber in mid-2012
+(House of Representatives 2018, ch.~21). As a result, the child-node
+under which Federation Chamber proceedings are nested is named
+\texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
+prior to 14 August 2012. Having developed our first script based on
+Hansard from recent years, all XPath expressions contain the
+\texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
+avoid causing issues in our first script which successfully parses about
+10 years of Hansard, we created a second script where we replaced all
+occurrences of \texttt{\textless{}fedchamb.xscript\textgreater{}} with
+\texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
+modification and accounting for other small changes such as time stamp
+formatting, this second script successfully parses all Hansard sitting
+days from 10 May 2011 to 28 June 2012 (inclusive).
 
-## Question Time {#sec-qa}
+While the modifications needed to develop the second script were quite
+straightforward, this was not the case for our next script. The typical
+tree structure of Hansard XMLs spanning from 1998 to March 2011 has an
+important difference from that of XMLs released after March 2011,
+necessitating many changes to be made in our methodology. In XMLs after
+March 2011, which our first two scripts successfully parse, the first
+two child-nodes of \texttt{\textless{}speech\textgreater{}} are
+typically \texttt{\textless{}talk.start\textgreater{}}, and
+\texttt{\textless{}talk.text\textgreater{}}. The first child-node
+contains data on the person whose turn it is to speak, and the second
+contains the entire contents of that speech --- including all
+interjections, comments and continuations. After the
+\texttt{\textless{}talk.text\textgreater{}} element closes, there are
+typically a series of other child-nodes which provide a skeleton
+structure for how the speech proceedings went in chronological order.
+For example, if the speech began, was interrupted by one member, and
+then continued uninterrupted until the end, there would be one
+\texttt{\textless{}interjection\textgreater{}} node and one
+\texttt{\textless{}continuation\textgreater{}} node following the
+\texttt{\textless{}talk.text\textgreater{}} node. These would contain
+details on the person who made each statement such as their party and
+electorate.
 
-A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions.
+In contrast, the speech contents in XMLs from 1998 up to and including
+24 March 2011 are nested differently --- there is no
+\texttt{\textless{}talk.text\textgreater{}} node. Rather than this
+single child-node that contains all speech content, statements are
+categorized in individual child-nodes. This means that unlike our code
+for parsing more current Hansards, we cannot specify a single XPath
+expression such as ``\texttt{debate/speech/talk.text}'' or
+``\texttt{debate/subdebate.1/speech/talk.text}'' to extract all
+speeches, in their entirety, at once. This difference in nesting
+structure made our second script unusable for parsing transcripts
+preceding 10 May 2011, and required us to change our data processing
+approach considerably.
+
+Since there are numerous speeches in a typical Hansard, each having
+multiple child-nodes with the same names
+(i.e.~\texttt{\textless{}continuation\textgreater{}},
+\texttt{\textless{}interjection\textgreater{}}), it is difficult to
+parse everything while maintaining the correct ordering of statements.
+We found that the most straightforward way to preserve the ordering of
+statements and to parse all speech contents at once was to parse from
+the \texttt{\textless{}debate\textgreater{}} element directly. The
+reason we did not use its \texttt{\textless{}speech\textgreater{}}
+child-node is because every speech has a unique structure of node
+children, and this makes it difficult to write code for data cleaning
+which is generalizable across all speeches and sitting days.
+
+The challenge with parsing through the
+\texttt{\textless{}debate\textgreater{}} element is that every piece of
+data stored in that element is parsed as a single string, including all
+\texttt{\textless{}talk.start\textgreater{}} data, and all nested
+sub-debate data. For example, the data shown in
+Figure~\ref{fig-patternEX} would be parsed as a single string preceding
+the speech content, like so:
+
+\begin{quote}
+\texttt{09:31:0010261Costello,\ Peter,\ MPMr\ COSTELLOCT4HigginsLPTreasurer10}
+\end{quote}
+
+\begin{figure}
+
+{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}
+
+}
+
+\caption{\label{fig-patternEX}Portion of XML file for Hansard on 12
+December 2002}
+
+\end{figure}
+
+This was not isolated to just the beginning of speeches --- details on
+individuals interjecting or commenting during speeches were also
+captured this way. To separate statements out correctly, we collected
+all of these patterns using the
+\texttt{\textless{}talk.start\textgreater{}} node, and used them to
+split statements wherever one of these patterns was found. After
+separating statements, we were later able remove these patterns from the
+body of text. We also used this method of extracting and later removing
+unwanted patterns for other pieces of data which did not belong to the
+debate proceedings, such as sub-debate titles.
+
+Once we finalized this new method of processing the data, we proceeded
+with data cleaning using the same general approach as in the first two
+scripts to produce the same structure of CSV output. We then worked
+backwards in time and modified the code as needed for generalizability.
+Throughout this process we found a number of transcription errors
+present in the XMLs from earlier years. We fixed these manually,
+deferring to the official release to ensure the correct information was
+filled in. Since there were a number of transcription errors specific to
+the 2000s, we chose to create a fourth script for parsing 1998 and 1999.
+This allowed us to remove all the code which was needed to resolve
+specific transcription errors of the 2000s, to avoid an overly long
+script and in turn improving computational efficiency. As such, our
+fourth script is essentially the same as the third, the only difference
+being that it has code specific to fixing transcription errors from 1998
+and 1999.
+
+\hypertarget{sec-qa}{%
+\subsection{Question Time}\label{sec-qa}}
+
+A key characteristic of the Australian parliament system is the ability
+for the executive government to be held accountable for their decisions.
 One core mechanism by which this is achieved is called Question Time.
-This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
-Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
-Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
-Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.
+This is a period on each sitting day in the Chamber where members of the
+House can ask ministers two types of questions: questions in writing
+which are written in advance, or questions without notice which are
+asked verbally in the Chamber and are responded to in real time (House
+of Representatives 2021). Parsing the components of Question Time
+required a slightly different approach than that of the debate speech,
+because of its unique structure in the XML document. Questions without
+notice are included directly in the \texttt{"chamber.xscript"} child
+node, with sub-child nodes called \texttt{"question"} and
+\texttt{"answer"} to differentiate the two. Questions in writing,
+however, are embedded in their own child node called
+\texttt{"answers.to.questions"} at the end of the XML file.
 
-To parse questions without notice and questions in writing in the first two scripts, we extracted all question and answer elements from the `"chamber.xscript"` and `"answers.to.questions"` child nodes.
-For the third and fourth scripts, our method of parsing the `"chamber.xscript"` speeches meant that all questions without notice content was already parsed in order.
-Similar to the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
-Finally, since questions in writing exist in their own child node we were able to use the same parsing method for the third and fourth scripts as we did for the first and second scripts.
+To parse questions without notice and questions in writing in the first
+two scripts, we extracted all question and answer elements from the
+\texttt{"chamber.xscript"} and \texttt{"answers.to.questions"} child
+nodes. For the third and fourth scripts, our method of parsing the
+\texttt{"chamber.xscript"} speeches meant that all questions without
+notice content was already parsed in order. Similar to the rest of the
+speech content, we used those patterns of data preceding the text to
+separate questions and answers. Finally, since questions in writing
+exist in their own child node we were able to use the same parsing
+method for the third and fourth scripts as we did for the first and
+second scripts.
 
-We then added binary flags to differentiate between questions and answers, determined by which sub-child node the statement was extracted from, that is, whether it came from a `<question>` node, or an `<answer>` node.
-Sometimes, questions were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags using the `str_detect` function from the `stringr` package.
-For instance, our code for parsing questions searches for any statements which include "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer.
-Once all questions and answers were correctly classified as such, we could then merge all the content back together such that each question was followed by its associated answer.
-This was straightforward due to the fact that by nature of XML parsing, all questions and answers were parsed in the order in which they appeared in the transcript.
+We then added binary flags to differentiate between questions and
+answers, determined by which sub-child node the statement was extracted
+from, that is, whether it came from a
+\texttt{\textless{}question\textgreater{}} node, or an
+\texttt{\textless{}answer\textgreater{}} node. Sometimes, questions were
+incorrectly transcribed under an answer node and vice-versa, in which
+cases we manually corrected the question and answer flags using the
+\texttt{str\_detect} function from the \texttt{stringr} package. For
+instance, our code for parsing questions searches for any statements
+which include ``has provided the following answer to the honourable
+member's question'', in which case we re-code that statement as an
+answer. Once all questions and answers were correctly classified as
+such, we could then merge all the content back together such that each
+question was followed by its associated answer. This was straightforward
+due to the fact that by nature of XML parsing, all questions and answers
+were parsed in the order in which they appeared in the transcript.
 
-The next step was to merge Question Time contents with all the debate speech.
-Doing so with the questions without notice content was straightforward.
-For the first and second scripts, we used the time stamp and page number associated with each question to maintain the correct order of statements.
-For the third and fourth scripts, our method of parsing meant that everything was already parsed together in order, so we did not have to perform any additional merging.
-While questions in writing do not contain time stamps, merging this content was also straightforward due to the fact that it is always at the very end of Hansard.
-This means that we could simply bind question in writing rows to the bottom of the main dataframe.
-This approach was used for all four scripts.
+The next step was to merge Question Time contents with all the debate
+speech. Doing so with the questions without notice content was
+straightforward. For the first and second scripts, we used the time
+stamp and page number associated with each question to maintain the
+correct order of statements. For the third and fourth scripts, our
+method of parsing meant that everything was already parsed together in
+order, so we did not have to perform any additional merging. While
+questions in writing do not contain time stamps, merging this content
+was also straightforward due to the fact that it is always at the very
+end of Hansard. This means that we could simply bind question in writing
+rows to the bottom of the main dataframe. This approach was used for all
+four scripts.
 
-## Interjections {#sec-interject}
+\hypertarget{sec-interject}{%
+\subsection{Interjections}\label{sec-interject}}
 
-As mentioned, the text was structured and parsed in such a way that various interjections and comments which happened during a speech were not separated onto individual rows.
-This was the case across the entire time frame of documents.
-We will first discuss the methodology employed to split interjections in the first and second scripts, as it informed our approach for the third and fourth scripts.
+As mentioned, the text was structured and parsed in such a way that
+various interjections and comments which happened during a speech were
+not separated onto individual rows. This was the case across the entire
+time frame of documents. We will first discuss the methodology employed
+to split interjections in the first and second scripts, as it informed
+our approach for the third and fourth scripts.
 
-Below is an example of part of a speech we would need to split, extracted from Hansard on 30 November 2021, where Mr.
-van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.
+Below is an example of part of a speech we would need to split,
+extracted from Hansard on 30 November 2021, where Mr.~van Manen is
+interrupted by The Speaker who states that the time for members'
+statements has concluded.
 
-> ```{r}
-> #| warning: false
-> #| echo: false
-> #| message: false
-> #| results: asis
-> >
-> # read in XML file
-> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
-> >
-> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
-> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
->                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
->   as_tibble() %>% 
->   slice(25) %>% 
->   pull(body)
-> >
-> # print example of text in quotations
-> cat(paste0('"', interject_text_ex, '"'))
-> ```
+\begin{quote}
+``Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great
+pleasure to share with the House that Windaroo Valley State High School
+has qualified for the finals of the Australian Space Design Competition,
+to begin in January next year. The competition is regarded as the
+premier STEM competition for high school students and is recognised by
+universities around the country. The students are required to respond to
+industry-level engineering and requests for tender for design and---The
+SPEAKER: Order! In accordance with standing order 43, the time for
+members' statements has concluded.''
+\end{quote}
 
-We want each statement on its own row with the correct name, name ID, electorate and party information on the individual speaking. We approached this task in a number of steps.
+We want each statement on its own row with the correct name, name ID,
+electorate and party information on the individual speaking. We
+approached this task in a number of steps.
 
-Once all parsed text from the XML was merged into one dataframe called `main`, our first step was to add a `"speech_no"` variable.
-This was done to keep track of which speech each interjection, comment, or continuation belonged to as we separated these components onto their own rows.
+Once all parsed text from the XML was merged into one dataframe called
+\texttt{main}, our first step was to add a \texttt{"speech\_no"}
+variable. This was done to keep track of which speech each interjection,
+comment, or continuation belonged to as we separated these components
+onto their own rows.
 
-The next step was to extract all the names and titles preceding these interjections, comments and continuations.
-This would enable us to then separate the speeches in the correct places using these names and titles in combination with regular expressions, which are patterns of characters that can be used to search bodies of text.
-We completed this extraction process with a few intermediate steps, due to the large number of name styles and interjection types that had to be accounted for, each requiring their own unique regular expression format.
+The next step was to extract all the names and titles preceding these
+interjections, comments and continuations. This would enable us to then
+separate the speeches in the correct places using these names and titles
+in combination with regular expressions, which are patterns of
+characters that can be used to search bodies of text. We completed this
+extraction process with a few intermediate steps, due to the large
+number of name styles and interjection types that had to be accounted
+for, each requiring their own unique regular expression format.
 
-As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech.
-@fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
-Looking at the element names highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
-However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on.
-Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
-We stored this as a dataframe called `"interject"`.[^1]
+As mentioned in Section~\ref{sec-diff}, more recent years of Hansard
+XMLs contain a series of child-nodes which exist to capture the
+structure of interruptions in that speech. Figure~\ref{fig-xml3}
+provides an example of this, where the speech was interrupted by a
+comment from The Deputy Speaker, and then the member continued their
+speech. Looking at the element names highlighted in blue, it is clear
+that these child-nodes do not contain the actual text for the
+interjection or continuation --- this text is embedded within the speech
+above it. However, as shown by the content highlighted in pink in
+Figure~\ref{fig-xml3}, we were able to extract useful details on the
+individual interjecting which we could use later on. Making use of this
+structure, we extracted names and information of all individuals that
+were categorized within the XML as interjections. We stored this as a
+dataframe called \texttt{"interject"}.\footnote{We decided not to
+  include this data in our final database, as it is all embedded in our
+  resulting datasets which have a flag for interjections.}
 
-[^1]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.
+\begin{figure}
 
-![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
+{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}
 
-We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
-We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
-When a Member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
-Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
-This variation demands careful consideration when writing regular expression patterns to search for in the text.
-In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
+}
 
-[^2]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
+\caption{\label{fig-xml3}Snapshot of XML structure with interjection and
+continuation from 03 February 2021 Hansard}
 
-Having these lists enabled us to extract the names of Members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns.
-We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds.
-A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
-These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.
+\end{figure}
 
-Once all interjections, comments and continuations were successfully split onto their own rows using the lists we created, we did one final check for any additional names that were not captured in these lists.
-To do so, we searched for any remaining name matches in speech bodies with general regular expressions and lookarounds, and separated text using those matches when found.
+We then created lists using both the \texttt{interject} and
+\texttt{main} dataframes to capture all the names of individuals who
+spoke that day. We added the names of all Members in a number of unique
+formats, due to the frequent variation in how names are transcribed in
+Hansard. When a Member interjects or continues a speech, the usual form
+of their name is a title followed by their first name or first initial
+and/or last name. There is also variation in the capitalization of these
+names.\footnote{Sometimes when someones first name is included, only
+  their last name is capitalized, while sometimes their full name is
+  capitalized, or other times neither are capitalized.} Another source
+of variation is in individuals with more than one first name, as
+sometimes only their first first name is written, while other times
+their entire first name is written. Additionally, some surnames have
+punctuation, and some surnames have specific capitalization such as
+``McCormack'', where even in full capitalization, the first ``c''
+remains lower case. This variation demands careful consideration when
+writing regular expression patterns to search for in the text. In these
+lists we also accounted for any general interjection statements
+transcribed that were not attributed to an individual, such as ``An
+opposition member interjecting-''.
 
-We then added an order variable to the dataset based on row number, to keep track of the order in which everything was said.
-The next step was to fill the name, name ID, electorate and party variables with the correct data for each row.
-We also wanted to add the gender and unique identifier for each individual as found in the `AustralianPoliticians` package.
-To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, party, gender and unique ID for that individual.
-@fig-lookup provides an example of this.
-We used the main dataset from the `AustralianPoliticians` package in the creation of each lookup table [@auspol].
+Having these lists enabled us to extract the names of Members and their
+associated titles as they exist in the text, by searching for exact
+matches with regular expression patterns. We then used these extracted
+names to split all the speeches up, using a number of regular
+expressions with lookarounds. A lookaround can be added to a regular
+expression pattern to enhance the specificity of matches. These were
+used to ensure that the text was not being split in the wrong places,
+such as places where Members were simply being named in the statement of
+another Member.
 
-![First 10 rows of lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
+Once all interjections, comments and continuations were successfully
+split onto their own rows using the lists we created, we did one final
+check for any additional names that were not captured in these lists. To
+do so, we searched for any remaining name matches in speech bodies with
+general regular expressions and lookarounds, and separated text using
+those matches when found.
 
-Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender and unique ID information.
-Finally, we were able to add a flag for interjections.
-Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak.
-@fig-interject provides an example of a Federation Chamber proceeding with interjections.
-Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
+We then added an order variable to the dataset based on row number, to
+keep track of the order in which everything was said. The next step was
+to fill the name, name ID, electorate and party variables with the
+correct data for each row. We also wanted to add the gender and unique
+identifier for each individual as found in the
+\texttt{AustralianPoliticians} package. To do so, we created a lookup
+table, which contained the unique incomplete form in which the name was
+transcribed, and the corresponding full name, name ID, electorate,
+party, gender and unique ID for that individual. Figure~\ref{fig-lookup}
+provides an example of this. We used the main dataset from the
+\texttt{AustralianPoliticians} package in the creation of each lookup
+table (Alexander and Hodgetts 2021).
 
-![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
+\begin{figure}
 
-Having developed a successful methodology for splitting interjections, we used this to inform our general approach in the third and fourth scripts.
-However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology.
-As discussed in @sec-diff, we used string patterns extracted from `<talk.start>` nodes to separate speeches.
-As evident in @fig-xml3, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process.
-In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process.
-This meant that we did not need to create lists of names and titles to search for in the text as we did before.
-However, we used the same list of general interjection statements to separate on that was used in the first two scripts.
-We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^3]
+{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}
 
-[^3]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
+}
 
-We then proceeded to clean up speeches and fill in correct speaker details.
-While we used the same lookup table approach as before, we did so in combination with another means of filling in speaker details.
-The patterns parsed from `<talk.start>` nodes contain important data on the speaker of each statement.
-As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `<talk.start/talker>`.
-We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement.
-@fig-patterns provides an example of that lookup table.
-This approach enabled us to fill in missing data on each speaker using data extracted directly from the XML.
-Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.
+\caption{\label{fig-lookup}First 10 rows of lookup table from 19 October
+2017 Hansard processing}
 
-![10 rows of pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}
+\end{figure}
 
-## Stage Directions {#sec-stage}
+Next, we merged our main dataframe with the lookup table to replace any
+incomplete names with their full names, and to fill in any gaps with
+available name ID, electorate, party, gender and unique ID information.
+Finally, we were able to add a flag for interjections. Grouping our data
+by the speech number, we defined an interjection as a statement made by
+anyone who is not The Speaker, The Deputy Speaker, or the Member whose
+turn it was to speak. Figure~\ref{fig-interject} provides an example of
+a Federation Chamber proceeding with interjections. Evidently,
+statements made by the original speaker Stuart Robert or by The Deputy
+Speaker Maria Vamvakinou are not flagged as interjections.
 
-When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by members.
-Stage directions are general statements included in the transcript to document happenings in parliament.
-Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned".
-It was unclear to us from the XML and PDF who exactly these statements were attributed to.
-For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament.
-For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
-This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
-Bill read a second time".
-For this reason, we filled the name variable for these statements with "stage direction".
-Note that stage directions were not flagged as interjections.
-These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches.
-We have built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.
+\begin{figure}
 
-# Data Records
+{\centering \includegraphics{interject_ex.png}
 
-Our database contains 1517 CSV files, covering all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022.
-All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336076 [@katz_2022].
-For each CSV file, each row contains an individual statement, with details on the individual speaking.
-Of course, for general statements transcribed as made by "Honourable members" for example, these variables cannot be specified.
-@tbl-vars provides an overview of each variable found in the database.
+}
 
-```{r}
-#| warning: false
-#| message: false
-#| echo: false
-#| label: tbl-vars
-#| tbl-cap: "Summary and description of variables in our database"
+\caption{\label{fig-interject}Example of speech with interjections from
+21 November 2016 Hansard}
 
-# read in packages
-library(readr)
-library(tidyverse)
-library(here)
-library(XML)
-library(lubridate)
-library(kableExtra)
+\end{figure}
 
-# read in example csv
-main_ex <- read_csv("/Volumes/Verbatim/output/main-2000-2011/2003-08-14-main.csv", show_col_types = F)
+Having developed a successful methodology for splitting interjections,
+we used this to inform our general approach in the third and fourth
+scripts. However, the difference in data cleaning used in these scripts
+necessitated some departure from the original methodology. As discussed
+in Section~\ref{sec-diff}, we used string patterns extracted from
+\texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
+As evident in Figure~\ref{fig-xml3},
+\texttt{\textless{}talk.start\textgreater{}} nodes are nested within
+\texttt{\textless{}interjection\textgreater{}} nodes, meaning that the
+patterns of data from interjection statements were separated out in the
+process. In other words, our approach to data cleaning in the third and
+fourth scripts separated out interjections in the process. This meant
+that we did not need to create lists of names and titles to search for
+in the text as we did before. However, we used the same list of general
+interjection statements to separate on that was used in the first two
+scripts. We then did an additional check for statements that may have
+not been separated due to how they were embedded in the XML, and
+separated those out where needed.\footnote{While most statements were
+  categorized in their own child-node and hence captured through
+  pattern-based separation, some were not individually categorized, and
+  had to be split manually in this step.}
 
-# create tibble with var names and descriptions
-main_ex_vars <- tibble("Variable" = names(main_ex),
-       "Description" = c("Name of speaker",
-                         "Row number",
-                         "Speech number",
-                         "Page number statement can be found on in official Hansard",
-                         "Time of statement",
-                         "Unique member identification code, based on the Parliamentary Handbook",
-                         "Speaking member's electorate",
-                         "Speaking member's party",
-                         "Flag for in government (1 if in government, 0 otherwise)",
-                         "Flag for first speech (1 if first speech, 0 otherwise)",
-                         "Statement text",
-                         "Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)",
-                         "Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)",
-                         "Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)",
-                         "Flag for question (1 if question, 0 otherwise)",
-                         "Flag for answer (1 if answer, 0 otherwise)",
-                         "Flag for question in writing (1 if question in writing, 0 otherwise)",
-                         "Flag for division (1 if division, 0 otherwise)",
-                         "Gender of speaker",
-                         "Unique identifier of speaker",
-                         "Flag for interjection (1 if statement is an interjection, 0 otherwise)"))
+We then proceeded to clean up speeches and fill in correct speaker
+details. While we used the same lookup table approach as before, we did
+so in combination with another means of filling in speaker details. The
+patterns parsed from \texttt{\textless{}talk.start\textgreater{}} nodes
+contain important data on the speaker of each statement. As such, we
+could extract those data associated with each pattern by parsing one
+element inward, using the XPath expression
+\texttt{\textless{}talk.start/talker\textgreater{}}. We created a
+pattern lookup table with these data, and merged it with the main
+Hansard dataframe by the first pattern detected in each statement.
+Figure~\ref{fig-patterns} provides an example of that lookup table. This
+approach enabled us to fill in missing data on each speaker using data
+extracted directly from the XML. Finally, we then used the
+\texttt{AustralianPoliticians} dataset to fill in other missing data,
+and flagged for interjections in the same manner as before.
 
-# print tibble using kable
-knitr::kable(main_ex_vars, booktabs=T) %>% 
-  kable_styling(full_width = F, latex_options = "HOLD_position")
-```
+\begin{figure}
 
-The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first,speech`, and `body` variables all came directly from the XML contents.
-In addition to these variables, we added a number of flags to enable easy filtering of statements.
-For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber.
-As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document.
-The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.
-We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for.
-The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package.
-Details on the usage of `uniqueID` will be provided in @sec-usage.
-Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.
-Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest.
-Finally, the `order` variable was added to maintain the order of proceedings.
+{\centering \includegraphics{pattern_lookup.png}
 
-**this paragraph is a bit repetitive and states everything found in the table, but i also feel like it's valuable to specify which ones we added and elaborate on their meaning. thoughts?**
+}
 
-## Descriptive Statistics {#sec-stats}
+\caption{\label{fig-patterns}10 rows of pattern lookup table from 12
+December 2012 Hansard processing}
 
-# Technical Validation
+\end{figure}
 
-We developed a script to perform seven automated tests on each file in our database, in an effort to enhance its quality and consistency.
-Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
-We validated that our file name and date was correct by checking the official PDF release from that sitting day.
+\hypertarget{sec-stage}{%
+\subsection{Stage Directions}\label{sec-stage}}
 
-[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
+When building our first scripts, one of the final components needed was
+to separate general stage directions out from statements made by
+members. Stage directions are general statements included in the
+transcript to document happenings in parliament. Examples of stage
+directions are ``Bill read a second time'', ``Question agreed to'' or
+``Debate adjourned''. It was unclear to us from the XML and PDF who
+exactly these statements were attributed to. For further clarification,
+we watched portions of the video recording for some sitting days, and
+noticed that where these statements are documented in Hansard, they are
+not explicitly stated in parliament. For example, when The Deputy
+Speaker says ``The question is that the bill be now read a second
+time'', members of the House take a vote, and if the majority is in
+favour, they proceed reading the bill the second time. This vote and
+second reading is not explicitly transcribed, rather what is written is:
+``Question agreed to. Bill read a second time''. For this reason, we
+filled the name variable for these statements with ``stage direction''.
+Note that stage directions were not flagged as interjections. These
+stage directions are not defined differently from the regular debate
+speech in the XML, meaning we had to manually create a list of stage
+directions to separate out of the speeches. We have built this list of
+stage directions as we worked backwards in parsing Hansard, and took the
+same approach across all four scripts.
 
-The second test checks that in each file, there is an equal number of flagged questions and answers.
-This test was motivated by the discrepancies in correct categorization of questions and answers we found when parsing Question Time, and allows us to check for the presence of any of these discrepancies which we have missed.
+\hypertarget{data-records}{%
+\section{Data Records}\label{data-records}}
 
-When a member runs out of allotted time for their speech, Hansard editors transcribe "(Time expired)" after their final word.
-As a means of checking that we have separated speeches out correctly, our third test checks that when the phrase "(Time expired)" exists in a body of text, it exists at the very end.
-When this is not the case, we know that we have missed the separation of the next statement onto its own row, and could fix this accordingly.
+Our database contains 1517 CSV files, covering all sitting days of the
+House of Representatives from 02 March 1998 to 08 September 2022. All
+data records are available on the general-purpose repository Zenodo, at
+https://doi.org/10.5281/zenodo.7336076 (Katz and Alexander 2022). For
+each CSV file, each row contains an individual statement, with details
+on the individual speaking. Of course, for general statements
+transcribed as made by ``Honourable members'' for example, these
+variables cannot be specified. Table~\ref{tbl-vars} provides an overview
+of each variable found in the database.
+
+\hypertarget{tbl-vars}{}
+\begin{table}[H]
+\caption{\label{tbl-vars}Summary and description of variables in our database }\tabularnewline
+
+\centering
+\begin{tabular}{ll}
+\toprule
+Variable & Description\\
+\midrule
+name & Name of speaker\\
+order & Row number\\
+speech\_no & Speech number\\
+page.no & Page number statement can be found on in official Hansard\\
+time.stamp & Time of statement\\
+\addlinespace
+name.id & Unique member identification code, based on the Parliamentary Handbook\\
+electorate & Speaking member's electorate\\
+party & Speaking member's party\\
+in.gov & Flag for in government (1 if in government, 0 otherwise)\\
+first.speech & Flag for first speech (1 if first speech, 0 otherwise)\\
+\addlinespace
+body & Statement text\\
+fedchamb\_flag & Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)\\
+sub1\_flag & Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)\\
+sub2\_flag & Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)\\
+question & Flag for question (1 if question, 0 otherwise)\\
+\addlinespace
+answer & Flag for answer (1 if answer, 0 otherwise)\\
+q\_in\_writing & Flag for question in writing (1 if question in writing, 0 otherwise)\\
+div\_flag & Flag for division (1 if division, 0 otherwise)\\
+gender & Gender of speaker\\
+uniqueID & Unique identifier of speaker\\
+\addlinespace
+interject & Flag for interjection (1 if statement is an interjection, 0 otherwise)\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
+\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
+\texttt{first,speech}, and \texttt{body} variables all came directly
+from the XML contents. In addition to these variables, we added a number
+of flags to enable easy filtering of statements. For example, adding the
+\texttt{fedchamb\_flag} provides a clear distinction between the
+proceedings of the Chamber with those of the Federation Chamber. As
+well, the \texttt{sub1\_flag} and \texttt{sub2\_flag} variables allow us
+to keep track of where various statements are being parsed from in the
+XML document. The \texttt{question}, \texttt{answer}, and
+\texttt{q\_in\_writing} flags were added to identify statements
+belonging to Question Time, and the nature of these statements. We also
+flagged for interjections (\texttt{interject}), and the
+\texttt{div\_flag} variable was added to flag when a division is called
+for. The \texttt{gender} and \texttt{uniqueID} variables were added
+based on the main dataset from the \texttt{AustralianPoliticians}
+package. Details on the usage of \texttt{uniqueID} will be provided in
+Section~\ref{sec-usage}. Further, the \texttt{speech\_no} variable
+allows us to keep track of the speech number that each statement and
+interjection belongs to. Having the speech number variable offers an
+easy way to group statements by speech or isolate specific speeches of
+interest. Finally, the \texttt{order} variable was added to maintain the
+order of proceedings.
+
+\textbf{this paragraph is a bit repetitive and states everything found
+in the table, but i also feel like it's valuable to specify which ones
+we added and elaborate on their meaning. thoughts?}
+
+\hypertarget{sec-stats}{%
+\subsection{Descriptive Statistics}\label{sec-stats}}
+
+\hypertarget{technical-validation}{%
+\section{Technical Validation}\label{technical-validation}}
+
+We developed a script to perform seven automated tests on each file in
+our database, in an effort to enhance its quality and consistency. Our
+first test validates that the date specified in each file name matches
+the date specified in its corresponding XML session header.\footnote{As
+  seen in Figure~\ref{fig-xml1}, the first child node of the
+  \texttt{\textless{}session.header\textgreater{}} element is the date.}
+Every file passed this test, and we detected one discrepancy in an XML
+file from 03 June 2009, where its session header contained the wrong
+date. We validated that our file name and date was correct by checking
+the official PDF release from that sitting day.
+
+The second test checks that in each file, there is an equal number of
+flagged questions and answers. This test was motivated by the
+discrepancies in correct categorization of questions and answers we
+found when parsing Question Time, and allows us to check for the
+presence of any of these discrepancies which we have missed.
+
+When a member runs out of allotted time for their speech, Hansard
+editors transcribe ``(Time expired)'' after their final word. As a means
+of checking that we have separated speeches out correctly, our third
+test checks that when the phrase ``(Time expired)'' exists in a body of
+text, it exists at the very end. When this is not the case, we know that
+we have missed the separation of the next statement onto its own row,
+and could fix this accordingly.
 
 The remaining tests focus on the members present on each sitting day.
-Our fourth test checks that there is one unique party and electorate attributed to each individual on each sitting day.
-As we parsed Hansard further back in time, we found a number of cases where an individual was associated with the wrong electorate or party due to transcription errors.
-When we found these data errors we corrected them based on the official release.
-This test provides us with an automated way to catch these errors and correct them at scale.
+Our fourth test checks that there is one unique party and electorate
+attributed to each individual on each sitting day. As we parsed Hansard
+further back in time, we found a number of cases where an individual was
+associated with the wrong electorate or party due to transcription
+errors. When we found these data errors we corrected them based on the
+official release. This test provides us with an automated way to catch
+these errors and correct them at scale.
 
-Next, we test that the unique name identification code attributed to each individual is found in the Australian Parliamentary Handbook.
-We do so using the `ausPH` package.
-This test serves as another means to correct for transcription errors, this time in the case of name IDs.
-We found and corrected for a number of common name ID transcription errors detected by this test, such as a capital letter "O" in place of a zero.
+Next, we test that the unique name identification code attributed to
+each individual is found in the Australian Parliamentary Handbook. We do
+so using the \texttt{ausPH} package. This test serves as another means
+to correct for transcription errors, this time in the case of name IDs.
+We found and corrected for a number of common name ID transcription
+errors detected by this test, such as a capital letter ``O'' in place of
+a zero.
 
-Our sixth test checks that on any given sitting day, the individuals identified are alive.
-To do so, we utilized the main dataset from the `AustralianPoliticians` package which contains the birth and where applicable death dates for every politician.
-This test confirmed that all members who are detected to speak on each sitting day are not deceased.
+Our sixth test checks that on any given sitting day, the individuals
+identified are alive. To do so, we utilized the main dataset from the
+\texttt{AustralianPoliticians} package which contains the birth and
+where applicable death dates for every politician. This test confirmed
+that all members who are detected to speak on each sitting day are not
+deceased.
 
-Finally, our seventh test validates that all individuals speaking are active members of parliament on that particular day.
-We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament.
-Using these dates, we check that each person speaking on each sitting day is in fact a Member of Parliament on that day.
+Finally, our seventh test validates that all individuals speaking are
+active members of parliament on that particular day. We use the
+\texttt{mps} dataset from the \texttt{AustralianPoliticians} package
+which has the dates of each Member's duration in parliament. Using these
+dates, we check that each person speaking on each sitting day is in fact
+a Member of Parliament on that day.
 
-# Usage Notes {#sec-usage}
+\hypertarget{sec-usage}{%
+\section{Usage Notes}\label{sec-usage}}
 
-To enhance the usability of our database, we added a `uniqueID` variable to each CSV file.
-This serves as a unique identifier for each speaking Member, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect].
-By including this variable, one can readily integrate our data records with those available in these two packages.
+To enhance the usability of our database, we added a \texttt{uniqueID}
+variable to each CSV file. This serves as a unique identifier for each
+speaking Member, and comes from the \texttt{uniqueID} variable present
+within data from both the \texttt{AustralianPoliticians} and
+\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
+Alexander 2019). By including this variable, one can readily integrate
+our data records with those available in these two packages.
 
-Further, the `name.id` variable found in each CSV is another unique identifier for each Member of Parliament.
-This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook.
-As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus].
-This will allow for convenient extraction of further details on each Member of Parliament in a tidy, ready to analyze format.
+Further, the \texttt{name.id} variable found in each CSV is another
+unique identifier for each Member of Parliament. This variable was
+parsed directly from the Hansard XML files, and can be found in the
+Australian Parliamentary Handbook. As such, our data records can be
+integrated with those from the \texttt{ausPH} package which provides
+datasets for contents of the Australian Parliamentary Handbook (Leslie
+2021). This will allow for convenient extraction of further details on
+each Member of Parliament in a tidy, ready to analyze format.
 
-# Code Availability
+\hypertarget{code-availability}{%
+\section{Code Availability}\label{code-availability}}
 
-The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj.
-All scripts were created using R software [@r_software].
-The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus.
-`XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in member details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.
+The code written to build this database is available on the GitHub
+repository associated with this paper:
+https://github.com/lindsaykatz/hansard-proj. All scripts were created
+using R software (R Core Team 2022). The core packages used to develop
+these scripts are: the \texttt{XML} package by Temple Lang (2022), the
+\texttt{xml2} package by Wickham, Hester, and Ooms (2021), the
+\texttt{tidyverse} R packages by Wickham et al. (2019), the
+\texttt{AustralianPoliticians} package by Alexander and Hodgetts (2021),
+and the \texttt{ausPH} package by Leslie (2021). \texttt{XML} and
+\texttt{xml2} were used for parsing the XML documents,
+\texttt{AustralianPoliticians} and \texttt{ausPH} were used for cleaning
+up and filling in member details in the datasets, and \texttt{tidyverse}
+packages were used in all steps, for tidy wrangling of data.
 
-# Acknowledgements
+\hypertarget{acknowledgements}{%
+\section{Acknowledgements}\label{acknowledgements}}
 
-# Author Contributions
+\hypertarget{author-contributions}{%
+\section{Author Contributions}\label{author-contributions}}
 
-# Competing Interests
+\hypertarget{competing-interests}{%
+\section{Competing Interests}\label{competing-interests}}
 
@@
 
-# References
+\hypertarget{references}{%
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-auselect}{}}%
+Alexander, Rohan. 2019. \emph{AustralianElections: Datasets on
+Australian Elections}.
+\url{https://github.com/RohanAlexander/AustralianElections}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
+Alexander, Rohan, and Monica Alexander. 2021. {``The Increased Effect of
+Elections and Changing Prime Ministers on Topics Discussed in the
+Australian Federal Parliament Between 1901 and 2018.''} \emph{arXiv
+Preprint arXiv:2111.09299}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
+Alexander, Rohan, and Paul A. Hodgetts. 2021.
+\emph{AustralianPoliticians: Provides Datasets about Australian
+Politicians}.
+\url{https://CRAN.R-project.org/package=AustralianPoliticians}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
+Beelen, Kaspar, Timothy Alberdingk Thijm, Christopher Cochrane, Kees
+Halvemaan, Graeme Hirst, Michael Kimmins, Sander Lijbrink, et al. 2017.
+{``Digitization of the Canadian Parliamentary Debates.''} \emph{Canadian
+Journal of Political Science/Revue Canadienne de Science Politique} 50
+(3): 849--64.
+
+\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
+Fraussen, Bert, Timothy Graham, and Darren R Halpin. 2018. {``Assessing
+the Prominence of Interest Groups in Parliament: A Supervised Machine
+Learning Approach.''} \emph{The Journal of Legislative Studies} 24 (4):
+450--74.
+
+\leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
+House of Representatives. 2018. Edited by D. R. Elder and P. E. Fowler.
+\emph{{House of Representatives Practice}}. 7th ed. {Australian
+Government - Department of the House of Representatives}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
+---------. 2021. \emph{{A window on the house: Practices and procedures
+relating to question time}}. {Parliament of Australia}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-katz_2022}{}}%
+Katz, Lindsay, and Rohan Alexander. 2022. {``{A new, comprehensive
+database of all proceedings of the Australian Parliamentary Debates}.''}
+Zenodo. \url{https://doi.org/10.5281/zenodo.7336076}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
+Leslie, Patrick. 2021. \emph{Members of the Australian House of
+Representatives (1945-2019)}.
+\url{https://github.com/palesl/AustralianHouseOfRepresentatives}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%
+R Core Team. 2022. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
+Rasiah, Parameswary. 2010. {``A Framework for the Systematic Analysis of
+Evasion in Parliamentary Discourse.''} \emph{Journal of Pragmatics} 42
+(3): 664--80.
+
+\leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
+Salisbury, Christopher. 2011. {``'Mr Speaker, i Withdraw...': Standards
+of (Mis) Behaviour in the Queensland, Western Australian and
+Commonwealth Parliaments Compared via Online Hansard.''}
+\emph{Australasian Parliamentary Review} 26 (1): 166--77.
+
+\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
+Sherratt, Tim. 2016. {``Documentation: Historic Hansard.''}
+\emph{Historic Hansard}.
+\url{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
+Temple Lang, Duncan. 2022. \emph{XML: Tools for Parsing and Generating
+XML Within r and s-Plus}. \url{https://CRAN.R-project.org/package=XML}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
+Vice, John, and Stephen Farrell. 2017. \emph{The History of Hansard}.
+House of Lords Library; House of Lords Hansard.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
+D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
+4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
+Wickham, Hadley, Jim Hester, and Jeroen Ooms. 2021. \emph{Xml2: Parse
+XML}. \url{https://CRAN.R-project.org/package=xml2}.
+
+\end{CSLReferences}
+
+\end{document}

### 2023-02-03 paper/paper.qmd
lots of updates

@@
 ---
-title: "Digitization of the Australian Parliamentary Debates (1901-2022)^[Code is available at: https://github.com/lindsaykatz/hansard-proj]"
+title: "Digitization of the Australian Parliamentary Debates, 1901-2022^[Code is available at: https://github.com/lindsaykatz/hansard-proj, data is available at https://doi.org/10.5281/zenodo.7336076]"
 number-sections: true
@@
   - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
-abstract: "Public knowledge of what is said in parliament is a key tenet of democracy.
-Parliamentary dialogue is also critical for political science research.
-In Australia, following the UK tradition, the written record of what is said in parliament is known as Hansard.
+abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and such parliamentary dialogue is critical for political science research.
+In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard.
 While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality to be credibly analysed with statistical models.
-Following the lead of the LiPaD project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard.
+Following the lead of the Linked Parliamentary Data project which achieved this for Canada, our project aims to provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1901 to the present day using Hansard.
 Our dataset will be publicly available and linked to other datasets such as election results.
@@
 This work will provide a thorough description of the creation and computational underpinnings of this database, followed by a discussion of some applications.
-To this point, we have completed this for 2011 to 2022."
+To this point, we have completed this for 1998 to 2022."
 ---
 
-# Introduction {#sec-intro}
+# Background & Summary {#sec-intro}
 
@@
 spoke out of turn).
-Thus far, this has been done for Hansard from mid-2011 to present.
+Thus far, this has been done for Hansard from 1998 to present.
 
@@
 
-# Existing Datasets {#sec-existing}
+## Existing Datasets {#sec-existing}
+*NOTE: THERE AREN'T ALLOWED TO BE SUBSECTIONS IN THIS FIRST SECTION, SO REMOVE THIS HEADING*
 
@@
 
-# Description of the Database {#sec-description}
+# Methods
 
-Our current database contains 670 comma-separated values (CSV) files, one for each sitting day of the House of Representatives from 10 May 2011 to 08 September 2022.
-We used two scripts to produce these files, which only have one subtle difference.
+Our current database contains 1516 comma-separated values (CSV) files, one for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022.
+We created four scripts to produce these files.
+As we worked backwards in time, the first script we developed parses everything from 14 August 2012 to 08 September 2022.
+The second script parses Hansard from 10 May 2011 to 28 June 2012, and the third script parses Hansard from 15 February 2000 to 24 March 2011.
+The fourth and final script parses Hansard for every sitting day in 1998 and 1999.
+In summary, these four scripts parse all available XML Hansard records for the House of Representatives from 1998 to the present.
+
+The approach to parsing contents of an XML document is heavily dependent on its tree structure.
+As such, to create this database, we started by looking at a single Hansard XML transcript.
+Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form.
+For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them.
+Parsing was performed in `R` using the `XML` package.
+Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible.
+Further, since we are looking at such a wide time span of documents, there are expectedly a number of changes in the way they are formatted.
+Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure.
+Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting.
+As mentioned in @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.
+
+@fig-xml1 provides an example of the beginning of an XML file for Hansard.
+The XML structure begins with a root or parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements with information such as the date, and parliament number, which are all highlighted in pink.
+Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1.
+On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too.
+This allows for the distinction of proceedings of the Chamber and Federation Chamber.
+As mentioned in @sec-description, each proceeding begins with the business start.
+The structure of this business start can be seen between the nodes highlighted in green in @fig-xml1.
+The content we parse from the business start are shown highlighted in orange in @fig-xml1.
+Next comes the debates and nested sub-debates, which follow the business start.
+Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it.
+That said, sometimes sub-debate 2 is not nested within sub-debate 1.
+Each of these three elements as well as their respective sub-elements contain important information on the title of the debate or sub-debate, who is speaking, and what is being said.
+As mentioned, in many cases speeches are interrupted by interjections, which are embedded in these sub-elements as well.
+The final key distinct component of Hansard is Question Time, in which question and answer elements are classified differently than general debate text.
+Sometimes questions and answers are nested within debate or sub-debate child nodes, and other times they have their own child node.
+More detail on the processing of Question Time will follow in @sec-qa.
+
+![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
+
+Once code was written to parse all components, it was organized into individual scripts.
+The first script includes everything from the session header element, the second contains everything from the debate element, and the third and fourth contain everything from the sub-debate 1 and 2 elements, respectively.
+The fifth script contains debate interjection information, and the sixth contains content from Question Time.
+The final script is a compilation of everything.
+The next step was to further develop these scripts to produce tidy data sets from each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order.
+This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
+The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
+In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
+As such, the name, name ID, electorate and party details were only provided for the person who's turn it was to speak.
+Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort.
+@sec-interject will provide further details on the intricacies of this task.
+
+When beginning to run these scripts on transcripts from other sitting days, it became clear that not every sitting day contains every possible XML element.
+For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding.
+To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
+For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.
+Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files.
+Specifically, the earliest date for which it works is 10 May 2011.
+Before writing a new script for parsing earlier Hansard, we decided to prioritize cleaning and finalizing what we have been able to parse.
+As such we continued building our scripts, fixing any issues we noticed in the resulting datasets, and splitting up any additional sections of the parsed text onto separate rows where necessary.
+Specifically, we added a section of our script to separate out general stage directions.
+More information on this separation will be provided in @sec-stage.
+
+After completing the scripts, they were formatted as functions which take a file name argument.
+The final script which parses everything from Hansard produces one CSV file with the data on all proceedings for each sitting day (example shown in @fig-main15rows).
+
+## Question Time {#sec-qa}
+
+A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions.
+One core mechanism by which this is achieved is called Question Time.
+This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
+Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
+Sometimes, questions in writing are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
+However, in other times, questions in writing are embedded in their own child node called `"answers.to.questions"` outside of `"chamber.xscript"`.
+Difficulty arose when trying to order these questions and answers correctly within the rest of the debate text, because unlike all other statements made which have both an associated page number and time stamp, these generally only have a page number.
+Time stamps have been a key variable for which we have arranged parsed text in chronological order, especially since many statements tend to be on the same page, meaning we cannot rely solely on page number to capture correct ordering.
+To approach this issue, we merged all parsed questions to be in a single dataframe, and all parsed answers in another dataframe.
+We then arranged each dataframe by page number, and merged the two dataframes in such a way that each question would be followed by its corresponding answer.
+
+## Interjections {#sec-interject}
+
+As mentioned, the text was structured and parsed in such a way that various interjections and comments which happened during a speech were not separated onto individual rows.
+Below is a simple example extracted from Hansard on 30 November 2021, where Mr.
+van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.
+
+> ```{r}
+> #| warning: false
+> #| echo: false
+> #| message: false
+> #| results: asis
+> >
+> # read in XML file
+> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
+> >
+> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
+> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
+>                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
+>   as_tibble() %>% 
+>   slice(25) %>% 
+>   pull(body)
+> >
+> # print example of text in quotations
+> cat(paste0('"', interject_text_ex, '"'))
+> ```
+
+As previously discussed, we wanted to have each statement on its own row, with the correct name, name ID, electorate and party information on the individual speaking.
+We approached this task in a number of steps.
+Once all parsed text from the XML was merged into one dataframe called `main`, we added a `"speech_no"` variable.
+As noted in @sec-description, this was done to keep track of which speech each interjection, comment, or continuation belonged to as we separated these components onto their own rows.
+
+The next step was to extract all the names and titles preceding these interjections, comments and continuations.
+This would enable us to then separate the speeches in the correct places using these names and titles in combination with regular expressions, which are patterns of characters that can be used to search bodies of text.
+We completed this extraction process with a few intermediate steps, due to the large number of name styles and interjection types that had to be accounted for, each requiring their own unique regular expression format.
+
+In many of the XML files, below the full speech including all interjections and continuations, there is a series of child-nodes which exist to capture the structure of interruptions in that speech.
+@fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
+Looking at the elements highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation.
+As mentioned, this text is embedded within the speech above it.
+However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on.
+Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
+We stored this as a dataframe called `"interject"`.[^2]
+
+[^2]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.
+
+![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
+
+We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
+We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
+When a Member interjects or continues a speech, the usual form of their name is a prefix followed by their first name or first initial and/or last name.
+There is also variation in the capitalization of these names.[^3] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
+Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
+This variation demands careful consideration when writing regular expression patterns to search for in the text.
+In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
+
+[^3]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
+
+Having these lists enabled us to extract the names of Members and their associated prefixes as they exist in the text, by searching for exact matches with regular expression patterns.
+We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds.
+A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
+These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.
+
+Once all interjections, comments and continuations were successfully split onto their own rows, we added a general order variable to the dataset based on row number, to keep track of the order in which everything was said.
+The next step was to fill the name, name ID, electorate and party variables with the correct data for each row.
+To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, and party for that individual [@fig-lookup].
+We used the main dataset from the `AustralianPoliticians` package in the creation of this lookup table [@auspol].
+
+![First 10 rows of lookup table from 10 May 2018 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
+
+Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps in the table with available name ID, electorate and party information.
+Finally, we were able to add a flag for interjections.
+Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak.
+@fig-interject provides an example of a Federation Chamber proceeding with interjections.
+Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
+
+![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
+
+## Stage Directions {#sec-stage}
+
+As mentioned, one of the final components added to our script was to separate general stage directions out from statements made by members.
+Stage directions are general statements included in the transcript to document happenings in parliament.
+Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned".
+It was unclear to us from the XML and PDF who exactly these statements were attributed to.
+For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament.
+For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
+This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
+Bill read a second time".
+For this reason, we filled the name variable for these statements with "stage direction".
+Note that stage directions were not flagged as interjections.
+These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches.
+We have been building upon this list of stage directions as we work backwards in parsing Hansard.
+
+While all scripts use the same approach and produce the same structure of data record, the first and second script use a slightly different method of data cleaning
+
+structural variation in XML over time necessitated the production of unique scripts to parse different time frames.
+
+The first and second scripts are very similar in structure, with one subtle difference.
+
+The third and fourth scripts are very similar to one another.
+
+The biggest difference between these scripts
+
+The first two scripts only have one subtle difference
+
 Since the Federation Chamber was renamed in mid-2012 from the original title of Main Committee, the element under which all the Federation Chamber contents are nested in the XML was renamed as well [@australia2018house, ch.
@@
 ![First 15 rows of CSV file for Hansard on 25 February 2020](main_ex15.png){#fig-main15rows}
+
+# Data Records
 
@@
 
-# Creation of the Database {#sec-create}
-
-The approach to parsing contents of an XML document is heavily dependent on its tree structure.
-As such, to create this database, we started by looking at a single Hansard XML transcript.
-Doing so enabled us to identify the various components of interest in the document, and how each one can be parsed according to its corresponding structural form.
-For example, the beginning of a speech may be followed by various interjections and continuations, all of which are structured as unique sub-elements containing further nested sub-elements within them.
-Parsing was performed in `R` using the `XML` package.
-Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible.
-Further, since we are looking at such a wide time span of documents, there are expectedly a number of changes in the way they are formatted.
-Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure.
-Smaller changes were accounted for as we became aware of them, and embedded into the final scripts in a way that would not cause issues for parsing more current Hansards with slightly different formatting.
-As mentioned in @sec-intro, the significant changes in XML structure of Hansard preceding 2011 necessitates much further development of our current scripts, which we are actively working to complete.
-
-@fig-xml1 provides an example of the beginning of an XML file for Hansard.
-The XML structure begins with a root or parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements with information such as the date, and parliament number, which are all highlighted in pink.
-Next there is a child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1.
-On sitting days where the Federation Chamber met as well, a child element exists for the Federation Chamber too.
-This allows for the distinction of proceedings of the Chamber and Federation Chamber.
-As mentioned in @sec-description, each proceeding begins with the business start.
-The structure of this business start can be seen between the nodes highlighted in green in @fig-xml1.
-The content we parse from the business start are shown highlighted in orange in @fig-xml1.
-Next comes the debates and nested sub-debates, which follow the business start.
-Broadly, the speeches within Hansard transcripts are structured with a debate node, containing a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it.
-That said, sometimes sub-debate 2 is not nested within sub-debate 1.
-Each of these three elements as well as their respective sub-elements contain important information on the title of the debate or sub-debate, who is speaking, and what is being said.
-As mentioned, in many cases speeches are interrupted by interjections, which are embedded in these sub-elements as well.
-The final key distinct component of Hansard is Question Time, in which question and answer elements are classified differently than general debate text.
-Sometimes questions and answers are nested within debate or sub-debate child nodes, and other times they have their own child node.
-More detail on the processing of Question Time will follow in @sec-qa.
-
-![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
-
-Once code was written to parse all components, it was organized into individual scripts.
-The first script includes everything from the session header element, the second contains everything from the debate element, and the third and fourth contain everything from the sub-debate 1 and 2 elements, respectively.
-The fifth script contains debate interjection information, and the sixth contains content from Question Time.
-The final script is a compilation of everything.
-The next step was to further develop these scripts to produce tidy data sets from each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order.
-This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
-The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
-In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
-As such, the name, name ID, electorate and party details were only provided for the person who's turn it was to speak.
-Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort.
-@sec-interject will provide further details on the intricacies of this task.
-
-When beginning to run these scripts on transcripts from other sitting days, it became clear that not every sitting day contains every possible XML element.
-For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding.
-To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
-For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.
-Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files.
-Specifically, the earliest date for which it works is 10 May 2011.
-Before writing a new script for parsing earlier Hansard, we decided to prioritize cleaning and finalizing what we have been able to parse.
-As such we continued building our scripts, fixing any issues we noticed in the resulting datasets, and splitting up any additional sections of the parsed text onto separate rows where necessary.
-Specifically, we added a section of our script to separate out general stage directions.
-More information on this separation will be provided in @sec-stage.
-
-After completing the scripts, they were formatted as functions which take a file name argument.
-The final script which parses everything from Hansard produces one CSV file with the data on all proceedings for each sitting day (example shown in @fig-main15rows).
-
-## Question Time {#sec-qa}
-
-A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions.
-One core mechanism by which this is achieved is called Question Time.
-This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
-Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
-Sometimes, questions in writing are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
-However, in other times, questions in writing are embedded in their own child node called `"answers.to.questions"` outside of `"chamber.xscript"`.
-Difficulty arose when trying to order these questions and answers correctly within the rest of the debate text, because unlike all other statements made which have both an associated page number and time stamp, these generally only have a page number.
-Time stamps have been a key variable for which we have arranged parsed text in chronological order, especially since many statements tend to be on the same page, meaning we cannot rely solely on page number to capture correct ordering.
-To approach this issue, we merged all parsed questions to be in a single dataframe, and all parsed answers in another dataframe.
-We then arranged each dataframe by page number, and merged the two dataframes in such a way that each question would be followed by its corresponding answer.
-
-## Interjections {#sec-interject}
-
-As mentioned, the text was structured and parsed in such a way that various interjections and comments which happened during a speech were not separated onto individual rows.
-Below is a simple example extracted from Hansard on 30 November 2021, where Mr.
-van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.
-
-> ```{r}
-> #| warning: false
-> #| echo: false
-> #| message: false
-> #| results: asis
-> >
-> # read in XML file
-> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
-> >
-> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
-> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
->                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
->   as_tibble() %>% 
->   slice(25) %>% 
->   pull(body)
-> >
-> # print example of text in quotations
-> cat(paste0('"', interject_text_ex, '"'))
-> ```
-
-As previously discussed, we wanted to have each statement on its own row, with the correct name, name ID, electorate and party information on the individual speaking.
-We approached this task in a number of steps.
-Once all parsed text from the XML was merged into one dataframe called `main`, we added a `"speech_no"` variable.
-As noted in @sec-description, this was done to keep track of which speech each interjection, comment, or continuation belonged to as we separated these components onto their own rows.
-
-The next step was to extract all the names and titles preceding these interjections, comments and continuations.
-This would enable us to then separate the speeches in the correct places using these names and titles in combination with regular expressions, which are patterns of characters that can be used to search bodies of text.
-We completed this extraction process with a few intermediate steps, due to the large number of name styles and interjection types that had to be accounted for, each requiring their own unique regular expression format.
-
-In many of the XML files, below the full speech including all interjections and continuations, there is a series of child-nodes which exist to capture the structure of interruptions in that speech.
-@fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
-Looking at the elements highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation.
-As mentioned, this text is embedded within the speech above it.
-However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on.
-Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
-We stored this as a dataframe called `"interject"`.[^2]
-
-[^2]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.
-
-![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
-
-We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
-We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
-When a Member interjects or continues a speech, the usual form of their name is a prefix followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.[^3] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
-Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
-This variation demands careful consideration when writing regular expression patterns to search for in the text.
-In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
-
-[^3]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
-
-Having these lists enabled us to extract the names of Members and their associated prefixes as they exist in the text, by searching for exact matches with regular expression patterns.
-We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds.
-A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
-These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.
-
-Once all interjections, comments and continuations were successfully split onto their own rows, we added a general order variable to the dataset based on row number, to keep track of the order in which everything was said.
-The next step was to fill the name, name ID, electorate and party variables with the correct data for each row.
-To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, and party for that individual [@fig-lookup].
-We used the main dataset from the `AustralianPoliticians` package in the creation of this lookup table [@auspol].
-
-![First 10 rows of lookup table from 10 May 2018 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
-
-Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps in the table with available name ID, electorate and party information.
-Finally, we were able to add a flag for interjections.
-Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak.
-@fig-interject provides an example of a Federation Chamber proceeding with interjections.
-Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
-
-![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
-
-## Stage Directions {#sec-stage}
-
-As mentioned, one of the final components added to our script was to separate general stage directions out from statements made by members.
-Stage directions are general statements included in the transcript to document happenings in parliament.
-Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned".
-It was unclear to us from the XML and PDF who exactly these statements were attributed to.
-For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament.
-For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
-This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
-Bill read a second time".
-For this reason, we filled the name variable for these statements with "stage direction".
-Note that stage directions were not flagged as interjections.
-These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches.
-We have been building upon this list of stage directions as we work backwards in parsing Hansard.
-
 # Conclusion {#sec-conclusion}
@@
 
+# Usage notes
+# Code availability
+# Acknowledgements
+# Author contributions
+# Competing interests
 # References

### 2023-02-03 scripts/99-everything-1998_to_1999.R

@@ -1,4 +1,3 @@
-# works from 15 February 2000 10 May 2011
 library(here)
 library(tidyverse)
 library(xml2)
@@ -29,13 +28,15 @@ item_df <- function(file, path){
 
 # grab "all" dataset from AusPol package
 all <- AustralianPoliticians::get_auspol('all')
-#all <- read.csv("/Volumes/Verbatim/all.csv")
+# all <- read.csv("/Volumes/Verbatim/all.csv")
 
-################### temp filename
-filename <- "2011-03-21.xml"
+#hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", "1999-06-22.xml"))
+#xml_df <- read_xml(here("/Volumes/Verbatim/input/", "1998-12-10.xml"))
 
-parse_hansard <- function(filename){ 
- 
+filename<-"1998-03-05.xml"
+
+parse_hansard_1998 <- function(filename){ 
+  
   hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
   xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
   
@@ -105,7 +106,7 @@ parse_hansard <- function(filename){
   # federation chamber
   if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//maincomm.xscript/business.start"), homogeneous = T, collectNames = F))>0) {
     bus_start_fed <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//maincomm.xscript/business.start"), homogeneous = T, collectNames = F), 
-                              fedchamb_flag = 1, .name_repair = "unique") %>% 
+                            fedchamb_flag = 1, .name_repair = "unique") %>% 
       rename(date = day.start) 
     
     if ("para" %in% names(bus_start_fed)) {
@@ -143,7 +144,7 @@ parse_hansard <- function(filename){
         select(date, fedchamb_flag, body, day_of_week, start_time)
     }
     
-
+    
     if ("interjection" %in% names(bus_start_fed)) {
       bus_start_fed <- bus_start_fed %>% unite("body", c(body, interjection), na.rm = T, sep=" ")
     }
@@ -262,31 +263,9 @@ parse_hansard <- function(filename){
   
   # in one case a pattern started with a "\" so remove that b\c gonna cause a lot of issues with regex matches later
   patterns_text <- patterns_text %>% as_tibble() %>% mutate(value = ifelse(str_detect(value, "^\\\\"),
-                                                          str_replace(value, "^\\\\", ""),
[…]

### 2023-02-03 scripts/99-everything-2011_to_2012.R

@@ -1,14 +1,18 @@
+# main committee
 # script to parse everything from Hansard
-# WORKS FOR 2012-08-14 TO PRESENT (that day is when the federation chamber was renamed)
+#### good for everything up to 2012-06-28 (last day before main committee was renamed to federation chamber)
 
 # read in necessary packages
 library(XML)
 library(here)
 library(tidyverse)
 
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
 # define function for splitting interjections, which will be referenced in parse_hansard function
 
-split_interjections <- function(main, interject, bus_start){
+split_interjections_maincomm <- function(main, interject, bus_start, sub1_q_a_writing, filename){
   
   #### step 1: add speech_no to make it easier to see where interjections happened 
   main <- rowid_to_column(main, "speech_no")
@@ -165,7 +169,7 @@ split_interjections <- function(main, interject, bus_start){
   interject_specific <- as_tibble(interject_names) %>% filter(!(value %in% interject_general)) %>% pull
   
   # now separate rows
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)(?!", interject_general, "[[:space:]]standing)(?!", interject_general, "[[:space:]]will )(?!", interject_general, "[[:space:]]can )",
+  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)(?!", interject_general, "[[:space:]]standing)(?!", interject_general, "[[:space:]]will )",
                                                collapse="|"))
   main <- separate_rows(main, body, sep=paste0("(?=", interject_specific, ")(?!", interject_specific, "[[:space:]]\\(.{1,30}\\)\\n[[:space:]]{11,22}\\()", collapse="|"))
   
@@ -216,6 +220,9 @@ split_interjections <- function(main, interject, bus_start){
[…]

### 2023-02-03 scripts/99-everything-2012_to_2022.R

@@ -1,15 +1,19 @@
-# main committee
 # script to parse everything from Hansard
-#### good for everything up to 2012-06-28 (last day before main committee was renamed to federation chamber)
+# WORKS FOR 2012-08-14 TO PRESENT (that day is when the federation chamber was renamed)
 
 # read in necessary packages
 library(XML)
 library(here)
 library(tidyverse)
 
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+#all <- read.csv("/Volumes/Verbatim/all.csv")
+
 # define function for splitting interjections, which will be referenced in parse_hansard function
 
-split_interjections_maincomm <- function(main, interject, bus_start){
+split_interjections <- function(main, interject, bus_start, sub1_q_a_writing, filename){
   
   #### step 1: add speech_no to make it easier to see where interjections happened 
   main <- rowid_to_column(main, "speech_no")
@@ -150,7 +154,7 @@ split_interjections_maincomm <- function(main, interject, bus_start){
     unique()
   
   #### step 4: extract all matches of the names in actual body, paste in possible prefixes, we will use these to separate rows next
-  names_use <- str_extract_all(main$body, paste0("(Dr|Mr|Mrs|Ms)[[:space:]]", all_names, "(?=[[:punct:]]|[[:blank:]])", collapse = "|")) %>% 
+  names_use <- str_extract_all(main$body, paste0("(?<!, )(Dr|Mr|Mrs|Ms)[[:space:]]", all_names, "(?=[[:punct:]]|[[:blank:]])", collapse = "|")) %>% 
     na.omit() %>% 
     unlist() %>% 
     unique()
@@ -166,7 +170,7 @@ split_interjections_maincomm <- function(main, interject, bus_start){
   interject_specific <- as_tibble(interject_names) %>% filter(!(value %in% interject_general)) %>% pull
   
   # now separate rows
-  main <- separate_rows(main, body, sep=paste0("(?=", interject_general, ")(?!", interject_general, "[[:space:]]on[[:space:]]my)(?!", interject_general, "[[:space:]]having)(?!", interject_general, "[[:space:]]standing)(?!", interject_general, "[[:space:]]will )",
[…]

### 2023-02-03 scripts/auspol_lookup.R

@@ -1,0 +1,336 @@
+library(tidyverse)
+
+# read in auspol dataset
+all_auspol <- AustralianPoliticians::get_auspol('all')
+
+# read in ausPH dataset
+all_ausPH <- ausPH::getIndividuals()
+
+# from auspol dataset, filter for members of the house, and select variables we want, and add name variables in full capitals - this is for merging later
+auspol <- all_auspol %>% filter(member==1) %>% 
+  select(uniqueID, surname, firstName, commonName, allOtherNames, displayName, earlierOrLaterNames, gender, title, deathDate) %>% 
+  mutate(surname_cap = str_to_upper(surname),
+         firstName_cap = str_to_upper(firstName),
+         commonName_cap = str_to_upper(commonName),
+         allOtherNames_cap = str_to_upper(allOtherNames),
+         displayName_cap = str_to_upper(displayName),
+         earlierOrLaterNames_cap = str_to_upper(earlierOrLaterNames))
+
+# select variables we want from ausPH, grab surnames, create surname_gender variable to match things with in the next step
+ausPH <- all_ausPH %>% select(PHID, DisplayName, Gender, Electorate, Party) %>% 
+  rename(phid = PHID,
+         displayName = DisplayName,
+         gender = Gender) %>% 
+  mutate(surname = str_extract(displayName, "^[[:alpha:]]+(?=,)|^[[:upper:]][[:alpha:]]+-[[:upper:]][[:alpha:]]+(?=,)|^[[:upper:]]+[[:space:]][[:upper:]]+(?=,)|^[[:upper:]]'[[:alpha:]]+(?=,)")) %>% 
+  mutate(surname = ifelse(is.na(surname) & str_detect(displayName, "\\(formerly"),
+                          str_extract(displayName, "^[[:alpha:]]+(?= \\(formerly)"),
+                          surname)) %>% 
+  mutate(surname = ifelse(surname=="COOK" & str_detect(displayName, "Hume"),
+                          "HUME COOK",
+                          surname)) %>% 
+  mutate(gender = ifelse(gender=="Male", "male", gender),
+         gender = ifelse(gender=="Female", "female", gender)) 
+
+# capitalization issue we need to fix manually to ensure successful merge
+# remove 2nd bob brown b/c it isn't in AusPol and causing issues when we merge later
+# keep the one with AM suffix b/c that's the one who matches the birth year in AusPol
[…]

### 2023-02-03 scripts/check_names.R

@@ -1,0 +1,88 @@
+# code to check for rows where names are missing
+
+library(tidyverse)
+
+files_1998 <- list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^1999-|^1998-")) %>% pull()
+files_2000 <- list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^2000-|^2001-|^2002-|^2003-|^2004-|^2005-|^2006-|^2007-|^2008-|^2009-|^2010-|^2011-")) %>% filter(value <= "2011-03-24.xml") %>% pull()
+files_2011 <- list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^2011-|^2012-")) %>% filter(value >= "2011-05-10.xml" & value <= "2012-06-28.xml") %>% pull(value)
+files_2012 <-  list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^2012-|^2013-|^2014-|^2015-|^2016-|^2017-|^2018-|^2019-|^2020-|^2021-|^2022-")) %>% filter(value>"2012-06-28.xml") %>% pull(value)
+
+missingNames1998 <- tibble()
+missingNames2000 <- tibble()
+missingNames2011 <- tibble()
+missingNames2012 <- tibble()
+
+
+# 1998
+for (i in 1:length(files_1998)){
+  
+  thisDate <- str_remove(files_1998[i], "\\.xml$")
+  
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-1998-1999/", thisDate, "-main.csv"), show_col_types = F)
+  
+  missingNames1998 <- thisFile %>% filter(is.na(name)) %>% 
+    select(order, body) %>% 
+    bind_cols(., thisDate %>% as_tibble()) %>% 
+    rename(date = value) %>% 
+    bind_rows(., missingNames1998)
+  
+}
+
+# 2000
+for (i in  1:length(files_2000)){
+  
+  thisDate <- str_remove(files_2000[i], "\\.xml$")
+  
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-2000-2011/", thisDate, "-main.csv"), show_col_types = F)
+  
+  missingNames2000 <- thisFile %>% filter(is.na(name)) %>% 
+    select(order, body) %>% 
[…]

### 2023-02-03 scripts/csv_to_parquet.R

@@ -1,0 +1,22 @@
+# script to convert all CSV files (version 2, filled) to parquet files, with correct variable classes
+library(arrow)
+library(tidyverse)
+
+# grab list of all file names
+files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv")
+
+# to loop through all our files
+for (i in 1:length(files_all)) {
+  
+  # read in file
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", files_all[i]), show_col_types = F)
+  
+  # modify variable classes
+  thisFile <- thisFile %>% mutate(party = as.factor(party),
+                                  gender = as.factor(gender))
+  
+  # export as parquet file
+  write_parquet(thisFile, paste0("/Volumes/Verbatim/output/main-filled-parquet/", str_remove(files_all[i], "csv"), "parquet"))
+  
+}
+

### 2023-02-03 scripts/data_validation.R

@@ -1,0 +1,350 @@
+# series of tests to validate our data
+library(tidyverse)
+
+# read in ausPH and auspol dataset
+ausPH <- ausPH::getIndividuals()
+
+all <- AustralianPoliticians::get_auspol('all')
+party <- AustralianPoliticians::get_auspol('allbyparty')
+mps <- AustralianPoliticians::get_auspol('mps')
+
+# read in my lookup table
+lookup <- read_csv("/Volumes/Verbatim/member_lookup.csv", show_col_types = F)
+
+# grab list of file names
+files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv")
+
+##### test 1 - date in filename must match one date in our list of dates from all session headers
+
+# grab session header csv - code to make this is in 01-session_info.R script
+session_headers <- read_csv("/Volumes/Verbatim/output/session_info/session_info_all.csv", show_col_types = F) %>% pull(date)
+
+# extract dates from file names, convert to date
+dates_all <- files_all %>% as_tibble() %>% mutate(value = as.Date(str_remove(value, "-main-v2.csv"))) %>% pull(value)
+
+# check that dates of our filenames match dates from session headers
+setdiff(as.character(dates_all), as.character(session_headers))
+
+# one difference - 2009-06-03
+# our filename is right, there is an error in the session header - it was transcribed as 2009-06-04, I checked official release to confirm we're right
+
+##### test 2 - equal number of flagged questions and answers
+# define empty tibble
+test2 <- tibble()
+
+# loop over all files
+for (i in 1:length(files_all)) {
+  # read in file
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", files_all[i]), show_col_types = F)
+  
+  # grab total qs and as, check if equal, add date
+  test2 <- thisFile %>% summarise(total_q = sum(question),
+                                  total_a = sum(answer),
+                                  equal = total_q==total_a) %>% 
+    mutate(date = str_remove(files_all[i], "-main-v2.csv")) %>% 
+    bind_rows(test2)
+  
+}
+
+# filter for days where test failed
+test2 <- test2 %>% filter(equal==FALSE) %>% select(-equal)
+
[…]

### 2023-02-03 scripts/descriptive_stats.R

@@ -1,0 +1,95 @@
+# descriptive stats
+library("quanteda")
+
+# read in file
+this_df <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", "2005-08-18-main-v2.csv"), show_col_types = F)
+
+# most common words
+hansard_corpus <- thisFile %>% select(order, body) %>% corpus(., docid_field = "order", text_field = "body")
+
+hansard_corpus %>% tokens() %>% dfm()
+
+stopwords(source="snowball")
+
+# average length of speeches
+
+# frequency of interjections by gender
+
+
+# average number of rows?
+
+
+
+# first grab list of all main CSVs
+all_dfs <- list.files("/Volumes/Verbatim/output/main")
+
+# define empty tibbles to store things in
+interject_data <- tibble()
+fedchamb_rows <- tibble()
+unique_data <- tibble()
+
+for(i in 1:length(all_dfs)){
+  # define df
+  this_df <- read_csv(paste0("/Volumes/Verbatim/output/main/", all_dfs[i]), show_col_types = F)
+  
+  # number of interjections
+  this_interject_data <- this_df %>% group_by(interject, gender) %>%
+    summarise(n_interject=n()) %>%
+    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
+    select(date, interject, n_interject)
+  
+  # number of rows in chamb and fedchamb
+  this_fedchamb_rows <- this_df %>% group_by(fedchamb_flag) %>% 
+    summarise(n_rows = n()) %>% 
+    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
+    select(date, fedchamb_flag, n_rows)
+  
+  # number of unique things (NAs omitted) - need to fix a tiny bit more but better for now
+  this_nameid <- this_df %>% select(name.id, fedchamb_flag) %>% 
+    group_by(fedchamb_flag) %>% 
+    unique() %>% 
+    na.omit() %>% 
+    summarise(n_name.id = n())
+  
+  this_electorate <- this_df %>% select(electorate, fedchamb_flag) %>% 
+    group_by(fedchamb_flag) %>% 
+    unique() %>% 
+    na.omit() %>% 
[…]

### 2023-02-03 scripts/fill_details.R

@@ -1,0 +1,264 @@
+# script to maximize completeness of hansard data by using AusPol lookup table
+# main goal is to replace short names with full names, and fill in any missing party, electorate, gender, or uniqueID details
+library(tidyverse)
+
+# read in master lookup table
+master_orig <- read_csv("/Volumes/Verbatim/member_lookup.csv", show_col_types = F) 
+speaker_list <- read_csv("/Volumes/Verbatim/speaker_lookup.csv", show_col_types = F) %>% unique()
+
+# setdiff(ausPH %>% select(phid) %>% unique(), master %>% select(phid) %>% unique())
+
+# rename phid to match with hansard, and change parties to hansard abbreviations for consistency
+# these are from: https://www.aph.gov.au/Parliamentary_Business/Committees/Senate/woc/wocjanjun08/a02
+master_orig <- master_orig %>% 
+  rename(name.id = phid) %>% 
+  mutate(party = case_when(party=="Australian Democrats" ~ "AD",
+                           party=="Australian Greens" ~ "AG",
+                           party=="Australian Labor Party" ~ "ALP",
+                           party=="Independent" ~ "Ind",
+                           party=="Liberal Party of Australia" ~ "LP",
+                           party=="The Nationals" ~ "NATS",
+                           party=="National Party of Australia" ~ "NATS"))
+
+# do same for speaker list
+speaker_list <- speaker_list %>% 
+  rename(name.id = phid) %>% 
+  mutate(party = case_when(party=="Australian Democrats" ~ "AD",
+                           party=="Australian Greens" ~ "AG",
+                           party=="Australian Labor Party" ~ "ALP",
+                           party=="Independent" ~ "Ind",
+                           party=="Liberal Party of Australia" ~ "LP",
+                           party=="National Party of Australia" ~ "NATS"))
+
+# define file-name
+#filename <- "2022-09-07-main.csv"
+
+fill_main <- function(filename) {
+  
+  # let's filter out people who have died prior to the Hansard date we're working with
+  # this will help reduce the number of people who share a surname and title
+  master <- master_orig %>% filter(deathDate >= paste0(str_remove(filename, "-main.csv")) | is.na(deathDate))
+  
+  # get list of people who share a title and surname (summarized by looking at form2 and form4)
+  # adding a few for ppl who got their seats in 2022 and aren't in AusPol yet
+  repeat_forms <- master %>% 
[…]

### 2023-02-28 paper/paper-nature_format.qmd
please work pt 2

@@
 
-![Snapshot of beginning of XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
+![Snapshot of beginning of XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}
 
@@
 
-![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}
+![Portion of XML file for Hansard on 12 December 2002](images/patternEX.png){#fig-patternEX width="315"}
 
@@
 
-![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
+![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](images/xml3.png){#fig-xml3 width="345"}
 
@@
 
-![First 10 rows of lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
+![First 10 rows of lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}
 
@@
 
-![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
+![Example of speech with interjections from 21 November 2016 Hansard](images/interject_ex.png){#fig-interject}
 
@@
 
-![10 rows of pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}
+![10 rows of pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}
 

### 2023-02-28 paper/paper-nature_format.tex
please work pt 2

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{January 20, 2023}
+\date{February 28, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, enhanced, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 
-{\centering \includegraphics{xml1.png}
+{\centering \includegraphics{images/xml1.png}
 
@@
 
-{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}
+{\centering \includegraphics[width=3.28125in,height=\textheight]{images/patternEX.png}
 
@@
 
-{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}
+{\centering \includegraphics[width=3.59375in,height=\textheight]{images/xml3.png}
 
@@
 
-{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}
+{\centering \includegraphics[width=4.66667in,height=\textheight]{images/lookup_ex.png}
 
@@
 
-{\centering \includegraphics{interject_ex.png}
+{\centering \includegraphics{images/interject_ex.png}
 
@@
 
-{\centering \includegraphics{pattern_lookup.png}
+{\centering \includegraphics{images/pattern_lookup.png}
 

### 2023-02-28 scripts/new_parsing_method.R

@@ -1,0 +1,648 @@
+# changing my approach to parsing so we don't have to merge stuff the way i originally had it
+# motivation - maintaining correct order
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+library(hms)
+
+# for parsing question time
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# define file name to parse
+filename<-"2011-05-11.xml"
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+
+# need to read the XML in in a different way for this so we can use the item_df function defined in global environment
+xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
+
+#################### CHAMBER ####################
+######### BUSINESS START #########
+# store business start in tibble, add flag for federation chamber, extract date, body, and start time
+# in rare cases (ex. 2016-08-30, there is no business start, so add if-else in case of this)
+if (nrow(tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"))))>0) {
+  bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start")), 
[…]

### 2023-02-28 scripts/99-everything-2011_to_2012-NEW.R
adding new scripts

@@ -1,0 +1,2106 @@
+# main committee
+# script to parse everything from Hansard
+#### good for everything up to 2012-06-28 (last day before main committee was renamed to federation chamber)
+
+# read in necessary packages
+library(XML)
+library(here)
+library(tidyverse)
+library(xml2)
+
+# for parsing question time
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+# define function for splitting interjections, which will be referenced in parse_hansard function
+
+split_interjections_maincomm <- function(main, interject, bus_start, q_in_writing, filename){
+  
+  #### step 1: add speech_no to make it easier to see where interjections happened 
+  main <- rowid_to_column(main, "speech_no")
+  
+  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
+  main_orig <- main
+  
+  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
+  
+  # start by re-formatting those with title of speaker or deputy speaker
+  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
+  if (nrow(interject)>0){
+    interject_names <- interject %>%
+      select(name) %>%
[…]

### 2023-02-28 scripts/99-everything-2012_to_2022-NEW.R

@@ -1,0 +1,1945 @@
+# script to parse everything from Hansard
+# WORKS FOR 2012-08-14 TO PRESENT (that day is when the federation chamber was renamed)
+
+# read in necessary packages
+library(XML)
+library(xml2)
+library(here)
+library(tidyverse)
+
+# for parsing question time
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+#all <- read.csv("/Volumes/Verbatim/all.csv")
+
+# define function for splitting interjections, which will be referenced in parse_hansard function
+
+split_interjections <- function(main, interject, bus_start, q_in_writing, filename){
+   
+  #### step 1: add speech_no to make it easier to see where interjections happened 
+  main <- rowid_to_column(main, "speech_no")
+  
+  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
+  main_orig <- main
+  
+  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
+  
+  # start by re-formatting those with title of speaker or deputy speaker
+  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
+  if (nrow(interject)>0){
+    interject_names <- interject %>%
+      select(name) %>%
[…]

### 2023-02-28 scripts/parse_question_time_new.R

@@ -1,0 +1,136 @@
+# trying method for pre 2011 on recent stuff, to deal with q/a issues
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+library(hms)
+
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+filename<-"2012-03-20.xml"
+
+hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
+
+################### QUESTIONS WITHOUT NOTICE ###################
+if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/question/talk.start/talker"))) > 0) {
+  
+  # grab all q and a content
+  q_wo_notice_content <- item_df(xml_df, "chamber.xscript//question | chamber.xscript//answer") %>% unnest(c(talk.text, talk.start)) %>% select(itemindex, talk.text)
+  
+  # grab all q and a info to merge with content
+  q_wo_notice_info <- item_df(xml_df, "chamber.xscript//question/talk.start/talker | chamber.xscript//answer/talk.start/talker") %>% unnest(everything())
+  
+  # left join by item index - questions without notice
+  q_wo_notice <- left_join(q_wo_notice_info, q_wo_notice_content, by="itemindex")
+  
+  # grab question text to flag for
[…]

### 2023-03-27 paper/paper-nature_format.qmd
minor edits

@@
   - Rohan Alexander^[University of Toronto, rohan.alexander@utoronto.ca]
-abstract: "Public knowledge of what is said in parliament is a key tenet of democracy, and a critical resource for political science research.
+abstract: "Public knowledge of what is said in parliament is a tenet of democracy, and a critical resource for political science research.
 In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard.
-While the Australian Hansard has always been publicly available, it has been difficult to use it for the purpose of large-scale macro and micro-level text analysis because it has not been available as a dataset of sufficient quality.
-Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard.
-The database is publicly available and can be readily linked to other datasets such as election results.
-The creation and accessibility of this database will enable the exploration of questions that are not currently possible to explore, serving as a valuable resource for both researchers and policymakers."
+While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro and micro-level text analysis because it has only been available as PDFs or XMLs.
+Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular, database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard.
+The database is publicly available and can be linked to other datasets such as election results.
+The creation and accessibility of this database enables the exploration of questions that have not been possible to explore, serving as a valuable resource for both researchers and policymakers."
 ---
@@
 The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
-Originating in the British parliament, the production of Hansard became tradition in a number of Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
+Originating in the British parliament, the production of Hansard became tradition in many Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
 Given the content and magnitude of these records, they have significance, particularly in the context of political science research.
-In the case of Canada, a team of researchers at the University of Toronto have digitized Hansard from 1901 to 2019, an endeavour called the Linked Parliamentary Data (LiPaD) project [@lipad].
+In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad].
 Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling.
-Following the lead of the LiPaD project, in this paper we introduce a novel database for the Australian Hansard.
-This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form which can be readily used by researchers.
+Following the lead of that project, in this paper we introduce a novel database for the Australian Hansard.
+This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
 With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.
 
-The House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
+The Australian House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
 1].
@@
 
-A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both static PDF and extensible markup language (XML) form.
-The PDF is the official release, which is converted to typed text using Optical Character Recognition (OCR) technology [@sherratt].
-This conversion allows for the production of the XML formatted transcript, though these are not always perfect conversions and are particularly flawed in the early decades of Hansard [@sherratt].
+A week or so after each sitting day, a transcript is available for download from the official Parliament of Australia website in both PDF and extensible markup language (XML) form.
+The PDF is the official release.
+For early decades there is a need to digitize PDFs using Optical Character Recognition (OCR) technology and there are many flaws [@sherratt].
 The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility.
 The nature of XML enables us to more easily use code to manipulate these records at scale, motivating our choice to develop our database solely using the XML formatted files.
-In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding if available.
+In cases where we were unsure on how to proceed with processing the XML, we defer first to the PDF, and then to the video recording of the proceeding, if available.
 
 At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis.
-To this point, various researchers have had to create their own databases in an attempt to produce usable, complete data based on content from the Australian Parliament website.
+To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website.
 For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files.
 These data can be navigated by year, parliament, people, and bills [@sherratt].
-In an effort to make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019.
-Further, @auspol created the `AustralianPoliticians` `R` package, which contains a number of datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
+To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019.
+Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
 
-A number of papers exist which utilize components of Australian Hansard to explore various research topics.
-For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where The Speaker tells that member to withdraw their remark.
+Many papers exist which use components of Australian Hansard to explore various research topics.
+For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where the Speaker tells that member to withdraw their remark.
 @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
@@
 
+> ```         
 >      <hansard>
@@
 >           b)  <answer>
+> ```
 
@@
 The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates.
-Debate nodes can contain a sub-debate 1 child-node which has a sub-debate 2 child-node nested within it.
-That said, sometimes sub-debate 2 is not nested within sub-debate 1.
+Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it.
+That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`.
 Each of these three elements (i.e.
@@
 
-**does this feel a bit repetitive? do you think it's worth keeping?**
-
-![Snapshot of beginning of XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}
+![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}
 
@@
 The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order.
-This first involved correcting the variable classes and adding a number of indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
+This first involved correcting the variable classes and adding serveral indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
 The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
@@
 
-Since we are looking at a wide time span of documents, there are expectedly a number of changes in the way they are formatted over time.
+Since we are looking at a wide time span of documents, there are many changes in the way they are formatted over time.
 These became apparent as we ran our script on XML files from earlier sitting days.
@@
 To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
-For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse actually exists in the file.
+For example, the entire Federation Chamber block of code is wrapped in an if-else statement for each script, so that it only executes if what the code attempts to parse exists in the file.
 
@@
 In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`.
-The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments and continuations.
+The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations.
 After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order.
@@
 To separate statements out correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found.
-After separating statements, we were later able remove these patterns from the body of text.
+After separating the statements, we were able to remove these patterns from the body of text.
 We also used this method of extracting and later removing unwanted patterns for other pieces of data which did not belong to the debate proceedings, such as sub-debate titles.
@@
 We then worked backwards in time and modified the code as needed for generalizability.
-Throughout this process we found a number of transcription errors present in the XMLs from earlier years.
+Throughout this process we found many transcription errors present in the XMLs from earlier years.
 We fixed these manually, deferring to the official release to ensure the correct information was filled in.
@@
 This allowed us to remove all the code which was needed to resolve specific transcription errors of the 2000s, to avoid an overly long script and in turn improving computational efficiency.
-As such, our fourth script is essentially the same as the third, the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.
+As such, our fourth script is essentially the same as the third, with the only difference being that it has code specific to fixing transcription errors from 1998 and 1999.
 
@@
 
-A key characteristic of the Australian parliament system is the ability for the executive government to be held accountable for their decisions.
+A key characteristic of the Australian parliamentary system is the ability for the executive government to be held accountable for their decisions.
 One core mechanism by which this is achieved is called Question Time.
-This is a period on each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
+This is a period of each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
 Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
@@
 For the third and fourth scripts, our method of parsing the `"chamber.xscript"` speeches meant that all questions without notice content was already parsed in order.
-Similar to the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
+Like the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
 Finally, since questions in writing exist in their own child node we were able to use the same parsing method for the third and fourth scripts as we did for the first and second scripts.
@@
 @fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
-Looking at the element names highlighted in blue, it is clear that these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
-However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later on.
+Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
+However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later.
 Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
@@
 When a Member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their first first name is written, while other times their entire first name is written.
+There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
 Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
@@
 
-[^2]: Sometimes when someones first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
+[^2]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
 
 Having these lists enabled us to extract the names of Members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns.
-We then used these extracted names to split all the speeches up, using a number of regular expressions with lookarounds.
+We then used these extracted names to split all the speeches up, using regular expressions with lookarounds.
 A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
@@
 We also wanted to add the gender and unique identifier for each individual as found in the `AustralianPoliticians` package.
-To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, party, gender and unique ID for that individual.
+To do so, we created a lookup table, which contained the unique incomplete form in which the name was transcribed, and the corresponding full name, name ID, electorate, party, gender, and unique ID for that individual.
 @fig-lookup provides an example of this.
@@
 
-Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender and unique ID information.
+Next, we merged our main dataframe with the lookup table to replace any incomplete names with their full names, and to fill in any gaps with available name ID, electorate, party, gender, and unique ID information.
 Finally, we were able to add a flag for interjections.

### 2023-03-30 scripts/99-everything-1998_to_1999-FINAL.R
version 2 scripts

@@ -1,0 +1,2415 @@
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+library(hms)
+
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+# all <- read.csv("/Volumes/Verbatim/all.csv")
+
+#hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", "1999-06-22.xml"))
+#xml_df <- read_xml(here("/Volumes/Verbatim/input/", "1998-12-10.xml"))
+
+filename<-"1999-03-25.xml"
+
+parse_hansard_1998 <- function(filename){ 
+  
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
+  
+  ######### BUSINESS START #########
+  # chamber
+  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F))>0) {
+    bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F), 
[…]

### 2023-03-30 scripts/99-everything-2012_to_2022-FINAL.R

@@ -1,0 +1,1972 @@
+# 2012 to 2022 new script, developed march 21, 2023
+# changing my approach to parsing so we don't have to merge stuff the way i originally had it
+# motivation - maintaining correct order
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+library(hms)
+
+# for parsing question time
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+split_interjections_fedchamb <- function(main, interject, filename){
+  
+  #### step 1: add speech_no to make it easier to see where interjections happened 
+  main <- rowid_to_column(main, "speech_no")
+  
+  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
+  main_orig <- main
+  
+  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
+  
+  # start by re-formatting those with title of speaker or deputy speaker
+  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
+  if (nrow(interject)>0){
+    interject_names <- interject %>%
+      select(name) %>%
+      filter(str_detect(name, "\\(The")) %>%
+      unique() %>%
+      mutate(name = str_remove(name, "[[:punct:]][[:space:]]MP|[[:space:]]MP"),
[…]

### 2023-03-30 scripts/csv_to_parquet.R

@@ -3,20 +3,46 @@ library(arrow)
 library(tidyverse)
 
 # grab list of all file names
-files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv")
+files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv-v2")
+
+files_all[i]
+fill_main(str_remove(files_all[i], "-v2"))
 
 # to loop through all our files
 for (i in 1:length(files_all)) {
   
   # read in file
-  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", files_all[i]), show_col_types = F)
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
   
   # modify variable classes
   thisFile <- thisFile %>% mutate(party = as.factor(party),
                                   gender = as.factor(gender))
   
+  stopifnot(ncol(thisFile)==21 & c("name", "order","speech_no","page.no", "time.stamp", "name.id", "electorate", "party", "in.gov", "first.speech",
+                                   "body", "fedchamb_flag", "sub1_flag", "sub2_flag","question", "answer", "q_in_writing", "div_flag", "gender", "uniqueID", "interject") %in% names(thisFile))
+  
+  stopifnot(str_detect(thisFile$order, "^\\d+$"))
+  
   # export as parquet file
-  write_parquet(thisFile, paste0("/Volumes/Verbatim/output/main-filled-parquet/", str_remove(files_all[i], "csv"), "parquet"))
+  write_parquet(thisFile, paste0("/Volumes/Verbatim/output/main-filled-parquet-v2/", str_remove(files_all[i], "csv"), "parquet"))
   
 }
 
+
+# just a final check that all column names are right etc
+# to loop through all our files
+for (i in 1:length(files_all)) {
+  
+  # read in file
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
+  
+  # modify variable classes
+  thisFile <- thisFile %>% mutate(party = as.factor(party),
+                                  gender = as.factor(gender))
+  
+  stopifnot(ncol(thisFile)==21 & c("name", "order","speech_no","page.no", "time.stamp", "name.id", "electorate", "party", "in.gov", "first.speech",
[…]

### 2023-03-30 scripts/data_validation.R

@@ -4,20 +4,23 @@ library(tidyverse)
 # read in ausPH and auspol dataset
 ausPH <- ausPH::getIndividuals()
 
+# for some reason ausPH wasn't working so i got data myself
+#ausPH <-rjson::fromJSON(file="/Volumes/Verbatim/lookup_tables/individuals.json")[["value"]]|>dplyr::bind_rows()
+
 all <- AustralianPoliticians::get_auspol('all')
 party <- AustralianPoliticians::get_auspol('allbyparty')
 mps <- AustralianPoliticians::get_auspol('mps')
 
 # read in my lookup table
-lookup <- read_csv("/Volumes/Verbatim/member_lookup.csv", show_col_types = F)
+lookup <- read_csv("/Volumes/Verbatim/lookup_tables/member_lookup.csv", show_col_types = F)
 
 # grab list of file names
-files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv")
+files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv-v2")
 
 ##### test 1 - date in filename must match one date in our list of dates from all session headers
 
 # grab session header csv - code to make this is in 01-session_info.R script
-session_headers <- read_csv("/Volumes/Verbatim/output/session_info/session_info_all.csv", show_col_types = F) %>% pull(date)
+session_headers <- read_csv("/Volumes/Verbatim/output/old-data/session_info/session_info_all.csv", show_col_types = F) %>% pull(date)
 
 # extract dates from file names, convert to date
 dates_all <- files_all %>% as_tibble() %>% mutate(value = as.Date(str_remove(value, "-main-v2.csv"))) %>% pull(value)
@@ -28,26 +31,20 @@ setdiff(as.character(dates_all), as.character(session_headers))
 # one difference - 2009-06-03
 # our filename is right, there is an error in the session header - it was transcribed as 2009-06-04, I checked official release to confirm we're right
 
-##### test 2 - equal number of flagged questions and answers
-# define empty tibble
+##### test 2 - checks whether two lines that immediately follow each other have the same "body" - NEW
 test2 <- tibble()
 
-# loop over all files
-for (i in 1:length(files_all)) {
+for(i in 1:length(files_all)) {
   # read in file
[…]

### 2023-03-30 scripts/fill_details.R

@@ -3,10 +3,8 @@
 library(tidyverse)
 
 # read in master lookup table
-master_orig <- read_csv("/Volumes/Verbatim/member_lookup.csv", show_col_types = F) 
-speaker_list <- read_csv("/Volumes/Verbatim/speaker_lookup.csv", show_col_types = F) %>% unique()
-
-# setdiff(ausPH %>% select(phid) %>% unique(), master %>% select(phid) %>% unique())
+master_orig <- read_csv("/Volumes/Verbatim/lookup_tables/member_lookup.csv", show_col_types = F) 
+speaker_list <- read_csv("/Volumes/Verbatim/lookup_tables/speaker_lookup.csv", show_col_types = F) %>% unique()
 
 # rename phid to match with hansard, and change parties to hansard abbreviations for consistency
 # these are from: https://www.aph.gov.au/Parliamentary_Business/Committees/Senate/woc/wocjanjun08/a02
@@ -31,7 +29,7 @@ speaker_list <- speaker_list %>%
                            party=="National Party of Australia" ~ "NATS"))
 
 # define file-name
-#filename <- "2022-09-07-main.csv"
+filename <- "2002-08-29-main.csv"
 
 fill_main <- function(filename) {
   
@@ -56,13 +54,13 @@ fill_main <- function(filename) {
   # read in file
   if (str_remove(filename, "-main.csv") > "2011-03-24") {
     # 2011-2022 (everything post name change from main committee to federation chamber)
-    thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-2011-2022/", filename), show_col_types = F)
+    thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-2011-2022-v2/", filename), show_col_types = F)
   } else if (str_remove(filename, "-main.csv") <= "2011-03-24" & str_remove(filename, "-main.csv") >= "2000-02-15") {
     # 2000-2011
-    thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-2000-2011/", filename), show_col_types = F)
+    thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-2000-2011-v2/", filename), show_col_types = F)
   } else if (str_remove(filename, "-main.csv") <= "1999-12-09") {
     # 1998-1999
-    thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-1998-1999/", filename), show_col_types = F)
[…]

### 2023-03-30 scripts/new_parsing_method.R

@@ -1,648 +1,0 @@
-# changing my approach to parsing so we don't have to merge stuff the way i originally had it
-# motivation - maintaining correct order
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# for parsing question time
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# define file name to parse
-filename<-"2011-05-11.xml"
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-
-# need to read the XML in in a different way for this so we can use the item_df function defined in global environment
-xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
-
-#################### CHAMBER ####################
-######### BUSINESS START #########
-# store business start in tibble, add flag for federation chamber, extract date, body, and start time
-# in rare cases (ex. 2016-08-30, there is no business start, so add if-else in case of this)
-if (nrow(tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"))))>0) {
-  bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start")), 
[…]

### 2023-03-30 scripts/old-versions/99-everything-2000_to_2011.R

@@ -1,4 +1,4 @@
-# works from 15 February 2000 10 May 2011
+# works from 15 February 2000 to 10 May 2011
 library(here)
 library(tidyverse)
 library(xml2)

### 2023-03-30 paper/paper-nature_format.qmd
paper updates

@@
 While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro and micro-level text analysis because it has only been available as PDFs or XMLs.
-Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular, database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard.
+Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard.
 The database is publicly available and can be linked to other datasets such as election results.
@@
 We will then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
+Finally, we will discuss the script we developed to fill in remaining missing speaker details, which each file in our database was passed to after being parsed and cleaned.
 
@@
 
-> ```         
 >          <hansard>
@@
 >               b)  <answer>
-> ```
 
@@
 @fig-xml1 provides an example of the beginning of an XML file for Hansard, which illustrates the structure outlined in the nested list above.
-As stated, the XML structure begins with a parent element `"hansard"` (highlighted in blue), followed by a child element `"session.header"` (highlighted in yellow) with sub-child elements such as the date and parliament number, which are all highlighted in pink.
-Next there is the child element containing everything that takes place in the Chamber, `"chamber.xscript"`, which is also highlighted in yellow in @fig-xml1.
-As previously mentioned, the first sub-node of `"chamber.xscript"` is the business start.
-The structure of the business start can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start are highlighted in orange.
+As stated, the XML structure begins with a parent element `<hansard>` (highlighted in blue), followed by a child element `<session.header>` (highlighted in yellow) with sub-child elements such as the date and parliament number, which are all highlighted in pink.
+Next there is the child element containing everything that takes place in the Chamber, `<chamber.xscript>`, which is also highlighted in yellow in @fig-xml1.
+As previously mentioned, the first sub-node of `<chamber.xscript>` is the business start.
+The structure of the business start can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start is highlighted in orange.
 
@@
 For example, the session header date in @fig-xml1 can be accessed using the XPath expression "`hansard/session.header/date`".
-We began our first script by parsing every piece of information contained in the XML document, using these unique XPath expressions to do so.
+When specifying an XPath expression, one can use an "or" operator to obtain elements from multiple node paths at once, in the order that they appear in the document.
+We did so throughout our script as we parsed uniquely nested speech content, as it allows for the correct ordering of elements to be maintained.
+We began our first script by parsing all the business start, speech text, and Question Time contents contained in the XML document, using these unique XPath expressions to do so.
+Hansard records contain a number of statements throughout that were not explicitly spoken in parliament.
+For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings.
+In contrast, the text which comes afterward was spoken aloud in parliament by The Speaker at 14:01.
+Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`.
+Importantly, in our work we focus primarily on parsing spoken speech content (i.e.
+what is nested within `<speech>` nodes), such as what is stated by The Speaker in @fig-content_ex.
+For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database.
+In future work, capturing this unspoken content in our database would be a priority.
 
-The next step was to further develop our script to produce tidy data sets containing each parsed element, where each statement is separated onto its own row with details about the speaker, and rows are placed in chronological order.
-This first involved correcting the variable classes and adding serveral indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
+![Snapshot from page 7129 of the PDF file for Hansard on 26 March 2013](images/content_ex.png){#fig-content_ex width="181"}
+
+The next step was to further develop our script to produce tidy data sets containing all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order.
+This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
 The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
@@
 Rather than this single child-node that contains all speech content, statements are categorized in individual child-nodes.
-This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`debate/speech/talk.text`" or "`debate/subdebate.1/speech/talk.text`" to extract all speeches, in their entirety, at once.
-This difference in nesting structure made our second script unusable for parsing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.
+This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`chamber.xscript//debate//speech/talk.text`" to extract all speeches, in their entirety, at once.
+This difference in nesting structure made many components of our second script unusable for processing transcripts preceding 10 May 2011, and required us to change our data processing approach considerably.
 
-Since there are numerous speeches in a typical Hansard, each having multiple child-nodes with the same names (i.e.
-`<continuation>`, `<interjection>`), it is difficult to parse everything while maintaining the correct ordering of statements.
-We found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly.
+Since the earlier Hansard XMLs do not have a `<talk.text>` node, we found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly.
 The reason we did not use its `<speech>` child-node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days.
-
 The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data.
@@
 This is a period of each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
-Parsing the components of Question Time required a slightly different approach than that of the debate speech, because of its unique structure in the XML document.
 Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
@@
 
-To parse questions without notice and questions in writing in the first two scripts, we extracted all question and answer elements from the `"chamber.xscript"` and `"answers.to.questions"` child nodes.
-For the third and fourth scripts, our method of parsing the `"chamber.xscript"` speeches meant that all questions without notice content was already parsed in order.
-Like the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
-Finally, since questions in writing exist in their own child node we were able to use the same parsing method for the third and fourth scripts as we did for the first and second scripts.
+Our approach to parse the `"chamber.xscript"` speeches used in all four scripts meant that all questions without notice content was already parsed in order.
+For the first two scripts, questions and answers were already separated onto their own rows.
+For the third and fourth scripts, just as we did with the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
+Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was simply to extract all question and answer elements from the `"answers.to.questions"` child node.
 
-We then added binary flags to differentiate between questions and answers, determined by which sub-child node the statement was extracted from, that is, whether it came from a `<question>` node, or an `<answer>` node.
+We then added binary flags to differentiate between questions and answers.
+To do this in the first and second scripts, we separately re-parsed question and answer content using the XPath expressions `"chamber.xscript//question"` and `"chamber.xscript//answer"`, added the correct question and answer flags accordingly, and then added those flags back to the main dataframe based on exact text matches.
+For the third and fourth scripts, we made use of the fact that the patterns preceding text transcribed under a question node were stored separately from those transcribed under an answer node.
+As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to.
 Sometimes, questions were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags using the `str_detect` function from the `stringr` package.
-For instance, our code for parsing questions searches for any statements which include "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer.
-Once all questions and answers were correctly classified as such, we could then merge all the content back together such that each question was followed by its associated answer.
-This was straightforward due to the fact that by nature of XML parsing, all questions and answers were parsed in the order in which they appeared in the transcript.
+For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer.
 
@@
 Doing so with the questions without notice content was straightforward.
-For the first and second scripts, we used the time stamp and page number associated with each question to maintain the correct order of statements.
-For the third and fourth scripts, our method of parsing meant that everything was already parsed together in order, so we did not have to perform any additional merging.
-While questions in writing do not contain time stamps, merging this content was also straightforward due to the fact that it is always at the very end of Hansard.
+As mentioned, our method of parsing meant that everything was already parsed together in order, so we did not have to perform any additional merging.
+For questions in writing, merging this content was also straightforward due to the fact that it is always at the very end of Hansard.
 This means that we could simply bind question in writing rows to the bottom of the main dataframe.
@@
 > # read in XML file
-> raw_ex <-  xmlParse(here("/Volumes/Verbatim/input/", "2021-11-30.xml"))
+> raw_ex <-  xmlParse(here("input/2021-11-30.xml"))
 > >
@@
 
+## Filling Missing Details
+
+While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e.
+"Mr Abbott" instead of "Abbott, Tony, MP").
+This was a particularly frequent occurrence for sitting days where a member spoke whose surname was shared by any other past or present member of parliament, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution.
+In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the speaker details in accordingly with data from the `AustralianPoliticians` package.
+This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details.
+Each file in our database passed through this script after being created, to ensure it is as complete as possible.
+
 # Data Records
@@
 
-# read in example csv
-main_ex <- read_csv("/Volumes/Verbatim/output/main-2000-2011/2003-08-14-main.csv", show_col_types = F)
-
 # create tibble with var names and descriptions
-main_ex_vars <- tibble("Variable" = names(main_ex),
+main_ex_vars <- tibble("Variable" = c("name",
+                                      "order",
+                                      "speech_no",
+                                      "page.no",
+                                      "time.stamp",
+                                      "name.id",
+                                      "electorate",
+                                      "party",
+                                      "in.gov",
+                                      "first.speech",
+                                      "body",
+                                      "fedchamb_flag",
+                                      "sub1_flag",
+                                      "sub2_flag",
+                                      "question",
+                                      "answer",
+                                      "q_in_writing",
+                                      "div_flag",
+                                      "gender",
+                                      "uniqueID",
+                                      "interject"),
        "Description" = c("Name of speaker",
@@
 
-**this paragraph is a bit repetitive and states everything found in the table, but i also feel like it's valuable to specify which ones we added and elaborate on their meaning. thoughts?**
-
-## Descriptive Statistics {#sec-stats}
-
 # Technical Validation
@@
 
-The second test checks that in each file, there is an equal number of flagged questions and answers.
-This test was motivated by the discrepancies in correct categorization of questions and answers we found when parsing Question Time, and allows us to check for the presence of any of these discrepancies which we have missed.
+The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e.
+spoken content).
+This test detected 129 dates on which duplicate statements were made, and one immediately follows the other.
+Note that this test does not account for who is making each statement, meaning one member repeating the words of another member would be picked up in this test as well.
+We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.
 
@@
 
+We thank Kristine Villaluna, Monica Alexander, and Jack Stephenson for helpful comments.
+
 # Author Contributions
+
+LK developed and implemented the code to obtain, create, and test, the datasets and wrote the first draft of the paper.
+RA conceptualized and designed the study, and contributed writing.
+Both authors approved the final version.
 

### 2023-03-30 paper/paper-nature_format.tex
paper updates

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{February 28, 2023}
+\date{March 30, 2023}
 
@@
 \begin{abstract}
-Public knowledge of what is said in parliament is a key tenet of
-democracy, and a critical resource for political science research. In
-Australia, following the British tradition, the written record of what
-is said in parliament is known as Hansard. While the Australian Hansard
-has always been publicly available, it has been difficult to use it for
-the purpose of large-scale macro and micro-level text analysis because
-it has not been available as a dataset of sufficient quality. Following
-the lead of the Linked Parliamentary Data project which achieved this
-for Canada, we provide a new, comprehensive, high-quality database that
-captures all proceedings of the Australian parliamentary debates from
-1998 to the present using Hansard. The database is publicly available
-and can be readily linked to other datasets such as election results.
-The creation and accessibility of this database will enable the
-exploration of questions that are not currently possible to explore,
-serving as a valuable resource for both researchers and policymakers.
+Public knowledge of what is said in parliament is a tenet of democracy,
+and a critical resource for political science research. In Australia,
+following the British tradition, the written record of what is said in
+parliament is known as Hansard. While the Australian Hansard has always
+been publicly available, it has been difficult to use for the purpose of
+large-scale macro and micro-level text analysis because it has only been
+available as PDFs or XMLs. Following the lead of the Linked
+Parliamentary Data project which achieved this for Canada, we provide a
+new, comprehensive, high-quality, rectangular database that captures all
+proceedings of the Australian parliamentary debates from 1998 to the
+present using Hansard. The database is publicly available and can be
+linked to other datasets such as election results. The creation and
+accessibility of this database enables the exploration of questions that
+have not been possible to explore, serving as a valuable resource for
+both researchers and policymakers.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, enhanced, sharp corners, frame hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi
 
@@
 questions. Originating in the British parliament, the production of
-Hansard became tradition in a number of Commonwealth countries such as
-Canada, the United Kingdom, and Australia (Vice and Farrell 2017). Given
-the content and magnitude of these records, they have significance,
+Hansard became tradition in many Commonwealth countries such as Canada,
+the United Kingdom, and Australia (Vice and Farrell 2017). Given the
+content and magnitude of these records, they have significance,
 particularly in the context of political science research. In the case
-of Canada, a team of researchers at the University of Toronto have
-digitized Hansard from 1901 to 2019, an endeavour called the Linked
-Parliamentary Data (LiPaD) project (Beelen et al. 2017). Having a
-digitized version of Hansard enables researchers to perform advanced
-analyses on these records using text analysis tools and statistical
-modelling. Following the lead of the LiPaD project, in this paper we
-introduce a novel database for the Australian Hansard. This is composed
-of individual datasets for each sitting day in the House of
+of Canada, the Hansard has been digitized for 1901 to 2019 (Beelen et
+al. 2017). Having a digitized version of Hansard enables researchers to
+perform advanced analyses on these records using text analysis tools and
+statistical modelling. Following the lead of that project, in this paper
+we introduce a novel database for the Australian Hansard. This is
+composed of individual datasets for each sitting day in the House of
 Representatives from 1998 to 2022, containing details on everything said
-in parliament in a form which can be readily used by researchers. With
+in parliament in a form that can be readily used by researchers. With
 the development of tools for large-scale text analysis, this database
@@
 
-The House of Representatives performs a number of crucial governmental
-functions, such as creating new laws and overseeing government
-expenditure (House of Representatives 2018, ch.~1). The House operates
-under a parallel chamber setup, meaning there are two debate venues
-where proceedings take place: the Chamber, and the Federation Chamber.
-Sittings of the House follow a predefined order of business, regulated
-by procedural rules called standing orders (House of Representatives
-2018, ch.~8). A typical sitting day in the Chamber has a number of
-scheduled proceedings including debates on government business, 90
-second member statements, and Question Time (House of Representatives
-2018, ch.~8). The Federation Chamber was created in 1994 as a
-subordinate debate venue of the Chamber. This allows for better time
-management of House business as its proceedings occur simultaneously
-with those of the Chamber (House of Representatives 2018, ch.~21).
-Sittings in the Federation Chamber are quite different to those of the
-Chamber in terms of their order of business and scope of discussion.
-Business matters discussed in the Federation Chamber are limited largely
-to intermediate stages of bill development, and the business of private
-Members (House of Representatives 2018, ch.~21). It is the recording and
-compilation of all of these proceedings on which Hansard is based, and
-it is essentially, but not entirely, verbatim.
+The Australian House of Representatives performs a number of crucial
+governmental functions, such as creating new laws and overseeing
+government expenditure (House of Representatives 2018, ch.~1). The House
+operates under a parallel chamber setup, meaning there are two debate
+venues where proceedings take place: the Chamber, and the Federation
+Chamber. Sittings of the House follow a predefined order of business,
+regulated by procedural rules called standing orders (House of
+Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
+number of scheduled proceedings including debates on government
+business, 90 second member statements, and Question Time (House of
+Representatives 2018, ch.~8). The Federation Chamber was created in 1994
+as a subordinate debate venue of the Chamber. This allows for better
+time management of House business as its proceedings occur
+simultaneously with those of the Chamber (House of Representatives 2018,
+ch.~21). Sittings in the Federation Chamber are quite different to those
+of the Chamber in terms of their order of business and scope of
+discussion. Business matters discussed in the Federation Chamber are
+limited largely to intermediate stages of bill development, and the
+business of private Members (House of Representatives 2018, ch.~21). It
+is the recording and compilation of all of these proceedings on which
+Hansard is based, and it is essentially, but not entirely, verbatim.
 
 A week or so after each sitting day, a transcript is available for
-download from the official Parliament of Australia website in both
-static PDF and extensible markup language (XML) form. The PDF is the
-official release, which is converted to typed text using Optical
-Character Recognition (OCR) technology (Sherratt 2016). This conversion
-allows for the production of the XML formatted transcript, though these
-are not always perfect conversions and are particularly flawed in the
-early decades of Hansard (Sherratt 2016). The PDF imposes formatting
-designed for humans to read with ease, whereas XML is designed for
-consistency and machine legibility. The nature of XML enables us to more
-easily use code to manipulate these records at scale, motivating our
-choice to develop our database solely using the XML formatted files. In
-cases where we were unsure on how to proceed with processing the XML, we
-defer first to the PDF, and then to the video recording of the
-proceeding if available.
+download from the official Parliament of Australia website in both PDF
+and extensible markup language (XML) form. The PDF is the official
+release. For early decades there is a need to digitize PDFs using
+Optical Character Recognition (OCR) technology and there are many flaws
+(Sherratt 2016). The PDF imposes formatting designed for humans to read
+with ease, whereas XML is designed for consistency and machine
+legibility. The nature of XML enables us to more easily use code to
+manipulate these records at scale, motivating our choice to develop our
+database solely using the XML formatted files. In cases where we were
+unsure on how to proceed with processing the XML, we defer first to the
+PDF, and then to the video recording of the proceeding, if available.
 
@@
 Australia website is not accessible for large scale analysis. To this
-point, various researchers have had to create their own databases in an
-attempt to produce usable, complete data based on content from the
-Australian Parliament website. For instance, Sherratt (2016) created an
-online, easy to read database of Hansard from 1901 to 1980 using the XML
-files. These data can be navigated by year, parliament, people, and
-bills (Sherratt 2016). In an effort to make the Australian Parliamentary
-Handbook more accessible, Leslie (2021) has released an \texttt{R}
-package which includes data on all Members of the Australian House of
-Representatives from 1945 to 2019. Further, Alexander and Hodgetts
-(2021) created the \texttt{AustralianPoliticians} \texttt{R} package,
-which contains a number of datasets related to the political and
-biographical information of Australian federal politicians who were
-active between 1901 and 2021.
-
-A number of papers exist which utilize components of Australian Hansard
-to explore various research topics. For example, Salisbury (2011) used
-online Hansard records to investigate the occurrences of unparliamentary
-comments by members of the House, where The Speaker tells that member to
+point, various researchers have had to create their own databases of
+usable, complete data based on content from the Australian Parliament
+website. For instance, Sherratt (2016) created an online, easy to read
+database of Hansard from 1901 to 1980 using the XML files. These data
+can be navigated by year, parliament, people, and bills (Sherratt 2016).
+To make the Australian Parliamentary Handbook more accessible, Leslie
+(2021) has released an \texttt{R} package which includes data on all
+Members of the Australian House of Representatives from 1945 to 2019.
+Further, Alexander and Hodgetts (2021) created the
+\texttt{AustralianPoliticians} \texttt{R} package, which contains
+several datasets related to the political and biographical information
+of Australian federal politicians who were active between 1901 and 2021.
+
+Many papers exist which use components of Australian Hansard to explore
+various research topics. For example, Salisbury (2011) used online
+Hansard records to investigate the occurrences of unparliamentary
+comments by members of the House, where the Speaker tells that member to
 withdraw their remark. Rasiah (2010) worked with Question Time data from
@@
 components of Hansard proceedings: Question Time, interjections, and
-stage directions.
+stage directions. Finally, we will discuss the script we developed to
+fill in remaining missing speaker details, which each file in our
+database was passed to after being parsed and cleaned.
 
@@
 the same, where the proceeding begins with a business start which is
-followed by a series of debates. Debate nodes can contain a sub-debate 1
-child-node which has a sub-debate 2 child-node nested within it. That
-said, sometimes sub-debate 2 is not nested within sub-debate 1. Each of
-these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
+followed by a series of debates. Debate nodes can contain a
+\texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
+\texttt{\textless{}subdebate.2\textgreater{}} child-node nested within
+it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
+is not nested within \texttt{\textless{}subdebate.1\textgreater{}}. Each
+of these three elements (i.e.~\texttt{\textless{}debate\textgreater{}},
 \texttt{\textless{}subdebate.1\textgreater{}}, and
@@
 list above. As stated, the XML structure begins with a parent element
-\texttt{"hansard"} (highlighted in blue), followed by a child element
-\texttt{"session.header"} (highlighted in yellow) with sub-child
-elements such as the date and parliament number, which are all
-highlighted in pink. Next there is the child element containing
-everything that takes place in the Chamber, \texttt{"chamber.xscript"},
-which is also highlighted in yellow in Figure~\ref{fig-xml1}. As
-previously mentioned, the first sub-node of \texttt{"chamber.xscript"}
+\texttt{\textless{}hansard\textgreater{}} (highlighted in blue),
+followed by a child element
+\texttt{\textless{}session.header\textgreater{}} (highlighted in yellow)
+with sub-child elements such as the date and parliament number, which
+are all highlighted in pink. Next there is the child element containing
+everything that takes place in the Chamber,
+\texttt{\textless{}chamber.xscript\textgreater{}}, which is also
+highlighted in yellow in Figure~\ref{fig-xml1}. As previously mentioned,
+the first sub-node of \texttt{\textless{}chamber.xscript\textgreater{}}
 is the business start. The structure of the business start can be seen
 between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
-the content we parse from the business start are highlighted in orange.
-
-\textbf{does this feel a bit repetitive? do you think it's worth
-keeping?}
+the content we parse from the business start is highlighted in orange.
 
@@
 
-\caption{\label{fig-xml1}Snapshot of beginning of XML file for Hansard
-on 25 February 2020}
+\caption{\label{fig-xml1}Snapshot of the beginning of the XML file for
+Hansard on 25 February 2020}
 
@@
 header date in Figure~\ref{fig-xml1} can be accessed using the XPath
-expression ``\texttt{hansard/session.header/date}''. We began our first
-script by parsing every piece of information contained in the XML
-document, using these unique XPath expressions to do so.
+expression ``\texttt{hansard/session.header/date}''. When specifying an
+XPath expression, one can use an ``or'' operator to obtain elements from
+multiple node paths at once, in the order that they appear in the
+document. We did so throughout our script as we parsed uniquely nested
+speech content, as it allows for the correct ordering of elements to be
+maintained. We began our first script by parsing all the business start,
+speech text, and Question Time contents contained in the XML document,
+using these unique XPath expressions to do so. Hansard records contain a
+number of statements throughout that were not explicitly spoken in
+parliament. For example, the text in Figure~\ref{fig-content_ex} beneath
+the bold subtitle ``Report from Federation Chamber'' is not attributed
+to a particular member and was not spoken aloud during the parliamentary
+proceedings. In contrast, the text which comes afterward was spoken
+aloud in parliament by The Speaker at 14:01. Generally, unspoken text is
+nested under \texttt{\textless{}debate.text\textgreater{}} or
+\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
+text is categorized under \texttt{\textless{}speech\textgreater{}}.
+Importantly, in our work we focus primarily on parsing spoken speech
+content (i.e.~what is nested within
+\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
+by The Speaker in Figure~\ref{fig-content_ex}. For this reason, many
+Hansard transcriptions which are not spoken text may not be captured in
+our database. In future work, capturing this unspoken content in our
+database would be a priority.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1.88542in,height=\textheight]{images/content_ex.png}
+
+}
+
+\caption{\label{fig-content_ex}Snapshot from page 7129 of the PDF file
+for Hansard on 26 March 2013}
+
+\end{figure}
 
 The next step was to further develop our script to produce tidy data
-sets containing each parsed element, where each statement is separated
-onto its own row with details about the speaker, and rows are placed in
-chronological order. This first involved correcting the variable classes
-and adding a number of indicator variables to differentiate where
-statements came from, such as Chamber versus Federation Chamber or
+sets containing all parsed text elements, where each statement is
+separated onto its own row with details about the speaker, and rows are
+maintained in chronological order. This first involved correcting the
+variable classes and adding several indicator variables to differentiate
+where statements came from, such as Chamber versus Federation Chamber or
 sub-debate 1 versus sub-debate 2. The next key task stemmed from the
@@
 
-Since we are looking at a wide time span of documents, there are
-expectedly a number of changes in the way they are formatted over time.
-These became apparent as we ran our script on XML files from earlier
-sitting days. Some changes are as subtle as a differently named
-child-node, while others are as extensive as a completely different
-nesting structure. Smaller changes were accounted for as we became aware
-of them, and embedded into the code in a way that would not cause issues
-for parsing more current Hansards with subtle differences in formatting.
-However, as mentioned, more significant changes in the XML structure of
-Hansard are what necessitated the development of separate scripts as we
-worked backwards in time. Further, while working backward in time, it
-became clear that not every sitting day contains every possible XML
-element. For example, some days did not have sub-debate 2 content, and
-some days did not have a Federation Chamber proceeding. To improve the
-generalizability of these scripts, if-else statements were embedded
-within the code wherever an error might arise due to a missing element.
-For example, the entire Federation Chamber block of code is wrapped in
-an if-else statement for each script, so that it only executes if what
-the code attempts to parse actually exists in the file.
+Since we are looking at a wide time span of documents, there are many
+changes in the way they are formatted over time. These became apparent
+as we ran our script on XML files from earlier sitting days. Some
+changes are as subtle as a differently named child-node, while others
+are as extensive as a completely different nesting structure. Smaller
+changes were accounted for as we became aware of them, and embedded into
+the code in a way that would not cause issues for parsing more current
+Hansards with subtle differences in formatting. However, as mentioned,
+more significant changes in the XML structure of Hansard are what
+necessitated the development of separate scripts as we worked backwards
+in time. Further, while working backward in time, it became clear that
+not every sitting day contains every possible XML element. For example,
+some days did not have sub-debate 2 content, and some days did not have
+a Federation Chamber proceeding. To improve the generalizability of
+these scripts, if-else statements were embedded within the code wherever
+an error might arise due to a missing element. For example, the entire
+Federation Chamber block of code is wrapped in an if-else statement for
+each script, so that it only executes if what the code attempts to parse
+exists in the file.
 
@@
 contains the entire contents of that speech --- including all
-interjections, comments and continuations. After the
+interjections, comments, and continuations. After the
 \texttt{\textless{}talk.text\textgreater{}} element closes, there are
@@
 for parsing more current Hansards, we cannot specify a single XPath
-expression such as ``\texttt{debate/speech/talk.text}'' or
-``\texttt{debate/subdebate.1/speech/talk.text}'' to extract all
+expression such as
+``\texttt{chamber.xscript//debate//speech/talk.text}'' to extract all
 speeches, in their entirety, at once. This difference in nesting
-structure made our second script unusable for parsing transcripts
-preceding 10 May 2011, and required us to change our data processing
-approach considerably.
-
-Since there are numerous speeches in a typical Hansard, each having
-multiple child-nodes with the same names
-(i.e.~\texttt{\textless{}continuation\textgreater{}},
-\texttt{\textless{}interjection\textgreater{}}), it is difficult to
-parse everything while maintaining the correct ordering of statements.
-We found that the most straightforward way to preserve the ordering of
-statements and to parse all speech contents at once was to parse from
-the \texttt{\textless{}debate\textgreater{}} element directly. The
-reason we did not use its \texttt{\textless{}speech\textgreater{}}
-child-node is because every speech has a unique structure of node
-children, and this makes it difficult to write code for data cleaning
-which is generalizable across all speeches and sitting days.
-
-The challenge with parsing through the
-\texttt{\textless{}debate\textgreater{}} element is that every piece of
-data stored in that element is parsed as a single string, including all
-\texttt{\textless{}talk.start\textgreater{}} data, and all nested
-sub-debate data. For example, the data shown in
+structure made many components of our second script unusable for
+processing transcripts preceding 10 May 2011, and required us to change
+our data processing approach considerably.
+
+Since the earlier Hansard XMLs do not have a
+\texttt{\textless{}talk.text\textgreater{}} node, we found that the most
+straightforward way to preserve the ordering of statements and to parse
+all speech contents at once was to parse from the
+\texttt{\textless{}debate\textgreater{}} element directly. The reason we
+did not use its \texttt{\textless{}speech\textgreater{}} child-node is
+because every speech has a unique structure of node children, and this
+makes it difficult to write code for data cleaning which is
+generalizable across all speeches and sitting days. The challenge with
+parsing through the \texttt{\textless{}debate\textgreater{}} element is
+that every piece of data stored in that element is parsed as a single
+string, including all \texttt{\textless{}talk.start\textgreater{}} data,
+and all nested sub-debate data. For example, the data shown in
 Figure~\ref{fig-patternEX} would be parsed as a single string preceding
@@
 split statements wherever one of these patterns was found. After
-separating statements, we were later able remove these patterns from the
-body of text. We also used this method of extracting and later removing
-unwanted patterns for other pieces of data which did not belong to the
-debate proceedings, such as sub-debate titles.
+separating the statements, we were able to remove these patterns from
+the body of text. We also used this method of extracting and later
+removing unwanted patterns for other pieces of data which did not belong
+to the debate proceedings, such as sub-debate titles.
 
@@
 backwards in time and modified the code as needed for generalizability.
-Throughout this process we found a number of transcription errors
-present in the XMLs from earlier years. We fixed these manually,
-deferring to the official release to ensure the correct information was
-filled in. Since there were a number of transcription errors specific to
-the 2000s, we chose to create a fourth script for parsing 1998 and 1999.
-This allowed us to remove all the code which was needed to resolve
-specific transcription errors of the 2000s, to avoid an overly long
-script and in turn improving computational efficiency. As such, our
-fourth script is essentially the same as the third, the only difference
-being that it has code specific to fixing transcription errors from 1998
-and 1999.
+Throughout this process we found many transcription errors present in
+the XMLs from earlier years. We fixed these manually, deferring to the
+official release to ensure the correct information was filled in. Since
+there were a number of transcription errors specific to the 2000s, we
+chose to create a fourth script for parsing 1998 and 1999. This allowed
+us to remove all the code which was needed to resolve specific
+transcription errors of the 2000s, to avoid an overly long script and in
+turn improving computational efficiency. As such, our fourth script is
+essentially the same as the third, with the only difference being that
+it has code specific to fixing transcription errors from 1998 and 1999.
 
@@
 
-A key characteristic of the Australian parliament system is the ability
-for the executive government to be held accountable for their decisions.
-One core mechanism by which this is achieved is called Question Time.
-This is a period on each sitting day in the Chamber where members of the
-House can ask ministers two types of questions: questions in writing
-which are written in advance, or questions without notice which are
-asked verbally in the Chamber and are responded to in real time (House
-of Representatives 2021). Parsing the components of Question Time
-required a slightly different approach than that of the debate speech,
-because of its unique structure in the XML document. Questions without
-notice are included directly in the \texttt{"chamber.xscript"} child
-node, with sub-child nodes called \texttt{"question"} and
-\texttt{"answer"} to differentiate the two. Questions in writing,
-however, are embedded in their own child node called
-\texttt{"answers.to.questions"} at the end of the XML file.
-
-To parse questions without notice and questions in writing in the first
-two scripts, we extracted all question and answer elements from the
-\texttt{"chamber.xscript"} and \texttt{"answers.to.questions"} child
-nodes. For the third and fourth scripts, our method of parsing the
-\texttt{"chamber.xscript"} speeches meant that all questions without
-notice content was already parsed in order. Similar to the rest of the
-speech content, we used those patterns of data preceding the text to
-separate questions and answers. Finally, since questions in writing
-exist in their own child node we were able to use the same parsing
-method for the third and fourth scripts as we did for the first and
-second scripts.
+A key characteristic of the Australian parliamentary system is the
+ability for the executive government to be held accountable for their
+decisions. One core mechanism by which this is achieved is called
+Question Time. This is a period of each sitting day in the Chamber where
+members of the House can ask ministers two types of questions: questions
+in writing which are written in advance, or questions without notice
+which are asked verbally in the Chamber and are responded to in real
+time (House of Representatives 2021). Questions without notice are
+included directly in the \texttt{"chamber.xscript"} child node, with
+sub-child nodes called \texttt{"question"} and \texttt{"answer"} to
+differentiate the two. Questions in writing, however, are embedded in
+their own child node called \texttt{"answers.to.questions"} at the end
+of the XML file.
+
+Our approach to parse the \texttt{"chamber.xscript"} speeches used in
+all four scripts meant that all questions without notice content was
+already parsed in order. For the first two scripts, questions and
+answers were already separated onto their own rows. For the third and
+fourth scripts, just as we did with the rest of the speech content, we
+used those patterns of data preceding the text to separate questions and
+answers. Finally, since questions in writing exist in their own child
+node we were able to use the same parsing method for all scripts, which
+was simply to extract all question and answer elements from the
+\texttt{"answers.to.questions"} child node.
 
 We then added binary flags to differentiate between questions and
-answers, determined by which sub-child node the statement was extracted
-from, that is, whether it came from a
-\texttt{\textless{}question\textgreater{}} node, or an
-\texttt{\textless{}answer\textgreater{}} node. Sometimes, questions were
-incorrectly transcribed under an answer node and vice-versa, in which
-cases we manually corrected the question and answer flags using the
-\texttt{str\_detect} function from the \texttt{stringr} package. For
-instance, our code for parsing questions searches for any statements
-which include ``has provided the following answer to the honourable
-member's question'', in which case we re-code that statement as an
-answer. Once all questions and answers were correctly classified as
-such, we could then merge all the content back together such that each
-question was followed by its associated answer. This was straightforward
-due to the fact that by nature of XML parsing, all questions and answers
-were parsed in the order in which they appeared in the transcript.
+answers. To do this in the first and second scripts, we separately
+re-parsed question and answer content using the XPath expressions
+\texttt{"chamber.xscript//question"} and
+\texttt{"chamber.xscript//answer"}, added the correct question and
+answer flags accordingly, and then added those flags back to the main
+dataframe based on exact text matches. For the third and fourth scripts,
+we made use of the fact that the patterns preceding text transcribed
+under a question node were stored separately from those transcribed
+under an answer node. As a result, we could readily use those patterns
+to flag questions and answers correctly based on which list of patterns
+it belonged to. Sometimes, questions were incorrectly transcribed under
+an answer node and vice-versa, in which cases we manually corrected the
+question and answer flags using the \texttt{str\_detect} function from
+the \texttt{stringr} package. For instance, we check for any statements
+flagged as questions which include the phrase ``has provided the
+following answer to the honourable member's question'', in which case we
+re-code that statement as an answer.
 
@@
 speech. Doing so with the questions without notice content was
-straightforward. For the first and second scripts, we used the time
-stamp and page number associated with each question to maintain the
-correct order of statements. For the third and fourth scripts, our
-method of parsing meant that everything was already parsed together in
-order, so we did not have to perform any additional merging. While
-questions in writing do not contain time stamps, merging this content
-was also straightforward due to the fact that it is always at the very
-end of Hansard. This means that we could simply bind question in writing
-rows to the bottom of the main dataframe. This approach was used for all
-four scripts.
+straightforward. As mentioned, our method of parsing meant that
+everything was already parsed together in order, so we did not have to
+perform any additional merging. For questions in writing, merging this
+content was also straightforward due to the fact that it is always at
+the very end of Hansard. This means that we could simply bind question
+in writing rows to the bottom of the main dataframe. This approach was
+used for all four scripts.
 
@@
 comment from The Deputy Speaker, and then the member continued their
-speech. Looking at the element names highlighted in blue, it is clear
-that these child-nodes do not contain the actual text for the
-interjection or continuation --- this text is embedded within the speech
-above it. However, as shown by the content highlighted in pink in
+speech. Looking at the element names highlighted in blue, these
+child-nodes do not contain the actual text for the interjection or
+continuation --- this text is embedded within the speech above it.
+However, as shown by the content highlighted in pink in
 Figure~\ref{fig-xml3}, we were able to extract useful details on the
-individual interjecting which we could use later on. Making use of this
+individual interjecting which we could use later. Making use of this
 structure, we extracted names and information of all individuals that
@@
 and/or last name. There is also variation in the capitalization of these
-names.\footnote{Sometimes when someones first name is included, only
+names.\footnote{Sometimes when someone's first name is included, only
   their last name is capitalized, while sometimes their full name is
@@
 of variation is in individuals with more than one first name, as
-sometimes only their first first name is written, while other times
+sometimes only their initial first name is written, while other times
 their entire first name is written. Additionally, some surnames have
@@
 matches with regular expression patterns. We then used these extracted
-names to split all the speeches up, using a number of regular
-expressions with lookarounds. A lookaround can be added to a regular
-expression pattern to enhance the specificity of matches. These were
-used to ensure that the text was not being split in the wrong places,
-such as places where Members were simply being named in the statement of
-another Member.
+names to split all the speeches up, using regular expressions with
+lookarounds. A lookaround can be added to a regular expression pattern
+to enhance the specificity of matches. These were used to ensure that
+the text was not being split in the wrong places, such as places where
+Members were simply being named in the statement of another Member.
 
@@
 transcribed, and the corresponding full name, name ID, electorate,
-party, gender and unique ID for that individual. Figure~\ref{fig-lookup}
-provides an example of this. We used the main dataset from the
-\texttt{AustralianPoliticians} package in the creation of each lookup
-table (Alexander and Hodgetts 2021).
+party, gender, and unique ID for that individual.
+Figure~\ref{fig-lookup} provides an example of this. We used the main
+dataset from the \texttt{AustralianPoliticians} package in the creation
+of each lookup table (Alexander and Hodgetts 2021).
 
@@
 incomplete names with their full names, and to fill in any gaps with
-available name ID, electorate, party, gender and unique ID information.
+available name ID, electorate, party, gender, and unique ID information.
 Finally, we were able to add a flag for interjections. Grouping our data
@@
 same approach across all four scripts.
+
+\hypertarget{filling-missing-details}{%
+\subsection{Filling Missing Details}\label{filling-missing-details}}
+
+While we did our best to maximize the completeness of the files in our
+database as they were processed in the initial four scripts, there were
+still a number of rows in which details on the person speaking were
+missing, or the name transcribed for that individual was in a short form
+(i.e.~``Mr Abbott'' instead of ``Abbott, Tony, MP''). This was a
+particularly frequent occurrence for sitting days where a member spoke
+whose surname was shared by any other past or present member of
+parliament, and automated filling of their details using data from the
+\texttt{AustralianPoliticians} package was avoided to prevent any
+incorrect detail attribution. In an effort to improve as many of these
+as possible, we developed a script which identifies short-form names
+belonging to people with common surnames in each CSV, looks for the full
+version of that individuals name if available in that same CSV file, and
+replaces the short-form name with the full name, and fills the rest of
+the speaker details in accordingly with data from the
+\texttt{AustralianPoliticians} package. This script does the same for
+anyone who does have a unique surname but is still missing the full name
+form or any gender, unique ID, name ID, party or electorate details.
+Each file in our database passed through this script after being
+created, to ensure it is as complete as possible.
 
@@
 
-\textbf{this paragraph is a bit repetitive and states everything found
-in the table, but i also feel like it's valuable to specify which ones
-we added and elaborate on their meaning. thoughts?}
-
-\hypertarget{sec-stats}{%
-\subsection{Descriptive Statistics}\label{sec-stats}}
-
 \hypertarget{technical-validation}{%
@@
 
-The second test checks that in each file, there is an equal number of
-flagged questions and answers. This test was motivated by the
-discrepancies in correct categorization of questions and answers we
-found when parsing Question Time, and allows us to check for the
-presence of any of these discrepancies which we have missed.
+The second test is designed to test for duplication errors in the data,
+by checking whether two lines that immediately follow each other have
+the same body (i.e.~spoken content). This test detected 129 dates on
+which duplicate statements were made, and one immediately follows the
+other. Note that this test does not account for who is making each
+statement, meaning one member repeating the words of another member
+would be picked up in this test as well. We checked a sample of 40\% of
+these duplicates, and manually validated that they are all repeated
+statements that do exist and are transcribed closely together in that
+day's XML file, and by our method should be parsed such that one of
+these statements is immediately followed by the other.
 
@@
 
+We thank Kristine Villaluna, Monica Alexander, and Jack Stephenson for
+helpful comments.
+
 \hypertarget{author-contributions}{%
 \section{Author Contributions}\label{author-contributions}}
+
+LK developed and implemented the code to obtain, create, and test, the
+datasets and wrote the first draft of the paper. RA conceptualized and
+designed the study, and contributed writing. Both authors approved the
+final version.
 

### 2023-03-30 paper/paper-nature_format.tex
updated zenodo link

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, sharp corners, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 data records are available on the general-purpose repository Zenodo, at
-https://doi.org/10.5281/zenodo.7336076 (Katz and Alexander 2022). For
+https://doi.org/10.5281/zenodo.7785767 (Katz and Alexander 2023). For
 each CSV file, each row contains an individual statement, with details
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-katz_2022}{}}%
-Katz, Lindsay, and Rohan Alexander. 2022. {``{A new, comprehensive
-database of all proceedings of the Australian Parliamentary Debates}.''}
-Zenodo. \url{https://doi.org/10.5281/zenodo.7336076}.
+\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
+Katz, Lindsay, and Rohan Alexander. 2023. {``{A new, comprehensive
+database of all proceedings of the Australian Parliamentary Debates
+(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7785767}.
 

### 2023-04-05 paper/paper-nature_format.qmd
updated zenodo link
Update the paper

@@
 In Australia, following the British tradition, the written record of what is said in parliament is known as Hansard.
-While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro and micro-level text analysis because it has only been available as PDFs or XMLs.
-Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular database that captures all proceedings of the Australian parliamentary debates from 1998 to the present using Hansard.
+While the Australian Hansard has always been publicly available, it has been difficult to use for the purpose of large-scale macro- and micro-level text analysis because it has only been available as PDFs or XMLs.
+Following the lead of the Linked Parliamentary Data project which achieved this for Canada, we provide a new, comprehensive, high-quality, rectangular database that captures proceedings of the Australian parliamentary debates from 1998 to 2022.
 The database is publicly available and can be linked to other datasets such as election results.
-The creation and accessibility of this database enables the exploration of questions that have not been possible to explore, serving as a valuable resource for both researchers and policymakers."
+The creation and accessibility of this database enables the exploration of new questions and serves as a valuable resource for both researchers and policymakers."
 ---
@@
 In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad].
-Having a digitized version of Hansard enables researchers to perform advanced analyses on these records using text analysis tools and statistical modelling.
-Following the lead of that project, in this paper we introduce a novel database for the Australian Hansard.
+Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling.
+Following the lead of that project, in this paper we introduce a similar database for Australia.
 This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
-With the development of tools for large-scale text analysis, this database will serve as a valuable resource for efficiently studying and exploring political behaviour in Australia over time.
+With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.
 
@@
 21].
-Sittings in the Federation Chamber are quite different to those of the Chamber in terms of their order of business and scope of discussion.
+Sittings in the Federation Chamber are different to those of the Chamber in terms of their order of business and scope of discussion.
 Business matters discussed in the Federation Chamber are limited largely to intermediate stages of bill development, and the business of private Members [@australia2018house, ch.
 21].
-It is the recording and compilation of all of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.
+It is the recording and compilation of these proceedings on which Hansard is based, and it is essentially, but not entirely, verbatim.
 
@@
 The PDF is the official release.
-For early decades there is a need to digitize PDFs using Optical Character Recognition (OCR) technology and there are many flaws [@sherratt].
 The PDF imposes formatting designed for humans to read with ease, whereas XML is designed for consistency and machine legibility.
@@
 @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
-In their work, @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
-Finally, the work of @alexander2021 offers a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
+@fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
+Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
 @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis.
@@
 While there is evidently a growing body of literature on this topic, there is still no comprehensive database for Australian Hansard based on XML that spans from 1901 to the present day.
-Our work serves to bridge this gap.
+Our work begins to bridge this gap.
 
@@
 
-Our database contains one comma-separated value (CSV) file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022.
-We developed four scripts to produce all of these files, where each script is designed to parse Hansard documents from a specific portion of the 1998 to 2022 time frame.
+Our database contains one comma-separated value (CSV) and one parquet file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022.
+We developed four scripts to produce these files.
+Each script parses Hansard documents from a specific portion of the 1998 to 2022 time frame.
 
-This section will be structured as follows.
-First, we will provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed all four scripts used to create our database.
+This section is structured as follows.
+First, we provide an overview of our approach to understanding and parsing an individual Hansard XML document, which informed the scripts used to create our database.
 This will be supplemented with an excerpt from a Hansard XML to provide a visual example of its structure.
-Next we will explain the specific differences between the four scripts, and outline what structural changes necessitated their separate development.
-We will then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
-Finally, we will discuss the script we developed to fill in remaining missing speaker details, which each file in our database was passed to after being parsed and cleaned.
+Next we will explain the specific differences between the scripts, and outline what structural changes necessitated their separate development.
+We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
+Finally, we discuss the script we developed to fill in remaining missing speaker details, which each file in our database was passed to after being parsed and cleaned.
 
@@
 
-The approach to parsing contents of an XML document is heavily dependent on its tree structure.
+The approach to parsing contents of an XML document depends on its tree structure.
 As such, to create this database, we started by looking at a single Hansard XML transcript from 2019.
@@
 Parsing was performed in `R` using the `XML` and `xml2` packages [@XML_pkg; @xml2_pkg].
-Focusing on one transcript also allowed us to ensure that all key components of the transcript were being parsed and captured with as much detail as possible.
+Focusing on one transcript also allowed us to ensure that all key components of the transcript were parsed and captured in as much detail as possible.
 The typical form of a Hansard XML transcript is summarized in the nested list below.
-Note that this provides a broad overview of the structure, and does not contain every possible nested element that may be found in a Hansard XML.
+This provides an overview, but does not contain every possible nested element that may be found in a Hansard XML.
 
@@
 Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings.
-Note that the Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file.
-The use of separate child nodes allows for the distinction of proceedings of the Chamber and Federation Chamber.
-The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with a business start which is followed by a series of debates.
+The Federation Chamber does not meet on every sitting day, so this child element is not present in every XML file.
+The use of separate child nodes allows for the distinction of proceedings between the Chamber and Federation Chamber.
+The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates.
 Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it.
@@
 As stated, the XML structure begins with a parent element `<hansard>` (highlighted in blue), followed by a child element `<session.header>` (highlighted in yellow) with sub-child elements such as the date and parliament number, which are all highlighted in pink.
-Next there is the child element containing everything that takes place in the Chamber, `<chamber.xscript>`, which is also highlighted in yellow in @fig-xml1.
-As previously mentioned, the first sub-node of `<chamber.xscript>` is the business start.
-The structure of the business start can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start is highlighted in orange.
+Next, there is the child element containing everything that takes place in the Chamber, `<chamber.xscript>`, which is also highlighted in yellow in @fig-xml1.
+As previously mentioned, the first sub-node of `<chamber.xscript>` is `<business.start>`.
+The structure of this can be seen between the nodes highlighted in green in @fig-xml1, where the content we parse from the business start is highlighted in orange.
 
@@
 Evidently, the nature of XML formatting means that different pieces of information are categorized under a series of uniquely named and nested nodes.
-As a result, to parse each piece of information, one must specify the unique hierarchy of nodes in which it is structured.
+As a result, to parse each piece of information, one must specify the unique hierarchy of the nodes in which it is structured.
 This is known as an XPath expression, and tells the parser how to navigate the XML document to obtain the desired information.
@@
 When specifying an XPath expression, one can use an "or" operator to obtain elements from multiple node paths at once, in the order that they appear in the document.
-We did so throughout our script as we parsed uniquely nested speech content, as it allows for the correct ordering of elements to be maintained.
+We did so throughout our script as we parsed uniquely nested speech content.
+This allows the correct ordering of elements to be maintained.
 We began our first script by parsing all the business start, speech text, and Question Time contents contained in the XML document, using these unique XPath expressions to do so.
-Hansard records contain a number of statements throughout that were not explicitly spoken in parliament.
-For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings.
-In contrast, the text which comes afterward was spoken aloud in parliament by The Speaker at 14:01.
-Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`.
-Importantly, in our work we focus primarily on parsing spoken speech content (i.e.
-what is nested within `<speech>` nodes), such as what is stated by The Speaker in @fig-content_ex.
-For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database.
-In future work, capturing this unspoken content in our database would be a priority.
 
-![Snapshot from page 7129 of the PDF file for Hansard on 26 March 2013](images/content_ex.png){#fig-content_ex width="181"}
-
-The next step was to further develop our script to produce tidy data sets containing all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order.
-This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or sub-debate 1 versus sub-debate 2.
+The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014.
+These contain all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order.
+This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus `<sub-debate.2>`.
 The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
@@
 As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak.
-Splitting up these speeches in a way which would be generalizable across sitting days required much thought and effort.
-@sec-interject will provide further details on the intricacies of this task.
+Further details on the intricacies of the task of splitting these speeches in a way that would be generalizable across sitting days are provided in @sec-interject.
 
-Since we are looking at a wide time span of documents, there are many changes in the way they are formatted over time.
+Since we are looking at a wide time span of documents, there are many changes in the way they are formatted.
 These became apparent as we ran our script on XML files from earlier sitting days.
@@
 Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting.
-However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards in time.
-Further, while working backward in time, it became clear that not every sitting day contains every possible XML element.
-For example, some days did not have sub-debate 2 content, and some days did not have a Federation Chamber proceeding.
+However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards.
+Further not every sitting day contains every possible XML element.
+For example, some days did not have `<sub-debate.2>` content, and some days did not have a Federation Chamber proceeding.
 To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
@@
 Once the script ran without error for a few recent years of Hansard, we continued to work backwards until extensive changes in tree structure made our script incompatible with parsing earlier XML files.
-The earliest sitting day our first script can successfully parse is 14 August 2012.
-Before developing new scripts to parse earlier Hansard documents, we decided to prioritize cleaning and finalizing what we have been able to parse.
+The earliest sitting day this first script can successfully parse is 14 August 2012.
+Before developing new scripts to parse earlier Hansard documents, we prioritized cleaning and finalizing what we had been able to parse.
 As such we continued building our script, fixing any problems we noticed in the resulting datasets such as excess whitespace or spacing issues, and splitting up any additional sections of the parsed text onto separate rows where necessary.
@@
 
-As previously mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents.
+As mentioned, we developed a total of four scripts to parse the 1998-2022 time frame of Hansard documents.
 Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts.
@@
 
-While the modifications needed to develop the second script were quite straightforward, this was not the case for our next script.
+While the modifications needed to develop the second script were straightforward, this was not the case for our next script.
 The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology.
@@
 For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node.
-These would contain details on the person who made each statement such as their party and electorate.
+These would contain details on the person who made each statement, such as their party and electorate.
 
@@
 This was not isolated to just the beginning of speeches --- details on individuals interjecting or commenting during speeches were also captured this way.
-To separate statements out correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found.
+To separate statements correctly, we collected all of these patterns using the `<talk.start>` node, and used them to split statements wherever one of these patterns was found.
 After separating the statements, we were able to remove these patterns from the body of text.
@@
 For the third and fourth scripts, just as we did with the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
-Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was simply to extract all question and answer elements from the `"answers.to.questions"` child node.
+Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was to extract all question and answer elements from the `"answers.to.questions"` child node.
 
@@
 As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to.
-Sometimes, questions were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags using the `str_detect` function from the `stringr` package.
+Sometimes, questions were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags.
 For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer.
@@
 The next step was to merge Question Time contents with all the debate speech.
-Doing so with the questions without notice content was straightforward.
-As mentioned, our method of parsing meant that everything was already parsed together in order, so we did not have to perform any additional merging.
-For questions in writing, merging this content was also straightforward due to the fact that it is always at the very end of Hansard.
-This means that we could simply bind question in writing rows to the bottom of the main dataframe.
+Our method of parsing meant that everything was already in order, so we did not have to perform any additional merging.
+For questions in writing, merging this content was also straightforward due to the fact that it is always at the end of Hansard.
+This means that we could bind question in writing rows to the bottom of the main dataframe.
 This approach was used for all four scripts.
@@
 
-Below is an example of part of a speech we would need to split, extracted from Hansard on 30 November 2021, where Mr.
-van Manen is interrupted by The Speaker who states that the time for members' statements has concluded.
+Below is an example of part of a speech we would need to split, extracted from Hansard on 30 November 2021, where Bert van Manen is interrupted by the Speaker who states that the time for members' statements has concluded.
 
@@
 As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech.
-@fig-xml3 provides an example of this, where the speech was interrupted by a comment from The Deputy Speaker, and then the member continued their speech.
+@fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the member continued their speech.
 Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
@@
 Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
-We stored this as a dataframe called `"interject"`.[^1]
-
-[^1]: We decided not to include this data in our final database, as it is all embedded in our resulting datasets which have a flag for interjections.
+We stored this as a dataframe called `"interject"`.
+We decided not to include this data in our final database, as it is embedded in our resulting datasets which have a flag for interjections.
 
@@
 We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
-We added the names of all Members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
-When a Member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
+We added the names of all members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
+When a member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
 There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
 Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
-This variation demands careful consideration when writing regular expression patterns to search for in the text.
-In these lists we also accounted for any general interjection statements transcribed that were not attributed to an individual, such as "An opposition member interjecting-".
+This variation demands careful consideration when writing regular expression patterns.
+In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".
 
@@
 
-Having these lists enabled us to extract the names of Members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns.
-We then used these extracted names to split all the speeches up, using regular expressions with lookarounds.
+Having these lists enabled us to extract the names of members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns.
+We then used these extracted names to split all the speeches, using regular expressions with lookarounds.
 A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
-These were used to ensure that the text was not being split in the wrong places, such as places where Members were simply being named in the statement of another Member.
+These were used to ensure that the text was not being split in the wrong places, such as places where members were being named in the statement of another member.
 
@@
 Finally, we were able to add a flag for interjections.
-Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not The Speaker, The Deputy Speaker, or the Member whose turn it was to speak.
+Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not the Speaker, the Deputy Speaker, or the member whose turn it was to speak.
 @fig-interject provides an example of a Federation Chamber proceeding with interjections.
-Evidently, statements made by the original speaker Stuart Robert or by The Deputy Speaker Maria Vamvakinou are not flagged as interjections.
+Statements made by the member whose turn it was to speak, or by the Deputy Speaker Maria Vamvakinou, are not flagged as interjections.
 
@@
 In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process.
-This meant that we did not need to create lists of names and titles to search for in the text as we did before.
-However, we used the same list of general interjection statements to separate on that was used in the first two scripts.
+This meant that we did not need to create lists of names and titles for which to search in the text as we did before.
+However, we used the same list of general interjection statements on which to separate as was used in the first two scripts.
 We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^3]
@@
 Stage directions are general statements included in the transcript to document happenings in parliament.
-Examples of stage directions are "Bill read a second time", "Question agreed to" or "Debate adjourned".
+Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned".
 It was unclear to us from the XML and PDF who exactly these statements were attributed to.
-For further clarification, we watched portions of the video recording for some sitting days, and noticed that where these statements are documented in Hansard, they are not explicitly stated in parliament.
-For example, when The Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
+For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament.
+For example, when the Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
 This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
@@
 For this reason, we filled the name variable for these statements with "stage direction".
-Note that stage directions were not flagged as interjections.
+Stage directions were not flagged as interjections.
 These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches.
-We have built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.
+We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.
 
@@
 
-Our database contains 1517 CSV files, covering all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022.
-All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336076 [@katz_2022].
-For each CSV file, each row contains an individual statement, with details on the individual speaking.
-Of course, for general statements transcribed as made by "Honourable members" for example, these variables cannot be specified.
+Our database is available in both CSV and parquet formats.
+It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022.
+So there are 1,517 files for each format.
+All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336075 [@katz_2023].
+For each file, each row contains an individual statement, with details on the individual speaking.
+For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified.
 @tbl-vars provides an overview of each variable found in the database.
@@
 
-We developed a script to perform seven automated tests on each file in our database, in an effort to enhance its quality and consistency.
+We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency.
 Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
@@
 
+# Next Steps
+
+While our database makes a substantial contribution to the field, there are a few areas for future development.
+
+One important contribution would be to take advantage of similar records that exist for the Senate over this same period and add them to our database.
+The main challenge of this would be accounting for different parliamentarians, but the broad structures would be similar.
+
+Earlier House of Representatives records also exist. In some cases it is difficult to get XML records for certain dates, and the earlier decades would require more cleaning.
+
+Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament.
+For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings.
+In contrast, the text which comes afterward was spoken aloud in parliament by The Speaker at 14:01.
+Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`.
+Importantly, in our work we focus primarily on parsing spoken speech content (i.e.
+what is nested within `<speech>` nodes), such as what is stated by The Speaker in @fig-content_ex.
+For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database.
+In future work, capturing this unspoken content in our database would be a priority.
+
+![Snapshot from page 7129 of the PDF file for Hansard on 26 March 2013](images/content_ex.png){#fig-content_ex width="181"}
+
 # Usage Notes {#sec-usage}

### 2023-04-05 paper/paper-nature_format.qmd
small edits

@@
 These contain all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order.
-This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus `<sub-debate.2>`.
+This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus`\<sub-debate.2\>\`.
 The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
@@
 As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak.
-Further details on the intricacies of the task of splitting these speeches in a way that would be generalizable across sitting days are provided in @sec-interject.
+There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days.
+Details on these are provided in @sec-interject.
 
@@
 When a member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.[^2] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
+There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
 Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
@@
 
-[^2]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
+[^1]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
 
@@
 However, we used the same list of general interjection statements on which to separate as was used in the first two scripts.
-We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^3]
+We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^2]
 
-[^3]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
+[^2]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
 
@@
 Our database is available in both CSV and parquet formats.
-It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022.
-So there are 1,517 files for each format.
+It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are 1,517 files for each format.
 All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336075 [@katz_2023].
@@
 We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency.
-Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
+Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^3] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
 We validated that our file name and date was correct by checking the official PDF release from that sitting day.
 
-[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
+[^3]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
 

### 2023-04-05 paper/paper-nature_format.qmd
added to next steps

@@
 One important contribution would be to take advantage of similar records that exist for the Senate over this same period and add them to our database.
-The main challenge of this would be accounting for different parliamentarians, but the broad structures would be similar.
+The main challenge of this would be accounting for different parliamentarians, but the broad structures would be similar, making many elements of our code and methodology applicable to this work.
 
-Earlier House of Representatives records also exist. In some cases it is difficult to get XML records for certain dates, and the earlier decades would require more cleaning.
+Earlier House of Representatives records also exist, and would be valuable to include in future versions of our database.
+In some cases however it is difficult to get XML records for certain dates, and the earlier decades would require more cleaning and likely additional script development to account for changes in structural formatting.
+
+Having completed this work, we recognize components of our scripts which could be developed in a more computationally efficient manner such as our approach to splitting interjections and filling in MP details.
+In future, it would be beneficial to review our methodological approach to these steps, and consider approaches which are more concise where appropriate.
 

### 2023-04-05 paper/paper-nature_format.qmd
more paper edits

@@
 We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
-Finally, we discuss the script we developed to fill in remaining missing speaker details, which each file in our database was passed to after being parsed and cleaned.
+Finally, we discuss the script we developed to fill in remaining missing details on the member of parliament speaking, which each file in our database was passed to after being parsed and cleaned.
 
@@
 The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate.
-A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the speaker and the time of their first statement.
+A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the member of parliament whose turn it is to speak and the time of their first statement.
 Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations.
@@
 The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014.
-These contain all parsed text elements, where each statement is separated onto its own row with details about the speaker, and rows are maintained in chronological order.
-This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<sub-debate.1> versus`\<sub-debate.2\>\`.
+These contain all parsed text elements, where each statement is separated onto its own row with details about the member of parliament who is speaking, and rows are maintained in chronological order.
+This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`.
 The next key task stemmed from the fact that the raw text data were not separated by each statement when parsed.
-In other words, any interjections, comments made by The Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
+In other words, any interjections, comments made by the Speaker or Deputy Speaker and continuations within an individual speech were all parsed together as a single string.
 As such, the name, name ID, electorate and party details were only provided for the person whose turn it was to speak.
@@
 Further not every sitting day contains every possible XML element.
-For example, some days did not have `<sub-debate.2>` content, and some days did not have a Federation Chamber proceeding.
+For example, some days did not have `<subdebate.2>` content, and some days did not have a Federation Chamber proceeding.
 To improve the generalizability of these scripts, if-else statements were embedded within the code wherever an error might arise due to a missing element.
@@
 
-We then proceeded to clean up speeches and fill in correct speaker details.
-While we used the same lookup table approach as before, we did so in combination with another means of filling in speaker details.
-The patterns parsed from `<talk.start>` nodes contain important data on the speaker of each statement.
-As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `<talk.start/talker>`.
+We then proceeded to clean up speeches and fill in correct details on the member of parliament speaking.
+While we used the same lookup table approach as before, we did so in combination with another means of filling in these details.
+The patterns parsed from `<talk.start>` nodes contain important data on the member of parliament making each statement.
+As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `"talk.start/talker"`.
 We created a pattern lookup table with these data, and merged it with the main Hansard dataframe by the first pattern detected in each statement.
 @fig-patterns provides an example of that lookup table.
-This approach enabled us to fill in missing data on each speaker using data extracted directly from the XML.
+This approach enabled us to fill in missing data on each member of parliament speaking using data extracted directly from the XML.
 Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.
@@
 This was a particularly frequent occurrence for sitting days where a member spoke whose surname was shared by any other past or present member of parliament, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution.
-In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the speaker details in accordingly with data from the `AustralianPoliticians` package.
+In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package.
 This script does the same for anyone who does have a unique surname but is still missing the full name form or any gender, unique ID, name ID, party or electorate details.
@@
 We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament.
-Using these dates, we check that each person speaking on each sitting day is in fact a Member of Parliament on that day.
+Using these dates, we check that each person speaking on each sitting day is in fact a member of parliament on that day.
 
@@
 For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings.
-In contrast, the text which comes afterward was spoken aloud in parliament by The Speaker at 14:01.
+In contrast, the text which comes afterward was spoken aloud in parliament by the Speaker at 14:01.
 Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`.
 Importantly, in our work we focus primarily on parsing spoken speech content (i.e.
-what is nested within `<speech>` nodes), such as what is stated by The Speaker in @fig-content_ex.
+what is nested within `<speech>` nodes), such as what is stated by the Speaker in @fig-content_ex.
 For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database.
@@
 
-Further, the `name.id` variable found in each CSV is another unique identifier for each Member of Parliament.
+Further, the `name.id` variable found in each CSV is another unique identifier for each member of parliament.
 This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook.
 As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus].
-This will allow for convenient extraction of further details on each Member of Parliament in a tidy, ready to analyze format.
+This will allow for convenient extraction of further details on each member of parliament in a tidy, ready to analyze format.
 

### 2023-04-05 paper/paper-nature_format.tex
more paper edits

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{March 30, 2023}
+\date{April 5, 2023}
 
@@
 been publicly available, it has been difficult to use for the purpose of
-large-scale macro and micro-level text analysis because it has only been
-available as PDFs or XMLs. Following the lead of the Linked
+large-scale macro- and micro-level text analysis because it has only
+been available as PDFs or XMLs. Following the lead of the Linked
 Parliamentary Data project which achieved this for Canada, we provide a
-new, comprehensive, high-quality, rectangular database that captures all
-proceedings of the Australian parliamentary debates from 1998 to the
-present using Hansard. The database is publicly available and can be
-linked to other datasets such as election results. The creation and
-accessibility of this database enables the exploration of questions that
-have not been possible to explore, serving as a valuable resource for
-both researchers and policymakers.
+new, comprehensive, high-quality, rectangular database that captures
+proceedings of the Australian parliamentary debates from 1998 to 2022.
+The database is publicly available and can be linked to other datasets
+such as election results. The creation and accessibility of this
+database enables the exploration of new questions and serves as a
+valuable resource for both researchers and policymakers.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, sharp corners, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 al. 2017). Having a digitized version of Hansard enables researchers to
-perform advanced analyses on these records using text analysis tools and
-statistical modelling. Following the lead of that project, in this paper
-we introduce a novel database for the Australian Hansard. This is
-composed of individual datasets for each sitting day in the House of
-Representatives from 1998 to 2022, containing details on everything said
-in parliament in a form that can be readily used by researchers. With
-the development of tools for large-scale text analysis, this database
-will serve as a valuable resource for efficiently studying and exploring
+conduct text analysis and statistical modelling. Following the lead of
+that project, in this paper we introduce a similar database for
+Australia. This is composed of individual datasets for each sitting day
+in the House of Representatives from 1998 to 2022, containing details on
+everything said in parliament in a form that can be readily used by
+researchers. With the development of tools for large-scale text
+analysis, this database will serve as a resource for understanding
 political behaviour in Australia over time.
@@
 simultaneously with those of the Chamber (House of Representatives 2018,
-ch.~21). Sittings in the Federation Chamber are quite different to those
-of the Chamber in terms of their order of business and scope of
-discussion. Business matters discussed in the Federation Chamber are
-limited largely to intermediate stages of bill development, and the
-business of private Members (House of Representatives 2018, ch.~21). It
-is the recording and compilation of all of these proceedings on which
-Hansard is based, and it is essentially, but not entirely, verbatim.
+ch.~21). Sittings in the Federation Chamber are different to those of
+the Chamber in terms of their order of business and scope of discussion.
+Business matters discussed in the Federation Chamber are limited largely
+to intermediate stages of bill development, and the business of private
+Members (House of Representatives 2018, ch.~21). It is the recording and
+compilation of these proceedings on which Hansard is based, and it is
+essentially, but not entirely, verbatim.
 
@@
 and extensible markup language (XML) form. The PDF is the official
-release. For early decades there is a need to digitize PDFs using
-Optical Character Recognition (OCR) technology and there are many flaws
-(Sherratt 2016). The PDF imposes formatting designed for humans to read
-with ease, whereas XML is designed for consistency and machine
-legibility. The nature of XML enables us to more easily use code to
-manipulate these records at scale, motivating our choice to develop our
-database solely using the XML formatted files. In cases where we were
-unsure on how to proceed with processing the XML, we defer first to the
-PDF, and then to the video recording of the proceeding, if available.
+release. The PDF imposes formatting designed for humans to read with
+ease, whereas XML is designed for consistency and machine legibility.
+The nature of XML enables us to more easily use code to manipulate these
+records at scale, motivating our choice to develop our database solely
+using the XML formatted files. In cases where we were unsure on how to
+proceed with processing the XML, we defer first to the PDF, and then to
+the video recording of the proceeding, if available.
 
@@
 Hansard transcripts during February and March of 2003, to investigate
-resistance of politicians in answering questions about Iraq. In their
-work, Fraussen, Graham, and Halpin (2018) use Hansard to quantify
-political prominence by investigating strategic mentions of interest
-groups by elected officials. Finally, the work of Alexander and
-Alexander (2021) offers a dataset of the Australian Hansard, along with
-an analysis of the effect of elections and changes in Prime Ministers
-upon topics mentioned in parliament. Alexander and Alexander (2021)
-created this database with the static PDF versions of Hansard, using OCR
-to digitize these files into text which is suitable for analysis. This
-means there are considerable digitization errors especially in the first
-half of the dataset.
+resistance of politicians in answering questions about Iraq. Fraussen,
+Graham, and Halpin (2018) use Hansard to quantify political prominence
+by investigating strategic mentions of interest groups by elected
+officials. Finally, Alexander and Alexander (2021) construct a dataset
+of the Australian Hansard, along with an analysis of the effect of
+elections and changes in Prime Ministers upon topics mentioned in
+parliament. Alexander and Alexander (2021) created this database with
+the static PDF versions of Hansard, using OCR to digitize these files
+into text which is suitable for analysis. This means there are
+considerable digitization errors especially in the first half of the
+dataset.
 
@@
 there is still no comprehensive database for Australian Hansard based on
-XML that spans from 1901 to the present day. Our work serves to bridge
+XML that spans from 1901 to the present day. Our work begins to bridge
 this gap.
@@
 
-Our database contains one comma-separated value (CSV) file for each
-sitting day of the House of Representatives from 02 March 1998 to 08
-September 2022. We developed four scripts to produce all of these files,
-where each script is designed to parse Hansard documents from a specific
-portion of the 1998 to 2022 time frame.
-
-This section will be structured as follows. First, we will provide an
-overview of our approach to understanding and parsing an individual
-Hansard XML document, which informed all four scripts used to create our
-database. This will be supplemented with an excerpt from a Hansard XML
-to provide a visual example of its structure. Next we will explain the
-specific differences between the four scripts, and outline what
-structural changes necessitated their separate development. We will then
-provide details on the methodological intricacies of three core
-components of Hansard proceedings: Question Time, interjections, and
-stage directions. Finally, we will discuss the script we developed to
-fill in remaining missing speaker details, which each file in our
+Our database contains one comma-separated value (CSV) and one parquet
+file for each sitting day of the House of Representatives from 02 March
+1998 to 08 September 2022. We developed four scripts to produce these
+files. Each script parses Hansard documents from a specific portion of
+the 1998 to 2022 time frame.
+
+This section is structured as follows. First, we provide an overview of
+our approach to understanding and parsing an individual Hansard XML
+document, which informed the scripts used to create our database. This
+will be supplemented with an excerpt from a Hansard XML to provide a
+visual example of its structure. Next we will explain the specific
+differences between the scripts, and outline what structural changes
+necessitated their separate development. We then provide details on the
+methodological intricacies of three core components of Hansard
+proceedings: Question Time, interjections, and stage directions.
+Finally, we discuss the script we developed to fill in remaining missing
+details on the member of parliament speaking, which each file in our
 database was passed to after being parsed and cleaned.
@@
 
-The approach to parsing contents of an XML document is heavily dependent
-on its tree structure. As such, to create this database, we started by
-looking at a single Hansard XML transcript from 2019. Doing so enabled
-us to identify the various components of interest in the document, and
-how each one can be parsed according to its corresponding structural
-form. Parsing was performed in \texttt{R} using the \texttt{XML} and
-\texttt{xml2} packages (Temple Lang 2022; Wickham, Hester, and Ooms
-2021). Focusing on one transcript also allowed us to ensure that all key
-components of the transcript were being parsed and captured with as much
-detail as possible. The typical form of a Hansard XML transcript is
-summarized in the nested list below. Note that this provides a broad
-overview of the structure, and does not contain every possible nested
-element that may be found in a Hansard XML.
+The approach to parsing contents of an XML document depends on its tree
+structure. As such, to create this database, we started by looking at a
+single Hansard XML transcript from 2019. Doing so enabled us to identify
+the various components of interest in the document, and how each one can
+be parsed according to its corresponding structural form. Parsing was
+performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
+packages (Temple Lang 2022; Wickham, Hester, and Ooms 2021). Focusing on
+one transcript also allowed us to ensure that all key components of the
+transcript were parsed and captured in as much detail as possible. The
+typical form of a Hansard XML transcript is summarized in the nested
+list below. This provides an overview, but does not contain every
+possible nested element that may be found in a Hansard XML.
 
@@
 \texttt{\textless{}answers.to.questions\textgreater{}} contains Question
-Time proceedings. Note that the Federation Chamber does not meet on
-every sitting day, so this child element is not present in every XML
-file. The use of separate child nodes allows for the distinction of
-proceedings of the Chamber and Federation Chamber. The structure of the
+Time proceedings. The Federation Chamber does not meet on every sitting
+day, so this child element is not present in every XML file. The use of
+separate child nodes allows for the distinction of proceedings between
+the Chamber and Federation Chamber. The structure of the
 \texttt{\textless{}chamber.xscript\textgreater{}} and
 \texttt{\textless{}fedchamb.xscript\textgreater{}} nodes are generally
-the same, where the proceeding begins with a business start which is
-followed by a series of debates. Debate nodes can contain a
+the same, where the proceeding begins with
+\texttt{\textless{}business.start\textgreater{}} which is followed by a
+series of debates. Debate nodes can contain a
 \texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
@@
 \texttt{\textless{}talk.start\textgreater{}} sub-node, providing
-information on the speaker and the time of their first statement.
-Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate
-settings --- they are often composed of a series of interjections and
-continuations. These statements are categorized under different
-sub-nodes depending on their nature, such as
-\texttt{\textless{}interjection\textgreater{}} or
+information on the member of parliament whose turn it is to speak and
+the time of their first statement. Unsurprisingly, speeches rarely go
+uninterrupted in parliamentary debate settings --- they are often
+composed of a series of interjections and continuations. These
+statements are categorized under different sub-nodes depending on their
+nature, such as \texttt{\textless{}interjection\textgreater{}} or
 \texttt{\textless{}continuation\textgreater{}}. The final key component
@@
 with sub-child elements such as the date and parliament number, which
-are all highlighted in pink. Next there is the child element containing
+are all highlighted in pink. Next, there is the child element containing
 everything that takes place in the Chamber,
@@
 the first sub-node of \texttt{\textless{}chamber.xscript\textgreater{}}
-is the business start. The structure of the business start can be seen
-between the nodes highlighted in green in Figure~\ref{fig-xml1}, where
-the content we parse from the business start is highlighted in orange.
+is \texttt{\textless{}business.start\textgreater{}}. The structure of
+this can be seen between the nodes highlighted in green in
+Figure~\ref{fig-xml1}, where the content we parse from the business
+start is highlighted in orange.
 
@@
 nodes. As a result, to parse each piece of information, one must specify
-the unique hierarchy of nodes in which it is structured. This is known
-as an XPath expression, and tells the parser how to navigate the XML
-document to obtain the desired information. For example, the session
+the unique hierarchy of the nodes in which it is structured. This is
+known as an XPath expression, and tells the parser how to navigate the
+XML document to obtain the desired information. For example, the session
 header date in Figure~\ref{fig-xml1} can be accessed using the XPath
@@
 document. We did so throughout our script as we parsed uniquely nested
-speech content, as it allows for the correct ordering of elements to be
+speech content. This allows the correct ordering of elements to be
 maintained. We began our first script by parsing all the business start,
 speech text, and Question Time contents contained in the XML document,
-using these unique XPath expressions to do so. Hansard records contain a
-number of statements throughout that were not explicitly spoken in
-parliament. For example, the text in Figure~\ref{fig-content_ex} beneath
-the bold subtitle ``Report from Federation Chamber'' is not attributed
-to a particular member and was not spoken aloud during the parliamentary
-proceedings. In contrast, the text which comes afterward was spoken
-aloud in parliament by The Speaker at 14:01. Generally, unspoken text is
-nested under \texttt{\textless{}debate.text\textgreater{}} or
-\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
-text is categorized under \texttt{\textless{}speech\textgreater{}}.
-Importantly, in our work we focus primarily on parsing spoken speech
-content (i.e.~what is nested within
-\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
-by The Speaker in Figure~\ref{fig-content_ex}. For this reason, many
-Hansard transcriptions which are not spoken text may not be captured in
-our database. In future work, capturing this unspoken content in our
-database would be a priority.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1.88542in,height=\textheight]{images/content_ex.png}
-
-}
-
-\caption{\label{fig-content_ex}Snapshot from page 7129 of the PDF file
-for Hansard on 26 March 2013}
-
-\end{figure}
+using these unique XPath expressions to do so.
 
 The next step was to further develop our script to produce tidy data
-sets containing all parsed text elements, where each statement is
-separated onto its own row with details about the speaker, and rows are
-maintained in chronological order. This first involved correcting the
-variable classes and adding several indicator variables to differentiate
-where statements came from, such as Chamber versus Federation Chamber or
-sub-debate 1 versus sub-debate 2. The next key task stemmed from the
-fact that the raw text data were not separated by each statement when
-parsed. In other words, any interjections, comments made by The Speaker
-or Deputy Speaker and continuations within an individual speech were all
-parsed together as a single string. As such, the name, name ID,
-electorate and party details were only provided for the person whose
-turn it was to speak. Splitting up these speeches in a way which would
-be generalizable across sitting days required much thought and effort.
-Section~\ref{sec-interject} will provide further details on the
-intricacies of this task.
+sets, as defined and introduced by Wickham (2014). These contain all
+parsed text elements, where each statement is separated onto its own row
+with details about the member of parliament who is speaking, and rows
+are maintained in chronological order. This first involved correcting
+the variable classes and adding several indicator variables to
+differentiate where statements came from, such as Chamber versus
+Federation Chamber or \texttt{\textless{}subdebate.1\textgreater{}}
+versus \texttt{\textless{}subdebate.2\textgreater{}}. The next key task
+stemmed from the fact that the raw text data were not separated by each
+statement when parsed. In other words, any interjections, comments made
+by the Speaker or Deputy Speaker and continuations within an individual
+speech were all parsed together as a single string. As such, the name,
+name ID, electorate and party details were only provided for the person
+whose turn it was to speak. There were many intricacies in the task of
+splitting these speeches in a way that would be generalizable across
+sitting days. Details on these are provided in
+Section~\ref{sec-interject}.
 
 Since we are looking at a wide time span of documents, there are many
-changes in the way they are formatted over time. These became apparent
-as we ran our script on XML files from earlier sitting days. Some
-changes are as subtle as a differently named child-node, while others
-are as extensive as a completely different nesting structure. Smaller
-changes were accounted for as we became aware of them, and embedded into
-the code in a way that would not cause issues for parsing more current
-Hansards with subtle differences in formatting. However, as mentioned,
-more significant changes in the XML structure of Hansard are what
-necessitated the development of separate scripts as we worked backwards
-in time. Further, while working backward in time, it became clear that
-not every sitting day contains every possible XML element. For example,
-some days did not have sub-debate 2 content, and some days did not have
-a Federation Chamber proceeding. To improve the generalizability of
-these scripts, if-else statements were embedded within the code wherever
-an error might arise due to a missing element. For example, the entire
-Federation Chamber block of code is wrapped in an if-else statement for
-each script, so that it only executes if what the code attempts to parse
-exists in the file.
+changes in the way they are formatted. These became apparent as we ran
+our script on XML files from earlier sitting days. Some changes are as
+subtle as a differently named child-node, while others are as extensive
+as a completely different nesting structure. Smaller changes were
+accounted for as we became aware of them, and embedded into the code in
+a way that would not cause issues for parsing more current Hansards with
+subtle differences in formatting. However, as mentioned, more
+significant changes in the XML structure of Hansard are what
+necessitated the development of separate scripts as we worked backwards.
+Further not every sitting day contains every possible XML element. For
+example, some days did not have
+\texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
+not have a Federation Chamber proceeding. To improve the
+generalizability of these scripts, if-else statements were embedded
+within the code wherever an error might arise due to a missing element.
+For example, the entire Federation Chamber block of code is wrapped in
+an if-else statement for each script, so that it only executes if what
+the code attempts to parse exists in the file.
 
@@
 made our script incompatible with parsing earlier XML files. The
-earliest sitting day our first script can successfully parse is 14
+earliest sitting day this first script can successfully parse is 14
 August 2012. Before developing new scripts to parse earlier Hansard
-documents, we decided to prioritize cleaning and finalizing what we have
-been able to parse. As such we continued building our script, fixing any
-problems we noticed in the resulting datasets such as excess whitespace
-or spacing issues, and splitting up any additional sections of the
-parsed text onto separate rows where necessary. Specifically, we added a
+documents, we prioritized cleaning and finalizing what we had been able
+to parse. As such we continued building our script, fixing any problems
+we noticed in the resulting datasets such as excess whitespace or
+spacing issues, and splitting up any additional sections of the parsed
+text onto separate rows where necessary. Specifically, we added a
 section of our script to separate out general stage directions. More
@@
 
-As previously mentioned, we developed a total of four scripts to parse
-the 1998-2022 time frame of Hansard documents. Two main factors
-motivated us to create four scripts as opposed to just one, the first
-being structural variation in XML over time, and the second being
-improved computational efficiency with separate scripts. While all four
-scripts use the same general approach to parsing described in
+As mentioned, we developed a total of four scripts to parse the
+1998-2022 time frame of Hansard documents. Two main factors motivated us
+to create four scripts as opposed to just one, the first being
+structural variation in XML over time, and the second being improved
+computational efficiency with separate scripts. While all four scripts
+use the same general approach to parsing described in
 Section~\ref{sec-overview} and produce the same CSV structure, the first
@@
 
-While the modifications needed to develop the second script were quite
+While the modifications needed to develop the second script were
 straightforward, this was not the case for our next script. The typical
@@
 \texttt{\textless{}talk.text\textgreater{}} node. These would contain
-details on the person who made each statement such as their party and
+details on the person who made each statement, such as their party and
 electorate.
@@
 individuals interjecting or commenting during speeches were also
-captured this way. To separate statements out correctly, we collected
-all of these patterns using the
-\texttt{\textless{}talk.start\textgreater{}} node, and used them to
-split statements wherever one of these patterns was found. After
-separating the statements, we were able to remove these patterns from
-the body of text. We also used this method of extracting and later
-removing unwanted patterns for other pieces of data which did not belong
-to the debate proceedings, such as sub-debate titles.
+captured this way. To separate statements correctly, we collected all of
+these patterns using the \texttt{\textless{}talk.start\textgreater{}}
+node, and used them to split statements wherever one of these patterns
+was found. After separating the statements, we were able to remove these
+patterns from the body of text. We also used this method of extracting
+and later removing unwanted patterns for other pieces of data which did
+not belong to the debate proceedings, such as sub-debate titles.
 
@@
 node we were able to use the same parsing method for all scripts, which
-was simply to extract all question and answer elements from the
+was to extract all question and answer elements from the
 \texttt{"answers.to.questions"} child node.
@@
 an answer node and vice-versa, in which cases we manually corrected the
-question and answer flags using the \texttt{str\_detect} function from
-the \texttt{stringr} package. For instance, we check for any statements
+question and answer flags. For instance, we check for any statements
 flagged as questions which include the phrase ``has provided the
@@
 The next step was to merge Question Time contents with all the debate
-speech. Doing so with the questions without notice content was
-straightforward. As mentioned, our method of parsing meant that
-everything was already parsed together in order, so we did not have to
-perform any additional merging. For questions in writing, merging this
-content was also straightforward due to the fact that it is always at
-the very end of Hansard. This means that we could simply bind question
-in writing rows to the bottom of the main dataframe. This approach was
-used for all four scripts.
+speech. Our method of parsing meant that everything was already in
+order, so we did not have to perform any additional merging. For
+questions in writing, merging this content was also straightforward due
+to the fact that it is always at the end of Hansard. This means that we
+could bind question in writing rows to the bottom of the main dataframe.
+This approach was used for all four scripts.
 
@@
 Below is an example of part of a speech we would need to split,
-extracted from Hansard on 30 November 2021, where Mr.~van Manen is
-interrupted by The Speaker who states that the time for members'
+extracted from Hansard on 30 November 2021, where Bert van Manen is
+interrupted by the Speaker who states that the time for members'
 statements has concluded.
@@
 provides an example of this, where the speech was interrupted by a
-comment from The Deputy Speaker, and then the member continued their
+comment from the Deputy Speaker, and then the member continued their
 speech. Looking at the element names highlighted in blue, these
@@
 were categorized within the XML as interjections. We stored this as a
-dataframe called \texttt{"interject"}.\footnote{We decided not to
-  include this data in our final database, as it is all embedded in our
-  resulting datasets which have a flag for interjections.}
+dataframe called \texttt{"interject"}. We decided not to include this
+data in our final database, as it is embedded in our resulting datasets
+which have a flag for interjections.
 
@@
 \texttt{main} dataframes to capture all the names of individuals who
-spoke that day. We added the names of all Members in a number of unique
+spoke that day. We added the names of all members in a number of unique
 formats, due to the frequent variation in how names are transcribed in
-Hansard. When a Member interjects or continues a speech, the usual form
+Hansard. When a member interjects or continues a speech, the usual form
 of their name is a title followed by their first name or first initial
@@
 remains lower case. This variation demands careful consideration when
-writing regular expression patterns to search for in the text. In these
-lists we also accounted for any general interjection statements
-transcribed that were not attributed to an individual, such as ``An
-opposition member interjecting-''.
-
-Having these lists enabled us to extract the names of Members and their
+writing regular expression patterns. In these lists we also accounted
+for any general interjection statements that were not attributed to an
+individual, such as ``An opposition member interjecting-''.
+
+Having these lists enabled us to extract the names of members and their
 associated titles as they exist in the text, by searching for exact
 matches with regular expression patterns. We then used these extracted
-names to split all the speeches up, using regular expressions with
+names to split all the speeches, using regular expressions with
 lookarounds. A lookaround can be added to a regular expression pattern
@@
 the text was not being split in the wrong places, such as places where
-Members were simply being named in the statement of another Member.
+members were being named in the statement of another member.
 
@@
 by the speech number, we defined an interjection as a statement made by
-anyone who is not The Speaker, The Deputy Speaker, or the Member whose
+anyone who is not the Speaker, the Deputy Speaker, or the member whose
 turn it was to speak. Figure~\ref{fig-interject} provides an example of
-a Federation Chamber proceeding with interjections. Evidently,
-statements made by the original speaker Stuart Robert or by The Deputy
-Speaker Maria Vamvakinou are not flagged as interjections.
+a Federation Chamber proceeding with interjections. Statements made by
+the member whose turn it was to speak, or by the Deputy Speaker Maria
+Vamvakinou, are not flagged as interjections.
 
@@
 fourth scripts separated out interjections in the process. This meant
-that we did not need to create lists of names and titles to search for
-in the text as we did before. However, we used the same list of general
-interjection statements to separate on that was used in the first two
-scripts. We then did an additional check for statements that may have
-not been separated due to how they were embedded in the XML, and
-separated those out where needed.\footnote{While most statements were
-  categorized in their own child-node and hence captured through
+that we did not need to create lists of names and titles for which to
+search in the text as we did before. However, we used the same list of
+general interjection statements on which to separate as was used in the
+first two scripts. We then did an additional check for statements that
+may have not been separated due to how they were embedded in the XML,
+and separated those out where needed.\footnote{While most statements
+  were categorized in their own child-node and hence captured through
   pattern-based separation, some were not individually categorized, and
@@
 
-We then proceeded to clean up speeches and fill in correct speaker
-details. While we used the same lookup table approach as before, we did
-so in combination with another means of filling in speaker details. The
-patterns parsed from \texttt{\textless{}talk.start\textgreater{}} nodes
-contain important data on the speaker of each statement. As such, we
+We then proceeded to clean up speeches and fill in correct details on
+the member of parliament speaking. While we used the same lookup table
+approach as before, we did so in combination with another means of
+filling in these details. The patterns parsed from
+\texttt{\textless{}talk.start\textgreater{}} nodes contain important
+data on the member of parliament making each statement. As such, we
 could extract those data associated with each pattern by parsing one
-element inward, using the XPath expression
-\texttt{\textless{}talk.start/talker\textgreater{}}. We created a
-pattern lookup table with these data, and merged it with the main
-Hansard dataframe by the first pattern detected in each statement.
-Figure~\ref{fig-patterns} provides an example of that lookup table. This
-approach enabled us to fill in missing data on each speaker using data
-extracted directly from the XML. Finally, we then used the
-\texttt{AustralianPoliticians} dataset to fill in other missing data,
-and flagged for interjections in the same manner as before.
+element inward, using the XPath expression \texttt{"talk.start/talker"}.
+We created a pattern lookup table with these data, and merged it with
+the main Hansard dataframe by the first pattern detected in each
+statement. Figure~\ref{fig-patterns} provides an example of that lookup
+table. This approach enabled us to fill in missing data on each member
+of parliament speaking using data extracted directly from the XML.
+Finally, we then used the \texttt{AustralianPoliticians} dataset to fill
+in other missing data, and flagged for interjections in the same manner
+as before.
 
@@
 transcript to document happenings in parliament. Examples of stage
-directions are ``Bill read a second time'', ``Question agreed to'' or
+directions are ``Bill read a second time'', ``Question agreed to'', or
 ``Debate adjourned''. It was unclear to us from the XML and PDF who
@@
 we watched portions of the video recording for some sitting days, and
-noticed that where these statements are documented in Hansard, they are
-not explicitly stated in parliament. For example, when The Deputy
+noticed that while these statements are documented in Hansard, they are
+not explicitly stated in parliament. For example, when the Deputy
 Speaker says ``The question is that the bill be now read a second
@@
 filled the name variable for these statements with ``stage direction''.
-Note that stage directions were not flagged as interjections. These
-stage directions are not defined differently from the regular debate
-speech in the XML, meaning we had to manually create a list of stage
-directions to separate out of the speeches. We have built this list of
-stage directions as we worked backwards in parsing Hansard, and took the
-same approach across all four scripts.
+Stage directions were not flagged as interjections. These stage
+directions are not defined differently from the regular debate speech in
+the XML, meaning we had to manually create a list of stage directions to
+separate out of the speeches. We built this list of stage directions as
+we worked backwards in parsing Hansard, and took the same approach
+across all four scripts.
 
@@
 replaces the short-form name with the full name, and fills the rest of
-the speaker details in accordingly with data from the
+the MP details in accordingly with data from the
 \texttt{AustralianPoliticians} package. This script does the same for
@@
 
-Our database contains 1517 CSV files, covering all sitting days of the
-House of Representatives from 02 March 1998 to 08 September 2022. All
-data records are available on the general-purpose repository Zenodo, at
-https://doi.org/10.5281/zenodo.7785767 (Katz and Alexander 2023). For
-each CSV file, each row contains an individual statement, with details
-on the individual speaking. Of course, for general statements
-transcribed as made by ``Honourable members'' for example, these
-variables cannot be specified. Table~\ref{tbl-vars} provides an overview
-of each variable found in the database.
+Our database is available in both CSV and parquet formats. It covers all
+sitting days of the House of Representatives from 02 March 1998 to 08
+September 2022, so there are 1,517 files for each format. All data
+records are available on the general-purpose repository Zenodo, at
+https://doi.org/10.5281/zenodo.7336075 (Katz and Alexander 2023). For
+each file, each row contains an individual statement, with details on
+the individual speaking. For general statements transcribed as made by
+``Honourable members'' for example, these variables cannot be specified.
+Table~\ref{tbl-vars} provides an overview of each variable found in the
+database.
 
@@
 
-We developed a script to perform seven automated tests on each file in
-our database, in an effort to enhance its quality and consistency. Our
-first test validates that the date specified in each file name matches
-the date specified in its corresponding XML session header.\footnote{As
-  seen in Figure~\ref{fig-xml1}, the first child node of the
+We developed a script to perform automated tests on each file in our
+database, to enhance its quality and consistency. Our first test
+validates that the date specified in each file name matches the date
+specified in its corresponding XML session header.\footnote{As seen in
+  Figure~\ref{fig-xml1}, the first child node of the
   \texttt{\textless{}session.header\textgreater{}} element is the date.}
@@
 dates, we check that each person speaking on each sitting day is in fact
-a Member of Parliament on that day.
+a member of parliament on that day.
+
+\hypertarget{next-steps}{%
+\section{Next Steps}\label{next-steps}}
+
+While our database makes a substantial contribution to the field, there
+are a few areas for future development.
+
+One important contribution would be to take advantage of similar records
+that exist for the Senate over this same period and add them to our
+database. The main challenge of this would be accounting for different
+parliamentarians, but the broad structures would be similar, making many
+elements of our code and methodology applicable to this work.
+
+Earlier House of Representatives records also exist, and would be
+valuable to include in future versions of our database. In some cases
+however it is difficult to get XML records for certain dates, and the
+earlier decades would require more cleaning and likely additional script
+development to account for changes in structural formatting.
+
+Having completed this work, we recognize components of our scripts which
+could be developed in a more computationally efficient manner such as
+our approach to splitting interjections and filling in MP details. In
+future, it would be beneficial to review our methodological approach to
+these steps, and consider approaches which are more concise where
+appropriate.
+
+Finally, Hansard records contain a number of statements throughout that
+were not explicitly spoken in parliament. For example, the text in
+Figure~\ref{fig-content_ex} beneath the bold subtitle ``Report from
+Federation Chamber'' is not attributed to a particular member and was
+not spoken aloud during the parliamentary proceedings. In contrast, the
+text which comes afterward was spoken aloud in parliament by the Speaker
+at 14:01. Generally, unspoken text is nested under
+\texttt{\textless{}debate.text\textgreater{}} or
+\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
+text is categorized under \texttt{\textless{}speech\textgreater{}}.
+Importantly, in our work we focus primarily on parsing spoken speech
+content (i.e.~what is nested within
+\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
+by the Speaker in Figure~\ref{fig-content_ex}. For this reason, many
+Hansard transcriptions which are not spoken text may not be captured in
+our database. In future work, capturing this unspoken content in our
+database would be a priority.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1.88542in,height=\textheight]{images/content_ex.png}
+
+}
+
+\caption{\label{fig-content_ex}Snapshot from page 7129 of the PDF file
+for Hansard on 26 March 2013}
+
+\end{figure}
 
@@
 Further, the \texttt{name.id} variable found in each CSV is another
-unique identifier for each Member of Parliament. This variable was
+unique identifier for each member of parliament. This variable was
 parsed directly from the Hansard XML files, and can be found in the
@@
 2021). This will allow for convenient extraction of further details on
-each Member of Parliament in a tidy, ready to analyze format.
+each member of parliament in a tidy, ready to analyze format.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
+Wickham, Hadley. 2014. {``Tidy Data.''} \emph{Journal of Statistical
+Software} 59 (10). \url{https://doi.org/10.18637/jss.v059.i10}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%

### 2023-04-06 paper/paper-nature_format.qmd
Update MPs

@@
 The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
-Originating in the British parliament, the production of Hansard became tradition in many Commonwealth countries such as Canada, the United Kingdom, and Australia [@vice2017history].
+Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history].
 Given the content and magnitude of these records, they have significance, particularly in the context of political science research.
@@
 
-The Australian House of Representatives performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
+The Australian House of Representatives 'the House' performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
 1].
+Politicians in the House are referred to as Members of Parliament (MPs).
 The House operates under a parallel chamber setup, meaning there are two debate venues where proceedings take place: the Chamber, and the Federation Chamber.
@@
 These data can be navigated by year, parliament, people, and bills [@sherratt].
-To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all Members of the Australian House of Representatives from 1945 to 2019.
+To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all MPs from 1945 to 2019.
 Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
@@
 Many papers exist which use components of Australian Hansard to explore various research topics.
-For example, @salisbury2011 used online Hansard records to investigate the occurrences of unparliamentary comments by members of the House, where the Speaker tells that member to withdraw their remark.
+For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where is the Speaker tells that MP to withdraw their remark.
 @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
@@
 We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
-Finally, we discuss the script we developed to fill in remaining missing details on the member of parliament speaking, which each file in our database was passed to after being parsed and cleaned.
+Finally, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned.
 
@@
 The `<speech>` node within each one contains the bulk of the text associated with that debate or sub-debate.
-A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the member of parliament whose turn it is to speak and the time of their first statement.
+A typical `<speech>` node begins with a `<talk.start>` sub-node, providing information on the MP whose turn it is to speak and the time of their first statement.
 Unsurprisingly, speeches rarely go uninterrupted in parliamentary debate settings --- they are often composed of a series of interjections and continuations.
@@
 The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014.
-These contain all parsed text elements, where each statement is separated onto its own row with details about the member of parliament who is speaking, and rows are maintained in chronological order.
+These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order.
 This first involved correcting the variable classes and adding several indicator variables to differentiate where statements came from, such as Chamber versus Federation Chamber or `<subdebate.1>` versus `<subdebate.2>`.
@@
 After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order.
-For example, if the speech began, was interrupted by one member, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node.
-These would contain details on the person who made each statement, such as their party and electorate.
+For example, if the speech began, was interrupted by an MP, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node.
+These would contain details on the MP who made each statement, such as their party and electorate.
 
@@
 One core mechanism by which this is achieved is called Question Time.
-This is a period of each sitting day in the Chamber where members of the House can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
+This is a period of each sitting day in the Chamber where MPs can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
 Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
@@
 As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech.
-@fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the member continued their speech.
+@fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech.
 Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
@@
 We then created lists using both the `interject` and `main` dataframes to capture all the names of individuals who spoke that day.
-We added the names of all members in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
-When a member interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
+We added the names of all MPs in a number of unique formats, due to the frequent variation in how names are transcribed in Hansard.
+When an MP interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
 There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
@@
 
-Having these lists enabled us to extract the names of members and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns.
+Having these lists enabled us to extract the names of MPs and their associated titles as they exist in the text, by searching for exact matches with regular expression patterns.
 We then used these extracted names to split all the speeches, using regular expressions with lookarounds.
 A lookaround can be added to a regular expression pattern to enhance the specificity of matches.
-These were used to ensure that the text was not being split in the wrong places, such as places where members were being named in the statement of another member.
+These were used to ensure that the text was not being split in the wrong places, such as places where MPs were being named in the statement of another MP.
 
@@
 Finally, we were able to add a flag for interjections.
-Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not the Speaker, the Deputy Speaker, or the member whose turn it was to speak.
+Grouping our data by the speech number, we defined an interjection as a statement made by anyone who is not the Speaker, the Deputy Speaker, or the MP whose turn it was to speak.
 @fig-interject provides an example of a Federation Chamber proceeding with interjections.
-Statements made by the member whose turn it was to speak, or by the Deputy Speaker Maria Vamvakinou, are not flagged as interjections.
+Statements made by the MP whose turn it was to speak, or by the Deputy Speaker Maria Vamvakinou, are not flagged as interjections.
 
@@
 
-We then proceeded to clean up speeches and fill in correct details on the member of parliament speaking.
+We then proceeded to clean up speeches and fill in correct details on the MP speaking.
 While we used the same lookup table approach as before, we did so in combination with another means of filling in these details.
-The patterns parsed from `<talk.start>` nodes contain important data on the member of parliament making each statement.
+The patterns parsed from `<talk.start>` nodes contain important data on the MP making each statement.
 As such, we could extract those data associated with each pattern by parsing one element inward, using the XPath expression `"talk.start/talker"`.
@@
 @fig-patterns provides an example of that lookup table.
-This approach enabled us to fill in missing data on each member of parliament speaking using data extracted directly from the XML.
+This approach enabled us to fill in missing data on each MP speaking using data extracted directly from the XML.
 Finally, we then used the `AustralianPoliticians` dataset to fill in other missing data, and flagged for interjections in the same manner as before.
@@
 
-When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by members.
+When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs.
 Stage directions are general statements included in the transcript to document happenings in parliament.
@@
 For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament.
-For example, when the Deputy Speaker says "The question is that the bill be now read a second time", members of the House take a vote, and if the majority is in favour, they proceed reading the bill the second time.
+For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time.
 This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to.
@@
 "Mr Abbott" instead of "Abbott, Tony, MP").
-This was a particularly frequent occurrence for sitting days where a member spoke whose surname was shared by any other past or present member of parliament, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution.
+This was a particularly frequent occurrence for sitting days where an MP spoke whose surname was shared by any other past or present MP, and automated filling of their details using data from the `AustralianPoliticians` package was avoided to prevent any incorrect detail attribution.
 In an effort to improve as many of these as possible, we developed a script which identifies short-form names belonging to people with common surnames in each CSV, looks for the full version of that individuals name if available in that same CSV file, and replaces the short-form name with the full name, and fills the rest of the MP details in accordingly with data from the `AustralianPoliticians` package.
@@
 This test detected 129 dates on which duplicate statements were made, and one immediately follows the other.
-Note that this test does not account for who is making each statement, meaning one member repeating the words of another member would be picked up in this test as well.
+Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well.
 We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.
 
-When a member runs out of allotted time for their speech, Hansard editors transcribe "(Time expired)" after their final word.
+When an MP runs out of allotted time for their speech, Hansard editors transcribe "(Time expired)" after their final word.
 As a means of checking that we have separated speeches out correctly, our third test checks that when the phrase "(Time expired)" exists in a body of text, it exists at the very end.
@@
 
-The remaining tests focus on the members present on each sitting day.
+The remaining tests focus on the MPs present on each sitting day.
 Our fourth test checks that there is one unique party and electorate attributed to each individual on each sitting day.
@@
 To do so, we utilized the main dataset from the `AustralianPoliticians` package which contains the birth and where applicable death dates for every politician.
-This test confirmed that all members who are detected to speak on each sitting day are not deceased.
+This test confirmed that all MPs who are detected to speak on each sitting day are not deceased.
 
-Finally, our seventh test validates that all individuals speaking are active members of parliament on that particular day.
-We use the `mps` dataset from the `AustralianPoliticians` package which has the dates of each Member's duration in parliament.
-Using these dates, we check that each person speaking on each sitting day is in fact a member of parliament on that day.
+Finally, our seventh test validates that all individuals speaking are MPs on that particular day.
+We use the `mps` dataset from the `AustralianPoliticians` package which has the dates when each MP was in parliament.
+Using these dates, we check that each person speaking on each sitting day is in fact an MP on that day.
 
@@
 Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament.
-For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular member and was not spoken aloud during the parliamentary proceedings.
+For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular MP and was not spoken aloud during the parliamentary proceedings.
 In contrast, the text which comes afterward was spoken aloud in parliament by the Speaker at 14:01.
@@
 To enhance the usability of our database, we added a `uniqueID` variable to each CSV file.
-This serves as a unique identifier for each speaking Member, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect].
+This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect].
 By including this variable, one can readily integrate our data records with those available in these two packages.
 
-Further, the `name.id` variable found in each CSV is another unique identifier for each member of parliament.
+Further, the `name.id` variable found in each CSV is another unique identifier for each MP.
 This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook.
 As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus].
-This will allow for convenient extraction of further details on each member of parliament in a tidy, ready to analyze format.
+This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.
 
@@
 The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus.
-`XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in member details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.
+`XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.
 

### 2023-04-06 paper/paper-nature_format.qmd
updated paper version

@@
 Many papers exist which use components of Australian Hansard to explore various research topics.
-For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where is the Speaker tells that MP to withdraw their remark.
+For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where the Speaker tells that MP to withdraw their remark.
 @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
@@
 
-Our database contains one comma-separated value (CSV) and one parquet file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022.
+Our database contains one comma-separated value (CSV) file and one parquet file for each sitting day of the House of Representatives from 02 March 1998 to 08 September 2022.
 We developed four scripts to produce these files.
@@
 The outer-most node, also known as the parent node, is denoted `<hansard>` and serves as a container for the entire document.
-This parent node may have up to four child-nodes, where the first child-node contains details on the specific sitting day.
+This parent node may have up to four child nodes, where the first child node contains details on the specific sitting day.
 Next, `<chamber.xscript>` contains all proceedings of the Chamber, `<fedchamb.xscript>` contains all proceedings of the Federation Chamber, and `<answers.to.questions>` contains Question Time proceedings.
@@
 The structure of the `<chamber.xscript>` and `<fedchamb.xscript>` nodes are generally the same, where the proceeding begins with `<business.start>` which is followed by a series of debates.
-Debate nodes can contain a `<subdebate.1>` child-node which has a `<subdebate.2>` child-node nested within it.
+Debate nodes can contain a `<subdebate.1>` child node which has a `<subdebate.2>` child node nested within it.
 That said, sometimes `<subdebate.2>` is not nested within `<subdebate.1>`.
@@
 These became apparent as we ran our script on XML files from earlier sitting days.
-Some changes are as subtle as a differently named child-node, while others are as extensive as a completely different nesting structure.
+Some changes are as subtle as a differently named child node, while others are as extensive as a completely different nesting structure.
 Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting.
@@
 21].
-As a result, the child-node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012.
+As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012.
 Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification.
@@
 The typical tree structure of Hansard XMLs spanning from 1998 to March 2011 has an important difference from that of XMLs released after March 2011, necessitating many changes to be made in our methodology.
-In XMLs after March 2011, which our first two scripts successfully parse, the first two child-nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`.
-The first child-node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations.
-After the `<talk.text>` element closes, there are typically a series of other child-nodes which provide a skeleton structure for how the speech proceedings went in chronological order.
+In XMLs after March 2011, which our first two scripts successfully parse, the first two child nodes of `<speech>` are typically `<talk.start>`, and `<talk.text>`.
+The first child node contains data on the person whose turn it is to speak, and the second contains the entire contents of that speech --- including all interjections, comments, and continuations.
+After the `<talk.text>` element closes, there are typically a series of other child nodes which provide a skeleton structure for how the speech proceedings went in chronological order.
 For example, if the speech began, was interrupted by an MP, and then continued uninterrupted until the end, there would be one `<interjection>` node and one `<continuation>` node following the `<talk.text>` node.
@@
 In contrast, the speech contents in XMLs from 1998 up to and including 24 March 2011 are nested differently --- there is no `<talk.text>` node.
-Rather than this single child-node that contains all speech content, statements are categorized in individual child-nodes.
+Rather than this single child node that contains all speech content, statements are categorized in individual child nodes.
 This means that unlike our code for parsing more current Hansards, we cannot specify a single XPath expression such as "`chamber.xscript//debate//speech/talk.text`" to extract all speeches, in their entirety, at once.
@@
 Since the earlier Hansard XMLs do not have a `<talk.text>` node, we found that the most straightforward way to preserve the ordering of statements and to parse all speech contents at once was to parse from the `<debate>` element directly.
-The reason we did not use its `<speech>` child-node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days.
+The reason we did not use its `<speech>` child node is because every speech has a unique structure of node children, and this makes it difficult to write code for data cleaning which is generalizable across all speeches and sitting days.
 The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data.
@@
 
-As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child-nodes which exist to capture the structure of interruptions in that speech.
+As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech.
 @fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech.
-Looking at the element names highlighted in blue, these child-nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
+Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
 However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later.
@@
 
-![First 10 rows of lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}
+![First 10 rows of the lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}
 
@@
 
-[^2]: While most statements were categorized in their own child-node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
+[^2]: While most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
 
@@
 
-![10 rows of pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}
+![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}
 
@@
 Each file in our database passed through this script after being created, to ensure it is as complete as possible.
+
+Due to the fact that the names of MPs with common surnames were not all in their complete form when we flagged for interjections the first time, it was possible that the name of the MP whose turn it was to speak was transcribed in different forms within their speech.
+For example,  “Smith, Tony, MP” at the start and then “Mr Smith” later on in the speech.
+By the nature of how we flagged for interjections, this means that rows where the short form like “Mr Smith” is the name would be flagged as an interjection, which is incorrect.
+To fix this, we re-flagged interjections using the same definition as before, once all names were filled in with this script.
 
@@
 
-The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first,speech`, and `body` variables all came directly from the XML contents.
+The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents.
 In addition to these variables, we added a number of flags to enable easy filtering of statements.
@@
 
-To enhance the usability of our database, we added a `uniqueID` variable to each CSV file.
+To enhance the usability of our database, we added a `uniqueID` variable to each file.
 This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect].
@@
 
-Further, the `name.id` variable found in each CSV is another unique identifier for each MP.
+Further, the `name.id` variable found in each file is another unique identifier for each MP.
 This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook.

### 2023-04-06 paper/paper-nature_format.tex
updated paper version

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{April 5, 2023}
+\date{April 6, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, interior hidden, boxrule=0pt, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners, enhanced, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 questions. Originating in the British parliament, the production of
-Hansard became tradition in many Commonwealth countries such as Canada,
-the United Kingdom, and Australia (Vice and Farrell 2017). Given the
-content and magnitude of these records, they have significance,
-particularly in the context of political science research. In the case
-of Canada, the Hansard has been digitized for 1901 to 2019 (Beelen et
-al. 2017). Having a digitized version of Hansard enables researchers to
-conduct text analysis and statistical modelling. Following the lead of
-that project, in this paper we introduce a similar database for
-Australia. This is composed of individual datasets for each sitting day
-in the House of Representatives from 1998 to 2022, containing details on
-everything said in parliament in a form that can be readily used by
-researchers. With the development of tools for large-scale text
-analysis, this database will serve as a resource for understanding
-political behaviour in Australia over time.
-
-The Australian House of Representatives performs a number of crucial
-governmental functions, such as creating new laws and overseeing
-government expenditure (House of Representatives 2018, ch.~1). The House
-operates under a parallel chamber setup, meaning there are two debate
-venues where proceedings take place: the Chamber, and the Federation
-Chamber. Sittings of the House follow a predefined order of business,
-regulated by procedural rules called standing orders (House of
+Hansard became tradition in many other Commonwealth countries, such as
+Canada and Australia (Vice and Farrell 2017). Given the content and
+magnitude of these records, they have significance, particularly in the
+context of political science research. In the case of Canada, the
+Hansard has been digitized for 1901 to 2019 (Beelen et al. 2017). Having
+a digitized version of Hansard enables researchers to conduct text
+analysis and statistical modelling. Following the lead of that project,
+in this paper we introduce a similar database for Australia. This is
+composed of individual datasets for each sitting day in the House of
+Representatives from 1998 to 2022, containing details on everything said
+in parliament in a form that can be readily used by researchers. With
+the development of tools for large-scale text analysis, this database
+will serve as a resource for understanding political behaviour in
+Australia over time.
+
+The Australian House of Representatives `the House' performs a number of
+crucial governmental functions, such as creating new laws and overseeing
+government expenditure (House of Representatives 2018, ch.~1).
+Politicians in the House are referred to as Members of Parliament (MPs).
+The House operates under a parallel chamber setup, meaning there are two
+debate venues where proceedings take place: the Chamber, and the
+Federation Chamber. Sittings of the House follow a predefined order of
+business, regulated by procedural rules called standing orders (House of
 Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
@@
 To make the Australian Parliamentary Handbook more accessible, Leslie
-(2021) has released an \texttt{R} package which includes data on all
-Members of the Australian House of Representatives from 1945 to 2019.
-Further, Alexander and Hodgetts (2021) created the
+(2021) has released an \texttt{R} package which includes data on all MPs
+from 1945 to 2019. Further, Alexander and Hodgetts (2021) created the
 \texttt{AustralianPoliticians} \texttt{R} package, which contains
@@
 Many papers exist which use components of Australian Hansard to explore
-various research topics. For example, Salisbury (2011) used online
-Hansard records to investigate the occurrences of unparliamentary
-comments by members of the House, where the Speaker tells that member to
-withdraw their remark. Rasiah (2010) worked with Question Time data from
-Hansard transcripts during February and March of 2003, to investigate
-resistance of politicians in answering questions about Iraq. Fraussen,
-Graham, and Halpin (2018) use Hansard to quantify political prominence
-by investigating strategic mentions of interest groups by elected
-officials. Finally, Alexander and Alexander (2021) construct a dataset
-of the Australian Hansard, along with an analysis of the effect of
-elections and changes in Prime Ministers upon topics mentioned in
-parliament. Alexander and Alexander (2021) created this database with
-the static PDF versions of Hansard, using OCR to digitize these files
-into text which is suitable for analysis. This means there are
-considerable digitization errors especially in the first half of the
-dataset.
+various research topics. For example, Salisbury (2011) used the Hansard
+to investigate occurrences of unparliamentary comments by MPs, where the
+Speaker tells that MP to withdraw their remark. Rasiah (2010) worked
+with Question Time data from Hansard transcripts during February and
+March of 2003, to investigate resistance of politicians in answering
+questions about Iraq. Fraussen, Graham, and Halpin (2018) use Hansard to
+quantify political prominence by investigating strategic mentions of
+interest groups by elected officials. Finally, Alexander and Alexander
+(2021) construct a dataset of the Australian Hansard, along with an
+analysis of the effect of elections and changes in Prime Ministers upon
+topics mentioned in parliament. Alexander and Alexander (2021) created
+this database with the static PDF versions of Hansard, using OCR to
+digitize these files into text which is suitable for analysis. This
+means there are considerable digitization errors especially in the first
+half of the dataset.
 
@@
 
-Our database contains one comma-separated value (CSV) and one parquet
-file for each sitting day of the House of Representatives from 02 March
-1998 to 08 September 2022. We developed four scripts to produce these
-files. Each script parses Hansard documents from a specific portion of
-the 1998 to 2022 time frame.
+Our database contains one comma-separated value (CSV) file and one
+parquet file for each sitting day of the House of Representatives from
+02 March 1998 to 08 September 2022. We developed four scripts to produce
+these files. Each script parses Hansard documents from a specific
+portion of the 1998 to 2022 time frame.
 
@@
 Finally, we discuss the script we developed to fill in remaining missing
-details on the member of parliament speaking, which each file in our
-database was passed to after being parsed and cleaned.
+details on the MP speaking, which each file in our database was passed
+to after being parsed and cleaned.
 
@@
 \texttt{\textless{}hansard\textgreater{}} and serves as a container for
-the entire document. This parent node may have up to four child-nodes,
-where the first child-node contains details on the specific sitting day.
+the entire document. This parent node may have up to four child nodes,
+where the first child node contains details on the specific sitting day.
 Next, \texttt{\textless{}chamber.xscript\textgreater{}} contains all
@@
 series of debates. Debate nodes can contain a
-\texttt{\textless{}subdebate.1\textgreater{}} child-node which has a
-\texttt{\textless{}subdebate.2\textgreater{}} child-node nested within
+\texttt{\textless{}subdebate.1\textgreater{}} child node which has a
+\texttt{\textless{}subdebate.2\textgreater{}} child node nested within
 it. That said, sometimes \texttt{\textless{}subdebate.2\textgreater{}}
@@
 \texttt{\textless{}talk.start\textgreater{}} sub-node, providing
-information on the member of parliament whose turn it is to speak and
-the time of their first statement. Unsurprisingly, speeches rarely go
-uninterrupted in parliamentary debate settings --- they are often
-composed of a series of interjections and continuations. These
-statements are categorized under different sub-nodes depending on their
-nature, such as \texttt{\textless{}interjection\textgreater{}} or
+information on the MP whose turn it is to speak and the time of their
+first statement. Unsurprisingly, speeches rarely go uninterrupted in
+parliamentary debate settings --- they are often composed of a series of
+interjections and continuations. These statements are categorized under
+different sub-nodes depending on their nature, such as
+\texttt{\textless{}interjection\textgreater{}} or
 \texttt{\textless{}continuation\textgreater{}}. The final key component
@@
 parsed text elements, where each statement is separated onto its own row
-with details about the member of parliament who is speaking, and rows
-are maintained in chronological order. This first involved correcting
-the variable classes and adding several indicator variables to
-differentiate where statements came from, such as Chamber versus
-Federation Chamber or \texttt{\textless{}subdebate.1\textgreater{}}
-versus \texttt{\textless{}subdebate.2\textgreater{}}. The next key task
-stemmed from the fact that the raw text data were not separated by each
+with details about the MP who is speaking, and rows are maintained in
+chronological order. This first involved correcting the variable classes
+and adding several indicator variables to differentiate where statements
+came from, such as Chamber versus Federation Chamber or
+\texttt{\textless{}subdebate.1\textgreater{}} versus
+\texttt{\textless{}subdebate.2\textgreater{}}. The next key task stemmed
+from the fact that the raw text data were not separated by each
 statement when parsed. In other words, any interjections, comments made
@@
 our script on XML files from earlier sitting days. Some changes are as
-subtle as a differently named child-node, while others are as extensive
+subtle as a differently named child node, while others are as extensive
 as a completely different nesting structure. Smaller changes were
@@
 The Main Committee was renamed to the Federation Chamber in mid-2012
-(House of Representatives 2018, ch.~21). As a result, the child-node
+(House of Representatives 2018, ch.~21). As a result, the child node
 under which Federation Chamber proceedings are nested is named
@@
 March 2011, which our first two scripts successfully parse, the first
-two child-nodes of \texttt{\textless{}speech\textgreater{}} are
+two child nodes of \texttt{\textless{}speech\textgreater{}} are
 typically \texttt{\textless{}talk.start\textgreater{}}, and
-\texttt{\textless{}talk.text\textgreater{}}. The first child-node
+\texttt{\textless{}talk.text\textgreater{}}. The first child node
 contains data on the person whose turn it is to speak, and the second
@@
 \texttt{\textless{}talk.text\textgreater{}} element closes, there are
-typically a series of other child-nodes which provide a skeleton
+typically a series of other child nodes which provide a skeleton
 structure for how the speech proceedings went in chronological order.
-For example, if the speech began, was interrupted by one member, and
-then continued uninterrupted until the end, there would be one
+For example, if the speech began, was interrupted by an MP, and then
+continued uninterrupted until the end, there would be one
 \texttt{\textless{}interjection\textgreater{}} node and one
@@
 \texttt{\textless{}talk.text\textgreater{}} node. These would contain
-details on the person who made each statement, such as their party and
+details on the MP who made each statement, such as their party and
 electorate.
@@
 \texttt{\textless{}talk.text\textgreater{}} node. Rather than this
-single child-node that contains all speech content, statements are
-categorized in individual child-nodes. This means that unlike our code
+single child node that contains all speech content, statements are
+categorized in individual child nodes. This means that unlike our code
 for parsing more current Hansards, we cannot specify a single XPath
@@
 \texttt{\textless{}debate\textgreater{}} element directly. The reason we
-did not use its \texttt{\textless{}speech\textgreater{}} child-node is
+did not use its \texttt{\textless{}speech\textgreater{}} child node is
 because every speech has a unique structure of node children, and this
@@
 Question Time. This is a period of each sitting day in the Chamber where
-members of the House can ask ministers two types of questions: questions
-in writing which are written in advance, or questions without notice
-which are asked verbally in the Chamber and are responded to in real
-time (House of Representatives 2021). Questions without notice are
-included directly in the \texttt{"chamber.xscript"} child node, with
-sub-child nodes called \texttt{"question"} and \texttt{"answer"} to
-differentiate the two. Questions in writing, however, are embedded in
-their own child node called \texttt{"answers.to.questions"} at the end
-of the XML file.
+MPs can ask ministers two types of questions: questions in writing which
+are written in advance, or questions without notice which are asked
+verbally in the Chamber and are responded to in real time (House of
+Representatives 2021). Questions without notice are included directly in
+the \texttt{"chamber.xscript"} child node, with sub-child nodes called
+\texttt{"question"} and \texttt{"answer"} to differentiate the two.
+Questions in writing, however, are embedded in their own child node
+called \texttt{"answers.to.questions"} at the end of the XML file.
 
@@
 As mentioned in Section~\ref{sec-diff}, more recent years of Hansard
-XMLs contain a series of child-nodes which exist to capture the
+XMLs contain a series of child nodes which exist to capture the
 structure of interruptions in that speech. Figure~\ref{fig-xml3}
 provides an example of this, where the speech was interrupted by a
-comment from the Deputy Speaker, and then the member continued their
-speech. Looking at the element names highlighted in blue, these
-child-nodes do not contain the actual text for the interjection or
-continuation --- this text is embedded within the speech above it.
-However, as shown by the content highlighted in pink in
-Figure~\ref{fig-xml3}, we were able to extract useful details on the
-individual interjecting which we could use later. Making use of this
-structure, we extracted names and information of all individuals that
-were categorized within the XML as interjections. We stored this as a
-dataframe called \texttt{"interject"}. We decided not to include this
-data in our final database, as it is embedded in our resulting datasets
-which have a flag for interjections.
+comment from the Deputy Speaker, and then the MP continued their speech.
+Looking at the element names highlighted in blue, these child nodes do
+not contain the actual text for the interjection or continuation ---
+this text is embedded within the speech above it. However, as shown by
+the content highlighted in pink in Figure~\ref{fig-xml3}, we were able
+to extract useful details on the individual interjecting which we could
+use later. Making use of this structure, we extracted names and
+information of all individuals that were categorized within the XML as
+interjections. We stored this as a dataframe called
+\texttt{"interject"}. We decided not to include this data in our final
+database, as it is embedded in our resulting datasets which have a flag
+for interjections.
 
@@
 \texttt{main} dataframes to capture all the names of individuals who
-spoke that day. We added the names of all members in a number of unique
+spoke that day. We added the names of all MPs in a number of unique
 formats, due to the frequent variation in how names are transcribed in
-Hansard. When a member interjects or continues a speech, the usual form
-of their name is a title followed by their first name or first initial
+Hansard. When an MP interjects or continues a speech, the usual form of
+their name is a title followed by their first name or first initial
 and/or last name. There is also variation in the capitalization of these
@@
 
-Having these lists enabled us to extract the names of members and their
+Having these lists enabled us to extract the names of MPs and their
 associated titles as they exist in the text, by searching for exact
@@
 the text was not being split in the wrong places, such as places where
-members were being named in the statement of another member.
+MPs were being named in the statement of another MP.
 
@@
 
-\caption{\label{fig-lookup}First 10 rows of lookup table from 19 October
-2017 Hansard processing}
+\caption{\label{fig-lookup}First 10 rows of the lookup table from 19
+October 2017 Hansard processing}
 
@@
 by the speech number, we defined an interjection as a statement made by
-anyone who is not the Speaker, the Deputy Speaker, or the member whose
-turn it was to speak. Figure~\ref{fig-interject} provides an example of
-a Federation Chamber proceeding with interjections. Statements made by
-the member whose turn it was to speak, or by the Deputy Speaker Maria
+anyone who is not the Speaker, the Deputy Speaker, or the MP whose turn
+it was to speak. Figure~\ref{fig-interject} provides an example of a
+Federation Chamber proceeding with interjections. Statements made by the
+MP whose turn it was to speak, or by the Deputy Speaker Maria
 Vamvakinou, are not flagged as interjections.
@@
 and separated those out where needed.\footnote{While most statements
-  were categorized in their own child-node and hence captured through
+  were categorized in their own child node and hence captured through
   pattern-based separation, some were not individually categorized, and
@@
 We then proceeded to clean up speeches and fill in correct details on
-the member of parliament speaking. While we used the same lookup table
-approach as before, we did so in combination with another means of
-filling in these details. The patterns parsed from
-\texttt{\textless{}talk.start\textgreater{}} nodes contain important
-data on the member of parliament making each statement. As such, we
-could extract those data associated with each pattern by parsing one
+the MP speaking. While we used the same lookup table approach as before,
+we did so in combination with another means of filling in these details.
+The patterns parsed from \texttt{\textless{}talk.start\textgreater{}}
+nodes contain important data on the MP making each statement. As such,
+we could extract those data associated with each pattern by parsing one
 element inward, using the XPath expression \texttt{"talk.start/talker"}.
@@
 statement. Figure~\ref{fig-patterns} provides an example of that lookup
-table. This approach enabled us to fill in missing data on each member
-of parliament speaking using data extracted directly from the XML.
-Finally, we then used the \texttt{AustralianPoliticians} dataset to fill
-in other missing data, and flagged for interjections in the same manner
-as before.
+table. This approach enabled us to fill in missing data on each MP
+speaking using data extracted directly from the XML. Finally, we then
+used the \texttt{AustralianPoliticians} dataset to fill in other missing
+data, and flagged for interjections in the same manner as before.
 
@@
 
-\caption{\label{fig-patterns}10 rows of pattern lookup table from 12
+\caption{\label{fig-patterns}10 rows of the pattern lookup table from 12
 December 2012 Hansard processing}
@@
 When building our first scripts, one of the final components needed was
-to separate general stage directions out from statements made by
-members. Stage directions are general statements included in the
-transcript to document happenings in parliament. Examples of stage
-directions are ``Bill read a second time'', ``Question agreed to'', or
-``Debate adjourned''. It was unclear to us from the XML and PDF who
-exactly these statements were attributed to. For further clarification,
-we watched portions of the video recording for some sitting days, and
-noticed that while these statements are documented in Hansard, they are
-not explicitly stated in parliament. For example, when the Deputy
-Speaker says ``The question is that the bill be now read a second
-time'', members of the House take a vote, and if the majority is in
-favour, they proceed reading the bill the second time. This vote and
-second reading is not explicitly transcribed, rather what is written is:
-``Question agreed to. Bill read a second time''. For this reason, we
-filled the name variable for these statements with ``stage direction''.
-Stage directions were not flagged as interjections. These stage
-directions are not defined differently from the regular debate speech in
-the XML, meaning we had to manually create a list of stage directions to
-separate out of the speeches. We built this list of stage directions as
-we worked backwards in parsing Hansard, and took the same approach
-across all four scripts.
+to separate general stage directions out from statements made by MPs.
+Stage directions are general statements included in the transcript to
+document happenings in parliament. Examples of stage directions are
+``Bill read a second time'', ``Question agreed to'', or ``Debate
+adjourned''. It was unclear to us from the XML and PDF who exactly these
+statements were attributed to. For further clarification, we watched
+portions of the video recording for some sitting days, and noticed that
+while these statements are documented in Hansard, they are not
+explicitly stated in parliament. For example, when the Deputy Speaker
+says ``The question is that the bill be now read a second time'', MPs
+vote, and if the majority is in favour, they proceed reading the bill
+the second time. This vote and second reading is not explicitly
+transcribed, rather what is written is: ``Question agreed to. Bill read
+a second time''. For this reason, we filled the name variable for these
+statements with ``stage direction''. Stage directions were not flagged
+as interjections. These stage directions are not defined differently
+from the regular debate speech in the XML, meaning we had to manually
+create a list of stage directions to separate out of the speeches. We
+built this list of stage directions as we worked backwards in parsing
+Hansard, and took the same approach across all four scripts.
 
@@
 (i.e.~``Mr Abbott'' instead of ``Abbott, Tony, MP''). This was a
-particularly frequent occurrence for sitting days where a member spoke
-whose surname was shared by any other past or present member of
-parliament, and automated filling of their details using data from the
+particularly frequent occurrence for sitting days where an MP spoke
+whose surname was shared by any other past or present MP, and automated
+filling of their details using data from the
 \texttt{AustralianPoliticians} package was avoided to prevent any
@@
 created, to ensure it is as complete as possible.
+
+Due to the fact that the names of MPs with common surnames were not all
+in their complete form when we flagged for interjections the first time,
+it was possible that the name of the MP whose turn it was to speak was
+transcribed in different forms within their speech. For example,
+``Smith, Tony, MP'' at the start and then ``Mr Smith'' later on in the
+speech. By the nature of how we flagged for interjections, this means
+that rows where the short form like ``Mr Smith'' is the name would be
+flagged as an interjection, which is incorrect. To fix this, we
+re-flagged interjections using the same definition as before, once all
+names were filled in with this script.
 
@@
 \texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
-\texttt{first,speech}, and \texttt{body} variables all came directly
+\texttt{first.speech}, and \texttt{body} variables all came directly
 from the XML contents. In addition to these variables, we added a number
@@
 other. Note that this test does not account for who is making each
-statement, meaning one member repeating the words of another member
-would be picked up in this test as well. We checked a sample of 40\% of
-these duplicates, and manually validated that they are all repeated
-statements that do exist and are transcribed closely together in that
-day's XML file, and by our method should be parsed such that one of
-these statements is immediately followed by the other.
-
-When a member runs out of allotted time for their speech, Hansard
-editors transcribe ``(Time expired)'' after their final word. As a means
-of checking that we have separated speeches out correctly, our third
-test checks that when the phrase ``(Time expired)'' exists in a body of
-text, it exists at the very end. When this is not the case, we know that
-we have missed the separation of the next statement onto its own row,
-and could fix this accordingly.
-
-The remaining tests focus on the members present on each sitting day.
-Our fourth test checks that there is one unique party and electorate
+statement, meaning one MP repeating the words of another MP would be
+picked up in this test as well. We checked a sample of 40\% of these
+duplicates, and manually validated that they are all repeated statements
+that do exist and are transcribed closely together in that day's XML
+file, and by our method should be parsed such that one of these
+statements is immediately followed by the other.
+
+When an MP runs out of allotted time for their speech, Hansard editors
+transcribe ``(Time expired)'' after their final word. As a means of
+checking that we have separated speeches out correctly, our third test
+checks that when the phrase ``(Time expired)'' exists in a body of text,
+it exists at the very end. When this is not the case, we know that we
+have missed the separation of the next statement onto its own row, and
+could fix this accordingly.
+
+The remaining tests focus on the MPs present on each sitting day. Our
+fourth test checks that there is one unique party and electorate
 attributed to each individual on each sitting day. As we parsed Hansard
@@
 where applicable death dates for every politician. This test confirmed
-that all members who are detected to speak on each sitting day are not
+that all MPs who are detected to speak on each sitting day are not
 deceased.
@@
 Finally, our seventh test validates that all individuals speaking are
-active members of parliament on that particular day. We use the
-\texttt{mps} dataset from the \texttt{AustralianPoliticians} package
-which has the dates of each Member's duration in parliament. Using these
-dates, we check that each person speaking on each sitting day is in fact
-a member of parliament on that day.
+MPs on that particular day. We use the \texttt{mps} dataset from the
+\texttt{AustralianPoliticians} package which has the dates when each MP
+was in parliament. Using these dates, we check that each person speaking
+on each sitting day is in fact an MP on that day.
 
@@
 Figure~\ref{fig-content_ex} beneath the bold subtitle ``Report from
-Federation Chamber'' is not attributed to a particular member and was
-not spoken aloud during the parliamentary proceedings. In contrast, the
-text which comes afterward was spoken aloud in parliament by the Speaker
-at 14:01. Generally, unspoken text is nested under
+Federation Chamber'' is not attributed to a particular MP and was not
+spoken aloud during the parliamentary proceedings. In contrast, the text
+which comes afterward was spoken aloud in parliament by the Speaker at
+14:01. Generally, unspoken text is nested under
 \texttt{\textless{}debate.text\textgreater{}} or
@@
 To enhance the usability of our database, we added a \texttt{uniqueID}
-variable to each CSV file. This serves as a unique identifier for each
-speaking Member, and comes from the \texttt{uniqueID} variable present
+variable to each file. This serves as a unique identifier for each
+speaking MP, and comes from the \texttt{uniqueID} variable present
 within data from both the \texttt{AustralianPoliticians} and
@@
 
-Further, the \texttt{name.id} variable found in each CSV is another
-unique identifier for each member of parliament. This variable was
-parsed directly from the Hansard XML files, and can be found in the
-Australian Parliamentary Handbook. As such, our data records can be
-integrated with those from the \texttt{ausPH} package which provides
-datasets for contents of the Australian Parliamentary Handbook (Leslie
-2021). This will allow for convenient extraction of further details on
-each member of parliament in a tidy, ready to analyze format.
+Further, the \texttt{name.id} variable found in each file is another
+unique identifier for each MP. This variable was parsed directly from
+the Hansard XML files, and can be found in the Australian Parliamentary
+Handbook. As such, our data records can be integrated with those from
+the \texttt{ausPH} package which provides datasets for contents of the
+Australian Parliamentary Handbook (Leslie 2021). This will allow for
+convenient extraction of further details on each MP in a tidy, ready to
+analyze format.
 
@@
 \texttt{AustralianPoliticians} and \texttt{ausPH} were used for cleaning
-up and filling in member details in the datasets, and \texttt{tidyverse}
+up and filling in MP details in the datasets, and \texttt{tidyverse}
 packages were used in all steps, for tidy wrangling of data.

### 2023-04-27 paper/paper-arxiv.tex
organizing paper versions

--- 2023-04-06 paper/paper-nature_format.tex
@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{April 6, 2023}
+\date{April 27, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, sharp corners, enhanced, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi
 

### 2023-04-27 paper/paper-nature.tex
organizing paper versions

--- 2023-04-27 paper/paper-arxiv.tex
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, enhanced, interior hidden, boxrule=0pt, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
 
@@
 
-\hypertarget{next-steps}{%
-\section{Next Steps}\label{next-steps}}
-
-While our database makes a substantial contribution to the field, there
-are a few areas for future development.
-
-One important contribution would be to take advantage of similar records
-that exist for the Senate over this same period and add them to our
-database. The main challenge of this would be accounting for different
-parliamentarians, but the broad structures would be similar, making many
-elements of our code and methodology applicable to this work.
-
-Earlier House of Representatives records also exist, and would be
-valuable to include in future versions of our database. In some cases
-however it is difficult to get XML records for certain dates, and the
-earlier decades would require more cleaning and likely additional script
-development to account for changes in structural formatting.
-
-Having completed this work, we recognize components of our scripts which
-could be developed in a more computationally efficient manner such as
-our approach to splitting interjections and filling in MP details. In
-future, it would be beneficial to review our methodological approach to
-these steps, and consider approaches which are more concise where
-appropriate.
-
-Finally, Hansard records contain a number of statements throughout that
-were not explicitly spoken in parliament. For example, the text in
-Figure~\ref{fig-content_ex} beneath the bold subtitle ``Report from
-Federation Chamber'' is not attributed to a particular MP and was not
-spoken aloud during the parliamentary proceedings. In contrast, the text
-which comes afterward was spoken aloud in parliament by the Speaker at
-14:01. Generally, unspoken text is nested under
-\texttt{\textless{}debate.text\textgreater{}} or
-\texttt{\textless{}subdebate.text\textgreater{}} nodes, while spoken
-text is categorized under \texttt{\textless{}speech\textgreater{}}.
-Importantly, in our work we focus primarily on parsing spoken speech
-content (i.e.~what is nested within
-\texttt{\textless{}speech\textgreater{}} nodes), such as what is stated
-by the Speaker in Figure~\ref{fig-content_ex}. For this reason, many
-Hansard transcriptions which are not spoken text may not be captured in
-our database. In future work, capturing this unspoken content in our
-database would be a priority.
-
-\begin{figure}
-
-{\centering \includegraphics[width=1.88542in,height=\textheight]{images/content_ex.png}
-
-}
-
-\caption{\label{fig-content_ex}Snapshot from page 7129 of the PDF file
-for Hansard on 26 March 2013}
-
-\end{figure}
-
 \hypertarget{sec-usage}{%

### 2023-04-27 paper/paper-nature.qmd
draft w/o next steps section

--- 2023-04-06 paper/paper-nature_format.qmd
@@
 Due to the fact that the names of MPs with common surnames were not all in their complete form when we flagged for interjections the first time, it was possible that the name of the MP whose turn it was to speak was transcribed in different forms within their speech.
-For example,  “Smith, Tony, MP” at the start and then “Mr Smith” later on in the speech.
-By the nature of how we flagged for interjections, this means that rows where the short form like “Mr Smith” is the name would be flagged as an interjection, which is incorrect.
+For example, "Smith, Tony, MP" at the start and then "Mr Smith" later on in the speech.
+By the nature of how we flagged for interjections, this means that rows where the short form like "Mr Smith" is the name would be flagged as an interjection, which is incorrect.
 To fix this, we re-flagged interjections using the same definition as before, once all names were filled in with this script.
@@
 
-# Next Steps
-
-While our database makes a substantial contribution to the field, there are a few areas for future development.
-
-One important contribution would be to take advantage of similar records that exist for the Senate over this same period and add them to our database.
-The main challenge of this would be accounting for different parliamentarians, but the broad structures would be similar, making many elements of our code and methodology applicable to this work.
-
-Earlier House of Representatives records also exist, and would be valuable to include in future versions of our database.
-In some cases however it is difficult to get XML records for certain dates, and the earlier decades would require more cleaning and likely additional script development to account for changes in structural formatting.
-
-Having completed this work, we recognize components of our scripts which could be developed in a more computationally efficient manner such as our approach to splitting interjections and filling in MP details.
-In future, it would be beneficial to review our methodological approach to these steps, and consider approaches which are more concise where appropriate.
-
-Finally, Hansard records contain a number of statements throughout that were not explicitly spoken in parliament.
-For example, the text in @fig-content_ex beneath the bold subtitle "Report from Federation Chamber" is not attributed to a particular MP and was not spoken aloud during the parliamentary proceedings.
-In contrast, the text which comes afterward was spoken aloud in parliament by the Speaker at 14:01.
-Generally, unspoken text is nested under `<debate.text>` or `<subdebate.text>` nodes, while spoken text is categorized under `<speech>`.
-Importantly, in our work we focus primarily on parsing spoken speech content (i.e.
-what is nested within `<speech>` nodes), such as what is stated by the Speaker in @fig-content_ex.
-For this reason, many Hansard transcriptions which are not spoken text may not be captured in our database.
-In future work, capturing this unspoken content in our database would be a priority.
-
-![Snapshot from page 7129 of the PDF file for Hansard on 26 March 2013](images/content_ex.png){#fig-content_ex width="181"}
-
 # Usage Notes {#sec-usage}

### 2023-06-25 scripts/add_party_facts.R
new scripts

@@ -1,0 +1,162 @@
+### script to add party facts column to our documents
+### code based on https://partyfacts.herokuapp.com/download/
+
+library(tidyverse)
+library(arrow)
+library(here)
+
+# download and read Party Facts mapping table
+file_name <- "partyfacts-mapping.csv"
+
+# download party facts mapping file
+if(!file_name %in% list.files()) {
+  url <- "https://partyfacts.herokuapp.com/download/external-parties-csv/"
+  download.file(url, file_name)
+}
+
+# read in party facts csv
+# note - there are parsing error warnings due to missingness
+partyfacts_raw <- read_csv(file_name, guess_max = 50000, show_col_types = F)
+
+# filter for only those for Australia, with a non-null party facts ID
+partyfacts_aus <- partyfacts_raw %>% filter(!is.na(partyfacts_id) & country=="AUS")
+
+# link datasets (select only linked parties) - using code from https://partyfacts.herokuapp.com/download/
+dataset_1 <- partyfacts_aus %>%  filter(dataset_key == "manifesto")
+dataset_2 <- partyfacts_aus %>% filter(dataset_key == "parlgov")
+link_table <- dataset_1 %>% inner_join(dataset_2, by = c("partyfacts_id", "country"))
+
+# select variables of interest
+link_table <- link_table %>% select(c(partyfacts_id, name_short.x, name_short.y, name.x, name.y))
+
+# pivot link table so we have all distinct name and abbreviations on separate rows
+pf_data <- link_table |>pivot_longer(name_short.x:name_short.y, names_to = "source", values_to = "name_short") |> 
+  pivot_longer(name.x:name.y, names_to = "name_source", values_to = "name") |> 
+  select(partyfacts_id, name_short, name) |> 
+  group_by(partyfacts_id, name) |> 
+  # this is b/c the abbreviation for Australian Greens is missing from one row
+  fill(name_short, .direction = "downup") |> 
+  ungroup() |> 
+  distinct() |> 
+  rename(name_short_pf = name_short,
+         name_pf = name)
+
+### Manual spelling/abbreviation fixes and filtering ###
+# a number of parties have two spelling variations in the party facts data, so let's only keep the ones that match AusPol spelling
+# and modify spelling if needed to match AusPol
+
+# fix Katter's name to match that in AusPol so we can merge, and only keep row where abbreviation is "KAT"
[…]

### 2023-06-25 scripts/check_time_stamps.R

@@ -1,0 +1,36 @@
+# script to detect bug in time stamps in our Hansard database
+library(tidyverse)
+
+# grab list of all file names
+all_files <- list.files("/Volumes/Verbatim/v3/hansard_1998_to_2022-csv")
+
+# define empty tibble to store loop output in
+times <- tibble()
+
+# define for loop to iterate over all our database files
+for (i in 1:length(all_files)) {
+  
+  # read in file
+  thisFile <- readr::read_csv(paste0("/Volumes/Verbatim/v3/hansard_1998_to_2022-csv/", all_files[i]), show_col_types = FALSE)
+  
+  # grab distinct time stamps and append date
+  thisFile_times <- thisFile %>% 
+    select(time.stamp) %>% 
+    filter(!is.na(time.stamp)) %>% 
+    #distinct() %>% 
+    mutate(date = str_remove(all_files[i], "\\.csv"),
+           time.stamp = as.character(time.stamp))
+  
+  # add above to tibble
+  times <- bind_rows(times, thisFile_times)
+  
+}
+
+# filter to only keep time stamps that do not fit the correct format hh:mm:ss
+wrong_times <- times %>% filter(!str_detect(time.stamp, "^\\d\\d:\\d\\d:\\d\\d$"))
+
+# grab random sample of 25% of wrong times to check
+sample_times <- slice_sample(wrong_times, prop = 0.25)
+
+### checked entire sample, all are confirmed transcription errors 
+### that is, these are all errors inherent to the XML files, not the result of our database construction process

### 2023-06-25 scripts/create_one_corpus.R

@@ -1,0 +1,47 @@
+### script to create a single corpus with our entire database
+
+# read in packages
+library(tidyverse)
+library(arrow)
+library(fs)
+
+# set working directory to where the database is stored
+# setwd("/Volumes/Verbatim/v4")
+
+# create list of all the CSV files
+all_files_csv <- dir_ls(path = "hansard_1998_to_2022-csv/")
+
+read_csv("hansard_1998_to_2022-csv/1998-03-02.csv")
+
+# read in and combine all CSVs, and extract just the date from each file name
+full_hansard <- all_files_csv %>% 
+  map_dfr(read_csv, col_types = list(name = col_character(),
+                                     order = col_double(),
+                                     speech_no = col_double(),
+                                     page.no = col_double(),
+                                     time.stamp = col_character(),
+                                     name.id = col_character(),
+                                     electorate = col_character(),
+                                     party = col_factor(),
+                                     in.gov = col_double(),
+                                     first.speech = col_double(),
+                                     body = col_character(),
+                                     fedchamb_flag = col_factor(),
+                                     question = col_factor(),
+                                     answer = col_factor(),
+                                     q_in_writing = col_factor(),
+                                     div_flag = col_factor(),
+                                     gender = col_factor(),
+                                     uniqueID = col_character(),
+                                     interject = col_factor()), .id = "date") %>% 
+  mutate(date = str_extract(date, "(?<=hansard_1998_to_2022-csv/)\\d{4}-\\d{2}-\\d{2}"))
+
+# export full_hansard data frame to CSV
+write_csv(full_hansard, "hansard_corpus_1998_to_2022.csv")
+
+# export full_hansard data frame to Parquet
+write_parquet(full_hansard, "hansard_corpus_1998_to_2022.parquet")
+
+# check file sizes
+file_size("hansard_corpus_1998_to_2022.csv")
+file_size("hansard_corpus_1998_to_2022.parquet")

### 2023-06-25 scripts/get_debate_topics.R

@@ -1,0 +1,72 @@
+# script to get debate and sub-debate 1 info from Hansard
+
+# read in necessary packages
+library(here)
+library(tidyverse)
+library(xml2)
+
+# define function which allows us to grab all XML node children that have the same name in order
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# define function to extract debate and subdebate 1 title and page number info
+get_debate_topics <- function(filename) {
+  
+  # parse xml file
+  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
+  
+  # grab sub-debate 1 titles and page numbers, create date variable
+  debate_info <- item_df(xml_df, "//debate/debateinfo | //subdebate.1/subdebateinfo") %>% 
+           # replace any null values with NA so the next mutate works
+    mutate(page.no =  map(page.no, `%||%`, NA),
+           # sometimes there are two page numbers, where the second is wrong (i.e. a debate title or time stamp or repeated number), so only take first
+           page.no = map_chr(page.no, first)) %>% 
+    unnest(title) %>% 
+    mutate(date = str_remove(filename, ".xml")) %>% 
+    select(date, itemindex, title, page.no)
+  
+  return(debate_info)
+}
+
+# grab list of Hansard XML files to iterate over
+files_all <- list.files("/Volumes/Verbatim/input/")
+
+# define empty tibble to store output
+all_debate_topics <- tibble()
+
+# define for loop, iterate over all XMLs
+for (i in 1:length(files_all)) {
+  
+  # store get_sub1_topics function output for individual file
[…]

### 2023-06-25 scripts/sample_code_README.R

@@ -1,0 +1,73 @@
+### sample code for readme ###
+
+# dependencies
+library(tidyverse)
+library(arrow)
+
+### how to read in a single sitting day file ###
+
+# set working directory to wherever you've downloaded the Hansard data
+setwd("/Volumes/Verbatim/v3/")
+
+# csv
+hansard_csv <- readr::read_csv("hansard_1998_to_2022-csv/2000-06-05.csv", 
+                               col_types = list(name = col_character(),
+                                                order = col_double(),
+                                                speech_no = col_double(),
+                                                page.no = col_double(),
+                                                time.stamp = col_character(),
+                                                name.id = col_character(),
+                                                electorate = col_character(),
+                                                party = col_factor(),
+                                                in.gov = col_double(),
+                                                first.speech = col_double(),
+                                                body = col_character(),
+                                                fedchamb_flag = col_factor(),
+                                                question = col_factor(),
+                                                answer = col_factor(),
+                                                q_in_writing = col_factor(),
+                                                div_flag = col_factor(),
+                                                gender = col_factor(),
+                                                uniqueID = col_character(),
+                                                interject = col_factor()))
+
+# parquet
+hansard_parquet <- arrow::read_parquet("hansard_1998_to_2022-parquet/2000-06-05.parquet")
+
+### use the corpus, filter for dates of interest, and split days into individual tibbles ###
+hansard_corpus <- arrow::read_parquet("hansard_corpus_1998_to_2022.parquet")
+
+# filter for dates of interest, and split each date into list of separate tibbles
+hansard_1990s <- hansard_corpus %>% 
+  filter(str_detect(date, "^199")) %>% 
+  group_split(date)
+
+### how to filter out stage directions ###
+
+# filter out rows where name includes "stage direction", and drop original order variable and create new one
+hansard_csv %>% 
+  filter(!str_detect(name, "stage direction")) %>% 
+  select(-order) %>% 
+  rowid_to_column("order")
+
+### how to merge debate topics with data
+
+# read in Hansard file
+hansard_parquet <- arrow::read_parquet("hansard_1998_to_2022-parquet/2000-06-05.parquet")
+
+# read in topics file (can do this for CSV as well)
[…]

### 2023-06-25 scripts/summary_stats.R

@@ -1,0 +1,85 @@
+# script to get summary statistics for Hansard
+library(tidyverse)
+library(here)
+library(arrow)
+
+# read in corpus
+corpus <- read_parquet("hansard_corpus_1998_to_2022.parquet")
+
+corpus |> select(date, name, order, speech_no, party_name_auspol) |> 
+  group_by(date, party_name_auspol) |> 
+  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
+  group_by(party_name_auspol) |> 
+  summarise(total_distinct_speeches = sum(n_distinct_speeches))
+
+# speeches per year
+speeches_per_year <- corpus %>% select(date, speech_no) %>%
+  mutate(year = str_extract(date, "^\\d{4}")) %>% 
+  distinct() %>% 
+  group_by(date) %>% 
+  filter(speech_no == max(speech_no, na.rm = TRUE)) %>% 
+  group_by(year) %>% 
+  summarise(total_speeches = sum(speech_no))
+
+# speeches per party
+### note - this will require some cleaning b/c of some variation in party abbrevation - may be better to do after party facts ID are added
+speeches_per_party <- corpus |> 
+  group_by(date, party_name_auspol) |> 
+  filter(speech_no == max(speech_no, na.rm = TRUE)) |> 
+  group_by(party_name_auspol) |> 
+  summarise(total_speeches_party = sum(speech_no))
+
+# speeches in gov
+corpus |> group_by(date) |> 
+  filter(speech_no == max(speech_no, na.rm = TRUE)) |> 
+  group_by(in.gov) |> 
+  summarise(total_speeches_in_gov = sum(speech_no))
+
+# speeches by electorate
+corpus |> group_by(date) |> 
+  filter(speech_no == max(speech_no, na.rm = TRUE)) |> 
+  group_by(electorate) |> 
+  summarise(total_speeches_electorate = sum(speech_no)) |> arrange(desc(total_speeches_electorate))
+
+# interjections by men vs by women per year
+interject_yr_sex <- corpus %>% select(date, gender, interject, fedchamb_flag) %>% 
+  mutate(year = str_extract(date, "^\\d{4}"),
+         gender = as.character(gender),
+         gender = ifelse(is.na(gender), "unknown", gender)) %>% 
+  filter(interject==1) %>% 
[…]

### 2023-06-25 paper/paper-nature-revised.qmd
paper updates

--- 2023-04-27 paper/paper-nature.qmd
@@
 As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to.
-Sometimes, questions were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags.
+Sometimes, **we identified** questions **which** were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags.
 For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer.
+**It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch.
+As such, users may identify and should be weary of occasional incorrectly flagged questions or answers in the data.**
 
@@
 We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.
+**It is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do.
+However, they provide valuable information about the inner-workings and structure of parliamentary events.**
 
@@
 
+## Debate Topics
+
+**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing the debate topics and their corresponding page numbers for each sitting day in our database.
+To extract these data, we wrote a script to parse all debate information and sub-debate information elements from each XML file in chronological order, and add a date variable with the date of each sitting day.
+This left us with a single dataframe containing the date, an item index variable to specify the order of proceedings (i.e.
+the order in which these topics were discussed), a title variable containing the debate or sub-debate title, and a page number variable specifying on which page that title can be found in the official Hansard PDF.**
+
+```{r, eval=F}
+# read in df
+topics <- arrow::read_parquet("../additional_data/all_debate_topics.parquet")
+
+# grab first 5 titles from some sitting day
+topics |> filter(date == "2015-03-16") |> slice(1:5) |> kableExtra::kable()
+```
+
 # Data Records
@@
 It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are 1,517 files for each format.
-All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336075 [@katz_2023].
+**Additionally, there is a single corpus Parquet file containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023].
 For each file, each row contains an individual statement, with details on the individual speaking.
@@
                                       "fedchamb_flag",
-                                      "sub1_flag",
-                                      "sub2_flag",
                                       "question",
@@
        "Description" = c("Name of speaker",
-                         "Row number",
-                         "Speech number",
+                         "Individual row numbering, based on our data processing and text separation method",
+                         "Index associated with each speech made on the given sitting day, including all statements, comments and interjections made in the duration of that speech",
                          "Page number statement can be found on in official Hansard",
@@
                          "Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)",
-                         "Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)",
-                         "Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)",
                          "Flag for question (1 if question, 0 otherwise)",
@@
 For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber.
-As well, the `sub1_flag` and `sub2_flag` variables allow us to keep track of where various statements are being parsed from in the XML document.
 The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.
@@
 Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest.
-Finally, the `order` variable was added to maintain the order of proceedings.
+**Finally, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.**
 
@@
 
+**The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all time stamps in our database which do not match the correct "HH:MM:SS" format.
+We found a total of 88 incorrectly formatted time stamps, with common issues such as the "HH" or "MM" component recorded as "NaN" (e.g.
+"NaN:28:00" or "09:NaN:00"), as well as timestamps with a third digit in the minute component (e.g.
+"09:497:00" or "13:445:00").
+We took a random sample of 25% of these incorrectly formatted timestamps, and manually checked whether or not they were transcribed as such in the original XML Hansard transcript.
+We found that every improperly formatted timestamp in our random sample was in fact transcribed as such in its original XML file, meaning these bugs are the result of a transcription error, rather than an error resulting from our data parsing or cleaning code.
+As such, we have left these timestamps in their originally transcribed format in our database.**
+
 The remaining tests focus on the MPs present on each sitting day.
-Our fourth test checks that there is one unique party and electorate attributed to each individual on each sitting day.
+Our fifth test checks that there is one unique party and electorate attributed to each individual on each sitting day.
 As we parsed Hansard further back in time, we found a number of cases where an individual was associated with the wrong electorate or party due to transcription errors.
@@
 
-Our sixth test checks that on any given sitting day, the individuals identified are alive.
+Our seventh test checks that on any given sitting day, the individuals identified are alive.
 To do so, we utilized the main dataset from the `AustralianPoliticians` package which contains the birth and where applicable death dates for every politician.
@@
 
-Finally, our seventh test validates that all individuals speaking are MPs on that particular day.
+Finally, our eighth test validates that all individuals speaking are MPs on that particular day.
 We use the `mps` dataset from the `AustralianPoliticians` package which has the dates when each MP was in parliament.
@@
 This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.
+
+**Finally, the README file on our GitHub repository contains example code on how to read in a file from our database, for both CSV and Parquet formats.
+Should a user wish to use the single Hansard corpus rather than individual sitting day files, we provide example code on how to read it in, filter for those sitting days of interest, and split them into distinct data frames.
+We have also added example code for filtering out stage directions, and updating the `order` variable to reflect the ordering of remaining rows, should the user wish to remove stage directions from their analysis.**
 

### 2023-07-01 paper/paper-nature-revised.qmd
paper revisions

@@
 We then provide details on the methodological intricacies of three core components of Hansard proceedings: Question Time, interjections, and stage directions.
-Finally, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned.
+Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned.
+**Finally, we review the supplementary Hansard debate topics dataset we created to expand the versatility of our database.**
 
@@
 > # read in XML file
-> raw_ex <-  xmlParse(here("input/2021-11-30.xml"))
+> raw_ex <-  xmlParse("/Volumes/Verbatim/input/2021-11-30.xml")
 > >
@@
 We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.
-**It is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do.
+**Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process.
+Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do.
 However, they provide valuable information about the inner-workings and structure of parliamentary events.**
@@
 
-**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing the debate topics and their corresponding page numbers for each sitting day in our database.
-To extract these data, we wrote a script to parse all debate information and sub-debate information elements from each XML file in chronological order, and add a date variable with the date of each sitting day.
-This left us with a single dataframe containing the date, an item index variable to specify the order of proceedings (i.e.
-the order in which these topics were discussed), a title variable containing the debate or sub-debate title, and a page number variable specifying on which page that title can be found in the official Hansard PDF.**
-
-```{r, eval=F}
-# read in df
-topics <- arrow::read_parquet("../additional_data/all_debate_topics.parquet")
-
-# grab first 5 titles from some sitting day
-topics |> filter(date == "2015-03-16") |> slice(1:5) |> kableExtra::kable()
-```
+**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database.
+To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day.
+Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error.
+Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a time stamp.
+Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset.**
 
@@
 Our database is available in both CSV and parquet formats.
-It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are 1,517 files for each format.
-**Additionally, there is a single corpus Parquet file containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023].
-For each file, each row contains an individual statement, with details on the individual speaking.
+It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are **1,527 individual sitting day** files for each format.
+**Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
+There is also a CSV and Parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023].
+For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking.
 For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified.
-@tbl-vars provides an overview of each variable found in the database.
+@tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.
 
@@
                                       "q_in_writing",
-                                      "div_flag",
                                       "gender",
                                       "uniqueID",
-                                      "interject"),
+                                      "interject",
+                                      "div_flag",
+                                      "partyfacts_id"),
        "Description" = c("Name of speaker",
@@
                          "Flag for question in writing (1 if question in writing, 0 otherwise)",
-                         "Flag for division (1 if division, 0 otherwise)",
                          "Gender of speaker",
                          "Unique identifier of speaker",
-                         "Flag for interjection (1 if statement is an interjection, 0 otherwise)"))
+                         "Flag for interjection (1 if statement is an interjection, 0 otherwise)",
+                         "Flag for division (1 if division, 0 otherwise)",
+                         "PartyFacts identification number, based on linked parties data from the Party Facts project"))
 
 # print tibble using kable
-knitr::kable(main_ex_vars, booktabs=T) %>% 
-  kable_styling(full_width = F, latex_options = "HOLD_position")
+knitr::kable(main_ex_vars, booktabs=T) |> 
+  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position") |> 
+  kableExtra::column_spec(1, width = "8em") |> 
+  kableExtra::column_spec(2, width="30em")
 ```
@@
 We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for.
-The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package.
-Details on the usage of `uniqueID` will be provided in @sec-usage.
+The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, **and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project [website](https://partyfacts.herokuapp.com).**[^3] Details on the usage of `uniqueID` **and `partyfacts_id`** will be provided in @sec-usage.
 Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.
 Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest.
-**Finally, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.**
+**Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.**
+
+[^3]: **Note that in accordance with the code provided on the Party Facts \[downloads page\](https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov.
+Details on these datasets can be found here: https://partyfacts.herokuapp.com/documentation/datasets/.**
+
+**As mentioned, in addition to the Hansard data described above, our database also contains a CSV and Parquet file with the parsed debate topics.
+This file is called `all_debate_topics`, and contains a `date` variable specifying the sitting day, an `item_index` variable to specify the order of proceedings (i.e.
+the order in which these topics were discussed), a `title` variable containing the debate or sub-debate title contents, and a `page.no` variable specifying on which page that title was recorded to be found in the official Hansard PDF.**
+
+**Finally, there is a CSV file in our database called `PartyFacts_map.csv`.
+This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable.
+As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data.
+Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package data in this dataframe for completeness.**
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-partyfacts-vars
+#| tbl-cap: "Summary and description of variables in our Party Facts mapping file"
+
+pf_vars <- tibble("Variable" = c("partyfacts_id",
+                                 "party_abb_hansard",
+                                 "party_abb_auspol",
+                                 "party_name_auspol"),
+                  "Description" = c("PartyFacts identification number, based on linked parties data from the Party Facts project",
+                                    "Party abbreviation as transcribed in the Hansard data",
+                                    "Party abbreviation as recorded in the `AustralianPoliticians` data",
+                                    "Party full name as recorded in the `AustralianPoliticians` data"))
+
+# print tibble using kable
+knitr::kable(pf_vars, booktabs=T) %>% 
+  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position") |> 
+  kableExtra::column_spec(1, width = "10em") |> 
+  kableExtra::column_spec(2, width="25em")
+```
 
@@
 We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency.
-Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^3] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
+Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
 We validated that our file name and date was correct by checking the official PDF release from that sitting day.
 
-[^3]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
+[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
 
@@
 spoken content).
-This test detected 129 dates on which duplicate statements were made, and one immediately follows the other.
+This test detected **130** dates on which duplicate statements were made, and one immediately follows the other.
 Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well.
@@
 By including this variable, one can readily integrate our data records with those available in these two packages.
+**Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.**
 
@@
 
-**Finally, the README file on our GitHub repository contains example code on how to read in a file from our database, for both CSV and Parquet formats.
+**Finally, the README file on our GitHub repository and on Zenodo contains example code on how to read in a file from our database, for both CSV and Parquet formats.
 Should a user wish to use the single Hansard corpus rather than individual sitting day files, we provide example code on how to read it in, filter for those sitting days of interest, and split them into distinct data frames.
-We have also added example code for filtering out stage directions, and updating the `order` variable to reflect the ordering of remaining rows, should the user wish to remove stage directions from their analysis.**
+We have also added example code for filtering out stage directions, and updating the `order` variable to reflect the ordering of remaining rows, should the user wish to remove stage directions from their analysis.
+Lastly, the README contains example code showing users how to merge the debate topics data with a Hansard data file for one sitting day.**
 

### 2023-07-01 paper/paper-nature-revised.tex
paper revisions

--- 2023-04-27 paper/paper-nature.tex
@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{April 27, 2023}
+\date{June 29, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, breakable]}{\end{tcolorbox}}\fi
 
@@
 proceedings: Question Time, interjections, and stage directions.
-Finally, we discuss the script we developed to fill in remaining missing
+Further, we discuss the script we developed to fill in remaining missing
 details on the MP speaking, which each file in our database was passed
-to after being parsed and cleaned.
+to after being parsed and cleaned. \textbf{Finally, we review the
+supplementary Hansard debate topics dataset we created to expand the
+versatility of our database.}
 
@@
 to flag questions and answers correctly based on which list of patterns
-it belonged to. Sometimes, questions were incorrectly transcribed under
-an answer node and vice-versa, in which cases we manually corrected the
-question and answer flags. For instance, we check for any statements
-flagged as questions which include the phrase ``has provided the
-following answer to the honourable member's question'', in which case we
-re-code that statement as an answer.
+it belonged to. Sometimes, \textbf{we identified} questions
+\textbf{which} were incorrectly transcribed under an answer node and
+vice-versa, in which cases we manually corrected the question and answer
+flags. For instance, we check for any statements flagged as questions
+which include the phrase ``has provided the following answer to the
+honourable member's question'', in which case we re-code that statement
+as an answer. \textbf{It is important to note, however, that because we
+identified and corrected for these transcription errors manually as we
+discovered them, additional flagging errors may exist which we did not
+catch. As such, users may identify and should be weary of occasional
+incorrectly flagged questions or answers in the data.}
 
@@
 Hansard, and took the same approach across all four scripts.
+\textbf{Despite our best efforts to capture all stage directions in this
+list, because it had to be built manually, users should be aware that it
+is possible that some stage directions were not separated onto their own
+rows in the process. Further, it is important to note that because they
+are not spoken aloud, stage directions do not represent speech
+components in the same way that all other components such as
+interjections and continuations do. However, they provide valuable
+information about the inner-workings and structure of parliamentary
+events.}
 
@@
 
+\hypertarget{debate-topics}{%
+\subsection{Debate Topics}\label{debate-topics}}
+
+\textbf{To enhance the range of research questions which can be explored
+with our data, we have created a supplementary file containing debate
+topics and their corresponding page numbers for each sitting day in our
+database. To extract these data, we wrote a script to parse debate and
+sub-debate 1 information elements from each XML file in chronological
+order using the XPath expression
+``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
+and added a date variable with the date of each sitting day. Note that
+in some cases there were multiple page number child nodes for the same
+debate or sub-debate title, likely due to manual transcription error.
+Upon manual inspection, we found that most often, the second page number
+node contained the same page number as the first node, and sometimes the
+second node contained a repeated debate title or a time stamp.
+Therefore, we took the first available page number child-node for each
+debate or sub-debate node to be the one we included in our dataset.}
+
 \hypertarget{data-records}{%
@@
 sitting days of the House of Representatives from 02 March 1998 to 08
-September 2022, so there are 1,517 files for each format. All data
-records are available on the general-purpose repository Zenodo, at
-https://doi.org/10.5281/zenodo.7336075 (Katz and Alexander 2023). For
-each file, each row contains an individual statement, with details on
-the individual speaking. For general statements transcribed as made by
-``Honourable members'' for example, these variables cannot be specified.
-Table~\ref{tbl-vars} provides an overview of each variable found in the
-database.
+September 2022, so there are 1,517 \textbf{individual sitting day} files
+for each format. \textbf{Additionally, there is a single corpus file in
+both CSV and Parquet forms containing the data from all sitting days,
+with a date variable added to allow for distinction and filtering of
+individual sitting days. There is also a CSV and Parquet file containing
+all parsed debate topics.} All data records are available on the
+general-purpose repository Zenodo, at
+https://doi.org/10.5281/zenodo.7799678 (Katz and Alexander 2023). For
+each \textbf{Hansard data} file, \textbf{that is, the corpus and the
+individual sitting day files}, each row contains an individual
+statement, with details on the individual speaking. For general
+statements transcribed as made by ``Honourable members'' for example,
+these variables cannot be specified. Table~\ref{tbl-vars} provides an
+overview of each variable found in the \textbf{Hansard data files in
+the} database.
 
@@
 \centering
-\begin{tabular}{ll}
+\begin{tabular}{>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{30em}}
 \toprule
@@
 name & Name of speaker\\
-order & Row number\\
-speech\_no & Speech number\\
+order & Individual row numbering, based on our data processing and text separation method\\
+speech\_no & Index associated with each speech made on the given sitting day, including all statements, comments and interjections made in the duration of that speech\\
 page.no & Page number statement can be found on in official Hansard\\
@@
 fedchamb\_flag & Flag for Federation Chamber (1 if Federation Chamber, 0 if Chamber)\\
-sub1\_flag & Flag for sub-debate 1 contents (1 if sub-debate 1, 0 otherwise)\\
-sub2\_flag & Flag for sub-debate 2 contents (1 if sub-debate 2, 0 otherwise)\\
 question & Flag for question (1 if question, 0 otherwise)\\
-\addlinespace
 answer & Flag for answer (1 if answer, 0 otherwise)\\
 q\_in\_writing & Flag for question in writing (1 if question in writing, 0 otherwise)\\
-div\_flag & Flag for division (1 if division, 0 otherwise)\\
+\addlinespace
 gender & Gender of speaker\\
 uniqueID & Unique identifier of speaker\\
-\addlinespace
 interject & Flag for interjection (1 if statement is an interjection, 0 otherwise)\\
+div\_flag & Flag for division (1 if division, 0 otherwise)\\
+partyfacts\_id & PartyFacts identification number, based on linked parties data from the Party Facts project\\
 \bottomrule
@@
 \texttt{fedchamb\_flag} provides a clear distinction between the
-proceedings of the Chamber with those of the Federation Chamber. As
-well, the \texttt{sub1\_flag} and \texttt{sub2\_flag} variables allow us
-to keep track of where various statements are being parsed from in the
-XML document. The \texttt{question}, \texttt{answer}, and
-\texttt{q\_in\_writing} flags were added to identify statements
-belonging to Question Time, and the nature of these statements. We also
-flagged for interjections (\texttt{interject}), and the
-\texttt{div\_flag} variable was added to flag when a division is called
-for. The \texttt{gender} and \texttt{uniqueID} variables were added
-based on the main dataset from the \texttt{AustralianPoliticians}
-package. Details on the usage of \texttt{uniqueID} will be provided in
-Section~\ref{sec-usage}. Further, the \texttt{speech\_no} variable
-allows us to keep track of the speech number that each statement and
-interjection belongs to. Having the speech number variable offers an
-easy way to group statements by speech or isolate specific speeches of
-interest. Finally, the \texttt{order} variable was added to maintain the
-order of proceedings.
+proceedings of the Chamber with those of the Federation Chamber. The
+\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
+were added to identify statements belonging to Question Time, and the
+nature of these statements. We also flagged for interjections
+(\texttt{interject}), and the \texttt{div\_flag} variable was added to
+flag when a division is called for. The \texttt{gender} and
+\texttt{uniqueID} variables were added based on the main dataset from
+the \texttt{AustralianPoliticians} package, \textbf{and the
+\texttt{partyfacts\_id} variable was added using code and data provided
+by the Party Facts Project
+\href{https://partyfacts.herokuapp.com}{website}.}\footnote{\textbf{Note
+  that in accordance with the code provided on the Party Facts
+  {[}downloads page{]}(https://partyfacts.herokuapp.com/download/), we
+  used only the core datasets maintained by the Party Facts project,
+  which are the Manifesto Project and ParlGov. Details on these datasets
+  can be found here:
+  https://partyfacts.herokuapp.com/documentation/datasets/.}} Details on
+the usage of \texttt{uniqueID} \textbf{and \texttt{partyfacts\_id}} will
+be provided in Section~\ref{sec-usage}. Further, the \texttt{speech\_no}
+variable allows us to keep track of the speech number that each
+statement and interjection belongs to. Having the speech number variable
+offers an easy way to group statements by speech or isolate specific
+speeches of interest. \textbf{Lastly, the \texttt{order} variable was
+added to maintain the order of proceedings, after all individual
+statements were separated onto their own rows.}
+
+\textbf{As mentioned, in addition to the Hansard data described above,
+our database also contains a CSV and Parquet file with the parsed debate
+topics. This file is called \texttt{all\_debate\_topics}, and contains a
+\texttt{date} variable specifying the sitting day, an
+\texttt{item\_index} variable to specify the order of proceedings
+(i.e.~the order in which these topics were discussed), a \texttt{title}
+variable containing the debate or sub-debate title contents, and a
+\texttt{page.no} variable specifying on which page that title was
+recorded to be found in the official Hansard PDF.}
+
+\textbf{Finally, there is a CSV file in our database called
+\texttt{PartyFacts\_map.csv}. This file was created using
+\texttt{AustralianPoliticians} data, data downloaded from the Party
+Facts project, and our own Hansard data \texttt{party} variable. As
+there are some party name and abbreviation spelling inconsistencies
+across these sources, creating this dataframe allowed us to ensure
+correct merging of PartyFacts ID numbers with their associated party, in
+accordance with the party abbreviation spelling transcribed in our
+Hansard data. Further, we included the corresponding party abbreviation
+and full name spelling found in the \texttt{AustralianPoliticians}
+package data in this dataframe for completeness.}
+
+\hypertarget{tbl-partyfacts-vars}{}
+\begin{table}[H]
+\caption{\label{tbl-partyfacts-vars}Summary and description of variables in our Party Facts mapping file }\tabularnewline
+
+\centering
+\begin{tabular}{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{25em}}
+\toprule
+Variable & Description\\
+\midrule
+partyfacts\_id & PartyFacts identification number, based on linked parties data from the Party Facts project\\
+party\_abb\_hansard & Party abbreviation as transcribed in the Hansard data\\
+party\_abb\_auspol & Party abbreviation as recorded in the `AustralianPoliticians` data\\
+party\_name\_auspol & Party full name as recorded in the `AustralianPoliticians` data\\
+\bottomrule
+\end{tabular}
+\end{table}
 
@@
 
+\textbf{The fourth test is designed to detect issues in timestamp
+formatting in the data, by detecting all time stamps in our database
+which do not match the correct ``HH:MM:SS'' format. We found a total of
+88 incorrectly formatted time stamps, with common issues such as the
+``HH'' or ``MM'' component recorded as ``NaN'' (e.g.~``NaN:28:00'' or
+``09:NaN:00''), as well as timestamps with a third digit in the minute
+component (e.g.~``09:497:00'' or ``13:445:00''). We took a random sample
+of 25\% of these incorrectly formatted timestamps, and manually checked
+whether or not they were transcribed as such in the original XML Hansard
+transcript. We found that every improperly formatted timestamp in our
+random sample was in fact transcribed as such in its original XML file,
+meaning these bugs are the result of a transcription error, rather than
+an error resulting from our data parsing or cleaning code. As such, we
+have left these timestamps in their originally transcribed format in our
+database.}
+
 The remaining tests focus on the MPs present on each sitting day. Our
-fourth test checks that there is one unique party and electorate
+fifth test checks that there is one unique party and electorate
 attributed to each individual on each sitting day. As we parsed Hansard
@@
 
-Our sixth test checks that on any given sitting day, the individuals
+Our seventh test checks that on any given sitting day, the individuals
 identified are alive. To do so, we utilized the main dataset from the
@@
 
-Finally, our seventh test validates that all individuals speaking are
-MPs on that particular day. We use the \texttt{mps} dataset from the
+Finally, our eighth test validates that all individuals speaking are MPs
+on that particular day. We use the \texttt{mps} dataset from the
 \texttt{AustralianPoliticians} package which has the dates when each MP
@@
 our data records with those available in these two packages.
+\textbf{Similarly, we added the \texttt{partyfacts\_id} variable to our
+data which allows users to link our data to external political party
+information.}
 
@@
 analyze format.
+
+\textbf{Finally, the README file on our GitHub repository and on Zenodo
+contains example code on how to read in a file from our database, for
+both CSV and Parquet formats. Should a user wish to use the single
+Hansard corpus rather than individual sitting day files, we provide
+example code on how to read it in, filter for those sitting days of
+interest, and split them into distinct data frames. We have also added
+example code for filtering out stage directions, and updating the
+\texttt{order} variable to reflect the ordering of remaining rows,
+should the user wish to remove stage directions from their analysis.
+Lastly, the README contains example code showing users how to merge the
+debate topics data with a Hansard data file for one sitting day.}
 
@@
 database of all proceedings of the Australian Parliamentary Debates
-(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7785767}.
+(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7799678}.
 

### 2023-07-01 scripts/old-scripts/99-everything-2011_to_2012-v1.R
cleaning repo

@@ -1,2092 +1,0 @@
-# main committee
-# script to parse everything from Hansard
-#### good for everything up to 2012-06-28 (last day before main committee was renamed to federation chamber)
-
-# read in necessary packages
-library(XML)
-library(here)
-library(tidyverse)
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-# define function for splitting interjections, which will be referenced in parse_hansard function
-
-split_interjections_maincomm <- function(main, interject, bus_start, sub1_q_a_writing, filename){
-  
-  #### step 1: add speech_no to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "speech_no")
-  
-  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
-  main_orig <- main
-  
-  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
-  
-  # start by re-formatting those with title of speaker or deputy speaker
-  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
-  if (nrow(interject)>0){
-    interject_names <- interject %>%
-      select(name) %>%
-      filter(str_detect(name, "\\(The")) %>%
-      unique() %>%
-      mutate(name = str_remove(name, "[[:punct:]][[:space:]]MP|[[:space:]]MP"),
-             title = str_extract(name, "The.{0,10}[:space:][:alpha:]{0,10}"),
-             last_name = str_extract(name, "^[:alpha:]{0,10}-[:alpha:]{0,35}|^[:alpha:]{0,10}'[:alpha:]{0,35}|^[:alpha:]{0,35}|^[:alpha:]{0,35}[:space:][:alpha:]{0,35}"),
-             first_name = str_extract(name, ",[:space:][:alpha:]{0,35}"),
-             first_name = str_replace_all(first_name, "[[:punct:]][[:space:]]", "")) %>%
-      summarise(form1 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
-                form2 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)"),
-                form3 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
[…]

### 2023-07-01 scripts/old-scripts/99-everything-2011_to_2012-v2.R

@@ -1,2106 +1,0 @@
-# main committee
-# script to parse everything from Hansard
-#### good for everything up to 2012-06-28 (last day before main committee was renamed to federation chamber)
-
-# read in necessary packages
-library(XML)
-library(here)
-library(tidyverse)
-library(xml2)
-
-# for parsing question time
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-# define function for splitting interjections, which will be referenced in parse_hansard function
-
-split_interjections_maincomm <- function(main, interject, bus_start, q_in_writing, filename){
-  
-  #### step 1: add speech_no to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "speech_no")
-  
-  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
-  main_orig <- main
-  
-  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
-  
-  # start by re-formatting those with title of speaker or deputy speaker
-  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
-  if (nrow(interject)>0){
-    interject_names <- interject %>%
-      select(name) %>%
[…]

### 2023-07-01 scripts/old-scripts/99-everything-2012_to_2022-v1.R

@@ -1,2064 +1,0 @@
-# script to parse everything from Hansard
-# WORKS FOR 2012-08-14 TO PRESENT (that day is when the federation chamber was renamed)
-
-# read in necessary packages
-library(XML)
-library(here)
-library(tidyverse)
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-#all <- read.csv("/Volumes/Verbatim/all.csv")
-
-# define function for splitting interjections, which will be referenced in parse_hansard function
-
-split_interjections <- function(main, interject, bus_start, sub1_q_a_writing, filename){
-  
-  #### step 1: add speech_no to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "speech_no")
-  
-  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
-  main_orig <- main
-  
-  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
-  
-  # start by re-formatting those with title of speaker or deputy speaker
-  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
-  if (nrow(interject)>0){
-    interject_names <- interject %>%
-      select(name) %>%
-      filter(str_detect(name, "\\(The")) %>%
-      unique() %>%
-      mutate(name = str_remove(name, "[[:punct:]][[:space:]]MP|[[:space:]]MP"),
-             title = str_extract(name, "The.{0,10}[:space:][:alpha:]{0,10}"),
-             last_name = str_extract(name, "^[:alpha:]{0,10}-[:alpha:]{0,35}|^[:alpha:]{0,10}'[:alpha:]{0,35}|^[:alpha:]{0,35}|^[:alpha:]{0,35}[:space:][:alpha:]{0,35}"),
-             first_name = str_extract(name, ",[:space:][:alpha:]{0,35}"),
-             first_name = str_replace_all(first_name, "[[:punct:]][[:space:]]", "")) %>%
-      summarise(form1 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
-                form2 = paste0(title, "[[:space:]]\\((Dr|Mr|Mrs|Ms)[[:space:]]", last_name, "\\)"),
-                form3 = paste0(title, "\n                  ", "\\((Dr|Mr|Mrs|Ms)[[:space:]]", first_name, "[[:space:]]", last_name, "\\)"),
[…]

### 2023-07-01 scripts/old-scripts/99-everything-2012_to_2022-v2.R

@@ -1,1945 +1,0 @@
-# script to parse everything from Hansard
-# WORKS FOR 2012-08-14 TO PRESENT (that day is when the federation chamber was renamed)
-
-# read in necessary packages
-library(XML)
-library(xml2)
-library(here)
-library(tidyverse)
-
-# for parsing question time
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-#all <- read.csv("/Volumes/Verbatim/all.csv")
-
-# define function for splitting interjections, which will be referenced in parse_hansard function
-
-split_interjections <- function(main, interject, bus_start, q_in_writing, filename){
-   
-  #### step 1: add speech_no to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "speech_no")
-  
-  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
-  main_orig <- main
-  
-  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
-  
-  # start by re-formatting those with title of speaker or deputy speaker
-  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
-  if (nrow(interject)>0){
-    interject_names <- interject %>%
-      select(name) %>%
[…]

### 2023-07-01 scripts/old-scripts/descriptive_stats.R

@@ -1,95 +1,0 @@
-# descriptive stats
-library("quanteda")
-
-# read in file
-this_df <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", "2005-08-18-main-v2.csv"), show_col_types = F)
-
-# most common words
-hansard_corpus <- thisFile %>% select(order, body) %>% corpus(., docid_field = "order", text_field = "body")
-
-hansard_corpus %>% tokens() %>% dfm()
-
-stopwords(source="snowball")
-
-# average length of speeches
-
-# frequency of interjections by gender
-
-
-# average number of rows?
-
-
-
-# first grab list of all main CSVs
-all_dfs <- list.files("/Volumes/Verbatim/output/main")
-
-# define empty tibbles to store things in
-interject_data <- tibble()
-fedchamb_rows <- tibble()
-unique_data <- tibble()
-
-for(i in 1:length(all_dfs)){
-  # define df
-  this_df <- read_csv(paste0("/Volumes/Verbatim/output/main/", all_dfs[i]), show_col_types = F)
-  
-  # number of interjections
-  this_interject_data <- this_df %>% group_by(interject, gender) %>%
-    summarise(n_interject=n()) %>%
-    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
-    select(date, interject, n_interject)
-  
-  # number of rows in chamb and fedchamb
-  this_fedchamb_rows <- this_df %>% group_by(fedchamb_flag) %>% 
-    summarise(n_rows = n()) %>% 
-    mutate(date = as.Date(str_extract(all_dfs[i], "\\d\\d\\d\\d\\-\\d\\d\\-\\d\\d"))) %>% 
-    select(date, fedchamb_flag, n_rows)
-  
-  # number of unique things (NAs omitted) - need to fix a tiny bit more but better for now
-  this_nameid <- this_df %>% select(name.id, fedchamb_flag) %>% 
-    group_by(fedchamb_flag) %>% 
-    unique() %>% 
-    na.omit() %>% 
-    summarise(n_name.id = n())
-  
-  this_electorate <- this_df %>% select(electorate, fedchamb_flag) %>% 
-    group_by(fedchamb_flag) %>% 
-    unique() %>% 
-    na.omit() %>% 
[…]

### 2023-07-01 scripts/old-scripts/parse_question_time_new.R

@@ -1,136 +1,0 @@
-# trying method for pre 2011 on recent stuff, to deal with q/a issues
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-filename<-"2012-03-20.xml"
-
-hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
-
-################### QUESTIONS WITHOUT NOTICE ###################
-if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/question/talk.start/talker"))) > 0) {
-  
-  # grab all q and a content
-  q_wo_notice_content <- item_df(xml_df, "chamber.xscript//question | chamber.xscript//answer") %>% unnest(c(talk.text, talk.start)) %>% select(itemindex, talk.text)
-  
-  # grab all q and a info to merge with content
-  q_wo_notice_info <- item_df(xml_df, "chamber.xscript//question/talk.start/talker | chamber.xscript//answer/talk.start/talker") %>% unnest(everything())
-  
-  # left join by item index - questions without notice
-  q_wo_notice <- left_join(q_wo_notice_info, q_wo_notice_content, by="itemindex")
-  
-  # grab question text to flag for
[…]

### 2023-07-01 scripts/csv_to_parquet.R
cleaning repo

@@ -1,48 +1,0 @@
-# script to convert all CSV files (version 2, filled) to parquet files, with correct variable classes
-library(arrow)
-library(tidyverse)
-
-# grab list of all file names
-files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv-v2")
-
-files_all[i]
-fill_main(str_remove(files_all[i], "-v2"))
-
-# to loop through all our files
-for (i in 1:length(files_all)) {
-  
-  # read in file
-  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
-  
-  # modify variable classes
-  thisFile <- thisFile %>% mutate(party = as.factor(party),
-                                  gender = as.factor(gender))
-  
-  stopifnot(ncol(thisFile)==21 & c("name", "order","speech_no","page.no", "time.stamp", "name.id", "electorate", "party", "in.gov", "first.speech",
-                                   "body", "fedchamb_flag", "sub1_flag", "sub2_flag","question", "answer", "q_in_writing", "div_flag", "gender", "uniqueID", "interject") %in% names(thisFile))
-  
-  stopifnot(str_detect(thisFile$order, "^\\d+$"))
-  
-  # export as parquet file
-  write_parquet(thisFile, paste0("/Volumes/Verbatim/output/main-filled-parquet-v2/", str_remove(files_all[i], "csv"), "parquet"))
-  
-}
-
-
-# just a final check that all column names are right etc
-# to loop through all our files
-for (i in 1:length(files_all)) {
-  
-  # read in file
-  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
-  
-  # modify variable classes
-  thisFile <- thisFile %>% mutate(party = as.factor(party),
-                                  gender = as.factor(gender))
-  
-  stopifnot(ncol(thisFile)==21 & c("name", "order","speech_no","page.no", "time.stamp", "name.id", "electorate", "party", "in.gov", "first.speech",
-                                   "body", "fedchamb_flag", "sub1_flag", "sub2_flag","question", "answer", "q_in_writing", "div_flag", "gender", "uniqueID", "interject") %in% names(thisFile))
-  
-  stopifnot(str_detect(thisFile$order, "^\\d+$"))
-  
-}

### 2023-07-01 scripts/data_validation.R

@@ -1,341 +1,0 @@
-# series of tests to validate our data
-library(tidyverse)
-
-# read in ausPH and auspol dataset
-ausPH <- ausPH::getIndividuals()
-
-# for some reason ausPH wasn't working so i got data myself
-#ausPH <-rjson::fromJSON(file="/Volumes/Verbatim/lookup_tables/individuals.json")[["value"]]|>dplyr::bind_rows()
-
-all <- AustralianPoliticians::get_auspol('all')
-party <- AustralianPoliticians::get_auspol('allbyparty')
-mps <- AustralianPoliticians::get_auspol('mps')
-
-# read in my lookup table
-lookup <- read_csv("/Volumes/Verbatim/lookup_tables/member_lookup.csv", show_col_types = F)
-
-# grab list of file names
-files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv-v2")
-
-##### test 1 - date in filename must match one date in our list of dates from all session headers
-
-# grab session header csv - code to make this is in 01-session_info.R script
-session_headers <- read_csv("/Volumes/Verbatim/output/old-data/session_info/session_info_all.csv", show_col_types = F) %>% pull(date)
-
-# extract dates from file names, convert to date
-dates_all <- files_all %>% as_tibble() %>% mutate(value = as.Date(str_remove(value, "-main-v2.csv"))) %>% pull(value)
-
-# check that dates of our filenames match dates from session headers
-setdiff(as.character(dates_all), as.character(session_headers))
-
-# one difference - 2009-06-03
-# our filename is right, there is an error in the session header - it was transcribed as 2009-06-04, I checked official release to confirm we're right
-
-##### test 2 - checks whether two lines that immediately follow each other have the same "body" - NEW
-test2 <- tibble()
-
-for(i in 1:length(files_all)) {
-  # read in file
-  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
-
-  test2 <-thisFile %>% filter(body == lead(body) | body == lag(body)) %>% 
-    select(name, order, body) %>% 
-    filter(body!="interjecting") %>% 
-    mutate(date = str_remove(files_all[i], "-main-v2.csv")) %>% 
-    bind_rows(test2, .)
-  
-}
-
[…]

### 2023-07-01 scripts/fill_details.R

@@ -1,269 +1,0 @@
-# script to maximize completeness of hansard data by using AusPol lookup table
-# main goal is to replace short names with full names, and fill in any missing party, electorate, gender, or uniqueID details
-library(tidyverse)
-
-# read in master lookup table
-master_orig <- read_csv("/Volumes/Verbatim/lookup_tables/member_lookup.csv", show_col_types = F) 
-speaker_list <- read_csv("/Volumes/Verbatim/lookup_tables/speaker_lookup.csv", show_col_types = F) %>% unique()
-
-# rename phid to match with hansard, and change parties to hansard abbreviations for consistency
-# these are from: https://www.aph.gov.au/Parliamentary_Business/Committees/Senate/woc/wocjanjun08/a02
-master_orig <- master_orig %>% 
-  rename(name.id = phid) %>% 
-  mutate(party = case_when(party=="Australian Democrats" ~ "AD",
-                           party=="Australian Greens" ~ "AG",
-                           party=="Australian Labor Party" ~ "ALP",
-                           party=="Independent" ~ "Ind",
-                           party=="Liberal Party of Australia" ~ "LP",
-                           party=="The Nationals" ~ "NATS",
-                           party=="National Party of Australia" ~ "NATS"))
-
-# do same for speaker list
-speaker_list <- speaker_list %>% 
-  rename(name.id = phid) %>% 
-  mutate(party = case_when(party=="Australian Democrats" ~ "AD",
-                           party=="Australian Greens" ~ "AG",
-                           party=="Australian Labor Party" ~ "ALP",
-                           party=="Independent" ~ "Ind",
-                           party=="Liberal Party of Australia" ~ "LP",
-                           party=="National Party of Australia" ~ "NATS"))
-
-# define file-name
-filename <- "2002-08-29-main.csv"
-
-fill_main <- function(filename) {
-  
-  # let's filter out people who have died prior to the Hansard date we're working with
-  # this will help reduce the number of people who share a surname and title
-  master <- master_orig %>% filter(deathDate >= paste0(str_remove(filename, "-main.csv")) | is.na(deathDate))
-  
-  # get list of people who share a title and surname (summarized by looking at form2 and form4)
-  # adding a few for ppl who got their seats in 2022 and aren't in AusPol yet
-  repeat_forms <- master %>% 
-    separate_rows(title, sep="\\|") %>% 
-    group_by(surname, title) %>% 
[…]

### 2023-07-01 scripts/get_debate_topics.R

@@ -1,72 +1,0 @@
-# script to get debate and sub-debate 1 info from Hansard
-
-# read in necessary packages
-library(here)
-library(tidyverse)
-library(xml2)
-
-# define function which allows us to grab all XML node children that have the same name in order
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# define function to extract debate and subdebate 1 title and page number info
-get_debate_topics <- function(filename) {
-  
-  # parse xml file
-  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
-  
-  # grab sub-debate 1 titles and page numbers, create date variable
-  debate_info <- item_df(xml_df, "//debate/debateinfo | //subdebate.1/subdebateinfo") %>% 
-           # replace any null values with NA so the next mutate works
-    mutate(page.no =  map(page.no, `%||%`, NA),
-           # sometimes there are two page numbers, where the second is wrong (i.e. a debate title or time stamp or repeated number), so only take first
-           page.no = map_chr(page.no, first)) %>% 
-    unnest(title) %>% 
-    mutate(date = str_remove(filename, ".xml")) %>% 
-    select(date, itemindex, title, page.no)
-  
-  return(debate_info)
-}
-
-# grab list of Hansard XML files to iterate over
-files_all <- list.files("/Volumes/Verbatim/input/")
-
-# define empty tibble to store output
-all_debate_topics <- tibble()
-
-# define for loop, iterate over all XMLs
-for (i in 1:length(files_all)) {
-  
-  # store get_sub1_topics function output for individual file
[…]

### 2023-07-01 scripts/old-scripts/99-everything-1998_to_1999.R

@@ -1,2395 +1,0 @@
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-# all <- read.csv("/Volumes/Verbatim/all.csv")
-
-#hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", "1999-06-22.xml"))
-#xml_df <- read_xml(here("/Volumes/Verbatim/input/", "1998-12-10.xml"))
-
-filename<-"1998-03-05.xml"
-
-parse_hansard_1998 <- function(filename){ 
-  
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
-  
-  ######### BUSINESS START #########
-  # chamber
-  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F))>0) {
-    bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F), 
[…]

### 2023-07-01 scripts/old-scripts/99-everything-2000_to_2011.R

@@ -1,2763 +1,0 @@
-# works from 15 February 2000 to 10 May 2011
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-#all <- read.csv("/Volumes/Verbatim/all.csv")
-
-################### temp filename
-filename <- "2011-03-21.xml"
-
-parse_hansard <- function(filename){ 
- 
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
-  
-  ######### BUSINESS START #########
-  # chamber
-  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F))>0) {
-    bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F), 
-                              fedchamb_flag = 0, .name_repair = "unique") %>% 
-      rename(date = day.start)
-    
[…]

### 2023-07-01 scripts/row-checks.R

@@ -1,88 +1,0 @@
-# script to check that number of rows hasn't changed as a result of new parsing method for 2011-2022
-
-new_method_filled <- list.files("/Volumes/Verbatim/output/main-filled-csv-2") %>% 
-  as_tibble() %>%
-  filter(value > "2012-06-28") %>% 
-  pull(value)
-
-old_method_filled <- list.files("/Volumes/Verbatim/output/main-filled-csv") %>% 
-  as_tibble() %>%
-  filter(value > "2012-06-28") %>% 
-  pull(value)
-
-row_check_filled <- tibble()
-
-for(i in 1:length(new_method_filled)){
-  thisFile_new <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-2/", new_method_filled[i]), show_col_types = F)
-  thisFile_old <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", old_method_filled[i]), show_col_types = F)
-  
-  row_check_filled <- tibble(nrow_new = nrow(thisFile_new),
-         nrow_old = nrow(thisFile_old),
-         date = str_extract(new_method_filled[i], "\\d{4}-\\d{2}-\\d{2}")) %>% 
-    bind_rows(row_check_filled, .)
-}
-
-
-row_check_filled <- row_check_filled %>% filter(nrow_new!=nrow_old)
-
-row_check_filled <- row_check_filled %>% filter(!(date %in% row_check$date))
-
-# THESE HAVE BEEN CHECKED, ALL GOOD
-rc_filled_new_less <- row_check_filled %>% filter(nrow_new < nrow_old)
-  
-rc_filled_new_more <- row_check_filled %>% filter(nrow_new > nrow_old)
-
-thisFile_new <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-2/", rc_filled_new_more$date[64], "-main-v2.csv"), show_col_types = F)
-thisFile_old <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", rc_filled_new_more$date[64], "-main-v2.csv"), show_col_types = F)
-
-nrow(thisFile_new)-nrow(thisFile_old)
-
-setdiff(select(thisFile_new, c(body)),select(thisFile_old, c(body)))
-setdiff(select(thisFile_old, c(body)),select(thisFile_new, c(body)))
-
[…]

### 2023-07-01 scripts/sample_code_README.R

@@ -1,73 +1,0 @@
-### sample code for readme ###
-
-# dependencies
-library(tidyverse)
-library(arrow)
-
-### how to read in a single sitting day file ###
-
-# set working directory to wherever you've downloaded the Hansard data
-setwd("/Volumes/Verbatim/v3/")
-
-# csv
-hansard_csv <- readr::read_csv("hansard_1998_to_2022-csv/2000-06-05.csv", 
-                               col_types = list(name = col_character(),
-                                                order = col_double(),
-                                                speech_no = col_double(),
-                                                page.no = col_double(),
-                                                time.stamp = col_character(),
-                                                name.id = col_character(),
-                                                electorate = col_character(),
-                                                party = col_factor(),
-                                                in.gov = col_double(),
-                                                first.speech = col_double(),
-                                                body = col_character(),
-                                                fedchamb_flag = col_factor(),
-                                                question = col_factor(),
-                                                answer = col_factor(),
-                                                q_in_writing = col_factor(),
-                                                div_flag = col_factor(),
-                                                gender = col_factor(),
-                                                uniqueID = col_character(),
-                                                interject = col_factor()))
-
-# parquet
-hansard_parquet <- arrow::read_parquet("hansard_1998_to_2022-parquet/2000-06-05.parquet")
-
-### use the corpus, filter for dates of interest, and split days into individual tibbles ###
-hansard_corpus <- arrow::read_parquet("hansard_corpus_1998_to_2022.parquet")
-
-# filter for dates of interest, and split each date into list of separate tibbles
-hansard_1990s <- hansard_corpus %>% 
-  filter(str_detect(date, "^199")) %>% 
-  group_split(date)
-
-### how to filter out stage directions ###
-
-# filter out rows where name includes "stage direction", and drop original order variable and create new one
-hansard_csv %>% 
-  filter(!str_detect(name, "stage direction")) %>% 
-  select(-order) %>% 
-  rowid_to_column("order")
-
-### how to merge debate topics with data
-
-# read in Hansard file
-hansard_parquet <- arrow::read_parquet("hansard_1998_to_2022-parquet/2000-06-05.parquet")
-
-# read in topics file (can do this for CSV as well)
[…]

### 2023-07-01 scripts/summary_stats.R

@@ -1,85 +1,0 @@
-# script to get summary statistics for Hansard
-library(tidyverse)
-library(here)
-library(arrow)
-
-# read in corpus
-corpus <- read_parquet("hansard_corpus_1998_to_2022.parquet")
-
-corpus |> select(date, name, order, speech_no, party_name_auspol) |> 
-  group_by(date, party_name_auspol) |> 
-  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
-  group_by(party_name_auspol) |> 
-  summarise(total_distinct_speeches = sum(n_distinct_speeches))
-
-# speeches per year
-speeches_per_year <- corpus %>% select(date, speech_no) %>%
-  mutate(year = str_extract(date, "^\\d{4}")) %>% 
-  distinct() %>% 
-  group_by(date) %>% 
-  filter(speech_no == max(speech_no, na.rm = TRUE)) %>% 
-  group_by(year) %>% 
-  summarise(total_speeches = sum(speech_no))
-
-# speeches per party
-### note - this will require some cleaning b/c of some variation in party abbrevation - may be better to do after party facts ID are added
-speeches_per_party <- corpus |> 
-  group_by(date, party_name_auspol) |> 
-  filter(speech_no == max(speech_no, na.rm = TRUE)) |> 
-  group_by(party_name_auspol) |> 
-  summarise(total_speeches_party = sum(speech_no))
-
-# speeches in gov
-corpus |> group_by(date) |> 
-  filter(speech_no == max(speech_no, na.rm = TRUE)) |> 
-  group_by(in.gov) |> 
-  summarise(total_speeches_in_gov = sum(speech_no))
-
-# speeches by electorate
-corpus |> group_by(date) |> 
-  filter(speech_no == max(speech_no, na.rm = TRUE)) |> 
-  group_by(electorate) |> 
-  summarise(total_speeches_electorate = sum(speech_no)) |> arrange(desc(total_speeches_electorate))
-
-# interjections by men vs by women per year
-interject_yr_sex <- corpus %>% select(date, gender, interject, fedchamb_flag) %>% 
-  mutate(year = str_extract(date, "^\\d{4}"),
-         gender = as.character(gender),
-         gender = ifelse(is.na(gender), "unknown", gender)) %>% 
-  filter(interject==1) %>% 
[…]

### 2023-07-01 scripts/03-subdebate_1.R
cleaning repo

@@ -1,107 +1,0 @@
-# script for getting sub-debate 1 info & text
-
-# load required packages
-library(XML)
-library(here)
-library(tidyverse)
-
-######## TUESDAY 6:00 NEED TO ADD IF-ELSE TO SUBDEBATE 1 CHAMBER.
-
-# define function
-parse_sub1 <- function(filename){
-  
-  # parse XML
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-
-  # # define interjection words - commenting this out b/c found better way to do so after everything is split (see 99-everything script)
-  # interject_words <- c("Order!", "Order.", "interjecting", "Interjecting", "interjected", "Interjected", "interjections", "interjection", "Interjections", 
-  #                      "Interjection", "interject", "Interject", "The time for the discussion has concluded", "I thank the honourable member for", 
-  #                      "I thank the member for", "should withdraw that remark", "In accordance with standing order 193 the time for constituency statements has concluded", 
-  #                      "There being no further grievances, the debate is adjourned", "the time for members' statements has concluded", 
-  #                      "The original question was that this bill be now read a second time", "Is the amendment seconded?",
-  #                      "Do you want to seek the call again?", "The question is that the amendment be disagreed to", "The question now is that the bill be agreed to", 
-  #                      "will resume his seat", "will resume her seat", "will resume their seat") 
-  
-  #### CHAMBER ####
-  # store sub-debate 1 information & text in tibble, correct variable class, add flag for federation chamber
-  sub1_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebateinfo")),
-                           xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.text"))) %>%
-    as_tibble() %>% 
-    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
-           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
-  
[…]

### 2023-07-01 scripts/04-subdebate_2.R

@@ -1,152 +1,0 @@
-# script for getting sub-debate 2 info & text
-# note: sub-debate 2 is nested within sub-debate 1
-
-# load required packages
-library(XML)
-library(here)
-library(tidyverse)
-
-parse_sub2 <- function(filename){
-  
-  # parse XML
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-
-  #### CHAMBER ####
-  # store sub-debate 2 information & text in tibble, correct variable class, add flag for federation chamber
-  # include if-else statements in case sub-debate 2 does not exist
-  sub2_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/subdebateinfo")),
-                           xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/subdebate.text"))) %>% 
-    as_tibble() %>% 
-    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
-           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
-  
-  # sometimes sub-debate 2 isn't nested in sub-debate 1 (most recent date where this is the case is 2021-10-21)
-  # if the number of rows of this is > 1, let's bind that onto what we already have to ensure we aren't missing anything
-  if (nrow(as_tibble(cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebateinfo")),
-                           xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebate.text"))))) > 0) {
-    
-    sub2_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebateinfo")),
-                             xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebate.text"))) %>% 
-      as_tibble() %>% 
-      mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
-             fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL}) %>% 
-      rbind(., sub2_info_chamb)
-    }
-  
[…]

### 2023-07-01 scripts/05-debate_interjections.R

@@ -1,75 +1,0 @@
-# script to get speech interjection info
-
-# load required packages
-library(XML)
-library(here)
-library(tidyverse)
-
-parse_interject <- function(filename){
-  
-  # parse XML
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-  
-  #### CHAMBER ####
-  # sub-debate 1 speech interjections in tibble, correct variable class, add flag for federation chamber
-  # use if-else statements in case there are no interjections
-  sub1_interject_chamb <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/speech/interjection/talk.start/talker")),
-                            xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/speech/interjection/talk.text"))) %>% 
-    as_tibble() %>% 
-    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
-           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
-  
-  # sub-debate 2 speech interjections in tibble, correct variable class, add flag for federation chamber
-  # use if-else statements in case there are no interjections, or there is no sub-debate 2
-  sub2_interject_chamb <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/speech/interjection/talk.start/talker")),
-                            xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/speech/interjection/talk.text"))) %>% 
-    as_tibble() %>% 
-    mutate(page.no ={if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
-           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
-  
-  #### FEDERATION CHAMBER ####
-  # sub-debate 1 speech interjections in tibble, correct variable class, add flag for federation chamber
-  # don't need if-else here b/c this only executes if interjections exist in sub-debate 1 (condition of outer if statement)
-  sub1_interject_fed <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//fedchamb.xscript/debate/subdebate.1/speech/interjection/talk.start/talker")),
[…]

### 2023-07-01 scripts/07-divisions_data.R

@@ -1,129 +1,0 @@
-# get divisions data
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab list of all file names
-files_all <- list.files("/Volumes/Verbatim/input/")
-
-# define empty tibble to store data in
-division_data <- tibble()
-
-for (i in 1:length(files_all)) {
-  # parse file
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", files_all[i]))
-  
-  # need to read the XML in in a different way for this so we can use the item_df function defined in global environment
-  xml_df <- read_xml(here("/Volumes/Verbatim/input/", files_all[i]))
-  
-  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript//division"), collectNames = F, homogeneous = T))>0){
-    
-    # grab header
-    if (nrow(item_df(xml_df, "chamber.xscript//division/division.header"))>0 & "para" %in% names(item_df(xml_df, "chamber.xscript//division/division.header"))) {
-      header <- item_df(xml_df, "chamber.xscript//division/division.header") %>% unnest(everything()) %>% 
-        select(-para)
-    } else if (nrow(item_df(xml_df, "chamber.xscript//division/division.header"))>0 & "body" %in% names(item_df(xml_df, "chamber.xscript//division/division.header"))) {
-      header <- item_df(xml_df, "chamber.xscript//division/division.header") %>% unnest(everything()) %>% 
[…]

### 2023-07-01 scripts/99-everything-1998_to_1999-FINAL.R

@@ -1,2415 +1,0 @@
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-# all <- read.csv("/Volumes/Verbatim/all.csv")
-
-#hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", "1999-06-22.xml"))
-#xml_df <- read_xml(here("/Volumes/Verbatim/input/", "1998-12-10.xml"))
-
-filename<-"1999-03-25.xml"
-
-parse_hansard_1998 <- function(filename){ 
-  
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
-  
-  ######### BUSINESS START #########
-  # chamber
-  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F))>0) {
-    bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start"), homogeneous = T, collectNames = F), 
[…]

### 2023-07-01 scripts/99-everything-2011_to_2012-FINAL.R

@@ -1,1912 +1,0 @@
-# changing my approach to parsing so we don't have to merge stuff the way i originally had it
-# motivation - maintaining correct order
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# for parsing question time
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-split_interjections_maincomm <- function(main, interject, filename){
-  
-  #### step 1: add speech_no to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "speech_no")
-  
-  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
-  main_orig <- main
-  
-  # remove business start for now and we can add back in later
-  #main_bus_start <- main %>% filter(name=="business start")
-  #main <- main %>% filter(name!="business start")
-  
-  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
-  
-  # start by re-formatting those with title of speaker or deputy speaker
-  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
-  if (nrow(interject)>0){
-    interject_names <- interject %>%
-      select(name) %>%
[…]

### 2023-07-01 scripts/99-everything-2012_to_2022-FINAL.R

@@ -1,1972 +1,0 @@
-# 2012 to 2022 new script, developed march 21, 2023
-# changing my approach to parsing so we don't have to merge stuff the way i originally had it
-# motivation - maintaining correct order
-library(here)
-library(tidyverse)
-library(xml2)
-library(XML)
-library(hms)
-
-# for parsing question time
-# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
-item_df <- function(file, path){
-  # find all items and store as a list
-  items <- xml_find_all(file, path)
-  
-  # extract all childrens names and values 
-  nodenames <- xml_name(xml_children(items))
-  contents <- trimws(xml_text(xml_children(items)))
-  
-  # need to create an index to associate the nodes/contents with each item
-  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
-  
-  # store all information in data frame.
-  df <- data.frame(itemindex, nodenames, contents)
-  
-  # Convert from long to wide format
-  # sometimes titles are split onto multiple lines, so fix that up too
-  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
-  
-  return(df)
-}
-
-# grab "all" dataset from AusPol package
-all <- AustralianPoliticians::get_auspol('all')
-
-split_interjections_fedchamb <- function(main, interject, filename){
-  
-  #### step 1: add speech_no to make it easier to see where interjections happened 
-  main <- rowid_to_column(main, "speech_no")
-  
-  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
-  main_orig <- main
-  
-  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
-  
-  # start by re-formatting those with title of speaker or deputy speaker
-  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
-  if (nrow(interject)>0){
-    interject_names <- interject %>%
-      select(name) %>%
-      filter(str_detect(name, "\\(The")) %>%
-      unique() %>%
-      mutate(name = str_remove(name, "[[:punct:]][[:space:]]MP|[[:space:]]MP"),
[…]

### 2023-07-01 scripts/add_party_facts.R

@@ -1,162 +1,0 @@
-### script to add party facts column to our documents
-### code based on https://partyfacts.herokuapp.com/download/
-
-library(tidyverse)
-library(arrow)
-library(here)
-
-# download and read Party Facts mapping table
-file_name <- "partyfacts-mapping.csv"
-
-# download party facts mapping file
-if(!file_name %in% list.files()) {
-  url <- "https://partyfacts.herokuapp.com/download/external-parties-csv/"
-  download.file(url, file_name)
-}
-
-# read in party facts csv
-# note - there are parsing error warnings due to missingness
-partyfacts_raw <- read_csv(file_name, guess_max = 50000, show_col_types = F)
-
-# filter for only those for Australia, with a non-null party facts ID
-partyfacts_aus <- partyfacts_raw %>% filter(!is.na(partyfacts_id) & country=="AUS")
-
-# link datasets (select only linked parties) - using code from https://partyfacts.herokuapp.com/download/
-dataset_1 <- partyfacts_aus %>%  filter(dataset_key == "manifesto")
-dataset_2 <- partyfacts_aus %>% filter(dataset_key == "parlgov")
-link_table <- dataset_1 %>% inner_join(dataset_2, by = c("partyfacts_id", "country"))
-
-# select variables of interest
-link_table <- link_table %>% select(c(partyfacts_id, name_short.x, name_short.y, name.x, name.y))
-
-# pivot link table so we have all distinct name and abbreviations on separate rows
-pf_data <- link_table |>pivot_longer(name_short.x:name_short.y, names_to = "source", values_to = "name_short") |> 
-  pivot_longer(name.x:name.y, names_to = "name_source", values_to = "name") |> 
-  select(partyfacts_id, name_short, name) |> 
-  group_by(partyfacts_id, name) |> 
-  # this is b/c the abbreviation for Australian Greens is missing from one row
-  fill(name_short, .direction = "downup") |> 
-  ungroup() |> 
-  distinct() |> 
-  rename(name_short_pf = name_short,
-         name_pf = name)
-
-### Manual spelling/abbreviation fixes and filtering ###
-# a number of parties have two spelling variations in the party facts data, so let's only keep the ones that match AusPol spelling
-# and modify spelling if needed to match AusPol
-
-# fix Katter's name to match that in AusPol so we can merge, and only keep row where abbreviation is "KAT"
[…]

### 2023-07-01 scripts/auspol_lookup.R

@@ -1,336 +1,0 @@
-library(tidyverse)
-
-# read in auspol dataset
-all_auspol <- AustralianPoliticians::get_auspol('all')
-
-# read in ausPH dataset
-all_ausPH <- ausPH::getIndividuals()
-
-# from auspol dataset, filter for members of the house, and select variables we want, and add name variables in full capitals - this is for merging later
-auspol <- all_auspol %>% filter(member==1) %>% 
-  select(uniqueID, surname, firstName, commonName, allOtherNames, displayName, earlierOrLaterNames, gender, title, deathDate) %>% 
-  mutate(surname_cap = str_to_upper(surname),
-         firstName_cap = str_to_upper(firstName),
-         commonName_cap = str_to_upper(commonName),
-         allOtherNames_cap = str_to_upper(allOtherNames),
-         displayName_cap = str_to_upper(displayName),
-         earlierOrLaterNames_cap = str_to_upper(earlierOrLaterNames))
-
-# select variables we want from ausPH, grab surnames, create surname_gender variable to match things with in the next step
-ausPH <- all_ausPH %>% select(PHID, DisplayName, Gender, Electorate, Party) %>% 
-  rename(phid = PHID,
-         displayName = DisplayName,
-         gender = Gender) %>% 
-  mutate(surname = str_extract(displayName, "^[[:alpha:]]+(?=,)|^[[:upper:]][[:alpha:]]+-[[:upper:]][[:alpha:]]+(?=,)|^[[:upper:]]+[[:space:]][[:upper:]]+(?=,)|^[[:upper:]]'[[:alpha:]]+(?=,)")) %>% 
-  mutate(surname = ifelse(is.na(surname) & str_detect(displayName, "\\(formerly"),
-                          str_extract(displayName, "^[[:alpha:]]+(?= \\(formerly)"),
-                          surname)) %>% 
-  mutate(surname = ifelse(surname=="COOK" & str_detect(displayName, "Hume"),
-                          "HUME COOK",
-                          surname)) %>% 
-  mutate(gender = ifelse(gender=="Male", "male", gender),
-         gender = ifelse(gender=="Female", "female", gender)) 
-
-# capitalization issue we need to fix manually to ensure successful merge
-# remove 2nd bob brown b/c it isn't in AusPol and causing issues when we merge later
-# keep the one with AM suffix b/c that's the one who matches the birth year in AusPol
[…]

### 2023-07-01 scripts/check_time_stamps.R

@@ -1,36 +1,0 @@
-# script to detect bug in time stamps in our Hansard database
-library(tidyverse)
-
-# grab list of all file names
-all_files <- list.files("/Volumes/Verbatim/v3/hansard_1998_to_2022-csv")
-
-# define empty tibble to store loop output in
-times <- tibble()
-
-# define for loop to iterate over all our database files
-for (i in 1:length(all_files)) {
-  
-  # read in file
-  thisFile <- readr::read_csv(paste0("/Volumes/Verbatim/v3/hansard_1998_to_2022-csv/", all_files[i]), show_col_types = FALSE)
-  
-  # grab distinct time stamps and append date
-  thisFile_times <- thisFile %>% 
-    select(time.stamp) %>% 
-    filter(!is.na(time.stamp)) %>% 
-    #distinct() %>% 
-    mutate(date = str_remove(all_files[i], "\\.csv"),
-           time.stamp = as.character(time.stamp))
-  
-  # add above to tibble
-  times <- bind_rows(times, thisFile_times)
-  
-}
-
-# filter to only keep time stamps that do not fit the correct format hh:mm:ss
-wrong_times <- times %>% filter(!str_detect(time.stamp, "^\\d\\d:\\d\\d:\\d\\d$"))
-
-# grab random sample of 25% of wrong times to check
-sample_times <- slice_sample(wrong_times, prop = 0.25)
-
-### checked entire sample, all are confirmed transcription errors 
-### that is, these are all errors inherent to the XML files, not the result of our database construction process

### 2023-07-01 scripts/create_one_corpus.R

@@ -1,47 +1,0 @@
-### script to create a single corpus with our entire database
-
-# read in packages
-library(tidyverse)
-library(arrow)
-library(fs)
-
-# set working directory to where the database is stored
-# setwd("/Volumes/Verbatim/v4")
-
-# create list of all the CSV files
-all_files_csv <- dir_ls(path = "hansard_1998_to_2022-csv/")
-
-read_csv("hansard_1998_to_2022-csv/1998-03-02.csv")
-
-# read in and combine all CSVs, and extract just the date from each file name
-full_hansard <- all_files_csv %>% 
-  map_dfr(read_csv, col_types = list(name = col_character(),
-                                     order = col_double(),
-                                     speech_no = col_double(),
-                                     page.no = col_double(),
-                                     time.stamp = col_character(),
-                                     name.id = col_character(),
-                                     electorate = col_character(),
-                                     party = col_factor(),
-                                     in.gov = col_double(),
-                                     first.speech = col_double(),
-                                     body = col_character(),
-                                     fedchamb_flag = col_factor(),
-                                     question = col_factor(),
-                                     answer = col_factor(),
-                                     q_in_writing = col_factor(),
-                                     div_flag = col_factor(),
-                                     gender = col_factor(),
-                                     uniqueID = col_character(),
-                                     interject = col_factor()), .id = "date") %>% 
-  mutate(date = str_extract(date, "(?<=hansard_1998_to_2022-csv/)\\d{4}-\\d{2}-\\d{2}"))
-
-# export full_hansard data frame to CSV
-write_csv(full_hansard, "hansard_corpus_1998_to_2022.csv")
-
-# export full_hansard data frame to Parquet
-write_parquet(full_hansard, "hansard_corpus_1998_to_2022.parquet")
-
-# check file sizes
-file_size("hansard_corpus_1998_to_2022.csv")
-file_size("hansard_corpus_1998_to_2022.parquet")

### 2023-07-01 old_scripts/02-debate_info.R
cleaning repo

@@ -1,0 +1,113 @@
+# script for getting debate information 
+# content includes: business start, title, page number, type, body
+
+# load required packages
+library(XML)
+library(here)
+library(tidyverse)
+
+# define function
+parse_debate_info <- function(filename){
+  
+  # parse XML file
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+  
+  #################### CHAMBER ####################
+  ######### BUSINESS START #########
+  # store business start in tibble, add flag for federation chamber, extract date, body, and start time
+  bus_start_chamb <- tibble(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/business.start")), 
+                            fedchamb_flag = 0) %>% 
+    mutate(day_of_week = str_extract(body, "^[:alpha:]{0,6}day"),
+           date = as.Date(str_extract(body, "^[:alpha:]{0,6}day,[:space:][:digit:]{0,2}[:space:][:alpha:]{0,9}[:space:][:digit:]{0,4}"), "%A, %d %B %Y"),
+           body = str_remove(body, "^[:alpha:]{0,6}day,[:space:][:digit:]{0,2}[:space:][:alpha:]{0,9}[:space:][:digit:]{0,4}"),
+           start_time = str_extract(body, "[:digit:]{0,2}[:punct:][:digit:][:digit:]"))
+  
+  ######### DEBATE INFORMATION #########
+  # store debate information in tibble, correct variable class, add flags for sub-debate 1 and 2, and federation chamber
+  debate_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/debateinfo")),
+                             xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/debate.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no = as.numeric(page.no),
+           fedchamb_flag = 0,
+           sub1_flag = 0,
+           sub2_flag = 0)
+  
+  ######### DEBATE SPEECH #########
+  debate_speech_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/speech/talk.start/talker")),
+                             xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/speech/talk.text"))) %>% 
+    as_tibble() %>% 
[…]

### 2023-07-01 old_scripts/03-subdebate_1.R

@@ -1,0 +1,107 @@
+# script for getting sub-debate 1 info & text
+
+# load required packages
+library(XML)
+library(here)
+library(tidyverse)
+
+######## TO ADD - IF-ELSE TO SUBDEBATE 1 CHAMBER.
+
+# define function
+parse_sub1 <- function(filename){
+  
+  # parse XML
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+
+  # # define interjection words - commenting this out b/c found better way to do so after everything is split (see 99-everything script)
+  # interject_words <- c("Order!", "Order.", "interjecting", "Interjecting", "interjected", "Interjected", "interjections", "interjection", "Interjections", 
+  #                      "Interjection", "interject", "Interject", "The time for the discussion has concluded", "I thank the honourable member for", 
+  #                      "I thank the member for", "should withdraw that remark", "In accordance with standing order 193 the time for constituency statements has concluded", 
+  #                      "There being no further grievances, the debate is adjourned", "the time for members' statements has concluded", 
+  #                      "The original question was that this bill be now read a second time", "Is the amendment seconded?",
+  #                      "Do you want to seek the call again?", "The question is that the amendment be disagreed to", "The question now is that the bill be agreed to", 
+  #                      "will resume his seat", "will resume her seat", "will resume their seat") 
+  
+  #### CHAMBER ####
+  # store sub-debate 1 information & text in tibble, correct variable class, add flag for federation chamber
+  sub1_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebateinfo")),
+                           xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.text"))) %>%
+    as_tibble() %>% 
+    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
+  
[…]

### 2023-07-01 old_scripts/04-subdebate_2.R

@@ -1,0 +1,152 @@
+# script for getting sub-debate 2 info & text
+# note: sub-debate 2 is nested within sub-debate 1
+
+# load required packages
+library(XML)
+library(here)
+library(tidyverse)
+
+parse_sub2 <- function(filename){
+  
+  # parse XML
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+
+  #### CHAMBER ####
+  # store sub-debate 2 information & text in tibble, correct variable class, add flag for federation chamber
+  # include if-else statements in case sub-debate 2 does not exist
+  sub2_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/subdebateinfo")),
+                           xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/subdebate.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
+  
+  # sometimes sub-debate 2 isn't nested in sub-debate 1 (most recent date where this is the case is 2021-10-21)
+  # if the number of rows of this is > 1, let's bind that onto what we already have to ensure we aren't missing anything
+  if (nrow(as_tibble(cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebateinfo")),
+                           xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebate.text"))))) > 0) {
+    
+    sub2_info_chamb <- cbind(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebateinfo")),
+                             xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.2/subdebate.text"))) %>% 
+      as_tibble() %>% 
+      mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+             fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL}) %>% 
+      rbind(., sub2_info_chamb)
+    }
+  
[…]

### 2023-07-01 old_scripts/05-debate_interjections.R

@@ -1,0 +1,75 @@
+# script to get speech interjection info
+
+# load required packages
+library(XML)
+library(here)
+library(tidyverse)
+
+parse_interject <- function(filename){
+  
+  # parse XML
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+  
+  #### CHAMBER ####
+  # sub-debate 1 speech interjections in tibble, correct variable class, add flag for federation chamber
+  # use if-else statements in case there are no interjections
+  sub1_interject_chamb <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/speech/interjection/talk.start/talker")),
+                            xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/speech/interjection/talk.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no = {if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
+  
+  # sub-debate 2 speech interjections in tibble, correct variable class, add flag for federation chamber
+  # use if-else statements in case there are no interjections, or there is no sub-debate 2
+  sub2_interject_chamb <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/speech/interjection/talk.start/talker")),
+                            xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/subdebate.2/speech/interjection/talk.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no ={if("page.no" %in% names(.)) as.numeric(page.no) else NULL},
+           fedchamb_flag = {if("page.no" %in% names(.)) 0 else NULL})
+  
+  #### FEDERATION CHAMBER ####
+  # sub-debate 1 speech interjections in tibble, correct variable class, add flag for federation chamber
+  # don't need if-else here b/c this only executes if interjections exist in sub-debate 1 (condition of outer if statement)
+  sub1_interject_fed <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//fedchamb.xscript/debate/subdebate.1/speech/interjection/talk.start/talker")),
[…]

### 2023-07-01 old_scripts/06-q_and_a.R

@@ -1,0 +1,97 @@
+# script to get questions and answers
+# question time only takes place in sub-debate 1, in Chamber
+
+# load required packages
+library(XML)
+library(here)
+library(tidyverse)
+
+parse_q_and_a <- function(filename){
+  
+  # parse XML
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
+  
+  #### QUESTION AND ANSWER INFO AND TEXT ####
+  # store questions in tibble, correct variable class, add flag for question/answer, extract time
+  sub1_q <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/question/talk.start/talker")),
+              xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/question/talk.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no = as.numeric(page.no),
+           party = as.factor(party),
+           question = 1,
+           answer = 0,
+           time.stamp = str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d"))
+  
+  # store answers in tibble, correct variable class, add flag for question/answer, extract time
+  sub1_a <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/answer/talk.start/talker")),
+              xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/answer/talk.text"))) %>% 
+    as_tibble() %>% 
+    mutate(page.no = as.numeric(page.no),
+           party = as.factor(party),
+           question = 0,
+           answer = 1,
+           time.stamp = str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d"))
+  
+  # merge questions and answers, add flag for sub-debate 1 and 2, and federation chamber (always 0 b/c only have question time in chamber)
+  # had to add order and fix things up b/c sometimes time stamp is the same and then things are ordered wrong
+  # if a question and answer have the same time stamp, and the question is preceeded by another question, swap the question with the answer that has the same time stamp
+   sub1_q_a <- rbind(sub1_q, sub1_a) %>% 
+    arrange(time.stamp) %>% 
+    rowid_to_column("order") %>% 
[…]

### 2023-07-01 old_scripts/07-divisions_data.R

@@ -1,0 +1,129 @@
+# get divisions data
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab list of all file names
+files_all <- list.files("/Volumes/Verbatim/input/")
+
+# define empty tibble to store data in
+division_data <- tibble()
+
+for (i in 1:length(files_all)) {
+  # parse file
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", files_all[i]))
+  
+  # need to read the XML in in a different way for this so we can use the item_df function defined in global environment
+  xml_df <- read_xml(here("/Volumes/Verbatim/input/", files_all[i]))
+  
+  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript//division"), collectNames = F, homogeneous = T))>0){
+    
+    # grab header
+    if (nrow(item_df(xml_df, "chamber.xscript//division/division.header"))>0 & "para" %in% names(item_df(xml_df, "chamber.xscript//division/division.header"))) {
+      header <- item_df(xml_df, "chamber.xscript//division/division.header") %>% unnest(everything()) %>% 
+        select(-para)
+    } else if (nrow(item_df(xml_df, "chamber.xscript//division/division.header"))>0 & "body" %in% names(item_df(xml_df, "chamber.xscript//division/division.header"))) {
+      header <- item_df(xml_df, "chamber.xscript//division/division.header") %>% unnest(everything()) %>% 
[…]

### 2023-07-01 old_scripts/final_checks_v4.R

@@ -1,0 +1,75 @@
+# checking the new corpus, that has additional 2022 dates. just want to make sure there are no weird changes happening after re-validating the data
+
+library(tidyverse)
+
+new <- read_csv("/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/hansard_corpus_1998_to_2022.csv", col_types=list(name = col_character(),
+                                                                                                           order = col_double(),
+                                                                                                           speech_no = col_double(),
+                                                                                                           page.no = col_double(),
+                                                                                                           time.stamp = col_character(),
+                                                                                                           name.id = col_character(),
+                                                                                                           electorate = col_character(),
+                                                                                                           party = col_factor(),
+                                                                                                           in.gov = col_double(),
+                                                                                                           first.speech = col_double(),
+                                                                                                           body = col_character(),
+                                                                                                           fedchamb_flag = col_factor(),
+                                                                                                           question = col_factor(),
+                                                                                                           answer = col_factor(),
+                                                                                                           q_in_writing = col_factor(),
+                                                                                                           div_flag = col_factor(),
+                                                                                                           gender = col_factor(),
+                                                                                                           uniqueID = col_character(),
+                                                                                                           interject = col_factor(),
+                                                                                                           partyfacts_id = col_double()))
+
+old <- read_csv("/Volumes/Verbatim/v4/hansard_corpus_1998_to_2022-orig.csv", col_types=list(name = col_character(),
+                                                                                  order = col_double(),
+                                                                                  speech_no = col_double(),
+                                                                                  page.no = col_double(),
+                                                                                  time.stamp = col_character(),
+                                                                                  name.id = col_character(),
+                                                                                  electorate = col_character(),
[…]

### 2023-07-01 old_scripts/row-checks.R

@@ -1,0 +1,88 @@
+# script to check that number of rows hasn't changed as a result of new parsing method for 2011-2022
+
+new_method_filled <- list.files("/Volumes/Verbatim/output/main-filled-csv-2") %>% 
+  as_tibble() %>%
+  filter(value > "2012-06-28") %>% 
+  pull(value)
+
+old_method_filled <- list.files("/Volumes/Verbatim/output/main-filled-csv") %>% 
+  as_tibble() %>%
+  filter(value > "2012-06-28") %>% 
+  pull(value)
+
+row_check_filled <- tibble()
+
+for(i in 1:length(new_method_filled)){
+  thisFile_new <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-2/", new_method_filled[i]), show_col_types = F)
+  thisFile_old <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", old_method_filled[i]), show_col_types = F)
+  
+  row_check_filled <- tibble(nrow_new = nrow(thisFile_new),
+         nrow_old = nrow(thisFile_old),
+         date = str_extract(new_method_filled[i], "\\d{4}-\\d{2}-\\d{2}")) %>% 
+    bind_rows(row_check_filled, .)
+}
+
+
+row_check_filled <- row_check_filled %>% filter(nrow_new!=nrow_old)
+
+row_check_filled <- row_check_filled %>% filter(!(date %in% row_check$date))
+
+# THESE HAVE BEEN CHECKED, ALL GOOD
+rc_filled_new_less <- row_check_filled %>% filter(nrow_new < nrow_old)
+  
+rc_filled_new_more <- row_check_filled %>% filter(nrow_new > nrow_old)
+
+thisFile_new <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-2/", rc_filled_new_more$date[64], "-main-v2.csv"), show_col_types = F)
+thisFile_old <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv/", rc_filled_new_more$date[64], "-main-v2.csv"), show_col_types = F)
+
+nrow(thisFile_new)-nrow(thisFile_old)
+
+setdiff(select(thisFile_new, c(body)),select(thisFile_old, c(body)))
+setdiff(select(thisFile_old, c(body)),select(thisFile_new, c(body)))
+
[…]

### 2023-07-01 scripts/00-scrape_files.R
cleaning repo

@@ -3,7 +3,6 @@ library(heapsofpapers)
 library(tidyverse)
 library(here)
 
-# 2010-2022
 # read in excel sheet with URLs
 urls_df <- read.csv(here("urls/hansard-urls-1998-1999.csv"))
 
@@ -24,6 +23,20 @@ urls_df <- read.csv(here("hansard-urls-2000-2009.csv"))
 
 # two dates are missing XMLs so I left the url blank, filter those out
 urls_df <- urls_df %>% filter(URL!="")
+
+# define tibble with URLs and file names
+urls <- tibble(locations_are = urls_df$URL, 
+               save_here = urls_df$file_name)
+
+# get and save files
+heapsofpapers::get_and_save(data=urls,
+                            links = "locations_are",
+                            save_names = "save_here",
+                            dir = "/Volumes/Verbatim/input",
+                            dupe_strategy = "overwrite")
+
+# read in excel sheet with URLs
+urls_df <- read_csv(here("urls/hansard-urls-2010-2022.csv"))
 
 # define tibble with URLs and file names
 urls <- tibble(locations_are = urls_df$URL, 

### 2023-07-01 scripts/01-session_info.R

@@ -26,7 +26,7 @@ parse_session_info <- function(filename){
 }
 
 # ex: call function, pass file name
-parse_session_info("2018-08-23.xml")
+# parse_session_info("2018-08-23.xml")
 
 # grab list of all file names
 files_all <- list.files("/Volumes/Verbatim/input/")
@@ -41,4 +41,4 @@ for(i in 1:length(files_all)){
 }
 
 # export all session info
-write.csv(session_info_all, paste0("/Volumes/Verbatim/output/session_info/session_info_all.csv"), row.names = FALSE)
+write.csv(session_info_all, paste0("/Volumes/Verbatim/output/old-data/session_info/session_info_all.csv"), row.names = FALSE)

### 2023-07-01 scripts/05-everything-2011_to_2012-FINAL.R

@@ -1,0 +1,1912 @@
+# changing my approach to parsing so we don't have to merge stuff the way i originally had it
+# motivation - maintaining correct order
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+library(hms)
+
+# for parsing question time
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab "all" dataset from AusPol package
+all <- AustralianPoliticians::get_auspol('all')
+
+split_interjections_maincomm <- function(main, interject, filename){
+  
+  #### step 1: add speech_no to make it easier to see where interjections happened 
+  main <- rowid_to_column(main, "speech_no")
+  
+  # keep original/unmodified version of main to grab names/name.id/electorate/party info from later on
+  main_orig <- main
+  
+  # remove business start for now and we can add back in later
+  #main_bus_start <- main %>% filter(name=="business start")
+  #main <- main %>% filter(name!="business start")
+  
+  #### step 2: we need a list of names or phrases to separate speech based on ("interject_names")
+  
+  # start by re-formatting those with title of speaker or deputy speaker
+  # paste in a few forms to be safe (w/ and w/out first name), add unique() in case of repeats
+  if (nrow(interject)>0){
+    interject_names <- interject %>%
+      select(name) %>%
[…]

### 2023-07-01 scripts/14-summary_stats.Rmd
cleaning repo

---
title: "summary_stats"
author: "Lindsay Katz"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

```{r}
library(tidyverse)
library(here)
library(arrow)

# read in corpus
corpus <- read_parquet("/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")

# read in party table
party_table_final <- read_csv("../additional_data/PartyFacts_map.csv", show_col_types = F)
```

## Total distinct speeches by party

```{r}
# only for those parties with a party facts ID
s_by_party <- corpus |> select(date, speech_no, partyfacts_id, party) |> 
  mutate(party = as.character(ifelse(str_detect(party, "^Ind"), "IND", as.character(party)))) |> 
  group_by(date, partyfacts_id) |> 
  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
  group_by(partyfacts_id) |> 
  summarise(total_distinct_speeches = sum(n_distinct_speeches)) |> 
  filter(!is.na(partyfacts_id)) |> 
  left_join(party_table_final |> 
              select(-party_abb_hansard, -party_abb_auspol) |> 
              distinct() |> 
              # b/c Centre Alliance is current name and they have the same party facts ID
              filter(party_name_auspol!="Nick Xenophon Team"), 
            by="partyfacts_id")

# rename vars
s_by_party |> select(party_name_auspol, everything()) |> 
  rename("Party Name" = party_name_auspol,
         "PartyFacts ID" = partyfacts_id,
         "# Distinct Speeches" = total_distinct_speeches) |> 
  kableExtra::kable()
```

## Total daily distinct speeches

```{r}
s_by_day <- corpus %>% select(date, speech_no, fedchamb_flag) %>%
  group_by(date, fedchamb_flag) %>% 
  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T))

# plot
ggplot(s_by_day, aes(x=as.Date(date), y=n_distinct_speeches)) + 
  geom_point() +
  geom_smooth(method="loess") +
  facet_wrap(~fedchamb_flag, labeller = as_labeller(c(`0` = "Chamber", `1` = "Federation Chamber"))) +
  labs(x = "date", y = "# distinct speeches")
```

## Total yearly distinct speeches

```{r}
s_by_year <- corpus %>% select(date, speech_no, fedchamb_flag) %>%
  group_by(date, fedchamb_flag) %>% 
  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) %>% 
  mutate(year = str_extract(date, "^\\d{4}")) %>% 
  group_by(year, fedchamb_flag) %>% 
  summarise(total_speeches = sum(n_distinct_speeches))

# plot
s_by_year |> filter(year!="2022") |> 
ggplot(aes(x=as.numeric(year), y=total_speeches)) + 
  geom_point() +
  geom_smooth(method="loess") +
  facet_wrap(~fedchamb_flag, labeller = as_labeller(c(`0` = "Chamber", `1` = "Federation Chamber"))) +
  labs(x = "year", y = "# distinct speeches")
```

## Distinct speeches by electorate

```{r}
s_by_electorate <- corpus |> group_by(date, electorate) |> 
  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
  group_by(electorate) |> 
  summarise(total_speeches_electorate = sum(n_distinct_speeches)) |> 
  filter(!is.na(electorate))

# look at avg
s_by_electorate |> summarise(avg = mean(total_speeches_electorate))

# look at min and max
s_by_electorate |> 
  filter(total_speeches_electorate==min(total_speeches_electorate) |
           total_speeches_electorate==max(total_speeches_electorate))
```

## Annual proportion of interjections, by gender

```{r}
### INTERJECTIONS BY GENDER, ANNUALLY ###
interject_yr_sex <- corpus %>% select(date, gender, interject, fedchamb_flag) %>% 
  mutate(year = str_extract(date, "^\\d{4}"),
         gender = as.character(gender),
         gender = ifelse(is.na(gender), "unknown", gender)) %>% 
  group_by(year, gender, fedchamb_flag, interject) %>% 
  summarise(n = n()) |> 
  group_by(year, fedchamb_flag) |> 
  mutate(total_rows = sum(n)) |> 
  filter(interject==1) |> 
  group_by(year, gender, fedchamb_flag) |> 
  summarise(prop_interject = 100*n/total_rows) %>% 
  ungroup()

# plot
interject_yr_sex |> filter(year!="2022") |> 
ggplot(aes(x=as.numeric(year), y=prop_interject, color=as.factor(gender))) +
  geom_point() +
  geom_smooth() +
  facet_wrap(~fedchamb_flag, labeller = as_labeller(c(`0` = "Chamber", `1` = "Federation Chamber"))) +
  labs(y = "Percent Interjections", x = "Year", color = "Gender") +
  theme(legend.position="bottom")
```

## Daily proportion of interjections, by gender

```{r}
### INTERJECTIONS BY GENDER, DAILY ###
interject_day_sex <- corpus %>% select(date, gender, interject, fedchamb_flag) %>% 
  mutate(gender = as.character(gender),
         gender = ifelse(is.na(gender), "unknown", gender)) %>% 
  group_by(date, gender, fedchamb_flag, interject) %>% 
  summarise(n = n()) %>% 
  group_by(date, fedchamb_flag) |> 
  mutate(total_rows = sum(n)) |> 
  filter(interject==1) |> 
  group_by(date, gender, fedchamb_flag) |> 
  summarise(prop_interject = 100*n/total_rows) %>% 
  ungroup()

# plot
ggplot(interject_day_sex, aes(x=as.Date(date), y=prop_interject, color=as.factor(gender))) +
  geom_point(alpha=0.25) +
  geom_smooth(method="loess") +
  facet_wrap(~fedchamb_flag, labeller = as_labeller(c(`0` = "Chamber", `1` = "Federation Chamber")), scales = "free_y") +
  labs(y = "Percent Interjections", x = "Date", color = "Gender") +
  theme(legend.position="bottom")
```

## Daily word count

```{r}
## DAILY WORD COUNT ##
daily_word_count <- corpus |> 
  group_by(date, fedchamb_flag) |> 
  summarise(word_count = sum(str_count(body)))

# plot
ggplot(daily_word_count, aes(x=as.Date(date), y=word_count, color = fedchamb_flag, fill=fedchamb_flag)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  labs(x="Date", y="Word Count", color=NULL, fill=NULL) +
  scale_color_discrete(labels=c("Chamber", "Federation Chamber")) +
  scale_fill_discrete(labels=c("Chamber", "Federation Chamber"))
```

## Daily number of unique names

```{r}
## DAILY # UNIQUE NAMES ##
daily_unique_names <- corpus |> 
  select(date, name, fedchamb_flag) |> 
  filter(name!="business start" & name!="stage direction" & !str_detect(name, "SPEAKER")) |> 
  group_by(date, name, fedchamb_flag) |> 
  distinct() |> 
  group_by(date, fedchamb_flag) |> 
  summarise(n=n())

# plot
ggplot(daily_unique_names, aes(x=as.Date(date), y = n, color=fedchamb_flag, fill=fedchamb_flag)) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  labs(x="Date", y="# Unique Names", color=NULL, fill=NULL) +
  scale_color_discrete(labels=c("Chamber", "Federation Chamber")) +
  scale_fill_discrete(labels=c("Chamber", "Federation Chamber"))
```

### 2023-07-01 scripts/07-fill_details.R

@@ -1,0 +1,269 @@
+# script to maximize completeness of hansard data by using AusPol lookup table
+# main goal is to replace short names with full names, and fill in any missing party, electorate, gender, or uniqueID details
+library(tidyverse)
+
+# read in master lookup table
+master_orig <- read_csv("/Volumes/Verbatim/lookup_tables/member_lookup.csv", show_col_types = F) 
+speaker_list <- read_csv("/Volumes/Verbatim/lookup_tables/speaker_lookup.csv", show_col_types = F) %>% unique()
+
+# rename phid to match with hansard, and change parties to hansard abbreviations for consistency
+# these are from: https://www.aph.gov.au/Parliamentary_Business/Committees/Senate/woc/wocjanjun08/a02
+master_orig <- master_orig %>% 
+  rename(name.id = phid) %>% 
+  mutate(party = case_when(party=="Australian Democrats" ~ "AD",
+                           party=="Australian Greens" ~ "AG",
+                           party=="Australian Labor Party" ~ "ALP",
+                           party=="Independent" ~ "Ind",
+                           party=="Liberal Party of Australia" ~ "LP",
+                           party=="The Nationals" ~ "NATS",
+                           party=="National Party of Australia" ~ "NATS"))
+
+# do same for speaker list
+speaker_list <- speaker_list %>% 
+  rename(name.id = phid) %>% 
+  mutate(party = case_when(party=="Australian Democrats" ~ "AD",
+                           party=="Australian Greens" ~ "AG",
+                           party=="Australian Labor Party" ~ "ALP",
+                           party=="Independent" ~ "Ind",
+                           party=="Liberal Party of Australia" ~ "LP",
+                           party=="National Party of Australia" ~ "NATS"))
+
+# define file-name
+filename <- "2002-08-29-main.csv"
+
+fill_main <- function(filename) {
+  
+  # let's filter out people who have died prior to the Hansard date we're working with
+  # this will help reduce the number of people who share a surname and title
+  master <- master_orig %>% filter(deathDate >= paste0(str_remove(filename, "-main.csv")) | is.na(deathDate))
+  
+  # get list of people who share a title and surname (summarized by looking at form2 and form4)
+  # adding a few for ppl who got their seats in 2022 and aren't in AusPol yet
+  repeat_forms <- master %>% 
+    separate_rows(title, sep="\\|") %>% 
+    group_by(surname, title) %>% 
[…]

### 2023-07-01 scripts/08-data_validation.R

@@ -1,0 +1,341 @@
+# series of tests to validate our data
+library(tidyverse)
+
+# read in ausPH and auspol dataset
+ausPH <- ausPH::getIndividuals()
+
+# for some reason ausPH wasn't working so i got data myself
+#ausPH <-rjson::fromJSON(file="/Volumes/Verbatim/lookup_tables/individuals.json")[["value"]]|>dplyr::bind_rows()
+
+all <- AustralianPoliticians::get_auspol('all')
+party <- AustralianPoliticians::get_auspol('allbyparty')
+mps <- AustralianPoliticians::get_auspol('mps')
+
+# read in my lookup table
+lookup <- read_csv("/Volumes/Verbatim/lookup_tables/member_lookup.csv", show_col_types = F)
+
+# grab list of file names
+files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv-v2")
+
+##### test 1 - date in filename must match one date in our list of dates from all session headers
+
+# grab session header csv - code to make this is in 01-session_info.R script
+session_headers <- read_csv("/Volumes/Verbatim/output/old-data/session_info/session_info_all.csv", show_col_types = F) %>% pull(date)
+
+# extract dates from file names, convert to date
+dates_all <- files_all %>% as_tibble() %>% mutate(value = as.Date(str_remove(value, "-main-v2.csv"))) %>% pull(value)
+
+# check that dates of our filenames match dates from session headers
+setdiff(as.character(dates_all), as.character(session_headers))
+
+# one difference - 2009-06-03
+# our filename is right, there is an error in the session header - it was transcribed as 2009-06-04, I checked official release to confirm we're right
+
+##### test 2 - checks whether two lines that immediately follow each other have the same "body" - NEW
+test2 <- tibble()
+
+for(i in 1:length(files_all)) {
+  # read in file
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
+
+  test2 <-thisFile %>% filter(body == lead(body) | body == lag(body)) %>% 
+    select(name, order, body) %>% 
+    filter(body!="interjecting") %>% 
+    mutate(date = str_remove(files_all[i], "-main-v2.csv")) %>% 
+    bind_rows(test2, .)
+  
+}
+
[…]

### 2023-07-01 scripts/09-csv_to_parquet.R

@@ -1,0 +1,48 @@
+# script to convert all CSV files (version 2, filled) to parquet files, with correct variable classes
+library(arrow)
+library(tidyverse)
+
+# grab list of all file names
+files_all <- list.files("/Volumes/Verbatim/output/main-filled-csv-v2")
+
+files_all[i]
+fill_main(str_remove(files_all[i], "-v2"))
+
+# to loop through all our files
+for (i in 1:length(files_all)) {
+  
+  # read in file
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
+  
+  # modify variable classes
+  thisFile <- thisFile %>% mutate(party = as.factor(party),
+                                  gender = as.factor(gender))
+  
+  stopifnot(ncol(thisFile)==21 & c("name", "order","speech_no","page.no", "time.stamp", "name.id", "electorate", "party", "in.gov", "first.speech",
+                                   "body", "fedchamb_flag", "sub1_flag", "sub2_flag","question", "answer", "q_in_writing", "div_flag", "gender", "uniqueID", "interject") %in% names(thisFile))
+  
+  stopifnot(str_detect(thisFile$order, "^\\d+$"))
+  
+  # export as parquet file
+  write_parquet(thisFile, paste0("/Volumes/Verbatim/output/main-filled-parquet-v2/", str_remove(files_all[i], "csv"), "parquet"))
+  
+}
+
+
+# just a final check that all column names are right etc
+# to loop through all our files
+for (i in 1:length(files_all)) {
+  
+  # read in file
+  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-filled-csv-v2/", files_all[i]), show_col_types = F)
+  
+  # modify variable classes
+  thisFile <- thisFile %>% mutate(party = as.factor(party),
+                                  gender = as.factor(gender))
+  
+  stopifnot(ncol(thisFile)==21 & c("name", "order","speech_no","page.no", "time.stamp", "name.id", "electorate", "party", "in.gov", "first.speech",
+                                   "body", "fedchamb_flag", "sub1_flag", "sub2_flag","question", "answer", "q_in_writing", "div_flag", "gender", "uniqueID", "interject") %in% names(thisFile))
+  
+  stopifnot(str_detect(thisFile$order, "^\\d+$"))
+  
+}

### 2023-07-01 scripts/11-add_party_facts.R

@@ -1,0 +1,170 @@
+### script to add party facts column to our documents
+### code based on https://partyfacts.herokuapp.com/download/
+
+library(tidyverse)
+library(arrow)
+library(here)
+
+# download and read Party Facts mapping table
+file_name <- "partyfacts-mapping.csv"
+
+# download party facts mapping file
+if(!file_name %in% list.files()) {
+  url <- "https://partyfacts.herokuapp.com/download/external-parties-csv/"
+  download.file(url, file_name)
+}
+
+# read in party facts csv
+# note - there are parsing error warnings due to missingness
+partyfacts_raw <- read_csv(file_name, guess_max = 50000, show_col_types = F)
+
+# filter for only those for Australia, with a non-null party facts ID
+partyfacts_aus <- partyfacts_raw %>% filter(!is.na(partyfacts_id) & country=="AUS")
+
+# link datasets (select only linked parties) - using code from https://partyfacts.herokuapp.com/download/
+dataset_1 <- partyfacts_aus %>%  filter(dataset_key == "manifesto")
+dataset_2 <- partyfacts_aus %>% filter(dataset_key == "parlgov")
+link_table <- dataset_1 %>% inner_join(dataset_2, by = c("partyfacts_id", "country"))
+
+# select variables of interest
+link_table <- link_table %>% select(c(partyfacts_id, name_short.x, name_short.y, name.x, name.y))
+
+# pivot link table so we have all distinct name and abbreviations on separate rows
+pf_data <- link_table |> pivot_longer(name_short.x:name_short.y, names_to = "source", values_to = "name_short") |> 
+  pivot_longer(name.x:name.y, names_to = "name_source", values_to = "name") |> 
+  select(partyfacts_id, name_short, name) |> 
+  group_by(partyfacts_id, name) |> 
+  # this is b/c the abbreviation for Australian Greens is missing from one row
+  fill(name_short, .direction = "downup") |> 
+  ungroup() |> 
+  distinct() |> 
+  rename(name_short_pf = name_short,
+         name_pf = name)
+
+### Manual spelling/abbreviation fixes and filtering ###
+# a number of parties have two spelling variations in the party facts data, so let's only keep the ones that match AusPol spelling
+# and modify spelling if needed to match AusPol
+
+# fix Katter's name to match that in AusPol so we can merge, and only keep row where abbreviation is "KAT"
[…]

### 2023-07-01 scripts/12-create_one_corpus.R

@@ -1,0 +1,42 @@
+### script to create a single corpus with our entire database
+
+# read in packages
+library(tidyverse)
+library(arrow)
+library(fs)
+
+# create list of all the CSV files
+all_files_csv <- dir_ls(path = "/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/", regexp= "\\d{4}-\\d{2}-\\d{2}\\.csv")
+
+# read in and combine all CSVs, and extract just the date from each file name
+full_hansard <- all_files_csv %>% 
+  map_dfr(read_csv, col_types = list(name = col_character(),
+                                     order = col_double(),
+                                     speech_no = col_double(),
+                                     page.no = col_double(),
+                                     time.stamp = col_character(),
+                                     name.id = col_character(),
+                                     electorate = col_character(),
+                                     party = col_factor(),
+                                     in.gov = col_double(),
+                                     first.speech = col_double(),
+                                     body = col_character(),
+                                     fedchamb_flag = col_factor(),
+                                     question = col_factor(),
+                                     answer = col_factor(),
+                                     q_in_writing = col_factor(),
+                                     div_flag = col_factor(),
+                                     gender = col_factor(),
+                                     uniqueID = col_character(),
+                                     interject = col_factor()), .id = "date") %>% 
+  mutate(date = str_extract(date, "(?<=hansard_1998_to_2022-csv/)\\d{4}-\\d{2}-\\d{2}"))
+
+# export full_hansard data frame to CSV
+write_csv(full_hansard, "/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/hansard_corpus_1998_to_2022.csv")
+
+# export full_hansard data frame to Parquet
+write_parquet(full_hansard, "/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")
+
+# check file sizes
+file_size("/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/hansard_corpus_1998_to_2022.csv")
+file_size("/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")

### 2023-07-01 scripts/13-get_debate_topics.R

@@ -1,0 +1,84 @@
+# script to get debate and sub-debate 1 info from Hansard
+
+# read in necessary packages
+library(here)
+library(tidyverse)
+library(xml2)
+
+# define function which allows us to grab all XML node children that have the same name in order
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# define function to extract debate and subdebate 1 title and page number info
+get_debate_topics <- function(filename) {
+  
+  # parse xml file
+  xml_df <- read_xml(here("/Volumes/Verbatim/input/", filename))
+  
+  # grab sub-debate 1 titles and page numbers, create date variable
+  debate_info <- item_df(xml_df, "//debate/debateinfo | //subdebate.1/subdebateinfo") %>% 
+           # replace any null values with NA so the next mutate works
+    mutate(page.no =  map(page.no, `%||%`, NA),
+           # sometimes there are two page numbers, where the second is wrong (i.e. a debate title or time stamp or repeated number), so only take first
+           page.no = map_chr(page.no, first)) %>% 
+    unnest(title) %>% 
+    mutate(date = str_remove(filename, ".xml")) %>% 
+    select(date, itemindex, title, page.no)
+  
+  return(debate_info)
+}
+
+# grab list of Hansard XML files to iterate over
+files_all <- list.files("/Volumes/Verbatim/input/")
+
+# define empty tibble to store output
+all_debate_topics <- tibble()
+
+# define for loop, iterate over all XMLs
+for (i in 1:length(files_all)) {
+  
[…]

### 2023-07-01 old_scripts/sample_code_README.R
cleaning repo

@@ -1,0 +1,74 @@
+### sample code for readme ###
+
+# dependencies
+library(tidyverse)
+library(arrow)
+
+### how to read in a single sitting day file ###
+
+# set working directory to wherever you've downloaded the Hansard data
+setwd("/Volumes/Verbatim/v3/")
+
+# csv
+hansard_csv <- readr::read_csv("hansard_1998_to_2022-csv/2000-06-05.csv", 
+                               col_types = list(name = col_character(),
+                                                order = col_double(),
+                                                speech_no = col_double(),
+                                                page.no = col_double(),
+                                                time.stamp = col_character(),
+                                                name.id = col_character(),
+                                                electorate = col_character(),
+                                                party = col_factor(),
+                                                in.gov = col_double(),
+                                                first.speech = col_double(),
+                                                body = col_character(),
+                                                fedchamb_flag = col_factor(),
+                                                question = col_factor(),
+                                                answer = col_factor(),
+                                                q_in_writing = col_factor(),
+                                                div_flag = col_factor(),
+                                                gender = col_factor(),
+                                                uniqueID = col_character(),
+                                                interject = col_factor(),
+                                                partyfacts_id = col_double()))
+
+# parquet
+hansard_parquet <- arrow::read_parquet("hansard_1998_to_2022-parquet/2000-06-05.parquet")
+
+### use the corpus, filter for dates of interest, and split days into individual tibbles ###
+hansard_corpus <- arrow::read_parquet("hansard_corpus_1998_to_2022.parquet")
+
+# filter for dates of interest, and split each date into list of separate tibbles
+hansard_1990s <- hansard_corpus %>% 
+  filter(str_detect(date, "^199")) %>% 
+  group_split(date)
+
+### how to filter out stage directions ###
+
+# filter out rows where name includes "stage direction", and drop original order variable and create new one
+hansard_csv %>% 
+  filter(!str_detect(name, "stage direction")) %>% 
+  select(-order) %>% 
+  rowid_to_column("order")
+
+### how to merge debate topics with data
+
+# read in Hansard file
+hansard_parquet <- arrow::read_parquet("hansard_1998_to_2022-parquet/2000-06-05.parquet")
+
[…]

### 2023-07-01 old_scripts/summary_stats.R

@@ -1,0 +1,156 @@
+# script to get summary statistics for Hansard
+library(tidyverse)
+library(here)
+library(arrow)
+
+# read in corpus
+corpus <- read_parquet("/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")
+
+# read in party table
+party_table_final <- read_csv("additional_data/PartyFacts_map.csv", show_col_types = F)
+
+### TOTAL DISTINCT SPEECHES BY PARTY ###
+# only for those parties with a party facts ID
+s_by_party <- corpus |> select(date, speech_no, partyfacts_id, party) |> 
+  mutate(party = as.character(ifelse(str_detect(party, "^Ind"), "IND", as.character(party)))) |> 
+  group_by(date, partyfacts_id) |> 
+  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
+  group_by(partyfacts_id) |> 
+  summarise(total_distinct_speeches = sum(n_distinct_speeches)) |> 
+  filter(!is.na(partyfacts_id)) |> 
+  left_join(party_table_final |> 
+              select(-party_abb_hansard, -party_abb_auspol) |> 
+              distinct() |> 
+              # b/c Centre Alliance is current name and they have the same party facts ID
+              filter(party_name_auspol!="Nick Xenophon Team"), 
+            by="partyfacts_id")
+
+# rename vars, kable
+s_by_party |> select(party_name_auspol, everything()) |> 
+  rename("Party Name" = party_name_auspol,
+         "PartyFacts ID" = partyfacts_id,
+         "# Distinct Speeches" = total_distinct_speeches) |> 
+  kableExtra::kable()
+
+### TOTAL DAILY DISTINCT SPEECHES ###
+s_by_day <- corpus %>% select(date, speech_no, fedchamb_flag) %>%
+  group_by(date, fedchamb_flag) %>% 
+  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T))
+
+# plot
+ggplot(s_by_day, aes(x=as.Date(date), y=n_distinct_speeches)) + 
+  geom_point() +
+  geom_smooth(method="loess") +
[…]

### 2023-07-01 old_scripts/06-q_and_a.R
updates

@@ -1,97 +1,0 @@
-# script to get questions and answers
-# question time only takes place in sub-debate 1, in Chamber
-
-# load required packages
-library(XML)
-library(here)
-library(tidyverse)
-
-parse_q_and_a <- function(filename){
-  
-  # parse XML
-  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", filename))
-  
-  #### QUESTION AND ANSWER INFO AND TEXT ####
-  # store questions in tibble, correct variable class, add flag for question/answer, extract time
-  sub1_q <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/question/talk.start/talker")),
-              xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/question/talk.text"))) %>% 
-    as_tibble() %>% 
-    mutate(page.no = as.numeric(page.no),
-           party = as.factor(party),
-           question = 1,
-           answer = 0,
-           time.stamp = str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d"))
-  
-  # store answers in tibble, correct variable class, add flag for question/answer, extract time
-  sub1_a <- c(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/answer/talk.start/talker")),
-              xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript/debate/subdebate.1/answer/talk.text"))) %>% 
-    as_tibble() %>% 
-    mutate(page.no = as.numeric(page.no),
-           party = as.factor(party),
-           question = 0,
-           answer = 1,
-           time.stamp = str_extract(body, "\\d\\d:\\d\\d|\\d:\\d\\d"))
-  
-  # merge questions and answers, add flag for sub-debate 1 and 2, and federation chamber (always 0 b/c only have question time in chamber)
-  # had to add order and fix things up b/c sometimes time stamp is the same and then things are ordered wrong
-  # if a question and answer have the same time stamp, and the question is preceeded by another question, swap the question with the answer that has the same time stamp
-   sub1_q_a <- rbind(sub1_q, sub1_a) %>% 
-    arrange(time.stamp) %>% 
-    rowid_to_column("order") %>% 
[…]

### 2023-07-01 old_scripts/check_names.R

@@ -1,88 +1,0 @@
-# code to check for rows where names are missing
-
-library(tidyverse)
-
-files_1998 <- list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^1999-|^1998-")) %>% pull()
-files_2000 <- list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^2000-|^2001-|^2002-|^2003-|^2004-|^2005-|^2006-|^2007-|^2008-|^2009-|^2010-|^2011-")) %>% filter(value <= "2011-03-24.xml") %>% pull()
-files_2011 <- list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^2011-|^2012-")) %>% filter(value >= "2011-05-10.xml" & value <= "2012-06-28.xml") %>% pull(value)
-files_2012 <-  list.files("/Volumes/Verbatim/input/") %>% as_tibble() %>% filter(str_detect(value, "^2012-|^2013-|^2014-|^2015-|^2016-|^2017-|^2018-|^2019-|^2020-|^2021-|^2022-")) %>% filter(value>"2012-06-28.xml") %>% pull(value)
-
-missingNames1998 <- tibble()
-missingNames2000 <- tibble()
-missingNames2011 <- tibble()
-missingNames2012 <- tibble()
-
-
-# 1998
-for (i in 1:length(files_1998)){
-  
-  thisDate <- str_remove(files_1998[i], "\\.xml$")
-  
-  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-1998-1999/", thisDate, "-main.csv"), show_col_types = F)
-  
-  missingNames1998 <- thisFile %>% filter(is.na(name)) %>% 
-    select(order, body) %>% 
-    bind_cols(., thisDate %>% as_tibble()) %>% 
-    rename(date = value) %>% 
-    bind_rows(., missingNames1998)
-  
-}
-
-# 2000
-for (i in  1:length(files_2000)){
-  
-  thisDate <- str_remove(files_2000[i], "\\.xml$")
-  
-  thisFile <- read_csv(paste0("/Volumes/Verbatim/output/main-2000-2011/", thisDate, "-main.csv"), show_col_types = F)
-  
-  missingNames2000 <- thisFile %>% filter(is.na(name)) %>% 
-    select(order, body) %>% 
[…]

### 2023-07-01 old_scripts/summary_stats.R

@@ -1,156 +1,0 @@
-# script to get summary statistics for Hansard
-library(tidyverse)
-library(here)
-library(arrow)
-
-# read in corpus
-corpus <- read_parquet("/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")
-
-# read in party table
-party_table_final <- read_csv("additional_data/PartyFacts_map.csv", show_col_types = F)
-
-### TOTAL DISTINCT SPEECHES BY PARTY ###
-# only for those parties with a party facts ID
-s_by_party <- corpus |> select(date, speech_no, partyfacts_id, party) |> 
-  mutate(party = as.character(ifelse(str_detect(party, "^Ind"), "IND", as.character(party)))) |> 
-  group_by(date, partyfacts_id) |> 
-  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
-  group_by(partyfacts_id) |> 
-  summarise(total_distinct_speeches = sum(n_distinct_speeches)) |> 
-  filter(!is.na(partyfacts_id)) |> 
-  left_join(party_table_final |> 
-              select(-party_abb_hansard, -party_abb_auspol) |> 
-              distinct() |> 
-              # b/c Centre Alliance is current name and they have the same party facts ID
-              filter(party_name_auspol!="Nick Xenophon Team"), 
-            by="partyfacts_id")
-
-# rename vars, kable
-s_by_party |> select(party_name_auspol, everything()) |> 
-  rename("Party Name" = party_name_auspol,
-         "PartyFacts ID" = partyfacts_id,
-         "# Distinct Speeches" = total_distinct_speeches) |> 
-  kableExtra::kable()
-
-### TOTAL DAILY DISTINCT SPEECHES ###
-s_by_day <- corpus %>% select(date, speech_no, fedchamb_flag) %>%
-  group_by(date, fedchamb_flag) %>% 
-  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T))
-
-# plot
-ggplot(s_by_day, aes(x=as.Date(date), y=n_distinct_speeches)) + 
-  geom_point() +
-  geom_smooth(method="loess") +
[…]

### 2023-07-03 scripts/13-summary_stats.Rmd
rename scripts and update readme

--- 2023-07-01 scripts/14-summary_stats.Rmd
@@
 library(tidyverse)
-library(here)
 library(arrow)
@@
 
-## Total distinct speeches by party
+## Total distinct speeches by party facts ID
 
@@
 s_by_party |> select(party_name_auspol, everything()) |> 
+  arrange(desc(total_distinct_speeches)) |> 
+  rename("Party Name" = party_name_auspol,
+         "PartyFacts ID" = partyfacts_id,
+         "# Distinct Speeches" = total_distinct_speeches) |> 
+  kableExtra::kable()
+```
+
+## Total distinct speeches by Australian Politicians party name
+
+```{r}
+corpus |> select(date, speech_no, party) |> 
+  filter(!is.na(party)) |> 
+  left_join(party_table_final, by=c("party" = "party_abb_hansard")) |> 
+  group_by(date, party_abb_auspol, party_name_auspol) |> 
+  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
+  group_by(party_abb_auspol, party_name_auspol) |> 
+  summarise(total_distinct_speeches = sum(n_distinct_speeches))
+
+# only for those parties with a party facts ID
+s_by_party <- corpus |> select(date, speech_no, partyfacts_id, party) |> 
+  mutate(party = as.character(ifelse(str_detect(party, "^Ind"), "IND", as.character(party)))) |> 
+  group_by(date, partyfacts_id) |> 
+  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
+  group_by(partyfacts_id) |> 
+  summarise(total_distinct_speeches = sum(n_distinct_speeches)) |> 
+  filter(!is.na(partyfacts_id)) |> 
+  left_join(party_table_final |> 
+              select(-party_abb_hansard, -party_abb_auspol) |> 
+              distinct() |> 
+              # b/c Centre Alliance is current name and they have the same party facts ID
+              filter(party_name_auspol!="Nick Xenophon Team"), 
+            by="partyfacts_id")
+
+# rename vars
+s_by_party |> select(party_name_auspol, everything()) |> 
+  arrange(desc(total_distinct_speeches)) |> 
   rename("Party Name" = party_name_auspol,
@@
 
-# look at min and max
-s_by_electorate |> 
-  filter(total_speeches_electorate==min(total_speeches_electorate) |
-           total_speeches_electorate==max(total_speeches_electorate))
+# look at top 10
+s_by_electorate |> arrange(desc(total_speeches_electorate)) |> slice(1:10)
+
+# look at bottom 10
+s_by_electorate |> arrange(total_speeches_electorate) |> slice(1:10)
 ```
@@
 # plot
+# remove 2022 b/c incomplete
 interject_yr_sex |> filter(year!="2022") |> 
@@
 daily_word_count <- corpus |> 
-  group_by(date, fedchamb_flag) |> 
-  summarise(word_count = sum(str_count(body)))
+  group_by(date) |> 
+  summarise(word_count = sum(str_count(body), na.rm = T))
+
+daily_word_count |> arrange(word_count)
+
+daily_word_count |> filter(is.na(word_count))
 
 # plot
-ggplot(daily_word_count, aes(x=as.Date(date), y=word_count, color = fedchamb_flag, fill=fedchamb_flag)) +
+ggplot(daily_word_count, aes(x=as.Date(date), y=word_count)) +
   geom_point(alpha = 0.5) +
   geom_smooth() +
-  labs(x="Date", y="Word Count", color=NULL, fill=NULL) +
-  scale_color_discrete(labels=c("Chamber", "Federation Chamber")) +
-  scale_fill_discrete(labels=c("Chamber", "Federation Chamber"))
+  labs(x="Date", y="Word Count") +
+  theme_bw()
+
+ggsave("../paper/word_count.png", width=8, height=5)
 ```
@@
   select(date, name, fedchamb_flag) |> 
-  filter(name!="business start" & name!="stage direction" & !str_detect(name, "SPEAKER")) |> 
+  filter(name!="business start" & name!="stage direction") |> 
   group_by(date, name, fedchamb_flag) |> 
@@
   geom_point(alpha = 0.5) +
-  geom_smooth() +
-  labs(x="Date", y="# Unique Names", color=NULL, fill=NULL) +
+  geom_smooth(method="loess") +
+  labs(x="Date", y="Number of unique names", color=NULL, fill=NULL) +
   scale_color_discrete(labels=c("Chamber", "Federation Chamber")) +
-  scale_fill_discrete(labels=c("Chamber", "Federation Chamber"))
+  scale_fill_discrete(labels=c("Chamber", "Federation Chamber")) +
+  theme_bw()
+
+ggsave("n_unique_names.png", path = "../paper/", width=8, height = 5)
 ```
+
+## Annual number of divisions
+
+```{r}
+corpus |> select(date, div_flag) |> 
+  mutate(year = str_extract(date, "^\\d{4}")) |> 
+  filter(div_flag==1) |> 
+  group_by(year) |> 
+  summarise(n_divs = n())
+
+# not sure why the numbers are so low for 2012 onward
+```
+
+## Meeting per year - chamber and federation chamber
+
+```{r}
+meeting_per_year <- corpus |> select(date, fedchamb_flag) |>
+  mutate(year = str_extract(date, "^\\d{4}")) |> 
+  group_by(year, fedchamb_flag) |> 
+  summarise(n_sittings = n_distinct(date))
+```
+
+These match well with the numbers [here](https://www.aph.gov.au/-/media/02_Parliamentary_Business/22_Chamber_Documents/224_Statistics/House_of_Representatives/Statistics_Historical/sittings_statistics.pdf?la=en&hash=5B5E7E9518C4D7A416D0846FE0D44E063A4AB3FD)
+
+```{r}
+sitting_stats <- read_csv("~/Desktop/RA/sitting_stats.txt", col_names = FALSE)
+
+sitting_stats <- sitting_stats |> select(X1, X3, X5) |> 
+  rename(year = X1,
+         chamb = X3,
+         fed_chamb = X5) |> 
+  pivot_longer(chamb:fed_chamb, names_to = "fedchamb_flag", values_to = "official_stats")
+
+# find years where there is a discrepancy in # of meetings
+# care more about chamber b/c often fedchamb is wrongly transcribed so there are bound to be discrepancies
+meeting_per_year |> mutate(fedchamb_flag = case_when(fedchamb_flag == 0 ~"chamb",
+                                                     fedchamb_flag == 1 ~"fed_chamb"),
+                           year = as.numeric(year)) |> 
+  left_join(sitting_stats, by=c("year", "fedchamb_flag")) |> 
+  filter(year!=2022) |> 
+  mutate(diff = abs(n_sittings-official_stats)) |> 
+  filter(diff!=0) |> 
+  arrange(desc(diff))
+```
+
+## Q in writing and Q without notice per year
+
+```{r}
+corpus |> select(date, question, q_in_writing) |>
+  mutate(year = str_extract(date, "^\\d{4}")) |> 
+  filter(question==1) |> 
+  group_by(year, q_in_writing) |> 
+  summarise(n())
+```
+
+https://www.aph.gov.au/-/media/02_Parliamentary_Business/22_Chamber_Documents/224_Statistics/House_of_Representatives/Statistics_Historical/questions_statistics.pdf?la=en&hash=A3B9F79402CC7D15B576EDAF1BC28259CDEC9553

### 2023-07-03 scripts/00-scrape_files.R

@@ -19,7 +19,7 @@ heapsofpapers::get_and_save(data=urls,
 
 # 2000-2009
 # read in excel sheet with URLs
-urls_df <- read.csv(here("hansard-urls-2000-2009.csv"))
+urls_df <- read.csv(here("urls/hansard-urls-2000-2009.csv"))
 
 # two dates are missing XMLs so I left the url blank, filter those out
 urls_df <- urls_df %>% filter(URL!="")
@@ -48,7 +48,3 @@ heapsofpapers::get_and_save(data=urls,
                             save_names = "save_here",
                             dir = "/Volumes/Verbatim/input",
                             dupe_strategy = "overwrite")
-
-
-
-

### 2023-07-03 scripts/11-create_one_corpus.R

@@ -32,11 +32,11 @@ full_hansard <- all_files_csv %>%
   mutate(date = str_extract(date, "(?<=hansard_1998_to_2022-csv/)\\d{4}-\\d{2}-\\d{2}"))
 
 # export full_hansard data frame to CSV
-write_csv(full_hansard, "/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/hansard_corpus_1998_to_2022.csv")
+write_csv(full_hansard, "/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.csv")
 
 # export full_hansard data frame to Parquet
-write_parquet(full_hansard, "/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")
+write_parquet(full_hansard, "/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.parquet")
 
 # check file sizes
-file_size("/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/hansard_corpus_1998_to_2022.csv")
-file_size("/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")
+file_size("/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.csv")
+file_size("/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.parquet")

### 2023-07-03 scripts/12-get_debate_topics.R

@@ -68,14 +68,14 @@ for (i in 1:length(files_all)) {
 all_debate_topics <- all_debate_topics %>% rename(item_index = itemindex) %>% mutate(page.no = as.double(page.no))
 
 # export tibble as csv and parquet files
-readr::write_csv(all_debate_topics, here("~/Desktop/RA/hansard/additional_data/all_debate_topics.csv"))
-arrow::write_parquet(all_debate_topics, here("~/Desktop/RA/hansard/additional_data/all_debate_topics.parquet"))
+readr::write_csv(all_debate_topics, here("/Volumes/Verbatim/v4/hansard-debate_topics/all_debate_topics.csv"))
+arrow::write_parquet(all_debate_topics, here("/Volumes/Verbatim/v4/hansard-debate_topics/all_debate_topics.parquet"))
 
 # example where there were two page.no nodes and one was not an actual page number:
 # 2005-05-12, cmd+F "<page.no>Biofuels</page.no>", cmd+F "<page.no>14.36 pm</page.no>"
 
 # check that things look ok
-topics <- read_csv("~/Desktop/RA/hansard/additional_data/all_debate_topics.csv", show_col_types = F)
+topics <- read_csv("/Volumes/Verbatim/v4/hansard-debate_topics/all_debate_topics.csv", show_col_types = F)
 
 # all page numbers have a digit and are numeric (read in as a double with no issue)
 topics |> filter(!str_detect(page.no, "\\d"))

### 2023-07-03 scripts/13-summary_stats.Rmd
summary stats

@@
 # read in corpus
-corpus <- read_parquet("/Volumes/Verbatim/v4/hansard_1998_to_2022-parquet/hansard_corpus_1998_to_2022.parquet")
+corpus <- read_parquet("/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.parquet")
 
@@
 ```{r}
-corpus |> select(date, speech_no, party) |> 
+### need to confirm party abbreviation mapping!!!!!
+s_by_party_name <- corpus |> select(date, speech_no, party) |> 
   filter(!is.na(party)) |> 
@@
   group_by(party_abb_auspol, party_name_auspol) |> 
-  summarise(total_distinct_speeches = sum(n_distinct_speeches))
+  summarise(total_distinct_speeches = sum(n_distinct_speeches)) |> 
+  select(party_name_auspol, everything()) |> 
+  arrange(desc(total_distinct_speeches)) |> 
+  filter(!is.na(party_abb_auspol)) |> 
+  rename("Party Name" = party_name_auspol,
+         "Party Abbreviation" = party_abb_auspol,
+         "Total # of Speeches" = total_distinct_speeches)
 
-# only for those parties with a party facts ID
-s_by_party <- corpus |> select(date, speech_no, partyfacts_id, party) |> 
-  mutate(party = as.character(ifelse(str_detect(party, "^Ind"), "IND", as.character(party)))) |> 
-  group_by(date, partyfacts_id) |> 
-  summarise(n_distinct_speeches = n_distinct(speech_no, na.rm=T)) |> 
-  group_by(partyfacts_id) |> 
-  summarise(total_distinct_speeches = sum(n_distinct_speeches)) |> 
-  filter(!is.na(partyfacts_id)) |> 
-  left_join(party_table_final |> 
-              select(-party_abb_hansard, -party_abb_auspol) |> 
-              distinct() |> 
-              # b/c Centre Alliance is current name and they have the same party facts ID
-              filter(party_name_auspol!="Nick Xenophon Team"), 
-            by="partyfacts_id")
+write_csv(s_by_party_name, "../paper/s_by_party_name.csv")
+```
 
-# rename vars
-s_by_party |> select(party_name_auspol, everything()) |> 
-  arrange(desc(total_distinct_speeches)) |> 
-  rename("Party Name" = party_name_auspol,
-         "PartyFacts ID" = partyfacts_id,
-         "# Distinct Speeches" = total_distinct_speeches) |> 
-  kableExtra::kable()
+```{r}
+parties_auspol <- AustralianPoliticians::get_auspol('allbyparty')
+
+parties_auspol |> select(partyAbbrev, partyName) |> distinct()
 ```
@@
 # plot
-ggplot(s_by_day, aes(x=as.Date(date), y=n_distinct_speeches)) + 
-  geom_point() +
-  geom_smooth(method="loess") +
-  facet_wrap(~fedchamb_flag, labeller = as_labeller(c(`0` = "Chamber", `1` = "Federation Chamber"))) +
-  labs(x = "date", y = "# distinct speeches")
+s_by_day |> filter(n_distinct_speeches!=0) |> 
+  ggplot(aes(x=as.Date(date), y=n_distinct_speeches, color=fedchamb_flag, fill=fedchamb_flag)) + 
+  geom_point(alpha=0.5) +
+  geom_smooth() +
+  #facet_wrap(~fedchamb_flag, labeller = as_labeller(c(`0` = "Chamber", `1` = "Federation Chamber"))) +
+  labs(x = "Date", y = "Number of speeches", color=NULL, fill=NULL) +
+  theme_bw() +
+  scale_color_discrete(labels=c("Chamber", "Federation Chamber")) +
+  scale_fill_discrete(labels=c("Chamber", "Federation Chamber"))
+
+ggsave("../paper/n_daily_speeches.png", width=8, height=5)
 ```
@@
   labs(y = "Percent Interjections", x = "Year", color = "Gender") +
-  theme(legend.position="bottom")
+  theme(legend.position="bottom") +
+  theme_bw()
 ```
@@
   labs(y = "Percent Interjections", x = "Date", color = "Gender") +
-  theme(legend.position="bottom")
+  theme(legend.position="bottom") +
+  theme_bw()
 ```
@@
 
-These match well with the numbers [here](https://www.aph.gov.au/-/media/02_Parliamentary_Business/22_Chamber_Documents/224_Statistics/House_of_Representatives/Statistics_Historical/sittings_statistics.pdf?la=en&hash=5B5E7E9518C4D7A416D0846FE0D44E063A4AB3FD)
+Let's compare to the numbers [here](https://www.aph.gov.au/-/media/02_Parliamentary_Business/22_Chamber_Documents/224_Statistics/House_of_Representatives/Statistics_Historical/sittings_statistics.pdf?la=en&hash=5B5E7E9518C4D7A416D0846FE0D44E063A4AB3FD).
 
@@
 
+# rename select vars based on columns in pdf linked above
 sitting_stats <- sitting_stats |> select(X1, X3, X5) |> 
@@
 # care more about chamber b/c often fedchamb is wrongly transcribed so there are bound to be discrepancies
+# remove 2022 b/c we don't have complete year's data
 meeting_per_year |> mutate(fedchamb_flag = case_when(fedchamb_flag == 0 ~"chamb",
@@
 ```
+I was able to manually check the discrepancies for the Chamber sittings, and found that there are two days in 1998 (May 6th and 7th) and two days in 2004 (February 10th and May 12th) where the House sat in the Chamber, but there is no XML transcript for Hansard available.
+The Federation Chamber discrepancies may be due to transcription errors - that is, Federation Chamber proceedings being nested in the Chamber proceedings node in the XML.
 
+```{r, eval=F, echo=F}
 ## Q in writing and Q without notice per year
-
-```{r}
 corpus |> select(date, question, q_in_writing) |>
@@
   summarise(n())
+
+#https://www.aph.gov.au/-/media/02_Parliamentary_Business/22_Chamber_Documents/224_Statistics/House_of_Representatives/Statistics_Historical/questions_statistics.pdf?la=en&hash=A3B9F79402CC7D15B576EDAF1BC28259CDEC9553
 ```
-
-https://www.aph.gov.au/-/media/02_Parliamentary_Business/22_Chamber_Documents/224_Statistics/House_of_Representatives/Statistics_Historical/questions_statistics.pdf?la=en&hash=A3B9F79402CC7D15B576EDAF1BC28259CDEC9553

### 2023-07-03 paper/paper-nature-revised.qmd
more paper revisions

@@
 
-> ```{r}
+> ```{r, eval = F, echo=F}
+> # pasting text in directly to avoid issues with rendering.
 > #| warning: false
@@
 > ```
+
+> "Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great pleasure to share with the House that Windaroo Valley State High School has qualified for the finals of the Australian Space Design Competition, to begin in January next year.
+The competition is regarded as the premier STEM competition for high school students and is recognised by universities around the country.
+The students are required to respond to industry-level engineering and requests for tender for design and---The SPEAKER: Order!
+In accordance with standing order 43, the time for members' statements has concluded."
 
@@
 Our database is available in both CSV and parquet formats.
-It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are **1,527 individual sitting day** files for each format.
+It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format.
 **Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
@@
 The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.
-We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for.
+We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag **those rows where "The House divided." was detected in the body variable**.
 The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, **and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project [website](https://partyfacts.herokuapp.com).**[^3] Details on the usage of `uniqueID` **and `partyfacts_id`** will be provided in @sec-usage.
@@
 
-[^3]: **Note that in accordance with the code provided on the Party Facts \[downloads page\](https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov.
+[^3]: **Note that in accordance with the code provided on the Party Facts [downloads page](https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov.
 Details on these datasets can be found here: https://partyfacts.herokuapp.com/documentation/datasets/.**
@@
 As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data.
-Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package data in this dataframe for completeness.**
+Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package for completeness.**
 
@@
                                     "Party abbreviation as transcribed in the Hansard data",
-                                    "Party abbreviation as recorded in the `AustralianPoliticians` data",
-                                    "Party full name as recorded in the `AustralianPoliticians` data"))
+                                    "Party abbreviation as recorded in the AustralianPoliticians R package data",
+                                    "Party full name as recorded in the AustralianPoliticians R package data"))
 
@@
 spoken content).
-This test detected **130** dates on which duplicate statements were made, and one immediately follows the other.
+This test detected **131** dates on which duplicate statements were made, and one immediately follows the other.
 Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well.
@@
 Using these dates, we check that each person speaking on each sitting day is in fact an MP on that day.
+
+## Summary Statistics
+
+**To further explore the quality of our data and detect any unexpected or distinct trends, we generated a number of summary statistics using the complete Hansard corpus.
+First, we looked at the number of speeches made each day, disaggregated by Chamber and Federation Chamber debate venues.
+As shown in @fig-dailyspeeches, there are consistently more speeches made in the Chamber proceedings than in the Federation Chamber, which aligns with the wider scope of business covered in the Chamber.
+Further, in both debate venues, the number of speeches each day appears to have increased slightly over time.**
+
+![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}
+
+**Next, we explored the number of unique names detected on each sitting day disaggregated by debate venue, visualized in @fig-names.
+As expected, there are generally more individual MPs detected to be present in the Chamber proceedings in our data than in the Federation Chamber proceedings.
+Further, in both venues, the number of individuals detected per sitting day appears to have increased since around 2008-2009, with a maximum of 116 and 87 unique names detected for the Chamber and Federation Chamber, respectively.
+Across the time frame of our data, there was a daily average of 84 unique names detected in the Chamber, and 34 in the Federation Chamber.
+These observations are in accordance with the official number of Members belonging to the House of Representatives, which was 148 in 1998, 150 in 2001, and then increased to 151 in the 2019 general election [@australia2018house].**
+
+![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}
+
+**We then computed the total number of speeches made in our database by political party, summarized in @tbl-speeches_by_party.
+We found that the Australian Labor Party made the most speeches overall, followed by the Liberal Party of Australia, and the Nationalist Party.
+These rankings are unsurprising, as those parties are the three main political parties in the Australian House of Representatives [@infosheet_parties].**
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-speeches_by_party
+#| tbl-cap: "Total number of speeches made in our database by political party"
+read_csv("s_by_party_name.csv", show_col_types = F) |> 
+  knitr::kable(booktabs=T) |> 
+  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
+#### check NAT vs NPA full names - are these correct? google is confusing me
+```
 

### 2023-07-03 paper/paper-nature-revised.tex
more paper revisions

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{June 29, 2023}
+\date{July 3, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
@@
 \begin{quote}
+\end{quote}
+
+\begin{quote}
 ``Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great
@@
 sitting days of the House of Representatives from 02 March 1998 to 08
-September 2022, so there are 1,517 \textbf{individual sitting day} files
-for each format. \textbf{Additionally, there is a single corpus file in
-both CSV and Parquet forms containing the data from all sitting days,
-with a date variable added to allow for distinction and filtering of
-individual sitting days. There is also a CSV and Parquet file containing
-all parsed debate topics.} All data records are available on the
-general-purpose repository Zenodo, at
-https://doi.org/10.5281/zenodo.7799678 (Katz and Alexander 2023). For
-each \textbf{Hansard data} file, \textbf{that is, the corpus and the
-individual sitting day files}, each row contains an individual
-statement, with details on the individual speaking. For general
-statements transcribed as made by ``Honourable members'' for example,
-these variables cannot be specified. Table~\ref{tbl-vars} provides an
-overview of each variable found in the \textbf{Hansard data files in
-the} database.
+September 2022 \textbf{where an XML transcript is available}, so there
+are \textbf{1,532 individual sitting day} files for each format.
+\textbf{Additionally, there is a single corpus file in both CSV and
+Parquet forms containing the data from all sitting days, with a date
+variable added to allow for distinction and filtering of individual
+sitting days. There is also a CSV and Parquet file containing all parsed
+debate topics.} All data records are available on the general-purpose
+repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 (Katz and
+Alexander 2023). For each \textbf{Hansard data} file, \textbf{that is,
+the corpus and the individual sitting day files}, each row contains an
+individual statement, with details on the individual speaking. For
+general statements transcribed as made by ``Honourable members'' for
+example, these variables cannot be specified. Table~\ref{tbl-vars}
+provides an overview of each variable found in the \textbf{Hansard data
+files in the} database.
 
@@
 (\texttt{interject}), and the \texttt{div\_flag} variable was added to
-flag when a division is called for. The \texttt{gender} and
-\texttt{uniqueID} variables were added based on the main dataset from
-the \texttt{AustralianPoliticians} package, \textbf{and the
-\texttt{partyfacts\_id} variable was added using code and data provided
-by the Party Facts Project
+flag \textbf{those rows where ``The House divided.'' was detected in the
+body variable}. The \texttt{gender} and \texttt{uniqueID} variables were
+added based on the main dataset from the \texttt{AustralianPoliticians}
+package, \textbf{and the \texttt{partyfacts\_id} variable was added
+using code and data provided by the Party Facts Project
 \href{https://partyfacts.herokuapp.com}{website}.}\footnote{\textbf{Note
   that in accordance with the code provided on the Party Facts
-  {[}downloads page{]}(https://partyfacts.herokuapp.com/download/), we
+  \href{https://partyfacts.herokuapp.com/download/}{downloads page}, we
   used only the core datasets maintained by the Party Facts project,
@@
 and full name spelling found in the \texttt{AustralianPoliticians}
-package data in this dataframe for completeness.}
+package for completeness.}
 
@@
 party\_abb\_hansard & Party abbreviation as transcribed in the Hansard data\\
-party\_abb\_auspol & Party abbreviation as recorded in the `AustralianPoliticians` data\\
-party\_name\_auspol & Party full name as recorded in the `AustralianPoliticians` data\\
+party\_abb\_auspol & Party abbreviation as recorded in the AustralianPoliticians R package data\\
+party\_name\_auspol & Party full name as recorded in the AustralianPoliticians R package data\\
 \bottomrule
@@
 by checking whether two lines that immediately follow each other have
-the same body (i.e.~spoken content). This test detected 129 dates on
-which duplicate statements were made, and one immediately follows the
-other. Note that this test does not account for who is making each
-statement, meaning one MP repeating the words of another MP would be
-picked up in this test as well. We checked a sample of 40\% of these
-duplicates, and manually validated that they are all repeated statements
-that do exist and are transcribed closely together in that day's XML
-file, and by our method should be parsed such that one of these
-statements is immediately followed by the other.
+the same body (i.e.~spoken content). This test detected \textbf{131}
+dates on which duplicate statements were made, and one immediately
+follows the other. Note that this test does not account for who is
+making each statement, meaning one MP repeating the words of another MP
+would be picked up in this test as well. We checked a sample of 40\% of
+these duplicates, and manually validated that they are all repeated
+statements that do exist and are transcribed closely together in that
+day's XML file, and by our method should be parsed such that one of
+these statements is immediately followed by the other.
 
@@
 
+\hypertarget{summary-statistics}{%
+\subsection{Summary Statistics}\label{summary-statistics}}
+
+\textbf{To further explore the quality of our data and detect any
+unexpected or distinct trends, we generated a number of summary
+statistics using the complete Hansard corpus. First, we looked at the
+number of speeches made each day, disaggregated by Chamber and
+Federation Chamber debate venues. As shown in
+Figure~\ref{fig-dailyspeeches}, there are consistently more speeches
+made in the Chamber proceedings than in the Federation Chamber, which
+aligns with the wider scope of business covered in the Chamber. Further,
+in both debate venues, the number of speeches each day appears to have
+increased slightly over time.}
+
+\begin{figure}
+
+{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}
+
+}
+
+\caption{\label{fig-dailyspeeches}Number of speeches made on each
+sitting day in the House of Representatives}
+
+\end{figure}
+
+\textbf{Next, we explored the number of unique names detected on each
+sitting day disaggregated by debate venue, visualized in
+Figure~\ref{fig-names}. As expected, there are generally more individual
+MPs detected to be present in the Chamber proceedings in our data than
+in the Federation Chamber proceedings. Further, in both venues, the
+number of individuals detected per sitting day appears to have increased
+since around 2008-2009, with a maximum of 116 and 87 unique names
+detected for the Chamber and Federation Chamber, respectively. Across
+the time frame of our data, there was a daily average of 84 unique names
+detected in the Chamber, and 34 in the Federation Chamber. These
+observations are in accordance with the official number of Members
+belonging to the House of Representatives, which was 148 in 1998, 150 in
+2001, and then increased to 151 in the 2019 general election (House of
+Representatives 2018).}
+
+\begin{figure}
+
+{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}
+
+}
+
+\caption{\label{fig-names}Daily number of unique names detected in our
+Hansard data}
+
+\end{figure}
+
+\textbf{We then computed the total number of speeches made in our
+database by political party, summarized in
+Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
+Party made the most speeches overall, followed by the Liberal Party of
+Australia, and the Nationalist Party. These rankings are unsurprising,
+as those parties are the three main political parties in the Australian
+House of Representatives (Parliament of Australia 2022).}
+
+\hypertarget{tbl-speeches_by_party}{}
+\begin{table}[H]
+\caption{\label{tbl-speeches_by_party}Total number of speeches made in our database by political party }\tabularnewline
+
+\centering
+\begin{tabular}{llr}
+\toprule
+Party Name & Party Abbreviation & Total \# of Speeches\\
+\midrule
+Australian Labor Party & ALP & 112268\\
+Liberal Party of Australia & LIB & 106139\\
+Nationalist Party & NAT & 15799\\
+Independent & IND & 5357\\
+National Party of Australia & NPA & 4580\\
+\addlinespace
+Australian Greens & GRN & 1446\\
+Country Liberal Party (Northern Territory) & CLP & 665\\
+Centre Alliance & CA & 638\\
+Katters Australian Party & KAP & 263\\
+Nick Xenophon Team & NXT & 186\\
+\addlinespace
+National Party of Australia (WA) & NATS WA & 68\\
+Palmer United Party & PUP & 64\\
+United Australia Party & UAP & 43\\
+\bottomrule
+\end{tabular}
+\end{table}
+
 \hypertarget{sec-usage}{%
@@
 data which allows users to link our data to external political party
-information.}
+data sources with this unique identifier.}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
+Parliament of Australia. 2022. {``Infosheet 22 - Political Parties.''}
+\emph{House of Representatives Infosheets}.
+\url{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%

### 2023-07-04 paper/paper-nature-revised.qmd
add csl to correct reference style

@@
 bibliography: references.bib
+csl: nature.csl
 editor: visual

### 2023-07-04 paper/paper-nature-revised.tex
add csl to correct reference style

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{July 3, 2023}
+\date{July 4, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 Hansard became tradition in many other Commonwealth countries, such as
-Canada and Australia (Vice and Farrell 2017). Given the content and
-magnitude of these records, they have significance, particularly in the
-context of political science research. In the case of Canada, the
-Hansard has been digitized for 1901 to 2019 (Beelen et al. 2017). Having
-a digitized version of Hansard enables researchers to conduct text
-analysis and statistical modelling. Following the lead of that project,
-in this paper we introduce a similar database for Australia. This is
-composed of individual datasets for each sitting day in the House of
-Representatives from 1998 to 2022, containing details on everything said
-in parliament in a form that can be readily used by researchers. With
-the development of tools for large-scale text analysis, this database
-will serve as a resource for understanding political behaviour in
-Australia over time.
+Canada and Australia\textsuperscript{1}. Given the content and magnitude
+of these records, they have significance, particularly in the context of
+political science research. In the case of Canada, the Hansard has been
+digitized for 1901 to 2019\textsuperscript{2}. Having a digitized
+version of Hansard enables researchers to conduct text analysis and
+statistical modelling. Following the lead of that project, in this paper
+we introduce a similar database for Australia. This is composed of
+individual datasets for each sitting day in the House of Representatives
+from 1998 to 2022, containing details on everything said in parliament
+in a form that can be readily used by researchers. With the development
+of tools for large-scale text analysis, this database will serve as a
+resource for understanding political behaviour in Australia over time.
 
@@
 crucial governmental functions, such as creating new laws and overseeing
-government expenditure (House of Representatives 2018, ch.~1).
-Politicians in the House are referred to as Members of Parliament (MPs).
-The House operates under a parallel chamber setup, meaning there are two
-debate venues where proceedings take place: the Chamber, and the
-Federation Chamber. Sittings of the House follow a predefined order of
-business, regulated by procedural rules called standing orders (House of
-Representatives 2018, ch.~8). A typical sitting day in the Chamber has a
-number of scheduled proceedings including debates on government
-business, 90 second member statements, and Question Time (House of
-Representatives 2018, ch.~8). The Federation Chamber was created in 1994
-as a subordinate debate venue of the Chamber. This allows for better
-time management of House business as its proceedings occur
-simultaneously with those of the Chamber (House of Representatives 2018,
-ch.~21). Sittings in the Federation Chamber are different to those of
+government expenditure\textsuperscript{3, ch.~1}. Politicians in the
+House are referred to as Members of Parliament (MPs). The House operates
+under a parallel chamber setup, meaning there are two debate venues
+where proceedings take place: the Chamber, and the Federation Chamber.
+Sittings of the House follow a predefined order of business, regulated
+by procedural rules called standing orders\textsuperscript{3, ch.~8}. A
+typical sitting day in the Chamber has a number of scheduled proceedings
+including debates on government business, 90 second member statements,
+and Question Time\textsuperscript{3, ch.~8}. The Federation Chamber was
+created in 1994 as a subordinate debate venue of the Chamber. This
+allows for better time management of House business as its proceedings
+occur simultaneously with those of the Chamber\textsuperscript{3,
+ch.~21}. Sittings in the Federation Chamber are different to those of
 the Chamber in terms of their order of business and scope of discussion.
@@
 to intermediate stages of bill development, and the business of private
-Members (House of Representatives 2018, ch.~21). It is the recording and
-compilation of these proceedings on which Hansard is based, and it is
-essentially, but not entirely, verbatim.
+Members\textsuperscript{3, ch.~21}. It is the recording and compilation
+of these proceedings on which Hansard is based, and it is essentially,
+but not entirely, verbatim.
 
@@
 usable, complete data based on content from the Australian Parliament
-website. For instance, Sherratt (2016) created an online, easy to read
-database of Hansard from 1901 to 1980 using the XML files. These data
-can be navigated by year, parliament, people, and bills (Sherratt 2016).
-To make the Australian Parliamentary Handbook more accessible, Leslie
-(2021) has released an \texttt{R} package which includes data on all MPs
-from 1945 to 2019. Further, Alexander and Hodgetts (2021) created the
-\texttt{AustralianPoliticians} \texttt{R} package, which contains
-several datasets related to the political and biographical information
-of Australian federal politicians who were active between 1901 and 2021.
+website. For instance,\textsuperscript{4} created an online, easy to
+read database of Hansard from 1901 to 1980 using the XML files. These
+data can be navigated by year, parliament, people, and
+bills\textsuperscript{4}. To make the Australian Parliamentary Handbook
+more accessible,\textsuperscript{5} has released an \texttt{R} package
+which includes data on all MPs from 1945 to 2019.
+Further,\textsuperscript{6} created the \texttt{AustralianPoliticians}
+\texttt{R} package, which contains several datasets related to the
+political and biographical information of Australian federal politicians
+who were active between 1901 and 2021.
 
 Many papers exist which use components of Australian Hansard to explore
-various research topics. For example, Salisbury (2011) used the Hansard
-to investigate occurrences of unparliamentary comments by MPs, where the
-Speaker tells that MP to withdraw their remark. Rasiah (2010) worked
-with Question Time data from Hansard transcripts during February and
-March of 2003, to investigate resistance of politicians in answering
-questions about Iraq. Fraussen, Graham, and Halpin (2018) use Hansard to
-quantify political prominence by investigating strategic mentions of
-interest groups by elected officials. Finally, Alexander and Alexander
-(2021) construct a dataset of the Australian Hansard, along with an
-analysis of the effect of elections and changes in Prime Ministers upon
-topics mentioned in parliament. Alexander and Alexander (2021) created
-this database with the static PDF versions of Hansard, using OCR to
-digitize these files into text which is suitable for analysis. This
-means there are considerable digitization errors especially in the first
-half of the dataset.
+various research topics. For example,\textsuperscript{7} used the
+Hansard to investigate occurrences of unparliamentary comments by MPs,
+where the Speaker tells that MP to withdraw their
+remark.\textsuperscript{8} worked with Question Time data from Hansard
+transcripts during February and March of 2003, to investigate resistance
+of politicians in answering questions about Iraq.\textsuperscript{9} use
+Hansard to quantify political prominence by investigating strategic
+mentions of interest groups by elected officials.
+Finally,\textsuperscript{10} construct a dataset of the Australian
+Hansard, along with an analysis of the effect of elections and changes
+in Prime Ministers upon topics mentioned in
+parliament.\textsuperscript{10} created this database with the static
+PDF versions of Hansard, using OCR to digitize these files into text
+which is suitable for analysis. This means there are considerable
+digitization errors especially in the first half of the dataset.
 
@@
 performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
-packages (Temple Lang 2022; Wickham, Hester, and Ooms 2021). Focusing on
-one transcript also allowed us to ensure that all key components of the
-transcript were parsed and captured in as much detail as possible. The
-typical form of a Hansard XML transcript is summarized in the nested
-list below. This provides an overview, but does not contain every
-possible nested element that may be found in a Hansard XML.
+packages\textsuperscript{11,12}. Focusing on one transcript also allowed
+us to ensure that all key components of the transcript were parsed and
+captured in as much detail as possible. The typical form of a Hansard
+XML transcript is summarized in the nested list below. This provides an
+overview, but does not contain every possible nested element that may be
+found in a Hansard XML.
 
@@
 The next step was to further develop our script to produce tidy data
-sets, as defined and introduced by Wickham (2014). These contain all
-parsed text elements, where each statement is separated onto its own row
-with details about the MP who is speaking, and rows are maintained in
-chronological order. This first involved correcting the variable classes
-and adding several indicator variables to differentiate where statements
-came from, such as Chamber versus Federation Chamber or
+sets, as defined and introduced by\textsuperscript{13}. These contain
+all parsed text elements, where each statement is separated onto its own
+row with details about the MP who is speaking, and rows are maintained
+in chronological order. This first involved correcting the variable
+classes and adding several indicator variables to differentiate where
+statements came from, such as Chamber versus Federation Chamber or
 \texttt{\textless{}subdebate.1\textgreater{}} versus
@@
 in 1994, the Federation Chamber was originally named the Main Committee.
-The Main Committee was renamed to the Federation Chamber in mid-2012
-(House of Representatives 2018, ch.~21). As a result, the child node
-under which Federation Chamber proceedings are nested is named
+The Main Committee was renamed to the Federation Chamber in
+mid-2012\textsuperscript{3, ch.~21}. As a result, the child node under
+which Federation Chamber proceedings are nested is named
 \texttt{\textless{}maincomm.xscript\textgreater{}} in all XML files
@@
 are written in advance, or questions without notice which are asked
-verbally in the Chamber and are responded to in real time (House of
-Representatives 2021). Questions without notice are included directly in
-the \texttt{"chamber.xscript"} child node, with sub-child nodes called
-\texttt{"question"} and \texttt{"answer"} to differentiate the two.
-Questions in writing, however, are embedded in their own child node
+verbally in the Chamber and are responded to in real
+time\textsuperscript{14}. Questions without notice are included directly
+in the \texttt{"chamber.xscript"} child node, with sub-child nodes
+called \texttt{"question"} and \texttt{"answer"} to differentiate the
+two. Questions in writing, however, are embedded in their own child node
 called \texttt{"answers.to.questions"} at the end of the XML file.
@@
 dataset from the \texttt{AustralianPoliticians} package in the creation
-of each lookup table (Alexander and Hodgetts 2021).
+of each lookup table\textsuperscript{6}.
 
@@
 debate topics.} All data records are available on the general-purpose
-repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 (Katz and
-Alexander 2023). For each \textbf{Hansard data} file, \textbf{that is,
-the corpus and the individual sitting day files}, each row contains an
-individual statement, with details on the individual speaking. For
-general statements transcribed as made by ``Honourable members'' for
-example, these variables cannot be specified. Table~\ref{tbl-vars}
-provides an overview of each variable found in the \textbf{Hansard data
-files in the} database.
+repository Zenodo, at
+https://doi.org/10.5281/zenodo.7799678\textsuperscript{15}. For each
+\textbf{Hansard data} file, \textbf{that is, the corpus and the
+individual sitting day files}, each row contains an individual
+statement, with details on the individual speaking. For general
+statements transcribed as made by ``Honourable members'' for example,
+these variables cannot be specified. Table~\ref{tbl-vars} provides an
+overview of each variable found in the \textbf{Hansard data files in
+the} database.
 
@@
 belonging to the House of Representatives, which was 148 in 1998, 150 in
-2001, and then increased to 151 in the 2019 general election (House of
-Representatives 2018).}
+2001, and then increased to 151 in the 2019 general
+election\textsuperscript{3}.}
 
@@
 as those parties are the three main political parties in the Australian
-House of Representatives (Parliament of Australia 2022).}
+House of Representatives\textsuperscript{16}.}
 
@@
 within data from both the \texttt{AustralianPoliticians} and
-\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
-Alexander 2019). By including this variable, one can readily integrate
-our data records with those available in these two packages.
-\textbf{Similarly, we added the \texttt{partyfacts\_id} variable to our
-data which allows users to link our data to external political party
-data sources with this unique identifier.}
+\texttt{AustralianElections} R packages\textsuperscript{6,17}. By
+including this variable, one can readily integrate our data records with
+those available in these two packages. \textbf{Similarly, we added the
+\texttt{partyfacts\_id} variable to our data which allows users to link
+our data to external political party data sources with this unique
+identifier.}
 
@@
 the \texttt{ausPH} package which provides datasets for contents of the
-Australian Parliamentary Handbook (Leslie 2021). This will allow for
-convenient extraction of further details on each MP in a tidy, ready to
-analyze format.
+Australian Parliamentary Handbook\textsuperscript{5}. This will allow
+for convenient extraction of further details on each MP in a tidy, ready
+to analyze format.
 
@@
 https://github.com/lindsaykatz/hansard-proj. All scripts were created
-using R software (R Core Team 2022). The core packages used to develop
-these scripts are: the \texttt{XML} package by Temple Lang (2022), the
-\texttt{xml2} package by Wickham, Hester, and Ooms (2021), the
-\texttt{tidyverse} R packages by Wickham et al. (2019), the
-\texttt{AustralianPoliticians} package by Alexander and Hodgetts (2021),
-and the \texttt{ausPH} package by Leslie (2021). \texttt{XML} and
-\texttt{xml2} were used for parsing the XML documents,
-\texttt{AustralianPoliticians} and \texttt{ausPH} were used for cleaning
-up and filling in MP details in the datasets, and \texttt{tidyverse}
-packages were used in all steps, for tidy wrangling of data.
+using R software\textsuperscript{18}. The core packages used to develop
+these scripts are: the \texttt{XML} package by\textsuperscript{11}, the
+\texttt{xml2} package by\textsuperscript{12}, the \texttt{tidyverse} R
+packages by\textsuperscript{19}, the \texttt{AustralianPoliticians}
+package by\textsuperscript{6}, and the \texttt{ausPH} package
+by\textsuperscript{5}. \texttt{XML} and \texttt{xml2} were used for
+parsing the XML documents, \texttt{AustralianPoliticians} and
+\texttt{ausPH} were used for cleaning up and filling in MP details in
+the datasets, and \texttt{tidyverse} packages were used in all steps,
+for tidy wrangling of data.
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
+\begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Vice, J. \& Farrell, S. \emph{The history of hansard}.
+(House of Lords Library; House of Lords Hansard, 2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
+\CSLLeftMargin{2. }%
+\CSLRightInline{Beelen, K. \emph{et al.} Digitization of the canadian
+parliamentary debates. \emph{Canadian Journal of Political Science/Revue
+canadienne de science politique} \textbf{50}, 849--864 (2017).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
+\CSLLeftMargin{3. }%
+\CSLRightInline{House of Representatives. \emph{{House of
+Representatives Practice}} ({Australian Government - Department of the
+House of Representatives}, 2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Sherratt, T.
+\href{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}{Documentation:
+Historic hansard}. \emph{Historic Hansard} (2016).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Leslie, P.
+\emph{\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
+of the australian house of representatives (1945-2019)}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Alexander, R. \& Hodgetts, P. A.
+\emph{\href{https://CRAN.R-project.org/package=AustralianPoliticians}{AustralianPoliticians:
+Provides datasets about australian politicians}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Salisbury, C. 'Mr speaker, i withdraw...': Standards of
+(mis) behaviour in the queensland, western australian and commonwealth
+parliaments compared via online hansard. \emph{Australasian
+Parliamentary Review} \textbf{26}, 166--177 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
+\CSLLeftMargin{8. }%
+\CSLRightInline{Rasiah, P. A framework for the systematic analysis of
+evasion in parliamentary discourse. \emph{Journal of Pragmatics}
+\textbf{42}, 664--680 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
+\CSLLeftMargin{9. }%
+\CSLRightInline{Fraussen, B., Graham, T. \& Halpin, D. R. Assessing the
+prominence of interest groups in parliament: A supervised machine
+learning approach. \emph{The Journal of Legislative Studies}
+\textbf{24}, 450--474 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
+\CSLLeftMargin{10. }%
+\CSLRightInline{Alexander, R. \& Alexander, M. The increased effect of
+elections and changing prime ministers on topics discussed in the
+australian federal parliament between 1901 and 2018. \emph{arXiv
+preprint arXiv:2111.09299} (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Temple Lang, D.
+\emph{\href{https://CRAN.R-project.org/package=XML}{XML: Tools for
+parsing and generating XML within r and s-plus}}. (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Wickham, H., Hester, J. \& Ooms, J.
+\emph{\href{https://CRAN.R-project.org/package=xml2}{xml2: Parse XML}}.
+(2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
+\CSLLeftMargin{13. }%
+\CSLRightInline{Wickham, H.
+\href{https://doi.org/10.18637/jss.v059.i10}{Tidy data}. \emph{Journal
+of Statistical Software} \textbf{59}, (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
+\CSLLeftMargin{14. }%
+\CSLRightInline{House of Representatives. \emph{{A window on the house:
+Practices and procedures relating to question time}}. ({Parliament of
+Australia}, 2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
+\CSLLeftMargin{15. }%
+\CSLRightInline{Katz, L. \& Alexander, R. {A new, comprehensive database
+of all proceedings of the Australian Parliamentary Debates (1998-2022)}.
+(2023)
+doi:\href{https://doi.org/10.5281/zenodo.7799678}{10.5281/zenodo.7799678}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
+\CSLLeftMargin{16. }%
+\CSLRightInline{Parliament of Australia.
+\href{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}{Infosheet
+22 - political parties}. \emph{House of Representatives Infosheets}
+(2022).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-auselect}{}}%
-Alexander, Rohan. 2019. \emph{AustralianElections: Datasets on
-Australian Elections}.
-\url{https://github.com/RohanAlexander/AustralianElections}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
-Alexander, Rohan, and Monica Alexander. 2021. {``The Increased Effect of
-Elections and Changing Prime Ministers on Topics Discussed in the
-Australian Federal Parliament Between 1901 and 2018.''} \emph{arXiv
-Preprint arXiv:2111.09299}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
-Alexander, Rohan, and Paul A. Hodgetts. 2021.
-\emph{AustralianPoliticians: Provides Datasets about Australian
-Politicians}.
-\url{https://CRAN.R-project.org/package=AustralianPoliticians}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
-Beelen, Kaspar, Timothy Alberdingk Thijm, Christopher Cochrane, Kees
-Halvemaan, Graeme Hirst, Michael Kimmins, Sander Lijbrink, et al. 2017.
-{``Digitization of the Canadian Parliamentary Debates.''} \emph{Canadian
-Journal of Political Science/Revue Canadienne de Science Politique} 50
-(3): 849--64.
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
-Fraussen, Bert, Timothy Graham, and Darren R Halpin. 2018. {``Assessing
-the Prominence of Interest Groups in Parliament: A Supervised Machine
-Learning Approach.''} \emph{The Journal of Legislative Studies} 24 (4):
-450--74.
-
-\leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
-House of Representatives. 2018. Edited by D. R. Elder and P. E. Fowler.
-\emph{{House of Representatives Practice}}. 7th ed. {Australian
-Government - Department of the House of Representatives}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
----------. 2021. \emph{{A window on the house: Practices and procedures
-relating to question time}}. {Parliament of Australia}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
-Katz, Lindsay, and Rohan Alexander. 2023. {``{A new, comprehensive
-database of all proceedings of the Australian Parliamentary Debates
-(1998-2022)}.''} Zenodo. \url{https://doi.org/10.5281/zenodo.7799678}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
-Leslie, Patrick. 2021. \emph{Members of the Australian House of
-Representatives (1945-2019)}.
-\url{https://github.com/palesl/AustralianHouseOfRepresentatives}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
-Parliament of Australia. 2022. {``Infosheet 22 - Political Parties.''}
-\emph{House of Representatives Infosheets}.
-\url{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}.
+\CSLLeftMargin{17. }%
+\CSLRightInline{Alexander, R.
+\emph{\href{https://github.com/RohanAlexander/AustralianElections}{AustralianElections:
+Datasets on australian elections}}. (2019).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%
-R Core Team. 2022. \emph{R: A Language and Environment for Statistical
-Computing}. Vienna, Austria: R Foundation for Statistical Computing.
-\url{https://www.R-project.org/}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
-Rasiah, Parameswary. 2010. {``A Framework for the Systematic Analysis of
-Evasion in Parliamentary Discourse.''} \emph{Journal of Pragmatics} 42
-(3): 664--80.
-
-\leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
-Salisbury, Christopher. 2011. {``'Mr Speaker, i Withdraw...': Standards
-of (Mis) Behaviour in the Queensland, Western Australian and
-Commonwealth Parliaments Compared via Online Hansard.''}
-\emph{Australasian Parliamentary Review} 26 (1): 166--77.
-
-\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
-Sherratt, Tim. 2016. {``Documentation: Historic Hansard.''}
-\emph{Historic Hansard}.
-\url{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
-Temple Lang, Duncan. 2022. \emph{XML: Tools for Parsing and Generating
-XML Within r and s-Plus}. \url{https://CRAN.R-project.org/package=XML}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
-Vice, John, and Stephen Farrell. 2017. \emph{The History of Hansard}.
-House of Lords Library; House of Lords Hansard.
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
-Wickham, Hadley. 2014. {``Tidy Data.''} \emph{Journal of Statistical
-Software} 59 (10). \url{https://doi.org/10.18637/jss.v059.i10}.
+\CSLLeftMargin{18. }%
+\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R:
+A language and environment for statistical computing}}. (R Foundation
+for Statistical Computing, 2022).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
-Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
-D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
-{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
-4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
-
-\leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
-Wickham, Hadley, Jim Hester, and Jeroen Ooms. 2021. \emph{Xml2: Parse
-XML}. \url{https://CRAN.R-project.org/package=xml2}.
+\CSLLeftMargin{19. }%
+\CSLRightInline{Wickham, H. \emph{et al.}
+\href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}.
+\emph{Journal of Open Source Software} \textbf{4}, 1686 (2019).}
 

### 2023-07-05 paper/paper-nature-revised.qmd
paper and script updates

@@
 Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned.
-**Finally, we review the supplementary Hansard debate topics dataset we created to expand the versatility of our database.**
+**Finally, we review the supplementary Hansard debate topics dataset and supplementary divisions dataset we created to expand the versatility of our database.**
 
@@
 
+## Divisions
+
+**Another fundamental component of parliamentary proceedings is voting.
+In the House, when a question arises such as “The question is that the amendment be agreed to”, Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house].
+Further, Members can vote in an unofficial arrangement called pairs, in which as written in Chapter 8 of @australia2018house, "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting".
+If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**
+
+**In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result.
+Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings.
+Our approach to parsing Hansard in the third and fourth scripts described in @sec-diff naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not.
+To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame.
+To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any time stamps where available, and did any additional data cleaning as necessary.
+We used a series of if-else statements in this script to account for variation in the structure of the `<divisions>` node over time.
+Finally, we then added a date variable to distinguish between sitting days.**
+
 # Data Records
@@
 
-**Finally, there is a CSV file in our database called `PartyFacts_map.csv`.
+**There is also a CSV file in our database called `PartyFacts_map.csv`.
 This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable.
@@
   kableExtra::column_spec(2, width="25em")
+```
+
+**Finally, our database contains a file with all parsed divisions data in our timeframe.
+This is called `division_data`, and is available in RDA form and in Parquet form.
+The reason it is not available in CSV form is because three of the variables (`names_AYES`, `names_NOES`, and `names_PAIRS`) are lists, which are not supported by the CSV rectangular data structure.
+The variables found in these data are summarized below, in @tbl-divisions.**
+
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-divisions
+#| tbl-cap: "Summary and description of variables in our divisions data file"
+tibble("Variable" = c("date",
+                      "div_num",
+                      "time.stamp",
+                      "num.votes_AYES",
+                      "num.votes_NOES",
+                      "num.votes_PAIRS",
+                      "names_AYES",
+                      "names_NOES",
+                      "names_PAIRS",
+                      "result"),
+       "Description" = c("Sitting day",
+                         "Index for each division parsed for that sitting day",
+                         "Time stamp associated with each division",
+                         "Number of votes in the affirmative",
+                         "Number of votes in the negative",
+                         "Number of votes in pairs",
+                         "List of the names of Members who voted in the affirmative",
+                         "List of the names of Members who voted in the negative",
+                         "List of the names of Members who votes in pairs",
+                         "Voting result")) |> 
+  kable(booktabs=T) %>% 
+  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
 ```
@@
   kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
-#### check NAT vs NPA full names - are these correct? google is confusing me
 ```

### 2023-07-05 paper/paper-nature-revised.tex
paper and script updates

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{July 4, 2023}
+\date{July 5, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
 
@@
 to after being parsed and cleaned. \textbf{Finally, we review the
-supplementary Hansard debate topics dataset we created to expand the
-versatility of our database.}
+supplementary Hansard debate topics dataset and supplementary divisions
+dataset we created to expand the versatility of our database.}
 
@@
 
+\hypertarget{divisions}{%
+\subsection{Divisions}\label{divisions}}
+
+\textbf{Another fundamental component of parliamentary proceedings is
+voting. In the House, when a question arises such as ``The question is
+that the amendment be agreed to'', Members are asked to cast their vote
+either in the affirmative or in the negative, and the majority of votes
+as judged by the Speaker determines the outcome\textsuperscript{3}.
+Further, Members can vote in an unofficial arrangement called pairs, in
+which as written in Chapter 8 of\textsuperscript{3}, ``can be used to
+enable a Member on one side of the House to be absent for any votes when
+a Member from the other side is to be absent at the same time or when,
+by agreement, a Member abstains from voting''. If the result as
+determined by the Speaker is challenged by more than one MP, this leads
+to a division of the House in which the question is re-stated and
+Members must move to the left or right of their chair depending on how
+they vote, so that the votes can be re-counted and
+recorded\textsuperscript{3}.}
+
+\textbf{In the Hansard XML files, divisions data are structured outside
+of the \texttt{\textless{}speech\textgreater{}} content in their own
+\texttt{\textless{}division\textgreater{}} nodes that contain the voting
+data and division result. Since we focus primarily on the spoken
+\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
+scripts do not necessarily capture all divisions data from House
+proceedings. Our approach to parsing Hansard in the third and fourth
+scripts described in Section~\ref{sec-diff} naturally allowed for much
+of the divisions data to be added to our resulting files for 1998 to
+March 2011, however the parsing scripts used for May 2011 to September
+2022 Hansard did not. To supplement our database and in an effort to
+fill this divisions data gap, we created an additional file containing
+all divisions data nested under the XPath
+``\texttt{//chamber.xscript//division}'' from the Hansard files in our
+time frame. To produce this data file, for each Hansard XML we parsed
+the \texttt{\textless{}division.header\textgreater{}},
+\texttt{\textless{}division.data\textgreater{}}, and
+\texttt{\textless{}division.result\textgreater{}} child-nodes where they
+existed, extracted any time stamps where available, and did any
+additional data cleaning as necessary. We used a series of if-else
+statements in this script to account for variation in the structure of
+the \texttt{\textless{}divisions\textgreater{}} node over time. Finally,
+we then added a date variable to distinguish between sitting days.}
+
 \hypertarget{data-records}{%
@@
 
-\textbf{Finally, there is a CSV file in our database called
+\textbf{There is also a CSV file in our database called
 \texttt{PartyFacts\_map.csv}. This file was created using
@@
 party\_name\_auspol & Party full name as recorded in the AustralianPoliticians R package data\\
+\bottomrule
+\end{tabular}
+\end{table}
+
+\textbf{Finally, our database contains a file with all parsed divisions
+data in our timeframe. This is called \texttt{division\_data}, and is
+available in RDA form and in Parquet form. The reason it is not
+available in CSV form is because three of the variables
+(\texttt{names\_AYES}, \texttt{names\_NOES}, and \texttt{names\_PAIRS})
+are lists, which are not supported by the CSV rectangular data
+structure. The variables found in these data are summarized below, in
+Table~\ref{tbl-divisions}.}
+
+\hypertarget{tbl-divisions}{}
+\begin{table}[H]
+\caption{\label{tbl-divisions}Summary and description of variables in our divisions data file }\tabularnewline
+
+\centering
+\begin{tabular}{ll}
+\toprule
+Variable & Description\\
+\midrule
+date & Sitting day\\
+div\_num & Index for each division parsed for that sitting day\\
+time.stamp & Time stamp associated with each division\\
+num.votes\_AYES & Number of votes in the affirmative\\
+num.votes\_NOES & Number of votes in the negative\\
+\addlinespace
+num.votes\_PAIRS & Number of votes in pairs\\
+names\_AYES & List of the names of Members who voted in the affirmative\\
+names\_NOES & List of the names of Members who voted in the negative\\
+names\_PAIRS & List of the names of Members who votes in pairs\\
+result & Voting result\\
 \bottomrule
@@
 Liberal Party of Australia & LIB & 106139\\
-Nationalist Party & NAT & 15799\\
+National Party of Australia & NPA & 20244\\
 Independent & IND & 5357\\
-National Party of Australia & NPA & 4580\\
+Australian Greens & GRN & 1446\\
 \addlinespace
-Australian Greens & GRN & 1446\\
 Country Liberal Party (Northern Territory) & CLP & 665\\
@@
 Nick Xenophon Team & NXT & 186\\
+National Party of Australia (WA) & NATS WA & 68\\
 \addlinespace
-National Party of Australia (WA) & NATS WA & 68\\
 Palmer United Party & PUP & 64\\

### 2023-07-05 scripts/10-add_party_facts.R

@@ -74,7 +74,7 @@ auspol_data <- AustralianPoliticians::get_auspol('allbyparty') |>
 party_table <- full_join(auspol_data, pf_data, by = c("name_auspol" = "name_pf"), multiple="all") |> select(name_auspol, name_short_auspol, partyfacts_id)
 
 # read in our Hansard corpus as of v3 (before we add party facts)
-corpus <- read_parquet(here("additional_data/hansard_corpus_1998_to_2022.parquet"))
+corpus <- read_parquet(here("/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.parquet"))
   
 # grab list of all unique party names found in corpus
 corpus_parties <- corpus %>% 
@@ -92,7 +92,7 @@ corpus_parties <- corpus_parties %>%
                                 party == "CLP" ~ "Country Liberal Party (Northern Territory)",
                                 party == "KAP" ~ "Katters Australian Party",
                                 party == "LNP" ~ "Liberal National Party of Queensland",
-                                party == "NATS" | party=="Nats" ~ "Nationalist Party",
+                                party == "NATS" | party=="Nats" ~ "National Party of Australia",
                                 party == "NatsWA" ~ "National Party of Australia (WA)",
                                 party == "PUP" ~ "Palmer United Party",
                                 party == "UAP" ~ "United Australia Party",
@@ -113,7 +113,9 @@ party_table_final <- left_join(party_table, corpus_parties, by=c("name_auspol"="
   select(partyfacts_id, party_abb_hansard, party_abb_auspol, party_name_auspol)
 
 # export clean party table to have
-# write_csv(party_table_final, "additional_data/party_table.csv")
+write_csv(party_table_final, "additional_data/PartyFacts_map.csv")
+write_csv(party_table_final, "/Volumes/Verbatim/v4/hansard-supplementary-data/PartyFacts_map.csv")
+
 party_table_final <- read_csv("additional_data/PartyFacts_map.csv", show_col_types = F)
 
 # grab list of filenames to iterate over
@@ -124,8 +126,9 @@ all_csvs <- list.files("/Volumes/Verbatim/v3/hansard_1998_to_2022-csv")
 # NOTE - splitting this up into a few hundred at a time is best to avoid weird errors / the session aborting
[…]

### 2023-07-05 scripts/11-create_one_corpus.R

@@ -6,7 +6,7 @@ library(arrow)
 library(fs)
 
 # create list of all the CSV files
-all_files_csv <- dir_ls(path = "/Volumes/Verbatim/v4/hansard_1998_to_2022-csv/", regexp= "\\d{4}-\\d{2}-\\d{2}\\.csv")
+all_files_csv <- dir_ls(path = "/Volumes/Verbatim/v4/hansard-daily-csv/", regexp= "\\d{4}-\\d{2}-\\d{2}\\.csv")
 
 # read in and combine all CSVs, and extract just the date from each file name
 full_hansard <- all_files_csv %>% 
@@ -28,8 +28,37 @@ full_hansard <- all_files_csv %>%
                                      div_flag = col_factor(),
                                      gender = col_factor(),
                                      uniqueID = col_character(),
-                                     interject = col_factor()), .id = "date") %>% 
-  mutate(date = str_extract(date, "(?<=hansard_1998_to_2022-csv/)\\d{4}-\\d{2}-\\d{2}"))
+                                     interject = col_factor(),
+                                     partyfacts_id = col_double()), .id = "date") %>% 
+  mutate(date = str_extract(date, "(?<=hansard-daily-csv/)\\d{4}-\\d{2}-\\d{2}"))
+
+old <- read_csv("/Volumes/Verbatim/v4/hansard-corpus/hansard_corpus_1998_to_2022.csv",
+                col_types = list(date=col_character(),
+                                 name = col_character(),
+                                 order = col_double(),
+                                 speech_no = col_double(),
+                                 page.no = col_double(),
+                                 time.stamp = col_character(),
+                                 name.id = col_character(),
+                                 electorate = col_character(),
+                                 party = col_factor(),
+                                 in.gov = col_double(),
+                                 first.speech = col_double(),
+                                 body = col_character(),
+                                 fedchamb_flag = col_factor(),
+                                 question = col_factor(),
+                                 answer = col_factor(),
+                                 q_in_writing = col_factor(),
+                                 div_flag = col_factor(),
+                                 gender = col_factor(),
+                                 uniqueID = col_character(),
+                                 interject = col_factor(),
+                                 partyfacts_id = col_double()))
+
+# compare to old corpus to see if any difference arise that are cause for concern
[…]

### 2023-07-05 scripts/13-divisions_data.R

@@ -1,0 +1,150 @@
+# get divisions data
+library(here)
+library(tidyverse)
+library(xml2)
+library(XML)
+
+# code in function below from https://stackoverflow.com/questions/58492429/xml—in—r—multiple—children—with—same—name—without—loops
+item_df <- function(file, path){
+  # find all items and store as a list
+  items <- xml_find_all(file, path)
+  
+  # extract all childrens names and values 
+  nodenames <- xml_name(xml_children(items))
+  contents <- trimws(xml_text(xml_children(items)))
+  
+  # need to create an index to associate the nodes/contents with each item
+  itemindex <- rep(1:length(items), times=sapply(items, function(x) {length(xml_children(x))}))
+  
+  # store all information in data frame.
+  df <- data.frame(itemindex, nodenames, contents)
+  
+  # Convert from long to wide format
+  # sometimes titles are split onto multiple lines, so fix that up too
+  df <- pivot_wider(df, id_cols = itemindex, names_from = nodenames, values_from = contents, values_fn = list) 
+  
+  return(df)
+}
+
+# grab list of all file names
+files_all <- list.files("/Volumes/Verbatim/input/")
+
+# define empty tibble to store data in
+division_data <- tibble()
+
+for (i in 1:length(files_all)) {
+  # parse file
+  hansard_xml <- xmlParse(here("/Volumes/Verbatim/input/", files_all[i]))
+  
+  # need to read the XML in in a different way for this so we can use the item_df function defined in global environment
+  xml_df <- read_xml(here("/Volumes/Verbatim/input/", files_all[i]))
+  
+  if (nrow(xmlToDataFrame(node=getNodeSet(hansard_xml, "//chamber.xscript//division"), collectNames = F, homogeneous = T))>0){
+    
+    # grab header
+    if (nrow(item_df(xml_df, "chamber.xscript//division/division.header"))>0 & "para" %in% names(item_df(xml_df, "chamber.xscript//division/division.header"))) {
+      header <- item_df(xml_df, "chamber.xscript//division/division.header") %>% unnest(everything()) %>% 
+        select(-para)
+    } else if (nrow(item_df(xml_df, "chamber.xscript//division/division.header"))>0 & "body" %in% names(item_df(xml_df, "chamber.xscript//division/division.header"))) {
[…]

### 2023-07-06 paper/paper-nature-revised.qmd
Add the aspects I had to redo

@@
 
-The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
+The official written record of parliamentary debates, **formally known as Hansard [@citehansard],** plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
 Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history].
@@
 With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.
+
+**There are a wide variety of potential applications of this database.
+For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined).
+Our dataset could be used to look at whether it is really getting worse in particular ways, and if so, why.
+We might also be interested in whether particular sub-populations are appropriately represented in what is talked about in parliament.
+For instance, there is often concern that regional areas are overlooked compared with metropolitan areas.
+Again, our database could be used to examine whether this has changed over time.
+We have developed our database in such a way that it could be linked with similar databases from other countries which would enable comparative analysis.
+For instance, we may be interested in how the policy focus of a parliament changes given various global events such as pandemics or wars.
+An international linkage provides a comparison case where domestic issues are different while international ones are common.
+As an example of enabling this linkage this we have included partyfacts IDs in our database.
+This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].**
 
@@
 
-At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis.
+At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis.
 To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website.
-For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files.
+For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created [@sherratt].
 These data can be navigated by year, parliament, people, and bills [@sherratt].
-To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all MPs from 1945 to 2019.
-Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.
+To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created @Leslie_2021_HoR_Aus.
+Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol.
+**And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021.
+Like us they scrape the Hansard record and link it with biographical data.
+They key difference is that our focus is on the database itself, while  are focused on using a database constructed from the same source to answer a particular question about speaker time.
+This different focus leads to different emphasis and approaches.**
 
 Many papers exist which use components of Australian Hansard to explore various research topics.
-For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where the Speaker tells that MP to withdraw their remark.
-@rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq.
-@fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials.
-Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament.
-@alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis.
+For example, the Hansard has been used to investigate occurrences of unparliamentary comments by MPs, where the Speaker tells that MP to withdraw their remark @salisbury2011.
+Question Time data from Hansard transcripts during February and March of 2003 has been used to investigate resistance of politicians in answering questions about Iraq @rasiah2010framework.
+Hansard has been used to quantify political prominence by investigating strategic mentions of interest groups by elected officials @fraussen2018.
+Finally, a dataset of the Australian Hansard has been constructed and then used to analyze the effect of elections and changes in Prime Ministers upon topics mentioned in parliament @alexander2021.
+This was created with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis.
 This means there are considerable digitization errors especially in the first half of the dataset.
@@
 **Another fundamental component of parliamentary proceedings is voting.
-In the House, when a question arises such as “The question is that the amendment be agreed to”, Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house].
-Further, Members can vote in an unofficial arrangement called pairs, in which as written in Chapter 8 of @australia2018house, "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting".
+In the House, when a question arises such as "The question is that the amendment be agreed to", Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house].
+Further, Members can vote in an unofficial arrangement called pairs, which "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting" @australia2018house.
 If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**
@@
 Our database is available in both CSV and parquet formats.
-It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format.
+Both CSV and parquet are open standards.
+We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class.
+Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format.
 **Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
@@
 
-![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}
+![Number of speeches made on each sitting day in the House of Representatives](images/n_daily_speeches.png){#fig-dailyspeeches width="440"}
 
@@
 
-![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}
+![Daily number of unique names detected in our Hansard data](images/n_unique_names.png){#fig-names width="440"}
 
@@
 All scripts were created using R software [@r_software].
-The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus.
+The core packages used to develop these scripts are: the `XML` package @XML_pkg, the `xml2` package @xml2_pkg, the `tidyverse` R packages @tidyverse, the `AustralianPoliticians` package @auspol, and the `ausPH` package @Leslie_2021_HoR_Aus.
 `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.
@@
 We thank Kristine Villaluna, Monica Alexander, and Jack Stephenson for helpful comments.
+We wish to especially thank Guy Jones, Chief Editor, the two anonymous reviewers, and the Editorial Board Member, Michael Jankowski for their comments.
 

### 2023-07-06 paper/paper-nature-revised.tex

@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
 \usepackage{iftex}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+\fi
+\usepackage{lmodern}
+\ifPDFTeX\else  
+    % xetex/luatex font selection
 \fi
@@
 \makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
+\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
 \makeatother
@@
 \@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
+\makeatother
+\makeatletter
 \makeatother
@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{July 5, 2023}
+\date{July 6, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi
 
@@
 
-The official written record of parliamentary debates, formally known as
-Hansard, plays a fundamental role in capturing the history of political
-proceedings and facilitating the exploration of valuable research
-questions. Originating in the British parliament, the production of
-Hansard became tradition in many other Commonwealth countries, such as
-Canada and Australia\textsuperscript{1}. Given the content and magnitude
-of these records, they have significance, particularly in the context of
-political science research. In the case of Canada, the Hansard has been
-digitized for 1901 to 2019\textsuperscript{2}. Having a digitized
-version of Hansard enables researchers to conduct text analysis and
-statistical modelling. Following the lead of that project, in this paper
-we introduce a similar database for Australia. This is composed of
-individual datasets for each sitting day in the House of Representatives
-from 1998 to 2022, containing details on everything said in parliament
-in a form that can be readily used by researchers. With the development
-of tools for large-scale text analysis, this database will serve as a
-resource for understanding political behaviour in Australia over time.
+The official written record of parliamentary debates, \textbf{formally
+known as Hansard\textsuperscript{1},} plays a fundamental role in
+capturing the history of political proceedings and facilitating the
+exploration of valuable research questions. Originating in the British
+parliament, the production of Hansard became tradition in many other
+Commonwealth countries, such as Canada and Australia\textsuperscript{2}.
+Given the content and magnitude of these records, they have
+significance, particularly in the context of political science research.
+In the case of Canada, the Hansard has been digitized for 1901 to
+2019\textsuperscript{3}. Having a digitized version of Hansard enables
+researchers to conduct text analysis and statistical modelling.
+Following the lead of that project, in this paper we introduce a similar
+database for Australia. This is composed of individual datasets for each
+sitting day in the House of Representatives from 1998 to 2022,
+containing details on everything said in parliament in a form that can
+be readily used by researchers. With the development of tools for
+large-scale text analysis, this database will serve as a resource for
+understanding political behaviour in Australia over time.
+
+\textbf{There are a wide variety of potential applications of this
+database. For instance, within Australia there is considerable concern
+that there has been a decline in the `quality' of public policy debate
+(however that might be defined). Our dataset could be used to look at
+whether it is really getting worse in particular ways, and if so, why.
+We might also be interested in whether particular sub-populations are
+appropriately represented in what is talked about in parliament. For
+instance, there is often concern that regional areas are overlooked
+compared with metropolitan areas. Again, our database could be used to
+examine whether this has changed over time. We have developed our
+database in such a way that it could be linked with similar databases
+from other countries which would enable comparative analysis. For
+instance, we may be interested in how the policy focus of a parliament
+changes given various global events such as pandemics or wars. An
+international linkage provides a comparison case where domestic issues
+are different while international ones are common. As an example of
+enabling this linkage this we have included partyfacts IDs in our
+database. This should make it possible to link our database with other
+large parliamentary speech collection projects, such as
+ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
+ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.}
 
@@
 crucial governmental functions, such as creating new laws and overseeing
-government expenditure\textsuperscript{3, ch.~1}. Politicians in the
+government expenditure\textsuperscript{8, ch.~1}. Politicians in the
 House are referred to as Members of Parliament (MPs). The House operates
@@
 Sittings of the House follow a predefined order of business, regulated
-by procedural rules called standing orders\textsuperscript{3, ch.~8}. A
+by procedural rules called standing orders\textsuperscript{8, ch.~8}. A
 typical sitting day in the Chamber has a number of scheduled proceedings
 including debates on government business, 90 second member statements,
-and Question Time\textsuperscript{3, ch.~8}. The Federation Chamber was
+and Question Time\textsuperscript{8, ch.~8}. The Federation Chamber was
 created in 1994 as a subordinate debate venue of the Chamber. This
 allows for better time management of House business as its proceedings
-occur simultaneously with those of the Chamber\textsuperscript{3,
+occur simultaneously with those of the Chamber\textsuperscript{8,
 ch.~21}. Sittings in the Federation Chamber are different to those of
@@
 to intermediate stages of bill development, and the business of private
-Members\textsuperscript{3, ch.~21}. It is the recording and compilation
+Members\textsuperscript{8, ch.~21}. It is the recording and compilation
 of these proceedings on which Hansard is based, and it is essentially,
@@
 At present, the Hansard format that is available on the Parliament of
-Australia website is not accessible for large scale analysis. To this
-point, various researchers have had to create their own databases of
-usable, complete data based on content from the Australian Parliament
-website. For instance,\textsuperscript{4} created an online, easy to
-read database of Hansard from 1901 to 1980 using the XML files. These
-data can be navigated by year, parliament, people, and
-bills\textsuperscript{4}. To make the Australian Parliamentary Handbook
-more accessible,\textsuperscript{5} has released an \texttt{R} package
-which includes data on all MPs from 1945 to 2019.
-Further,\textsuperscript{6} created the \texttt{AustralianPoliticians}
-\texttt{R} package, which contains several datasets related to the
-political and biographical information of Australian federal politicians
-who were active between 1901 and 2021.
+Australia website is not easily accessible for large scale analysis. To
+this point, various researchers have had to create their own databases
+of usable, complete data based on content from the Australian Parliament
+website. For instance, an online, easy to read database of Hansard from
+1901 to 1980 using the XML files has been created\textsuperscript{9}.
+These data can be navigated by year, parliament, people, and
+bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
+more accessible, an \texttt{R} package which includes data on all MPs
+from 1945 to 2019 has been created\textsuperscript{10}. Further, there
+is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
+several datasets related to the political and biographical information
+of Australian federal politicians who were active between 1901 and
+2021\textsuperscript{11}. \textbf{And finally, there has been
+examination of speech and MP level data between 1990 and 2019 in
+Australia\textsuperscript{12}. Like us they scrape the Hansard record
+and link it with biographical data. They key difference is that our
+focus is on the database itself, while are focused on using a database
+constructed from the same source to answer a particular question about
+speaker time. This different focus leads to different emphasis and
+approaches.}
 
 Many papers exist which use components of Australian Hansard to explore
-various research topics. For example,\textsuperscript{7} used the
-Hansard to investigate occurrences of unparliamentary comments by MPs,
-where the Speaker tells that MP to withdraw their
-remark.\textsuperscript{8} worked with Question Time data from Hansard
-transcripts during February and March of 2003, to investigate resistance
-of politicians in answering questions about Iraq.\textsuperscript{9} use
-Hansard to quantify political prominence by investigating strategic
-mentions of interest groups by elected officials.
-Finally,\textsuperscript{10} construct a dataset of the Australian
-Hansard, along with an analysis of the effect of elections and changes
-in Prime Ministers upon topics mentioned in
-parliament.\textsuperscript{10} created this database with the static
-PDF versions of Hansard, using OCR to digitize these files into text
-which is suitable for analysis. This means there are considerable
-digitization errors especially in the first half of the dataset.
+various research topics. For example, the Hansard has been used to
+investigate occurrences of unparliamentary comments by MPs, where the
+Speaker tells that MP to withdraw their remark\textsuperscript{13}.
+Question Time data from Hansard transcripts during February and March of
+2003 has been used to investigate resistance of politicians in answering
+questions about Iraq\textsuperscript{14}. Hansard has been used to
+quantify political prominence by investigating strategic mentions of
+interest groups by elected officials\textsuperscript{15}. Finally, a
+dataset of the Australian Hansard has been constructed and then used to
+analyze the effect of elections and changes in Prime Ministers upon
+topics mentioned in parliament\textsuperscript{16}. This was created
+with the static PDF versions of Hansard, using OCR to digitize these
+files into text which is suitable for analysis. This means there are
+considerable digitization errors especially in the first half of the
+dataset.
 
@@
 performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
-packages\textsuperscript{11,12}. Focusing on one transcript also allowed
+packages\textsuperscript{17,18}. Focusing on one transcript also allowed
 us to ensure that all key components of the transcript were parsed and
@@
 The next step was to further develop our script to produce tidy data
-sets, as defined and introduced by\textsuperscript{13}. These contain
+sets, as defined and introduced by\textsuperscript{19}. These contain
 all parsed text elements, where each statement is separated onto its own
@@
 The Main Committee was renamed to the Federation Chamber in
-mid-2012\textsuperscript{3, ch.~21}. As a result, the child node under
+mid-2012\textsuperscript{8, ch.~21}. As a result, the child node under
 which Federation Chamber proceedings are nested is named
@@
 verbally in the Chamber and are responded to in real
-time\textsuperscript{14}. Questions without notice are included directly
+time\textsuperscript{20}. Questions without notice are included directly
 in the \texttt{"chamber.xscript"} child node, with sub-child nodes
@@
 dataset from the \texttt{AustralianPoliticians} package in the creation
-of each lookup table\textsuperscript{6}.
+of each lookup table\textsuperscript{11}.
 
@@
 either in the affirmative or in the negative, and the majority of votes
-as judged by the Speaker determines the outcome\textsuperscript{3}.
-Further, Members can vote in an unofficial arrangement called pairs, in
-which as written in Chapter 8 of\textsuperscript{3}, ``can be used to
-enable a Member on one side of the House to be absent for any votes when
-a Member from the other side is to be absent at the same time or when,
-by agreement, a Member abstains from voting''. If the result as
-determined by the Speaker is challenged by more than one MP, this leads
-to a division of the House in which the question is re-stated and
-Members must move to the left or right of their chair depending on how
-they vote, so that the votes can be re-counted and
-recorded\textsuperscript{3}.}
+as judged by the Speaker determines the outcome\textsuperscript{8}.
+Further, Members can vote in an unofficial arrangement called pairs,
+which ``can be used to enable a Member on one side of the House to be
+absent for any votes when a Member from the other side is to be absent
+at the same time or when, by agreement, a Member abstains from
+voting''\textsuperscript{8}. If the result as determined by the Speaker
+is challenged by more than one MP, this leads to a division of the House
+in which the question is re-stated and Members must move to the left or
+right of their chair depending on how they vote, so that the votes can
+be re-counted and recorded\textsuperscript{8}.}
 
@@
 
-Our database is available in both CSV and parquet formats. It covers all
-sitting days of the House of Representatives from 02 March 1998 to 08
-September 2022 \textbf{where an XML transcript is available}, so there
-are \textbf{1,532 individual sitting day} files for each format.
+Our database is available in both CSV and parquet formats. Both CSV and
+parquet are open standards. We provide both because while CSVs are
+commonly used and can be manually inspected, parquet files are typically
+smaller and preserve class. Our database covers all sitting days of the
+House of Representatives from 02 March 1998 to 08 September 2022
+\textbf{where an XML transcript is available}, so there are
+\textbf{1,532 individual sitting day} files for each format.
 \textbf{Additionally, there is a single corpus file in both CSV and
@@
 repository Zenodo, at
-https://doi.org/10.5281/zenodo.7799678\textsuperscript{15}. For each
+https://doi.org/10.5281/zenodo.7799678\textsuperscript{21}. For each
 \textbf{Hansard data} file, \textbf{that is, the corpus and the
@@
 
-{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}
+{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_daily_speeches.png}
 
@@
 2001, and then increased to 151 in the 2019 general
-election\textsuperscript{3}.}
+election\textsuperscript{8}.}
 
@@
 
-{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}
+{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_unique_names.png}
 
@@
 as those parties are the three main political parties in the Australian
-House of Representatives\textsuperscript{16}.}
+House of Representatives\textsuperscript{22}.}
 
@@
 within data from both the \texttt{AustralianPoliticians} and
-\texttt{AustralianElections} R packages\textsuperscript{6,17}. By
+\texttt{AustralianElections} R packages\textsuperscript{11,23}. By
 including this variable, one can readily integrate our data records with
@@
 the \texttt{ausPH} package which provides datasets for contents of the
-Australian Parliamentary Handbook\textsuperscript{5}. This will allow
+Australian Parliamentary Handbook\textsuperscript{10}. This will allow
 for convenient extraction of further details on each MP in a tidy, ready
@@
 https://github.com/lindsaykatz/hansard-proj. All scripts were created
-using R software\textsuperscript{18}. The core packages used to develop
-these scripts are: the \texttt{XML} package by\textsuperscript{11}, the
-\texttt{xml2} package by\textsuperscript{12}, the \texttt{tidyverse} R
-packages by\textsuperscript{19}, the \texttt{AustralianPoliticians}
-package by\textsuperscript{6}, and the \texttt{ausPH} package
-by\textsuperscript{5}. \texttt{XML} and \texttt{xml2} were used for
-parsing the XML documents, \texttt{AustralianPoliticians} and
+using R software\textsuperscript{24}. The core packages used to develop
+these scripts are: the \texttt{XML} package\textsuperscript{17}, the
+\texttt{xml2} package\textsuperscript{18}, the \texttt{tidyverse} R
+packages\textsuperscript{25}, the \texttt{AustralianPoliticians}
+package\textsuperscript{11}, and the \texttt{ausPH}
+package\textsuperscript{10}. \texttt{XML} and \texttt{xml2} were used
+for parsing the XML documents, \texttt{AustralianPoliticians} and
 \texttt{ausPH} were used for cleaning up and filling in MP details in
@@
 We thank Kristine Villaluna, Monica Alexander, and Jack Stephenson for
-helpful comments.
+helpful comments. We wish to especially thank Guy Jones, Chief Editor,
+the two anonymous reviewers, and the Editorial Board Member, Michael
+Jankowski for their comments.
 
@@
 \begin{CSLReferences}{0}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-citehansard}{}}%
+\CSLLeftMargin{1. }%
+\CSLRightInline{Commonwealth of Australia.
+\href{https://www.aph.gov.au/Parliamentary_Business/Hansard}{Parliamentary
+debates, house of representatives}. (2023).}
+
 \leavevmode\vadjust pre{\hypertarget{ref-vice2017history}{}}%
-\CSLLeftMargin{1. }%
+\CSLLeftMargin{2. }%
 \CSLRightInline{Vice, J. \& Farrell, S. \emph{The history of hansard}.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-lipad}{}}%
-\CSLLeftMargin{2. }%
+\CSLLeftMargin{3. }%
 \CSLRightInline{Beelen, K. \emph{et al.} Digitization of the canadian
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Erjavec2022}{}}%
+\CSLLeftMargin{4. }%
+\CSLRightInline{Erjavec, T. \emph{et al.}
+\href{https://doi.org/10.1007/s10579-021-09574-0}{The {ParlaMint}
+corpora of parliamentary proceedings}. \emph{Language Resources and
+Evaluation} \textbf{57}, 415--448 (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Rauh}{}}%
+\CSLLeftMargin{5. }%
+\CSLRightInline{Rauh, C. \& Schwalbach, J. The ParlSpeech V2 data set:
+Full-text corpora of 6.3 million parliamentary speeches in the key
+legislative chambers of nine representative democracies. (2020)
+doi:\href{https://doi.org/10.7910/DVN/L4OAKN}{10.7910/DVN/L4OAKN}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-parlee}{}}%
+\CSLLeftMargin{6. }%
+\CSLRightInline{Sylvester, C., Ershova, A., Khokhlova, A., Yordanova, N.
+\& Greene, Z. {ParlEE plenary speeches V2 data set: Annotated full-text
+of 15.1 million sentence-level plenary speeches of six EU legislative
+chambers}. \emph{Harvard Dataverse} (2023)
+doi:\href{https://doi.org/10.7910/DVN/VOPK0E}{10.7910/DVN/VOPK0E}.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-maple}{}}%
+\CSLLeftMargin{7. }%
+\CSLRightInline{Kartalis, Y. \& Costa Lobo, M. MAPLE parliamentary
+datasets: Full-text and annotated corpora of parliamentary speeches in
+the legislatures of six european democracies. (2021)
+doi:\href{https://doi.org/10.7910/DVN/9MN0RL}{10.7910/DVN/9MN0RL}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-australia2018house}{}}%
-\CSLLeftMargin{3. }%
+\CSLLeftMargin{8. }%
 \CSLRightInline{House of Representatives. \emph{{House of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
-\CSLLeftMargin{4. }%
+\CSLLeftMargin{9. }%
 \CSLRightInline{Sherratt, T.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
-\CSLLeftMargin{5. }%
+\CSLLeftMargin{10. }%
 \CSLRightInline{Leslie, P.
-\emph{\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
-of the australian house of representatives (1945-2019)}}. (2021).}
+\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
+of the australian house of representatives (1945-2019)}. (2021).}
 
 \leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
-\CSLLeftMargin{6. }%
+\CSLLeftMargin{11. }%
 \CSLRightInline{Alexander, R. \& Hodgetts, P. A.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-Dowding2021}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Dowding, K., Leslie, P. \& Taflaga, M. Australia. in
+\emph{The politics of legislative debates} 130--151 (Oxford University
+Press, 2021).
+doi:\href{https://doi.org/10.1093/oso/9780198849063.003.0008}{10.1093/oso/9780198849063.003.0008}.}
+
 \leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
-\CSLLeftMargin{7. }%
+\CSLLeftMargin{13. }%
 \CSLRightInline{Salisbury, C. 'Mr speaker, i withdraw...': Standards of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
-\CSLLeftMargin{8. }%
+\CSLLeftMargin{14. }%
 \CSLRightInline{Rasiah, P. A framework for the systematic analysis of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
-\CSLLeftMargin{9. }%
+\CSLLeftMargin{15. }%
 \CSLRightInline{Fraussen, B., Graham, T. \& Halpin, D. R. Assessing the
@@
 \leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
-\CSLLeftMargin{10. }%
+\CSLLeftMargin{16. }%
 \CSLRightInline{Alexander, R. \& Alexander, M. The increased effect of
@@
 \leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
-\CSLLeftMargin{11. }%
+\CSLLeftMargin{17. }%
 \CSLRightInline{Temple Lang, D.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
-\CSLLeftMargin{12. }%
+\CSLLeftMargin{18. }%
 \CSLRightInline{Wickham, H., Hester, J. \& Ooms, J.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
-\CSLLeftMargin{13. }%
+\CSLLeftMargin{19. }%
 \CSLRightInline{Wickham, H.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
-\CSLLeftMargin{14. }%
+\CSLLeftMargin{20. }%
 \CSLRightInline{House of Representatives. \emph{{A window on the house:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
-\CSLLeftMargin{15. }%
+\CSLLeftMargin{21. }%
 \CSLRightInline{Katz, L. \& Alexander, R. {A new, comprehensive database
@@
 \leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
-\CSLLeftMargin{16. }%
+\CSLLeftMargin{22. }%
 \CSLRightInline{Parliament of Australia.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-auselect}{}}%
-\CSLLeftMargin{17. }%
+\CSLLeftMargin{23. }%
 \CSLRightInline{Alexander, R.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%
-\CSLLeftMargin{18. }%
+\CSLLeftMargin{24. }%
 \CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
-\CSLLeftMargin{19. }%
+\CSLLeftMargin{25. }%
 \CSLRightInline{Wickham, H. \emph{et al.}

### 2023-07-06 paper/paper-nature-revised.qmd
lindsay updates

@@
 Following the lead of that project, in this paper we introduce a similar database for Australia.
-This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
+This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to **September** 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
 With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.
@@
 An international linkage provides a comparison case where domestic issues are different while international ones are common.
-As an example of enabling this linkage this we have included partyfacts IDs in our database.
+As an example of enabling this linkage we have included PartyFacts IDs in our database.
 This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].**
@@
 Like us they scrape the Hansard record and link it with biographical data.
-They key difference is that our focus is on the database itself, while  are focused on using a database constructed from the same source to answer a particular question about speaker time.
+The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time.
 This different focus leads to different emphasis and approaches.**
@@
 Question Time data from Hansard transcripts during February and March of 2003 has been used to investigate resistance of politicians in answering questions about Iraq @rasiah2010framework.
-Hansard has been used to quantify political prominence by investigating strategic mentions of interest groups by elected officials @fraussen2018.
+Hansard has also been used to quantify political prominence by investigating strategic mentions of interest groups by elected officials @fraussen2018.
 Finally, a dataset of the Australian Hansard has been constructed and then used to analyze the effect of elections and changes in Prime Ministers upon topics mentioned in parliament @alexander2021.
@@
 > ```
-
+>
 > "Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great pleasure to share with the House that Windaroo Valley State High School has qualified for the finals of the Australian Space Design Competition, to begin in January next year.
@@
 Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do.
-However, they provide valuable information about the inner-workings and structure of parliamentary events.**
+However, they provide valuable information about the inner-workings and structure of parliamentary events.
+If the focus on the user’s research does not require stage directions, then this can be removed by filtering observations in name equal to “business start”, or “stage direction”.**
 
@@
 Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a time stamp.
-Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset.**
+Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset.
+After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.**
 
@@
 To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any time stamps where available, and did any additional data cleaning as necessary.
-We used a series of if-else statements in this script to account for variation in the structure of the `<divisions>` node over time.
+We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time.
 Finally, we then added a date variable to distinguish between sitting days.**
@@
 Our database is available in both CSV and parquet formats.
-Both CSV and parquet are open standards.
-We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class.
-Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format.
-**Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
-There is also a CSV and Parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023].
+**Both CSV and parquet are open standards.
+We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class.** Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format.
+**Additionally, there is a single corpus file in both CSV and parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
+There is also a CSV and parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at <https://doi.org/10.5281/zenodo.7336075> [@katz_2023].
 For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking.
@@
 
-**As mentioned, in addition to the Hansard data described above, our database also contains a CSV and Parquet file with the parsed debate topics.
+**As mentioned, in addition to the Hansard data described above, our database also contains a CSV and parquet file with the parsed debate topics.
 This file is called `all_debate_topics`, and contains a `date` variable specifying the sitting day, an `item_index` variable to specify the order of proceedings (i.e.
@@
 **Finally, our database contains a file with all parsed divisions data in our timeframe.
-This is called `division_data`, and is available in RDA form and in Parquet form.
+This is called `division_data`, and is available in RDA form and in parquet form.
 The reason it is not available in CSV form is because three of the variables (`names_AYES`, `names_NOES`, and `names_PAIRS`) are lists, which are not supported by the CSV rectangular data structure.
@@
 **We then computed the total number of speeches made in our database by political party, summarized in @tbl-speeches_by_party.
-We found that the Australian Labor Party made the most speeches overall, followed by the Liberal Party of Australia, and the Nationalist Party.
+We found that the Australian Labor Party made the most speeches overall, followed by the Liberal Party of Australia, and the National Party of Australia.
 These rankings are unsurprising, as those parties are the three main political parties in the Australian House of Representatives [@infosheet_parties].**
@@
 
-**Finally, the README file on our GitHub repository and on Zenodo contains example code on how to read in a file from our database, for both CSV and Parquet formats.
+**Finally, the README file on our GitHub repository and on Zenodo contains example code on how to read in a file from our database, for both CSV and parquet formats.
 Should a user wish to use the single Hansard corpus rather than individual sitting day files, we provide example code on how to read it in, filter for those sitting days of interest, and split them into distinct data frames.

### 2023-07-06 paper/paper-nature-revised.tex
lindsay updates

@@
 \usepackage{amsmath,amssymb}
+\usepackage{lmodern}
 \usepackage{iftex}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-\usepackage{lmodern}
-\ifPDFTeX\else  
-    % xetex/luatex font selection
 \fi
@@
 \makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
+\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
 \makeatother
@@
 \@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
 \makeatother
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable]}{\end{tcolorbox}}\fi
 
@@
 database for Australia. This is composed of individual datasets for each
-sitting day in the House of Representatives from 1998 to 2022,
-containing details on everything said in parliament in a form that can
-be readily used by researchers. With the development of tools for
-large-scale text analysis, this database will serve as a resource for
-understanding political behaviour in Australia over time.
+sitting day in the House of Representatives from 1998 to
+\textbf{September} 2022, containing details on everything said in
+parliament in a form that can be readily used by researchers. With the
+development of tools for large-scale text analysis, this database will
+serve as a resource for understanding political behaviour in Australia
+over time.
 
@@
 are different while international ones are common. As an example of
-enabling this linkage this we have included partyfacts IDs in our
-database. This should make it possible to link our database with other
-large parliamentary speech collection projects, such as
+enabling this linkage we have included PartyFacts IDs in our database.
+This should make it possible to link our database with other large
+parliamentary speech collection projects, such as
 ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
@@
 Australia\textsuperscript{12}. Like us they scrape the Hansard record
-and link it with biographical data. They key difference is that our
-focus is on the database itself, while are focused on using a database
+and link it with biographical data. The key difference is that our focus
+is on the database itself, while they are focused on using a database
 constructed from the same source to answer a particular question about
@@
 2003 has been used to investigate resistance of politicians in answering
-questions about Iraq\textsuperscript{14}. Hansard has been used to
+questions about Iraq\textsuperscript{14}. Hansard has also been used to
 quantify political prominence by investigating strategic mentions of
@@
 \begin{quote}
-\end{quote}
-
-\begin{quote}
 ``Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great
@@
 information about the inner-workings and structure of parliamentary
-events.}
+events. If the focus on the user's research does not require stage
+directions, then this can be removed by filtering observations in name
+equal to ``business start'', or ``stage direction''.}
 
@@
 Therefore, we took the first available page number child-node for each
-debate or sub-debate node to be the one we included in our dataset.}
+debate or sub-debate node to be the one we included in our dataset.
+After summarizing, these topics can be added to the main text by
+joining, and example code is provided in the README.}
 
@@
 statements in this script to account for variation in the structure of
-the \texttt{\textless{}divisions\textgreater{}} node over time. Finally,
+the \texttt{\textless{}division\textgreater{}} node over time. Finally,
 we then added a date variable to distinguish between sitting days.}
@@
 
-Our database is available in both CSV and parquet formats. Both CSV and
-parquet are open standards. We provide both because while CSVs are
-commonly used and can be manually inspected, parquet files are typically
-smaller and preserve class. Our database covers all sitting days of the
-House of Representatives from 02 March 1998 to 08 September 2022
-\textbf{where an XML transcript is available}, so there are
+Our database is available in both CSV and parquet formats. \textbf{Both
+CSV and parquet are open standards. We provide both because while CSVs
+are commonly used and can be manually inspected, parquet files are
+typically smaller and preserve class.} Our database covers all sitting
+days of the House of Representatives from 02 March 1998 to 08 September
+2022 \textbf{where an XML transcript is available}, so there are
 \textbf{1,532 individual sitting day} files for each format.
 \textbf{Additionally, there is a single corpus file in both CSV and
-Parquet forms containing the data from all sitting days, with a date
+parquet forms containing the data from all sitting days, with a date
 variable added to allow for distinction and filtering of individual
-sitting days. There is also a CSV and Parquet file containing all parsed
+sitting days. There is also a CSV and parquet file containing all parsed
 debate topics.} All data records are available on the general-purpose
 repository Zenodo, at
-https://doi.org/10.5281/zenodo.7799678\textsuperscript{21}. For each
-\textbf{Hansard data} file, \textbf{that is, the corpus and the
+\url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{21}. For
+each \textbf{Hansard data} file, \textbf{that is, the corpus and the
 individual sitting day files}, each row contains an individual
@@
 \textbf{As mentioned, in addition to the Hansard data described above,
-our database also contains a CSV and Parquet file with the parsed debate
+our database also contains a CSV and parquet file with the parsed debate
 topics. This file is called \texttt{all\_debate\_topics}, and contains a
@@
 data in our timeframe. This is called \texttt{division\_data}, and is
-available in RDA form and in Parquet form. The reason it is not
+available in RDA form and in parquet form. The reason it is not
 available in CSV form is because three of the variables
@@
 Party made the most speeches overall, followed by the Liberal Party of
-Australia, and the Nationalist Party. These rankings are unsurprising,
-as those parties are the three main political parties in the Australian
-House of Representatives\textsuperscript{22}.}
+Australia, and the National Party of Australia. These rankings are
+unsurprising, as those parties are the three main political parties in
+the Australian House of Representatives\textsuperscript{22}.}
 
@@
 contains example code on how to read in a file from our database, for
-both CSV and Parquet formats. Should a user wish to use the single
+both CSV and parquet formats. Should a user wish to use the single
 Hansard corpus rather than individual sitting day files, we provide
@@
 \CSLRightInline{Leslie, P.
-\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
-of the australian house of representatives (1945-2019)}. (2021).}
+\emph{\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
+of the australian house of representatives (1945-2019)}}. (2021).}
 
@@
 (2023)
-doi:\href{https://doi.org/10.5281/zenodo.7799678}{10.5281/zenodo.7799678}.}
+doi:\href{https://doi.org/10.5281/zenodo.7336075}{10.5281/zenodo.7336075}.}
 

### 2023-07-06 paper/paper-nature-revised.qmd
final small changes

@@
 **It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch.
-As such, users may identify and should be weary of occasional incorrectly flagged questions or answers in the data.**
+As such, users may identify and should be wary of occasional incorrectly flagged questions or answers in the data.**
 
@@
 However, they provide valuable information about the inner-workings and structure of parliamentary events.
-If the focus on the user’s research does not require stage directions, then this can be removed by filtering observations in name equal to “business start”, or “stage direction”.**
+If the focus of the user’s research does not require stage directions, then this can be removed by filtering observations in `name` equal to “business start”, or “stage direction”.**
 

### 2023-07-06 paper/paper-nature-revised.tex
final small changes

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, interior hidden, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 discovered them, additional flagging errors may exist which we did not
-catch. As such, users may identify and should be weary of occasional
+catch. As such, users may identify and should be wary of occasional
 incorrectly flagged questions or answers in the data.}
@@
 information about the inner-workings and structure of parliamentary
-events. If the focus on the user's research does not require stage
-directions, then this can be removed by filtering observations in name
-equal to ``business start'', or ``stage direction''.}
+events. If the focus of the user's research does not require stage
+directions, then this can be removed by filtering observations in
+\texttt{name} equal to ``business start'', or ``stage direction''.}
 

### 2023-07-06 paper/paper-nature-revised.qmd
fixed inconsistent timestamp spelling

@@
 To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`.
-After making this modification and accounting for other small changes such as time stamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).
+After making this modification and accounting for other small changes such as timestamp formatting, this second script successfully parses all Hansard sitting days from 10 May 2011 to 28 June 2012 (inclusive).
 
@@
 Note that in some cases there were multiple page number child nodes for the same debate or sub-debate title, likely due to manual transcription error.
-Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a time stamp.
+Upon manual inspection, we found that most often, the second page number node contained the same page number as the first node, and sometimes the second node contained a repeated debate title or a timestamp.
 Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset.
@@
 To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame.
-To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any time stamps where available, and did any additional data cleaning as necessary.
+To produce this data file, for each Hansard XML we parsed the `<division.header>`, `<division.data>`, and `<division.result>` child-nodes where they existed, extracted any timestamps where available, and did any additional data cleaning as necessary.
 We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time.
@@
                          "Index for each division parsed for that sitting day",
-                         "Time stamp associated with each division",
+                         "Timestamp associated with each division",
                          "Number of votes in the affirmative",
@@
 
-**The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all time stamps in our database which do not match the correct "HH:MM:SS" format.
-We found a total of 88 incorrectly formatted time stamps, with common issues such as the "HH" or "MM" component recorded as "NaN" (e.g.
+**The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all timestamps in our database which do not match the correct "HH:MM:SS" format.
+We found a total of 88 incorrectly formatted timestamps, with common issues such as the "HH" or "MM" component recorded as "NaN" (e.g.
 "NaN:28:00" or "09:NaN:00"), as well as timestamps with a third digit in the minute component (e.g.

### 2023-07-06 paper/paper-nature-revised.tex
fixed inconsistent timestamp spelling

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, interior hidden, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, frame hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
 
@@
 \texttt{\textless{}maincomm.xscript\textgreater{}}. After making this
-modification and accounting for other small changes such as time stamp
+modification and accounting for other small changes such as timestamp
 formatting, this second script successfully parses all Hansard sitting
@@
 node contained the same page number as the first node, and sometimes the
-second node contained a repeated debate title or a time stamp.
-Therefore, we took the first available page number child-node for each
-debate or sub-debate node to be the one we included in our dataset.
-After summarizing, these topics can be added to the main text by
-joining, and example code is provided in the README.}
+second node contained a repeated debate title or a timestamp. Therefore,
+we took the first available page number child-node for each debate or
+sub-debate node to be the one we included in our dataset. After
+summarizing, these topics can be added to the main text by joining, and
+example code is provided in the README.}
 
@@
 \texttt{\textless{}division.result\textgreater{}} child-nodes where they
-existed, extracted any time stamps where available, and did any
+existed, extracted any timestamps where available, and did any
 additional data cleaning as necessary. We used a series of if-else
@@
 div\_num & Index for each division parsed for that sitting day\\
-time.stamp & Time stamp associated with each division\\
+time.stamp & Timestamp associated with each division\\
 num.votes\_AYES & Number of votes in the affirmative\\
@@
 \textbf{The fourth test is designed to detect issues in timestamp
-formatting in the data, by detecting all time stamps in our database
+formatting in the data, by detecting all timestamps in our database
 which do not match the correct ``HH:MM:SS'' format. We found a total of
-88 incorrectly formatted time stamps, with common issues such as the
+88 incorrectly formatted timestamps, with common issues such as the
 ``HH'' or ``MM'' component recorded as ``NaN'' (e.g.~``NaN:28:00'' or

### 2023-07-06 paper/first-draft/paper-nature.qmd
moving old files to folder

--- 2023-07-06 paper/first-draft/paper-arxiv.qmd
@@
 It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are 1,517 files for each format.
-All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7336075 [@katz_2023].
+All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023].
 For each file, each row contains an individual statement, with details on the individual speaking.

### 2023-07-06 paper/first-draft/paper-nature.tex
moving old files to folder

--- 2023-04-27 paper/paper-nature.tex
@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{April 27, 2023}
+\date{May 3, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, interior hidden, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[frame hidden, enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 records are available on the general-purpose repository Zenodo, at
-https://doi.org/10.5281/zenodo.7336075 (Katz and Alexander 2023). For
+https://doi.org/10.5281/zenodo.7799678 (Katz and Alexander 2023). For
 each file, each row contains an individual statement, with details on

### 2023-07-06 paper/paper-nature-revised.qmd
changed filepaths

@@
 
-![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](images/xml1.png){#fig-xml1}
+![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
 
@@
 
-![Portion of XML file for Hansard on 12 December 2002](images/patternEX.png){#fig-patternEX width="315"}
+![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}
 
@@
 
-![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](images/xml3.png){#fig-xml3 width="345"}
+![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
 
@@
 
-![First 10 rows of the lookup table from 19 October 2017 Hansard processing](images/lookup_ex.png){#fig-lookup width="448"}
+![First 10 rows of the lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
 
@@
 
-![Example of speech with interjections from 21 November 2016 Hansard](images/interject_ex.png){#fig-interject}
+![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
 
@@
 
-![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](images/pattern_lookup.png){#fig-patterns}
+![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}
 
@@
 
-![Number of speeches made on each sitting day in the House of Representatives](images/n_daily_speeches.png){#fig-dailyspeeches width="440"}
+![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}
 
@@
 
-![Daily number of unique names detected in our Hansard data](images/n_unique_names.png){#fig-names width="440"}
+![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}
 

### 2023-07-06 paper/paper-nature-revised.tex
changed filepaths

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, boxrule=0pt, interior hidden, frame hidden, enhanced, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 
-{\centering \includegraphics{images/xml1.png}
+{\centering \includegraphics{xml1.png}
 
@@
 
-{\centering \includegraphics[width=3.28125in,height=\textheight]{images/patternEX.png}
+{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}
 
@@
 
-{\centering \includegraphics[width=3.59375in,height=\textheight]{images/xml3.png}
+{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}
 
@@
 
-{\centering \includegraphics[width=4.66667in,height=\textheight]{images/lookup_ex.png}
+{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}
 
@@
 
-{\centering \includegraphics{images/interject_ex.png}
+{\centering \includegraphics{interject_ex.png}
 
@@
 
-{\centering \includegraphics{images/pattern_lookup.png}
+{\centering \includegraphics{pattern_lookup.png}
 
@@
 
-{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_daily_speeches.png}
+{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}
 
@@
 
-{\centering \includegraphics[width=4.58333in,height=\textheight]{images/n_unique_names.png}
+{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}
 

### 2023-07-27 paper/paper-nature-revised.qmd
minor editorial revisions

@@
 title: "Digitization of the Australian Parliamentary Debates, 1998-2022"
-number-sections: true
+number-sections: false
 format: 
@@
 
-The official written record of parliamentary debates, **formally known as Hansard [@citehansard],** plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
+The official written record of parliamentary debates, formally known as Hansard [@citehansard], plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions.
 Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history].
@@
 Following the lead of that project, in this paper we introduce a similar database for Australia.
-This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to **September** 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
+This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to September 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
 With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.
 
-**There are a wide variety of potential applications of this database.
+There are a wide variety of potential applications of this database.
 For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined).
@@
 As an example of enabling this linkage we have included PartyFacts IDs in our database.
-This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].**
+This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].
 
@@
 Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol.
-**And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021.
+And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021.
 Like us they scrape the Hansard record and link it with biographical data.
 The key difference is that our focus is on the database itself, while they are focused on using a database constructed from the same source to answer a particular question about speaker time.
-This different focus leads to different emphasis and approaches.**
+This different focus leads to different emphasis and approaches.
 
@@
 Further, we discuss the script we developed to fill in remaining missing details on the MP speaking, which each file in our database was passed to after being parsed and cleaned.
-**Finally, we review the supplementary Hansard debate topics dataset and supplementary divisions dataset we created to expand the versatility of our database.**
+Finally, we review the supplementary Hansard debate topics dataset and supplementary divisions dataset we created to expand the versatility of our database.
 
@@
 The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements.
-More detail on the purpose and processing of Question Time will follow in @sec-qa.
+More detail on the purpose and processing of Question Time will [follow](#sec-qa).
 
@@
 
-![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](xml1.png){#fig-xml1}
+![Snapshot of the beginning of the XML file for Hansard on 25 February 2020](xml1.jpg){#fig-xml1}
 
@@
 There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days.
-Details on these are provided in @sec-interject.
+Details on these are provided in the Interjections [section](#sec-interject) to follow.
 
@@
 Specifically, we added a section of our script to separate out general stage directions.
-More information on this separation will be provided in @sec-stage.
+More information on this separation will be provided in the subsequent Stage Directions [section](#sec-stage).
 After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.
@@
 Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts.
-While all four scripts use the same general approach to parsing described in @sec-overview and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.
+While all four scripts use the same general approach to parsing described in the Overview [section](#sec-overview) and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.
 
@@
 
-![Portion of XML file for Hansard on 12 December 2002](patternEX.png){#fig-patternEX width="315"}
+![Portion of XML file for Hansard on 12 December 2002](patternEX.jpg){#fig-patternEX width="315"}
 
@@
 As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to.
-Sometimes, **we identified** questions **which** were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags.
+Sometimes, we identified questions which were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags.
 For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer.
-**It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch.
-As such, users may identify and should be wary of occasional incorrectly flagged questions or answers in the data.**
+It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch.
+As such, users may identify and should be wary of occasional incorrectly flagged questions or answers in the data.
 
@@
 
-As mentioned in @sec-diff, more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech.
-@fig-xml3 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech.
+As mentioned in the Script Differences [section](#sec-diff), more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech.
+@fig-xml2 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech.
 Looking at the element names highlighted in blue, these child nodes do not contain the actual text for the interjection or continuation --- this text is embedded within the speech above it.
-However, as shown by the content highlighted in pink in @fig-xml3, we were able to extract useful details on the individual interjecting which we could use later.
+However, as shown by the content highlighted in pink in @fig-xml2, we were able to extract useful details on the individual interjecting which we could use later.
 Making use of this structure, we extracted names and information of all individuals that were categorized within the XML as interjections.
@@
 
-![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml3.png){#fig-xml3 width="345"}
+![Snapshot of XML structure with interjection and continuation from 03 February 2021 Hansard](xml2.jpg){#fig-xml2 width="345"}
 
@@
 When an MP interjects or continues a speech, the usual form of their name is a title followed by their first name or first initial and/or last name.
-There is also variation in the capitalization of these names.[^1] Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
+There is also variation in the capitalization of these names.
+Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
+Another source of variation is in individuals with more than one first name, as sometimes only their initial first name is written, while other times their entire first name is written.
 Additionally, some surnames have punctuation, and some surnames have specific capitalization such as "McCormack", where even in full capitalization, the first "c" remains lower case.
@@
 In these lists we also accounted for any general interjection statements that were not attributed to an individual, such as "An opposition member interjecting-".
-
-[^1]: Sometimes when someone's first name is included, only their last name is capitalized, while sometimes their full name is capitalized, or other times neither are capitalized.
 
@@
 
-![First 10 rows of the lookup table from 19 October 2017 Hansard processing](lookup_ex.png){#fig-lookup width="448"}
+![First 10 rows of the lookup table from 19 October 2017 Hansard processing](lookup_ex.jpg){#fig-lookup width="448"}
 
@@
 
-![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.png){#fig-interject}
+![Example of speech with interjections from 21 November 2016 Hansard](interject_ex.jpg){#fig-interject}
 
@@
 However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology.
-As discussed in @sec-diff, we used string patterns extracted from `<talk.start>` nodes to separate speeches.
-As evident in @fig-xml3, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process.
+As discussed in the Script Differences [section](#sec-diff), we used string patterns extracted from `<talk.start>` nodes to separate speeches.
+As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process.
 In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process.
@@
 However, we used the same list of general interjection statements on which to separate as was used in the first two scripts.
-We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.[^2]
-
-[^2]: While most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
+We then did an additional check for statements that may have not been separated due to how they were embedded in the XML, and separated those out where needed.
+In particular, while most statements were categorized in their own child node and hence captured through pattern-based separation, some were not individually categorized, and had to be split manually in this step.
 
@@
 
-![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.png){#fig-patterns}
+![10 rows of the pattern lookup table from 12 December 2012 Hansard processing](pattern_lookup.jpg){#fig-patterns}
 
@@
 We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts.
-**Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process.
+Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process.
 Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do.
 However, they provide valuable information about the inner-workings and structure of parliamentary events.
-If the focus of the user’s research does not require stage directions, then this can be removed by filtering observations in `name` equal to “business start”, or “stage direction”.**
+If the focus of the user's research does not require stage directions, then this can be removed by filtering observations in `name` equal to "business start", or "stage direction".
 
@@
 
-**To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database.
+To enhance the range of research questions which can be explored with our data, we have created a supplementary file containing debate topics and their corresponding page numbers for each sitting day in our database.
 To extract these data, we wrote a script to parse debate and sub-debate 1 information elements from each XML file in chronological order using the XPath expression "`//debate/debateinfo | //subdebate.1/subdebateinfo`", and added a date variable with the date of each sitting day.
@@
 Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset.
-After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.**
+After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.
 
@@
 
-**Another fundamental component of parliamentary proceedings is voting.
+Another fundamental component of parliamentary proceedings is voting.
 In the House, when a question arises such as "The question is that the amendment be agreed to", Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house].
 Further, Members can vote in an unofficial arrangement called pairs, which "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting" @australia2018house.
-If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**
+If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].
 
-**In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result.
+In the Hansard XML files, divisions data are structured outside of the `<speech>` content in their own `<division>` nodes that contain the voting data and division result.
 Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings.
-Our approach to parsing Hansard in the third and fourth scripts described in @sec-diff naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not.
+Our approach to parsing Hansard in the third and fourth scripts described in the Script Differences [section](#sec-diff) naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not.
 To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame.
@@
 We used a series of if-else statements in this script to account for variation in the structure of the `<division>` node over time.
-Finally, we then added a date variable to distinguish between sitting days.**
+Finally, we then added a date variable to distinguish between sitting days.
 
@@
 Our database is available in both CSV and parquet formats.
-**Both CSV and parquet are open standards.
-We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class.** Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format.
-**Additionally, there is a single corpus file in both CSV and parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
-There is also a CSV and parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at <https://doi.org/10.5281/zenodo.7336075> [@katz_2023].
-For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking.
+Both CSV and parquet are open standards.
+We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class.
+Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 where an XML transcript is available, so there are 1,532 individual sitting day files for each format.
+Additionally, there is a single corpus file in both CSV and parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days.
+There is also a CSV and parquet file containing all parsed debate topics.
+All data records are available on the general-purpose repository Zenodo, at <https://doi.org/10.5281/zenodo.7336075> [@katz_2023].
+For each Hansard data file, that is, the corpus and the individual sitting day files, each row contains an individual statement, with details on the individual speaking.
 For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified.
-@tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.
+@tbl-vars provides an overview of each variable found in the Hansard data files in the database.
 
@@
 The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements.
-We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag **those rows where "The House divided." was detected in the body variable**.
-The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, **and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project [website](https://partyfacts.herokuapp.com).**[^3] Details on the usage of `uniqueID` **and `partyfacts_id`** will be provided in @sec-usage.
+We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag those rows where "The House divided." was detected in the body variable.
+The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website (https://partyfacts.herokuapp.com).
+Note that in accordance with the code provided on the Party Facts downloads page (https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov.
+Details on these datasets can be found on the Party Facts datasets documentation page (https://partyfacts.herokuapp.com/documentation/datasets/).
+Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the [Usage Notes](#sec-usage) to follow.
 Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.
 Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest.
-**Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.**
+Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.
 
-[^3]: **Note that in accordance with the code provided on the Party Facts [downloads page](https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov.
-Details on these datasets can be found here: https://partyfacts.herokuapp.com/documentation/datasets/.**
+As mentioned, in addition to the Hansard data described above, our database also contains a CSV and parquet file with the parsed debate topics.
+This file is called `all_debate_topics`, and contains a `date` variable specifying the sitting day, an `item_index` variable to specify the order of proceedings (i.e.
+the order in which these topics were discussed), a `title` variable containing the debate or sub-debate title contents, and a `page.no` variable specifying on which page that title was recorded to be found in the official Hansard PDF.
 
-**As mentioned, in addition to the Hansard data described above, our database also contains a CSV and parquet file with the parsed debate topics.
-This file is called `all_debate_topics`, and contains a `date` variable specifying the sitting day, an `item_index` variable to specify the order of proceedings (i.e.
-the order in which these topics were discussed), a `title` variable containing the debate or sub-debate title contents, and a `page.no` variable specifying on which page that title was recorded to be found in the official Hansard PDF.**
-
-**There is also a CSV file in our database called `PartyFacts_map.csv`.
+There is also a CSV file in our database called `PartyFacts_map.csv`.
 This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable.
 As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data.
-Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package for completeness.**
+Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package for completeness.
 
@@
 
-**Finally, our database contains a file with all parsed divisions data in our timeframe.
+Finally, our database contains a file with all parsed divisions data in our timeframe.
 This is called `division_data`, and is available in RDA form and in parquet form.
 The reason it is not available in CSV form is because three of the variables (`names_AYES`, `names_NOES`, and `names_PAIRS`) are lists, which are not supported by the CSV rectangular data structure.
-The variables found in these data are summarized below, in @tbl-divisions.**
+The variables found in these data are summarized below, in @tbl-divisions.
 
@@
 We developed a script to perform automated tests on each file in our database, to enhance its quality and consistency.
-Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.[^4] Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
+Our first test validates that the date specified in each file name matches the date specified in its corresponding XML session header.
+This XML component can be seen in @fig-xml1, where the first child node of the `<session.header>` element is the date.
+Every file passed this test, and we detected one discrepancy in an XML file from 03 June 2009, where its session header contained the wrong date.
 We validated that our file name and date was correct by checking the official PDF release from that sitting day.
-
-[^4]: As seen in @fig-xml1, the first child node of the `<session.header>` element is the date.
 
@@
 spoken content).
-This test detected **131** dates on which duplicate statements were made, and one immediately follows the other.
+This test detected 131 dates on which duplicate statements were made, and one immediately follows the other.
 Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well.
@@
 
-**The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all timestamps in our database which do not match the correct "HH:MM:SS" format.
+The fourth test is designed to detect issues in timestamp formatting in the data, by detecting all timestamps in our database which do not match the correct "HH:MM:SS" format.
 We found a total of 88 incorrectly formatted timestamps, with common issues such as the "HH" or "MM" component recorded as "NaN" (e.g.
@@
 We found that every improperly formatted timestamp in our random sample was in fact transcribed as such in its original XML file, meaning these bugs are the result of a transcription error, rather than an error resulting from our data parsing or cleaning code.
-As such, we have left these timestamps in their originally transcribed format in our database.**
+As such, we have left these timestamps in their originally transcribed format in our database.
 
@@
 
-**To further explore the quality of our data and detect any unexpected or distinct trends, we generated a number of summary statistics using the complete Hansard corpus.
+To further explore the quality of our data and detect any unexpected or distinct trends, we generated a number of summary statistics using the complete Hansard corpus.
 First, we looked at the number of speeches made each day, disaggregated by Chamber and Federation Chamber debate venues.
 As shown in @fig-dailyspeeches, there are consistently more speeches made in the Chamber proceedings than in the Federation Chamber, which aligns with the wider scope of business covered in the Chamber.
-Further, in both debate venues, the number of speeches each day appears to have increased slightly over time.**
+Further, in both debate venues, the number of speeches each day appears to have increased slightly over time.
 
-![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}
+![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.jpg){#fig-dailyspeeches width="440"}
 
-**Next, we explored the number of unique names detected on each sitting day disaggregated by debate venue, visualized in @fig-names.
+Next, we explored the number of unique names detected on each sitting day disaggregated by debate venue, visualized in @fig-names.
 As expected, there are generally more individual MPs detected to be present in the Chamber proceedings in our data than in the Federation Chamber proceedings.
@@
 Across the time frame of our data, there was a daily average of 84 unique names detected in the Chamber, and 34 in the Federation Chamber.
-These observations are in accordance with the official number of Members belonging to the House of Representatives, which was 148 in 1998, 150 in 2001, and then increased to 151 in the 2019 general election [@australia2018house].**
+These observations are in accordance with the official number of Members belonging to the House of Representatives, which was 148 in 1998, 150 in 2001, and then increased to 151 in the 2019 general election [@australia2018house].
 
-![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}
+![Daily number of unique names detected in our Hansard data](n_unique_names.jpg){#fig-names width="440"}
 
-**We then computed the total number of speeches made in our database by political party, summarized in @tbl-speeches_by_party.
+We then computed the total number of speeches made in our database by political party, summarized in @tbl-speeches_by_party.
 We found that the Australian Labor Party made the most speeches overall, followed by the Liberal Party of Australia, and the National Party of Australia.
-These rankings are unsurprising, as those parties are the three main political parties in the Australian House of Representatives [@infosheet_parties].**
+These rankings are unsurprising, as those parties are the three main political parties in the Australian House of Representatives [@infosheet_parties].
 
@@
 read_csv("s_by_party_name.csv", show_col_types = F) |> 
-  knitr::kable(booktabs=T) |> 
+  knitr::kable(booktabs=T, format.args = list(big.mark = ",")) |> 
   kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
@@
 By including this variable, one can readily integrate our data records with those available in these two packages.
-**Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.**
+Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.
 
@@
 
-**Finally, the README file on our GitHub repository and on Zenodo contains example code on how to read in a file from our database, for both CSV and parquet formats.
+Finally, the README file on our GitHub repository and on Zenodo contains example code on how to read in a file from our database, for both CSV and parquet formats.
 Should a user wish to use the single Hansard corpus rather than individual sitting day files, we provide example code on how to read it in, filter for those sitting days of interest, and split them into distinct data frames.
 We have also added example code for filtering out stage directions, and updating the `order` variable to reflect the ordering of remaining rows, should the user wish to remove stage directions from their analysis.
-Lastly, the README contains example code showing users how to merge the debate topics data with a Hansard data file for one sitting day.**
+Lastly, the README contains example code showing users how to merge the debate topics data with a Hansard data file for one sitting day.
 
@@
 
-The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj.
+The code written to build this database is available on the GitHub repository associated with this paper (https://github.com/lindsaykatz/hansard-proj).
 All scripts were created using R software [@r_software].

### 2023-07-27 paper/paper-nature-revised.tex
minor editorial revisions

@@
 \setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
 % Make \paragraph and \subparagraph free-standing
@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{July 6, 2023}
+\date{July 26, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, frame hidden, enhanced, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 
-The official written record of parliamentary debates, \textbf{formally
-known as Hansard\textsuperscript{1},} plays a fundamental role in
-capturing the history of political proceedings and facilitating the
-exploration of valuable research questions. Originating in the British
-parliament, the production of Hansard became tradition in many other
-Commonwealth countries, such as Canada and Australia\textsuperscript{2}.
-Given the content and magnitude of these records, they have
-significance, particularly in the context of political science research.
-In the case of Canada, the Hansard has been digitized for 1901 to
+The official written record of parliamentary debates, formally known as
+Hansard\textsuperscript{1}, plays a fundamental role in capturing the
+history of political proceedings and facilitating the exploration of
+valuable research questions. Originating in the British parliament, the
+production of Hansard became tradition in many other Commonwealth
+countries, such as Canada and Australia\textsuperscript{2}. Given the
+content and magnitude of these records, they have significance,
+particularly in the context of political science research. In the case
+of Canada, the Hansard has been digitized for 1901 to
 2019\textsuperscript{3}. Having a digitized version of Hansard enables
@@
 database for Australia. This is composed of individual datasets for each
-sitting day in the House of Representatives from 1998 to
-\textbf{September} 2022, containing details on everything said in
-parliament in a form that can be readily used by researchers. With the
-development of tools for large-scale text analysis, this database will
-serve as a resource for understanding political behaviour in Australia
-over time.
-
-\textbf{There are a wide variety of potential applications of this
-database. For instance, within Australia there is considerable concern
-that there has been a decline in the `quality' of public policy debate
-(however that might be defined). Our dataset could be used to look at
-whether it is really getting worse in particular ways, and if so, why.
-We might also be interested in whether particular sub-populations are
-appropriately represented in what is talked about in parliament. For
-instance, there is often concern that regional areas are overlooked
-compared with metropolitan areas. Again, our database could be used to
-examine whether this has changed over time. We have developed our
-database in such a way that it could be linked with similar databases
-from other countries which would enable comparative analysis. For
-instance, we may be interested in how the policy focus of a parliament
-changes given various global events such as pandemics or wars. An
-international linkage provides a comparison case where domestic issues
-are different while international ones are common. As an example of
-enabling this linkage we have included PartyFacts IDs in our database.
-This should make it possible to link our database with other large
-parliamentary speech collection projects, such as
-ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
-ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.}
+sitting day in the House of Representatives from 1998 to September 2022,
+containing details on everything said in parliament in a form that can
+be readily used by researchers. With the development of tools for
+large-scale text analysis, this database will serve as a resource for
+understanding political behaviour in Australia over time.
+
+There are a wide variety of potential applications of this database. For
+instance, within Australia there is considerable concern that there has
+been a decline in the `quality' of public policy debate (however that
+might be defined). Our dataset could be used to look at whether it is
+really getting worse in particular ways, and if so, why. We might also
+be interested in whether particular sub-populations are appropriately
+represented in what is talked about in parliament. For instance, there
+is often concern that regional areas are overlooked compared with
+metropolitan areas. Again, our database could be used to examine whether
+this has changed over time. We have developed our database in such a way
+that it could be linked with similar databases from other countries
+which would enable comparative analysis. For instance, we may be
+interested in how the policy focus of a parliament changes given various
+global events such as pandemics or wars. An international linkage
+provides a comparison case where domestic issues are different while
+international ones are common. As an example of enabling this linkage we
+have included PartyFacts IDs in our database. This should make it
+possible to link our database with other large parliamentary speech
+collection projects, such as ParlaMint\textsuperscript{4},
+ParlSpeech\textsuperscript{5}, ParlEE\textsuperscript{6}, and
+MAPLE\textsuperscript{7}.
 
@@
 of Australian federal politicians who were active between 1901 and
-2021\textsuperscript{11}. \textbf{And finally, there has been
-examination of speech and MP level data between 1990 and 2019 in
+2021\textsuperscript{11}. And finally, there has been examination of
+speech and MP level data between 1990 and 2019 in
 Australia\textsuperscript{12}. Like us they scrape the Hansard record
@@
 speaker time. This different focus leads to different emphasis and
-approaches.}
+approaches.
 
@@
 details on the MP speaking, which each file in our database was passed
-to after being parsed and cleaned. \textbf{Finally, we review the
-supplementary Hansard debate topics dataset and supplementary divisions
-dataset we created to expand the versatility of our database.}
+to after being parsed and cleaned. Finally, we review the supplementary
+Hansard debate topics dataset and supplementary divisions dataset we
+created to expand the versatility of our database.
 
@@
 classified as unique elements. More detail on the purpose and processing
-of Question Time will follow in Section~\ref{sec-qa}.
+of Question Time will \protect\hyperlink{sec-qa}{follow}.
 
@@
 
-{\centering \includegraphics{xml1.png}
+{\centering \includegraphics{xml1.jpg}
 
@@
 splitting these speeches in a way that would be generalizable across
-sitting days. Details on these are provided in
-Section~\ref{sec-interject}.
+sitting days. Details on these are provided in the Interjections
+\protect\hyperlink{sec-interject}{section} to follow.
 
@@
 section of our script to separate out general stage directions. More
-information on this separation will be provided in
-Section~\ref{sec-stage}. After completing our first script, it was
-formatted as a function which takes a single file name argument and
-produces one CSV file containing data on all proceedings from the given
-sitting day.
+information on this separation will be provided in the subsequent Stage
+Directions \protect\hyperlink{sec-stage}{section}. After completing our
+first script, it was formatted as a function which takes a single file
+name argument and produces one CSV file containing data on all
+proceedings from the given sitting day.
 
@@
 computational efficiency with separate scripts. While all four scripts
-use the same general approach to parsing described in
-Section~\ref{sec-overview} and produce the same CSV structure, the first
-and second scripts use a different method of data processing than the
-third and fourth scripts.
+use the same general approach to parsing described in the Overview
+\protect\hyperlink{sec-overview}{section} and produce the same CSV
+structure, the first and second scripts use a different method of data
+processing than the third and fourth scripts.
 
@@
 
-{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.png}
+{\centering \includegraphics[width=3.28125in,height=\textheight]{patternEX.jpg}
 
@@
 to flag questions and answers correctly based on which list of patterns
-it belonged to. Sometimes, \textbf{we identified} questions
-\textbf{which} were incorrectly transcribed under an answer node and
-vice-versa, in which cases we manually corrected the question and answer
-flags. For instance, we check for any statements flagged as questions
-which include the phrase ``has provided the following answer to the
-honourable member's question'', in which case we re-code that statement
-as an answer. \textbf{It is important to note, however, that because we
-identified and corrected for these transcription errors manually as we
-discovered them, additional flagging errors may exist which we did not
-catch. As such, users may identify and should be wary of occasional
-incorrectly flagged questions or answers in the data.}
+it belonged to. Sometimes, we identified questions which were
+incorrectly transcribed under an answer node and vice-versa, in which
+cases we manually corrected the question and answer flags. For instance,
+we check for any statements flagged as questions which include the
+phrase ``has provided the following answer to the honourable member's
+question'', in which case we re-code that statement as an answer. It is
+important to note, however, that because we identified and corrected for
+these transcription errors manually as we discovered them, additional
+flagging errors may exist which we did not catch. As such, users may
+identify and should be wary of occasional incorrectly flagged questions
+or answers in the data.
 
@@
 
-As mentioned in Section~\ref{sec-diff}, more recent years of Hansard
-XMLs contain a series of child nodes which exist to capture the
-structure of interruptions in that speech. Figure~\ref{fig-xml3}
-provides an example of this, where the speech was interrupted by a
-comment from the Deputy Speaker, and then the MP continued their speech.
-Looking at the element names highlighted in blue, these child nodes do
-not contain the actual text for the interjection or continuation ---
-this text is embedded within the speech above it. However, as shown by
-the content highlighted in pink in Figure~\ref{fig-xml3}, we were able
-to extract useful details on the individual interjecting which we could
-use later. Making use of this structure, we extracted names and
-information of all individuals that were categorized within the XML as
-interjections. We stored this as a dataframe called
-\texttt{"interject"}. We decided not to include this data in our final
-database, as it is embedded in our resulting datasets which have a flag
-for interjections.
+As mentioned in the Script Differences
+\protect\hyperlink{sec-diff}{section}, more recent years of Hansard XMLs
+contain a series of child nodes which exist to capture the structure of
+interruptions in that speech. Figure~\ref{fig-xml2} provides an example
+of this, where the speech was interrupted by a comment from the Deputy
+Speaker, and then the MP continued their speech. Looking at the element
+names highlighted in blue, these child nodes do not contain the actual
+text for the interjection or continuation --- this text is embedded
+within the speech above it. However, as shown by the content highlighted
+in pink in Figure~\ref{fig-xml2}, we were able to extract useful details
+on the individual interjecting which we could use later. Making use of
+this structure, we extracted names and information of all individuals
+that were categorized within the XML as interjections. We stored this as
+a dataframe called \texttt{"interject"}. We decided not to include this
+data in our final database, as it is embedded in our resulting datasets
+which have a flag for interjections.
 
@@
 
-{\centering \includegraphics[width=3.59375in,height=\textheight]{xml3.png}
+{\centering \includegraphics[width=3.59375in,height=\textheight]{xml2.jpg}
 
@@
 
-\caption{\label{fig-xml3}Snapshot of XML structure with interjection and
+\caption{\label{fig-xml2}Snapshot of XML structure with interjection and
 continuation from 03 February 2021 Hansard}
@@
 and/or last name. There is also variation in the capitalization of these
-names.\footnote{Sometimes when someone's first name is included, only
-  their last name is capitalized, while sometimes their full name is
-  capitalized, or other times neither are capitalized.} Another source
-of variation is in individuals with more than one first name, as
-sometimes only their initial first name is written, while other times
-their entire first name is written. Additionally, some surnames have
-punctuation, and some surnames have specific capitalization such as
-``McCormack'', where even in full capitalization, the first ``c''
-remains lower case. This variation demands careful consideration when
-writing regular expression patterns. In these lists we also accounted
-for any general interjection statements that were not attributed to an
-individual, such as ``An opposition member interjecting-''.
+names. Sometimes when someone's first name is included, only their last
+name is capitalized, while sometimes their full name is capitalized, or
+other times neither are capitalized. Another source of variation is in
+individuals with more than one first name, as sometimes only their
+initial first name is written, while other times their entire first name
+is written. Additionally, some surnames have punctuation, and some
+surnames have specific capitalization such as ``McCormack'', where even
+in full capitalization, the first ``c'' remains lower case. This
+variation demands careful consideration when writing regular expression
+patterns. In these lists we also accounted for any general interjection
+statements that were not attributed to an individual, such as ``An
+opposition member interjecting-''.
 
@@
 
-{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.png}
+{\centering \includegraphics[width=4.66667in,height=\textheight]{lookup_ex.jpg}
 
@@
 
-{\centering \includegraphics{interject_ex.png}
+{\centering \includegraphics{interject_ex.jpg}
 
@@
 necessitated some departure from the original methodology. As discussed
-in Section~\ref{sec-diff}, we used string patterns extracted from
+in the Script Differences \protect\hyperlink{sec-diff}{section}, we used
+string patterns extracted from
 \texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
-As evident in Figure~\ref{fig-xml3},
+As evident in Figure~\ref{fig-xml2},
 \texttt{\textless{}talk.start\textgreater{}} nodes are nested within
@@
 may have not been separated due to how they were embedded in the XML,
-and separated those out where needed.\footnote{While most statements
-  were categorized in their own child node and hence captured through
-  pattern-based separation, some were not individually categorized, and
-  had to be split manually in this step.}
+and separated those out where needed. In particular, while most
+statements were categorized in their own child node and hence captured
+through pattern-based separation, some were not individually
+categorized, and had to be split manually in this step.
 
@@
 
-{\centering \includegraphics{pattern_lookup.png}
+{\centering \includegraphics{pattern_lookup.jpg}
 
@@
 built this list of stage directions as we worked backwards in parsing
-Hansard, and took the same approach across all four scripts.
-\textbf{Despite our best efforts to capture all stage directions in this
-list, because it had to be built manually, users should be aware that it
-is possible that some stage directions were not separated onto their own
-rows in the process. Further, it is important to note that because they
-are not spoken aloud, stage directions do not represent speech
-components in the same way that all other components such as
-interjections and continuations do. However, they provide valuable
-information about the inner-workings and structure of parliamentary
-events. If the focus of the user's research does not require stage
-directions, then this can be removed by filtering observations in
-\texttt{name} equal to ``business start'', or ``stage direction''.}
+Hansard, and took the same approach across all four scripts. Despite our
+best efforts to capture all stage directions in this list, because it
+had to be built manually, users should be aware that it is possible that
+some stage directions were not separated onto their own rows in the
+process. Further, it is important to note that because they are not
+spoken aloud, stage directions do not represent speech components in the
+same way that all other components such as interjections and
+continuations do. However, they provide valuable information about the
+inner-workings and structure of parliamentary events. If the focus of
+the user's research does not require stage directions, then this can be
+removed by filtering observations in \texttt{name} equal to ``business
+start'', or ``stage direction''.
 
@@
 
-\textbf{To enhance the range of research questions which can be explored
-with our data, we have created a supplementary file containing debate
-topics and their corresponding page numbers for each sitting day in our
+To enhance the range of research questions which can be explored with
+our data, we have created a supplementary file containing debate topics
+and their corresponding page numbers for each sitting day in our
 database. To extract these data, we wrote a script to parse debate and
@@
 summarizing, these topics can be added to the main text by joining, and
-example code is provided in the README.}
+example code is provided in the README.
 
@@
 
-\textbf{Another fundamental component of parliamentary proceedings is
-voting. In the House, when a question arises such as ``The question is
-that the amendment be agreed to'', Members are asked to cast their vote
-either in the affirmative or in the negative, and the majority of votes
-as judged by the Speaker determines the outcome\textsuperscript{8}.
-Further, Members can vote in an unofficial arrangement called pairs,
-which ``can be used to enable a Member on one side of the House to be
-absent for any votes when a Member from the other side is to be absent
-at the same time or when, by agreement, a Member abstains from
+Another fundamental component of parliamentary proceedings is voting. In
+the House, when a question arises such as ``The question is that the
+amendment be agreed to'', Members are asked to cast their vote either in
+the affirmative or in the negative, and the majority of votes as judged
+by the Speaker determines the outcome\textsuperscript{8}. Further,
+Members can vote in an unofficial arrangement called pairs, which ``can
+be used to enable a Member on one side of the House to be absent for any
+votes when a Member from the other side is to be absent at the same time
+or when, by agreement, a Member abstains from
 voting''\textsuperscript{8}. If the result as determined by the Speaker
@@
 right of their chair depending on how they vote, so that the votes can
-be re-counted and recorded\textsuperscript{8}.}
-
-\textbf{In the Hansard XML files, divisions data are structured outside
-of the \texttt{\textless{}speech\textgreater{}} content in their own
+be re-counted and recorded\textsuperscript{8}.
+
+In the Hansard XML files, divisions data are structured outside of the
+\texttt{\textless{}speech\textgreater{}} content in their own
 \texttt{\textless{}division\textgreater{}} nodes that contain the voting
@@
 proceedings. Our approach to parsing Hansard in the third and fourth
-scripts described in Section~\ref{sec-diff} naturally allowed for much
-of the divisions data to be added to our resulting files for 1998 to
-March 2011, however the parsing scripts used for May 2011 to September
-2022 Hansard did not. To supplement our database and in an effort to
-fill this divisions data gap, we created an additional file containing
-all divisions data nested under the XPath
+scripts described in the Script Differences
+\protect\hyperlink{sec-diff}{section} naturally allowed for much of the
+divisions data to be added to our resulting files for 1998 to March
+2011, however the parsing scripts used for May 2011 to September 2022
+Hansard did not. To supplement our database and in an effort to fill
+this divisions data gap, we created an additional file containing all
+divisions data nested under the XPath
 ``\texttt{//chamber.xscript//division}'' from the Hansard files in our
@@
 the \texttt{\textless{}division\textgreater{}} node over time. Finally,
-we then added a date variable to distinguish between sitting days.}
+we then added a date variable to distinguish between sitting days.
 
@@
 
-Our database is available in both CSV and parquet formats. \textbf{Both
-CSV and parquet are open standards. We provide both because while CSVs
-are commonly used and can be manually inspected, parquet files are
-typically smaller and preserve class.} Our database covers all sitting
-days of the House of Representatives from 02 March 1998 to 08 September
-2022 \textbf{where an XML transcript is available}, so there are
-\textbf{1,532 individual sitting day} files for each format.
-\textbf{Additionally, there is a single corpus file in both CSV and
-parquet forms containing the data from all sitting days, with a date
-variable added to allow for distinction and filtering of individual
-sitting days. There is also a CSV and parquet file containing all parsed
-debate topics.} All data records are available on the general-purpose
-repository Zenodo, at
+Our database is available in both CSV and parquet formats. Both CSV and
+parquet are open standards. We provide both because while CSVs are
+commonly used and can be manually inspected, parquet files are typically
+smaller and preserve class. Our database covers all sitting days of the
+House of Representatives from 02 March 1998 to 08 September 2022 where
+an XML transcript is available, so there are 1,532 individual sitting
+day files for each format. Additionally, there is a single corpus file
+in both CSV and parquet forms containing the data from all sitting days,
+with a date variable added to allow for distinction and filtering of
+individual sitting days. There is also a CSV and parquet file containing
+all parsed debate topics. All data records are available on the
+general-purpose repository Zenodo, at
 \url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{21}. For
-each \textbf{Hansard data} file, \textbf{that is, the corpus and the
-individual sitting day files}, each row contains an individual
-statement, with details on the individual speaking. For general
-statements transcribed as made by ``Honourable members'' for example,
-these variables cannot be specified. Table~\ref{tbl-vars} provides an
-overview of each variable found in the \textbf{Hansard data files in
-the} database.
+each Hansard data file, that is, the corpus and the individual sitting
+day files, each row contains an individual statement, with details on
+the individual speaking. For general statements transcribed as made by
+``Honourable members'' for example, these variables cannot be specified.
+Table~\ref{tbl-vars} provides an overview of each variable found in the
+Hansard data files in the database.
 
@@
 (\texttt{interject}), and the \texttt{div\_flag} variable was added to
-flag \textbf{those rows where ``The House divided.'' was detected in the
-body variable}. The \texttt{gender} and \texttt{uniqueID} variables were
-added based on the main dataset from the \texttt{AustralianPoliticians}
-package, \textbf{and the \texttt{partyfacts\_id} variable was added
-using code and data provided by the Party Facts Project
-\href{https://partyfacts.herokuapp.com}{website}.}\footnote{\textbf{Note
-  that in accordance with the code provided on the Party Facts
-  \href{https://partyfacts.herokuapp.com/download/}{downloads page}, we
-  used only the core datasets maintained by the Party Facts project,
-  which are the Manifesto Project and ParlGov. Details on these datasets
-  can be found here:
-  https://partyfacts.herokuapp.com/documentation/datasets/.}} Details on
-the usage of \texttt{uniqueID} \textbf{and \texttt{partyfacts\_id}} will
-be provided in Section~\ref{sec-usage}. Further, the \texttt{speech\_no}
-variable allows us to keep track of the speech number that each
-statement and interjection belongs to. Having the speech number variable
-offers an easy way to group statements by speech or isolate specific
-speeches of interest. \textbf{Lastly, the \texttt{order} variable was
-added to maintain the order of proceedings, after all individual
-statements were separated onto their own rows.}
-
-\textbf{As mentioned, in addition to the Hansard data described above,
-our database also contains a CSV and parquet file with the parsed debate
+flag those rows where ``The House divided.'' was detected in the body
+variable. The \texttt{gender} and \texttt{uniqueID} variables were added
+based on the main dataset from the \texttt{AustralianPoliticians}
+package, and the \texttt{partyfacts\_id} variable was added using code
+and data provided by the Party Facts Project website
+(https://partyfacts.herokuapp.com). Note that in accordance with the
+code provided on the Party Facts downloads page
+(https://partyfacts.herokuapp.com/download/), we used only the core
+datasets maintained by the Party Facts project, which are the Manifesto
+Project and ParlGov. Details on these datasets can be found on the Party
+Facts datasets documentation page
+(https://partyfacts.herokuapp.com/documentation/datasets/). Details on
+the usage of \texttt{uniqueID} and \texttt{partyfacts\_id} will be
+provided in the \protect\hyperlink{sec-usage}{Usage Notes} to follow.
+Further, the \texttt{speech\_no} variable allows us to keep track of the
+speech number that each statement and interjection belongs to. Having
+the speech number variable offers an easy way to group statements by
+speech or isolate specific speeches of interest. Lastly, the
+\texttt{order} variable was added to maintain the order of proceedings,
+after all individual statements were separated onto their own rows.
+
+As mentioned, in addition to the Hansard data described above, our
+database also contains a CSV and parquet file with the parsed debate
 topics. This file is called \texttt{all\_debate\_topics}, and contains a
@@
 \texttt{page.no} variable specifying on which page that title was
-recorded to be found in the official Hansard PDF.}
-
-\textbf{There is also a CSV file in our database called
+recorded to be found in the official Hansard PDF.
+
+There is also a CSV file in our database called
 \texttt{PartyFacts\_map.csv}. This file was created using
@@
 and full name spelling found in the \texttt{AustralianPoliticians}
-package for completeness.}
+package for completeness.
 
@@
 
-\textbf{Finally, our database contains a file with all parsed divisions
-data in our timeframe. This is called \texttt{division\_data}, and is
-available in RDA form and in parquet form. The reason it is not
-available in CSV form is because three of the variables
-(\texttt{names\_AYES}, \texttt{names\_NOES}, and \texttt{names\_PAIRS})
-are lists, which are not supported by the CSV rectangular data
-structure. The variables found in these data are summarized below, in
-Table~\ref{tbl-divisions}.}
+Finally, our database contains a file with all parsed divisions data in
+our timeframe. This is called \texttt{division\_data}, and is available
+in RDA form and in parquet form. The reason it is not available in CSV
+form is because three of the variables (\texttt{names\_AYES},
+\texttt{names\_NOES}, and \texttt{names\_PAIRS}) are lists, which are
+not supported by the CSV rectangular data structure. The variables found
+in these data are summarized below, in Table~\ref{tbl-divisions}.
 
@@
 validates that the date specified in each file name matches the date
-specified in its corresponding XML session header.\footnote{As seen in
-  Figure~\ref{fig-xml1}, the first child node of the
-  \texttt{\textless{}session.header\textgreater{}} element is the date.}
+specified in its corresponding XML session header. This XML component
+can be seen in Figure~\ref{fig-xml1}, where the first child node of the
+\texttt{\textless{}session.header\textgreater{}} element is the date.
 Every file passed this test, and we detected one discrepancy in an XML
@@
 by checking whether two lines that immediately follow each other have
-the same body (i.e.~spoken content). This test detected \textbf{131}
-dates on which duplicate statements were made, and one immediately
-follows the other. Note that this test does not account for who is
-making each statement, meaning one MP repeating the words of another MP
-would be picked up in this test as well. We checked a sample of 40\% of
-these duplicates, and manually validated that they are all repeated
-statements that do exist and are transcribed closely together in that
-day's XML file, and by our method should be parsed such that one of
-these statements is immediately followed by the other.
+the same body (i.e.~spoken content). This test detected 131 dates on
+which duplicate statements were made, and one immediately follows the
+other. Note that this test does not account for who is making each
+statement, meaning one MP repeating the words of another MP would be
+picked up in this test as well. We checked a sample of 40\% of these
+duplicates, and manually validated that they are all repeated statements
+that do exist and are transcribed closely together in that day's XML
+file, and by our method should be parsed such that one of these
+statements is immediately followed by the other.
 
@@
 
-\textbf{The fourth test is designed to detect issues in timestamp
-formatting in the data, by detecting all timestamps in our database
-which do not match the correct ``HH:MM:SS'' format. We found a total of
-88 incorrectly formatted timestamps, with common issues such as the
-``HH'' or ``MM'' component recorded as ``NaN'' (e.g.~``NaN:28:00'' or
-``09:NaN:00''), as well as timestamps with a third digit in the minute
-component (e.g.~``09:497:00'' or ``13:445:00''). We took a random sample
-of 25\% of these incorrectly formatted timestamps, and manually checked
-whether or not they were transcribed as such in the original XML Hansard
+The fourth test is designed to detect issues in timestamp formatting in
+the data, by detecting all timestamps in our database which do not match
+the correct ``HH:MM:SS'' format. We found a total of 88 incorrectly
+formatted timestamps, with common issues such as the ``HH'' or ``MM''
+component recorded as ``NaN'' (e.g.~``NaN:28:00'' or ``09:NaN:00''), as
+well as timestamps with a third digit in the minute component
+(e.g.~``09:497:00'' or ``13:445:00''). We took a random sample of 25\%
+of these incorrectly formatted timestamps, and manually checked whether
+or not they were transcribed as such in the original XML Hansard
 transcript. We found that every improperly formatted timestamp in our
@@
 have left these timestamps in their originally transcribed format in our
-database.}
+database.
 
@@
 
-\textbf{To further explore the quality of our data and detect any
-unexpected or distinct trends, we generated a number of summary
-statistics using the complete Hansard corpus. First, we looked at the
-number of speeches made each day, disaggregated by Chamber and
-Federation Chamber debate venues. As shown in
-Figure~\ref{fig-dailyspeeches}, there are consistently more speeches
-made in the Chamber proceedings than in the Federation Chamber, which
-aligns with the wider scope of business covered in the Chamber. Further,
-in both debate venues, the number of speeches each day appears to have
-increased slightly over time.}
+To further explore the quality of our data and detect any unexpected or
+distinct trends, we generated a number of summary statistics using the
+complete Hansard corpus. First, we looked at the number of speeches made
+each day, disaggregated by Chamber and Federation Chamber debate venues.
+As shown in Figure~\ref{fig-dailyspeeches}, there are consistently more
+speeches made in the Chamber proceedings than in the Federation Chamber,
+which aligns with the wider scope of business covered in the Chamber.
+Further, in both debate venues, the number of speeches each day appears
+to have increased slightly over time.
 
@@
 
-{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}
+{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.jpg}
 
@@
 
-\textbf{Next, we explored the number of unique names detected on each
-sitting day disaggregated by debate venue, visualized in
-Figure~\ref{fig-names}. As expected, there are generally more individual
-MPs detected to be present in the Chamber proceedings in our data than
-in the Federation Chamber proceedings. Further, in both venues, the
-number of individuals detected per sitting day appears to have increased
-since around 2008-2009, with a maximum of 116 and 87 unique names
-detected for the Chamber and Federation Chamber, respectively. Across
-the time frame of our data, there was a daily average of 84 unique names
-detected in the Chamber, and 34 in the Federation Chamber. These
-observations are in accordance with the official number of Members
-belonging to the House of Representatives, which was 148 in 1998, 150 in
-2001, and then increased to 151 in the 2019 general
-election\textsuperscript{8}.}
+Next, we explored the number of unique names detected on each sitting
+day disaggregated by debate venue, visualized in Figure~\ref{fig-names}.
+As expected, there are generally more individual MPs detected to be
+present in the Chamber proceedings in our data than in the Federation
+Chamber proceedings. Further, in both venues, the number of individuals
+detected per sitting day appears to have increased since around
+2008-2009, with a maximum of 116 and 87 unique names detected for the
+Chamber and Federation Chamber, respectively. Across the time frame of
+our data, there was a daily average of 84 unique names detected in the
+Chamber, and 34 in the Federation Chamber. These observations are in
+accordance with the official number of Members belonging to the House of
+Representatives, which was 148 in 1998, 150 in 2001, and then increased
+to 151 in the 2019 general election\textsuperscript{8}.
 
@@
 
-{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}
+{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.jpg}
 
@@
 
-\textbf{We then computed the total number of speeches made in our
-database by political party, summarized in
-Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
-Party made the most speeches overall, followed by the Liberal Party of
-Australia, and the National Party of Australia. These rankings are
-unsurprising, as those parties are the three main political parties in
-the Australian House of Representatives\textsuperscript{22}.}
+We then computed the total number of speeches made in our database by
+political party, summarized in Table~\ref{tbl-speeches_by_party}. We
+found that the Australian Labor Party made the most speeches overall,
+followed by the Liberal Party of Australia, and the National Party of
+Australia. These rankings are unsurprising, as those parties are the
+three main political parties in the Australian House of
+Representatives\textsuperscript{22}.
 
@@
 \midrule
-Australian Labor Party & ALP & 112268\\
-Liberal Party of Australia & LIB & 106139\\
-National Party of Australia & NPA & 20244\\
-Independent & IND & 5357\\
-Australian Greens & GRN & 1446\\
+Australian Labor Party & ALP & 112,268\\
+Liberal Party of Australia & LIB & 106,139\\
+National Party of Australia & NPA & 20,244\\
+Independent & IND & 5,357\\
+Australian Greens & GRN & 1,446\\
 \addlinespace
@@
 including this variable, one can readily integrate our data records with
-those available in these two packages. \textbf{Similarly, we added the
+those available in these two packages. Similarly, we added the
 \texttt{partyfacts\_id} variable to our data which allows users to link
 our data to external political party data sources with this unique
-identifier.}
+identifier.
 
@@
 
-\textbf{Finally, the README file on our GitHub repository and on Zenodo
-contains example code on how to read in a file from our database, for
-both CSV and parquet formats. Should a user wish to use the single
-Hansard corpus rather than individual sitting day files, we provide
-example code on how to read it in, filter for those sitting days of
-interest, and split them into distinct data frames. We have also added
-example code for filtering out stage directions, and updating the
-\texttt{order} variable to reflect the ordering of remaining rows,
-should the user wish to remove stage directions from their analysis.
-Lastly, the README contains example code showing users how to merge the
-debate topics data with a Hansard data file for one sitting day.}
+Finally, the README file on our GitHub repository and on Zenodo contains
+example code on how to read in a file from our database, for both CSV
+and parquet formats. Should a user wish to use the single Hansard corpus
+rather than individual sitting day files, we provide example code on how
+to read it in, filter for those sitting days of interest, and split them
+into distinct data frames. We have also added example code for filtering
+out stage directions, and updating the \texttt{order} variable to
+reflect the ordering of remaining rows, should the user wish to remove
+stage directions from their analysis. Lastly, the README contains
+example code showing users how to merge the debate topics data with a
+Hansard data file for one sitting day.
 
@@
 The code written to build this database is available on the GitHub
-repository associated with this paper:
-https://github.com/lindsaykatz/hansard-proj. All scripts were created
+repository associated with this paper
+(https://github.com/lindsaykatz/hansard-proj). All scripts were created
 using R software\textsuperscript{24}. The core packages used to develop

### 2023-08-04 paper/paper-nature-revised.qmd
small changes, updated bib

@@
 Following the lead of that project, in this paper we introduce a similar database for Australia.
-This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to September 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
+This is composed of individual datasets for each sitting day in the House of Representatives from March 1998 to September 2022, containing details on everything said in parliament in a form that can be readily used by researchers.
 With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.
@@
 To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website.
-For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created [@sherratt].
-These data can be navigated by year, parliament, people, and bills [@sherratt].
-To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created @Leslie_2021_HoR_Aus.
+For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created (http://historichansard.net/).
+These data can be navigated by year, parliament, people, and bills.
+To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created (https://github.com/palesl/AustralianHouseOfRepresentatives).
 Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol.
@@
 The final key component of Hansard is Question Time, in which questions and answers are classified as unique elements.
-More detail on the purpose and processing of Question Time will [follow](#sec-qa).
+More detail on the purpose and processing of Question Time will follow.
 
@@
 
-The next step was to further develop our script to produce tidy data sets, as defined and introduced by @Wickham2014.
+The next step was to further develop our script to produce tidy data sets [@Wickham2014].
 These contain all parsed text elements, where each statement is separated onto its own row with details about the MP who is speaking, and rows are maintained in chronological order.
@@
 There were many intricacies in the task of splitting these speeches in a way that would be generalizable across sitting days.
-Details on these are provided in the Interjections [section](#sec-interject) to follow.
+Details on these are provided later.
 
@@
 These became apparent as we ran our script on XML files from earlier sitting days.
-Some changes are as subtle as a differently named child node, while others are as extensive as a completely different nesting structure.
+Some changes are as subtle as a differently named child node, while others are as extensive as a different nesting structure.
 Smaller changes were accounted for as we became aware of them, and embedded into the code in a way that would not cause issues for parsing more current Hansards with subtle differences in formatting.
-However, as mentioned, more significant changes in the XML structure of Hansard are what necessitated the development of separate scripts as we worked backwards.
+However, as mentioned, more significant changes in the XML structure of Hansard necessitated the development of separate scripts as we worked backwards.
 Further not every sitting day contains every possible XML element.
@@
 Specifically, we added a section of our script to separate out general stage directions.
-More information on this separation will be provided in the subsequent Stage Directions [section](#sec-stage).
+More information on this separation will be provided in the Stage Directions section.
 After completing our first script, it was formatted as a function which takes a single file name argument and produces one CSV file containing data on all proceedings from the given sitting day.
@@
 Two main factors motivated us to create four scripts as opposed to just one, the first being structural variation in XML over time, and the second being improved computational efficiency with separate scripts.
-While all four scripts use the same general approach to parsing described in the Overview [section](#sec-overview) and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.
+While all four scripts use the same general approach to parsing described in the Overview section and produce the same CSV structure, the first and second scripts use a different method of data processing than the third and fourth scripts.
 
@@
 We then worked backwards in time and modified the code as needed for generalizability.
-Throughout this process we found many transcription errors present in the XMLs from earlier years.
+Throughout this process we found a number of transcription errors present in the XMLs from earlier years.
 We fixed these manually, deferring to the official release to ensure the correct information was filled in.
@@
 
-As mentioned in the Script Differences [section](#sec-diff), more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech.
+As mentioned earlier, more recent years of Hansard XMLs contain a series of child nodes which exist to capture the structure of interruptions in that speech.
 @fig-xml2 provides an example of this, where the speech was interrupted by a comment from the Deputy Speaker, and then the MP continued their speech.
@@
 However, the difference in data cleaning used in these scripts necessitated some departure from the original methodology.
-As discussed in the Script Differences [section](#sec-diff), we used string patterns extracted from `<talk.start>` nodes to separate speeches.
+As discussed earlier, we used string patterns extracted from `<talk.start>` nodes to separate speeches.
 As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process.
@@
 Since we focus primarily on the spoken `<speech>` Hansard content, our parsing scripts do not necessarily capture all divisions data from House proceedings.
-Our approach to parsing Hansard in the third and fourth scripts described in the Script Differences [section](#sec-diff) naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not.
+Our approach to parsing Hansard in the third and fourth scripts described in the Script Differences section naturally allowed for much of the divisions data to be added to our resulting files for 1998 to March 2011, however the parsing scripts used for May 2011 to September 2022 Hansard did not.
 To supplement our database and in an effort to fill this divisions data gap, we created an additional file containing all divisions data nested under the XPath "`//chamber.xscript//division`" from the Hansard files in our time frame.
@@
 To enhance the usability of our database, we added a `uniqueID` variable to each file.
-This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` and `AustralianElections` R packages [@auspol; @auselect].
-By including this variable, one can readily integrate our data records with those available in these two packages.
+This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` [@auspol] and `AustralianElections` R packages (https://github.com/RohanAlexander/AustralianElections).
+By including this variable, one can integrate our data records with those available in these two packages.
 Similarly, we added the `partyfacts_id` variable to our data which allows users to link our data to external political party data sources with this unique identifier.
@@
 This variable was parsed directly from the Hansard XML files, and can be found in the Australian Parliamentary Handbook.
-As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook [@Leslie_2021_HoR_Aus].
+As such, our data records can be integrated with those from the `ausPH` package which provides datasets for contents of the Australian Parliamentary Handbook.
 This will allow for convenient extraction of further details on each MP in a tidy, ready to analyze format.
@@
 All scripts were created using R software [@r_software].
-The core packages used to develop these scripts are: the `XML` package @XML_pkg, the `xml2` package @xml2_pkg, the `tidyverse` R packages @tidyverse, the `AustralianPoliticians` package @auspol, and the `ausPH` package @Leslie_2021_HoR_Aus.
+The core packages used to develop these scripts are: the `XML` package @XML_pkg, the `xml2` package @xml2_pkg, the `tidyverse` R packages @tidyverse, the `AustralianPoliticians` package @auspol, and the `ausPH` package.
 `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.

### 2023-08-04 paper/paper-nature-revised.tex
small changes, updated bib

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{July 26, 2023}
+\date{August 3, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, interior hidden, breakable, frame hidden, enhanced, sharp corners, boxrule=0pt]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, enhanced, interior hidden, sharp corners]}{\end{tcolorbox}}\fi
 
@@
 database for Australia. This is composed of individual datasets for each
-sitting day in the House of Representatives from 1998 to September 2022,
-containing details on everything said in parliament in a form that can
-be readily used by researchers. With the development of tools for
+sitting day in the House of Representatives from March 1998 to September
+2022, containing details on everything said in parliament in a form that
+can be readily used by researchers. With the development of tools for
 large-scale text analysis, this database will serve as a resource for
@@
 website. For instance, an online, easy to read database of Hansard from
-1901 to 1980 using the XML files has been created\textsuperscript{9}.
-These data can be navigated by year, parliament, people, and
-bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
-more accessible, an \texttt{R} package which includes data on all MPs
-from 1945 to 2019 has been created\textsuperscript{10}. Further, there
-is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
-several datasets related to the political and biographical information
-of Australian federal politicians who were active between 1901 and
-2021\textsuperscript{11}. And finally, there has been examination of
-speech and MP level data between 1990 and 2019 in
-Australia\textsuperscript{12}. Like us they scrape the Hansard record
+1901 to 1980 using the XML files has been created
+(http://historichansard.net/). These data can be navigated by year,
+parliament, people, and bills. To make the Australian Parliamentary
+Handbook more accessible, an \texttt{R} package which includes data on
+all MPs from 1945 to 2019 has been created
+(https://github.com/palesl/AustralianHouseOfRepresentatives). Further,
+there is the \texttt{AustralianPoliticians} \texttt{R} package, which
+contains several datasets related to the political and biographical
+information of Australian federal politicians who were active between
+1901 and 2021\textsuperscript{9}. And finally, there has been
+examination of speech and MP level data between 1990 and 2019 in
+Australia\textsuperscript{10}. Like us they scrape the Hansard record
 and link it with biographical data. The key difference is that our focus
@@
 investigate occurrences of unparliamentary comments by MPs, where the
-Speaker tells that MP to withdraw their remark\textsuperscript{13}.
+Speaker tells that MP to withdraw their remark\textsuperscript{11}.
 Question Time data from Hansard transcripts during February and March of
 2003 has been used to investigate resistance of politicians in answering
-questions about Iraq\textsuperscript{14}. Hansard has also been used to
+questions about Iraq\textsuperscript{12}. Hansard has also been used to
 quantify political prominence by investigating strategic mentions of
-interest groups by elected officials\textsuperscript{15}. Finally, a
+interest groups by elected officials\textsuperscript{13}. Finally, a
 dataset of the Australian Hansard has been constructed and then used to
 analyze the effect of elections and changes in Prime Ministers upon
-topics mentioned in parliament\textsuperscript{16}. This was created
+topics mentioned in parliament\textsuperscript{14}. This was created
 with the static PDF versions of Hansard, using OCR to digitize these
@@
 performed in \texttt{R} using the \texttt{XML} and \texttt{xml2}
-packages\textsuperscript{17,18}. Focusing on one transcript also allowed
+packages\textsuperscript{15,16}. Focusing on one transcript also allowed
 us to ensure that all key components of the transcript were parsed and
@@
 classified as unique elements. More detail on the purpose and processing
-of Question Time will \protect\hyperlink{sec-qa}{follow}.
+of Question Time will follow.
 
@@
 The next step was to further develop our script to produce tidy data
-sets, as defined and introduced by\textsuperscript{19}. These contain
-all parsed text elements, where each statement is separated onto its own
-row with details about the MP who is speaking, and rows are maintained
-in chronological order. This first involved correcting the variable
-classes and adding several indicator variables to differentiate where
-statements came from, such as Chamber versus Federation Chamber or
+sets\textsuperscript{17}. These contain all parsed text elements, where
+each statement is separated onto its own row with details about the MP
+who is speaking, and rows are maintained in chronological order. This
+first involved correcting the variable classes and adding several
+indicator variables to differentiate where statements came from, such as
+Chamber versus Federation Chamber or
 \texttt{\textless{}subdebate.1\textgreater{}} versus
@@
 splitting these speeches in a way that would be generalizable across
-sitting days. Details on these are provided in the Interjections
-\protect\hyperlink{sec-interject}{section} to follow.
+sitting days. Details on these are provided later.
 
@@
 subtle as a differently named child node, while others are as extensive
-as a completely different nesting structure. Smaller changes were
-accounted for as we became aware of them, and embedded into the code in
-a way that would not cause issues for parsing more current Hansards with
-subtle differences in formatting. However, as mentioned, more
-significant changes in the XML structure of Hansard are what
-necessitated the development of separate scripts as we worked backwards.
-Further not every sitting day contains every possible XML element. For
-example, some days did not have
+as a different nesting structure. Smaller changes were accounted for as
+we became aware of them, and embedded into the code in a way that would
+not cause issues for parsing more current Hansards with subtle
+differences in formatting. However, as mentioned, more significant
+changes in the XML structure of Hansard necessitated the development of
+separate scripts as we worked backwards. Further not every sitting day
+contains every possible XML element. For example, some days did not have
 \texttt{\textless{}subdebate.2\textgreater{}} content, and some days did
@@
 section of our script to separate out general stage directions. More
-information on this separation will be provided in the subsequent Stage
-Directions \protect\hyperlink{sec-stage}{section}. After completing our
-first script, it was formatted as a function which takes a single file
-name argument and produces one CSV file containing data on all
-proceedings from the given sitting day.
+information on this separation will be provided in the Stage Directions
+section. After completing our first script, it was formatted as a
+function which takes a single file name argument and produces one CSV
+file containing data on all proceedings from the given sitting day.
 
@@
 use the same general approach to parsing described in the Overview
-\protect\hyperlink{sec-overview}{section} and produce the same CSV
-structure, the first and second scripts use a different method of data
-processing than the third and fourth scripts.
+section and produce the same CSV structure, the first and second scripts
+use a different method of data processing than the third and fourth
+scripts.
 
@@
 backwards in time and modified the code as needed for generalizability.
-Throughout this process we found many transcription errors present in
-the XMLs from earlier years. We fixed these manually, deferring to the
-official release to ensure the correct information was filled in. Since
-there were a number of transcription errors specific to the 2000s, we
-chose to create a fourth script for parsing 1998 and 1999. This allowed
-us to remove all the code which was needed to resolve specific
-transcription errors of the 2000s, to avoid an overly long script and in
-turn improving computational efficiency. As such, our fourth script is
-essentially the same as the third, with the only difference being that
-it has code specific to fixing transcription errors from 1998 and 1999.
+Throughout this process we found a number of transcription errors
+present in the XMLs from earlier years. We fixed these manually,
+deferring to the official release to ensure the correct information was
+filled in. Since there were a number of transcription errors specific to
+the 2000s, we chose to create a fourth script for parsing 1998 and 1999.
+This allowed us to remove all the code which was needed to resolve
+specific transcription errors of the 2000s, to avoid an overly long
+script and in turn improving computational efficiency. As such, our
+fourth script is essentially the same as the third, with the only
+difference being that it has code specific to fixing transcription
+errors from 1998 and 1999.
 
@@
 verbally in the Chamber and are responded to in real
-time\textsuperscript{20}. Questions without notice are included directly
+time\textsuperscript{18}. Questions without notice are included directly
 in the \texttt{"chamber.xscript"} child node, with sub-child nodes
@@
 
-As mentioned in the Script Differences
-\protect\hyperlink{sec-diff}{section}, more recent years of Hansard XMLs
-contain a series of child nodes which exist to capture the structure of
-interruptions in that speech. Figure~\ref{fig-xml2} provides an example
-of this, where the speech was interrupted by a comment from the Deputy
-Speaker, and then the MP continued their speech. Looking at the element
-names highlighted in blue, these child nodes do not contain the actual
-text for the interjection or continuation --- this text is embedded
-within the speech above it. However, as shown by the content highlighted
-in pink in Figure~\ref{fig-xml2}, we were able to extract useful details
-on the individual interjecting which we could use later. Making use of
-this structure, we extracted names and information of all individuals
-that were categorized within the XML as interjections. We stored this as
-a dataframe called \texttt{"interject"}. We decided not to include this
+As mentioned earlier, more recent years of Hansard XMLs contain a series
+of child nodes which exist to capture the structure of interruptions in
+that speech. Figure~\ref{fig-xml2} provides an example of this, where
+the speech was interrupted by a comment from the Deputy Speaker, and
+then the MP continued their speech. Looking at the element names
+highlighted in blue, these child nodes do not contain the actual text
+for the interjection or continuation --- this text is embedded within
+the speech above it. However, as shown by the content highlighted in
+pink in Figure~\ref{fig-xml2}, we were able to extract useful details on
+the individual interjecting which we could use later. Making use of this
+structure, we extracted names and information of all individuals that
+were categorized within the XML as interjections. We stored this as a
+dataframe called \texttt{"interject"}. We decided not to include this
 data in our final database, as it is embedded in our resulting datasets
@@
 dataset from the \texttt{AustralianPoliticians} package in the creation
-of each lookup table\textsuperscript{11}.
+of each lookup table\textsuperscript{9}.
 
@@
 necessitated some departure from the original methodology. As discussed
-in the Script Differences \protect\hyperlink{sec-diff}{section}, we used
-string patterns extracted from
+earlier, we used string patterns extracted from
 \texttt{\textless{}talk.start\textgreater{}} nodes to separate speeches.
@@
 proceedings. Our approach to parsing Hansard in the third and fourth
-scripts described in the Script Differences
-\protect\hyperlink{sec-diff}{section} naturally allowed for much of the
-divisions data to be added to our resulting files for 1998 to March
-2011, however the parsing scripts used for May 2011 to September 2022
-Hansard did not. To supplement our database and in an effort to fill
-this divisions data gap, we created an additional file containing all
-divisions data nested under the XPath
+scripts described in the Script Differences section naturally allowed
+for much of the divisions data to be added to our resulting files for
+1998 to March 2011, however the parsing scripts used for May 2011 to
+September 2022 Hansard did not. To supplement our database and in an
+effort to fill this divisions data gap, we created an additional file
+containing all divisions data nested under the XPath
 ``\texttt{//chamber.xscript//division}'' from the Hansard files in our
@@
 general-purpose repository Zenodo, at
-\url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{21}. For
+\url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{19}. For
 each Hansard data file, that is, the corpus and the individual sitting
@@
 three main political parties in the Australian House of
-Representatives\textsuperscript{22}.
+Representatives\textsuperscript{20}.
 
@@
 speaking MP, and comes from the \texttt{uniqueID} variable present
-within data from both the \texttt{AustralianPoliticians} and
-\texttt{AustralianElections} R packages\textsuperscript{11,23}. By
-including this variable, one can readily integrate our data records with
-those available in these two packages. Similarly, we added the
-\texttt{partyfacts\_id} variable to our data which allows users to link
-our data to external political party data sources with this unique
-identifier.
+within data from both the
+\texttt{AustralianPoliticians}\textsuperscript{9} and
+\texttt{AustralianElections} R packages
+(https://github.com/RohanAlexander/AustralianElections). By including
+this variable, one can integrate our data records with those available
+in these two packages. Similarly, we added the \texttt{partyfacts\_id}
+variable to our data which allows users to link our data to external
+political party data sources with this unique identifier.
 
@@
 the \texttt{ausPH} package which provides datasets for contents of the
-Australian Parliamentary Handbook\textsuperscript{10}. This will allow
-for convenient extraction of further details on each MP in a tidy, ready
-to analyze format.
+Australian Parliamentary Handbook. This will allow for convenient
+extraction of further details on each MP in a tidy, ready to analyze
+format.
 
@@
 (https://github.com/lindsaykatz/hansard-proj). All scripts were created
-using R software\textsuperscript{24}. The core packages used to develop
-these scripts are: the \texttt{XML} package\textsuperscript{17}, the
-\texttt{xml2} package\textsuperscript{18}, the \texttt{tidyverse} R
-packages\textsuperscript{25}, the \texttt{AustralianPoliticians}
-package\textsuperscript{11}, and the \texttt{ausPH}
-package\textsuperscript{10}. \texttt{XML} and \texttt{xml2} were used
-for parsing the XML documents, \texttt{AustralianPoliticians} and
-\texttt{ausPH} were used for cleaning up and filling in MP details in
-the datasets, and \texttt{tidyverse} packages were used in all steps,
-for tidy wrangling of data.
+using R software\textsuperscript{21}. The core packages used to develop
+these scripts are: the \texttt{XML} package\textsuperscript{15}, the
+\texttt{xml2} package\textsuperscript{16}, the \texttt{tidyverse} R
+packages\textsuperscript{22}, the \texttt{AustralianPoliticians}
+package\textsuperscript{9}, and the \texttt{ausPH} package. \texttt{XML}
+and \texttt{xml2} were used for parsing the XML documents,
+\texttt{AustralianPoliticians} and \texttt{ausPH} were used for cleaning
+up and filling in MP details in the datasets, and \texttt{tidyverse}
+packages were used in all steps, for tidy wrangling of data.
 
@@
 \CSLRightInline{Commonwealth of Australia.
-\href{https://www.aph.gov.au/Parliamentary_Business/Hansard}{Parliamentary
-debates, house of representatives}. (2023).}
+\href{https://www.aph.gov.au/Parliamentary_Business/Hansard}{{Parliamentary
+Debates, House of Representatives}}. (2023).}
 
@@
 \CSLLeftMargin{2. }%
-\CSLRightInline{Vice, J. \& Farrell, S. \emph{The history of hansard}.
+\CSLRightInline{Vice, J. \& Farrell, S. \emph{{The history of Hansard}}.
 (House of Lords Library; House of Lords Hansard, 2017).}
@@
 \CSLLeftMargin{3. }%
-\CSLRightInline{Beelen, K. \emph{et al.} Digitization of the canadian
-parliamentary debates. \emph{Canadian Journal of Political Science/Revue
-canadienne de science politique} \textbf{50}, 849--864 (2017).}
+\CSLRightInline{Beelen, K. \emph{et al.} {Digitization of the Canadian
+parliamentary debates}. \emph{Canadian Journal of Political
+Science/Revue canadienne de science politique} \textbf{50}, 849--864
+(2017).}
 
@@
 \CSLRightInline{Erjavec, T. \emph{et al.}
-\href{https://doi.org/10.1007/s10579-021-09574-0}{The {ParlaMint}
-corpora of parliamentary proceedings}. \emph{Language Resources and
-Evaluation} \textbf{57}, 415--448 (2022).}
+\href{https://doi.org/10.1007/s10579-021-09574-0}{{The ParlaMint corpora
+of parliamentary proceedings}}. \emph{Language Resources and Evaluation}
+\textbf{57}, 415--448 (2022).}
 
@@
 \CSLLeftMargin{5. }%
-\CSLRightInline{Rauh, C. \& Schwalbach, J. The ParlSpeech V2 data set:
+\CSLRightInline{Rauh, C. \& Schwalbach, J. {The ParlSpeech V2 data set:
 Full-text corpora of 6.3 million parliamentary speeches in the key
-legislative chambers of nine representative democracies. (2020)
+legislative chambers of nine representative democracies}. (2020)
 doi:\href{https://doi.org/10.7910/DVN/L4OAKN}{10.7910/DVN/L4OAKN}.}
@@
 \CSLLeftMargin{7. }%
-\CSLRightInline{Kartalis, Y. \& Costa Lobo, M. MAPLE parliamentary
-datasets: Full-text and annotated corpora of parliamentary speeches in
-the legislatures of six european democracies. (2021)
+\CSLRightInline{Kartalis, Y. \& Costa Lobo, M. {MAPLE Parliamentary
+Datasets: Full-text and annotated corpora of parliamentary speeches in
+the legislatures of six European democracies}. (2021)
 doi:\href{https://doi.org/10.7910/DVN/9MN0RL}{10.7910/DVN/9MN0RL}.}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-sherratt}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
 \CSLLeftMargin{9. }%
-\CSLRightInline{Sherratt, T.
-\href{http://timsherratt.org/digital-heritage-handbook/docs/historic-hansard/\#}{Documentation:
-Historic hansard}. \emph{Historic Hansard} (2016).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
+\CSLRightInline{Alexander, R. \& Hodgetts, P. A.
+\emph{\href{https://CRAN.R-project.org/package=AustralianPoliticians}{{AustralianPoliticians:
+Provides Datasets About Australian Politicians}}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Dowding2021}{}}%
 \CSLLeftMargin{10. }%
-\CSLRightInline{Leslie, P.
-\emph{\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
-of the australian house of representatives (1945-2019)}}. (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-auspol}{}}%
-\CSLLeftMargin{11. }%
-\CSLRightInline{Alexander, R. \& Hodgetts, P. A.
-\emph{\href{https://CRAN.R-project.org/package=AustralianPoliticians}{AustralianPoliticians:
-Provides datasets about australian politicians}}. (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Dowding2021}{}}%
-\CSLLeftMargin{12. }%
-\CSLRightInline{Dowding, K., Leslie, P. \& Taflaga, M. Australia. in
-\emph{The politics of legislative debates} 130--151 (Oxford University
+\CSLRightInline{Dowding, K., Leslie, P. \& Taflaga, M. {Australia}. in
+\emph{{The Politics of Legislative Debates}} 130--151 (Oxford University
 Press, 2021).
@@
 \leavevmode\vadjust pre{\hypertarget{ref-salisbury2011}{}}%
+\CSLLeftMargin{11. }%
+\CSLRightInline{Salisbury, C. {'Mr Speaker, I withdraw...': standards of
+(mis) behaviour in the Queensland, Western Australian and Commonwealth
+parliaments compared via online Hansard}. \emph{Australasian
+Parliamentary Review} \textbf{26}, 166--177 (2011).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
+\CSLLeftMargin{12. }%
+\CSLRightInline{Rasiah, P. {A framework for the systematic analysis of
+evasion in parliamentary discourse}. \emph{Journal of Pragmatics}
+\textbf{42}, 664--680 (2010).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
 \CSLLeftMargin{13. }%
-\CSLRightInline{Salisbury, C. 'Mr speaker, i withdraw...': Standards of
-(mis) behaviour in the queensland, western australian and commonwealth
-parliaments compared via online hansard. \emph{Australasian
-Parliamentary Review} \textbf{26}, 166--177 (2011).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-rasiah2010framework}{}}%
+\CSLRightInline{Fraussen, B., Graham, T. \& Halpin, D. R. {Assessing the
+prominence of interest groups in parliament: a supervised machine
+learning approach}. \emph{The Journal of Legislative Studies}
+\textbf{24}, 450--474 (2018).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
 \CSLLeftMargin{14. }%
-\CSLRightInline{Rasiah, P. A framework for the systematic analysis of
-evasion in parliamentary discourse. \emph{Journal of Pragmatics}
-\textbf{42}, 664--680 (2010).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-fraussen2018}{}}%
+\CSLRightInline{Alexander, R. \& Alexander, M. {The Increased Effect of
+Elections and Changing Prime Ministers on Topics Discussed in the
+Australian Federal Parliament between 1901 and 2018}. \emph{arXiv
+preprint arXiv:2111.09299} (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
 \CSLLeftMargin{15. }%
-\CSLRightInline{Fraussen, B., Graham, T. \& Halpin, D. R. Assessing the
-prominence of interest groups in parliament: A supervised machine
-learning approach. \emph{The Journal of Legislative Studies}
-\textbf{24}, 450--474 (2018).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-alexander2021}{}}%
+\CSLRightInline{Temple Lang, D.
+\emph{\href{https://CRAN.R-project.org/package=XML}{{XML: Tools for
+Parsing and Generating XML Within R and S-Plus}}}. (2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
 \CSLLeftMargin{16. }%
-\CSLRightInline{Alexander, R. \& Alexander, M. The increased effect of
-elections and changing prime ministers on topics discussed in the
-australian federal parliament between 1901 and 2018. \emph{arXiv
-preprint arXiv:2111.09299} (2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-XML_pkg}{}}%
+\CSLRightInline{Wickham, H., Hester, J. \& Ooms, J.
+\emph{\href{https://CRAN.R-project.org/package=xml2}{{xml2: Parse
+XML}}}. (2021).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
 \CSLLeftMargin{17. }%
-\CSLRightInline{Temple Lang, D.
-\emph{\href{https://CRAN.R-project.org/package=XML}{XML: Tools for
-parsing and generating XML within r and s-plus}}. (2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-xml2_pkg}{}}%
+\CSLRightInline{Wickham, H.
+\href{https://doi.org/10.18637/jss.v059.i10}{{Tidy Data}}. \emph{Journal
+of Statistical Software} \textbf{59}, (2014).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
 \CSLLeftMargin{18. }%
-\CSLRightInline{Wickham, H., Hester, J. \& Ooms, J.
-\emph{\href{https://CRAN.R-project.org/package=xml2}{xml2: Parse XML}}.
-(2021).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Wickham2014}{}}%
-\CSLLeftMargin{19. }%
-\CSLRightInline{Wickham, H.
-\href{https://doi.org/10.18637/jss.v059.i10}{Tidy data}. \emph{Journal
-of Statistical Software} \textbf{59}, (2014).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-house2021}{}}%
-\CSLLeftMargin{20. }%
 \CSLRightInline{House of Representatives. \emph{{A window on the house:
@@
 \leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
-\CSLLeftMargin{21. }%
+\CSLLeftMargin{19. }%
 \CSLRightInline{Katz, L. \& Alexander, R. {A new, comprehensive database
@@
 \leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
+\CSLLeftMargin{20. }%
+\CSLRightInline{Parliament of Australia.
+\href{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}{{Infosheet
+22 - Political parties}}. \emph{House of Representatives Infosheets}
+(2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%
+\CSLLeftMargin{21. }%
+\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{{R:
+A Language and Environment for Statistical Computing}}}. (R Foundation
+for Statistical Computing, 2022).}
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
 \CSLLeftMargin{22. }%
-\CSLRightInline{Parliament of Australia.
-\href{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}{Infosheet
-22 - political parties}. \emph{House of Representatives Infosheets}
-(2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-auselect}{}}%
-\CSLLeftMargin{23. }%
-\CSLRightInline{Alexander, R.
-\emph{\href{https://github.com/RohanAlexander/AustralianElections}{AustralianElections:
-Datasets on australian elections}}. (2019).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-r_software}{}}%
-\CSLLeftMargin{24. }%
-\CSLRightInline{R Core Team. \emph{\href{https://www.R-project.org/}{R:
-A language and environment for statistical computing}}. (R Foundation
-for Statistical Computing, 2022).}
-
-\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
-\CSLLeftMargin{25. }%
 \CSLRightInline{Wickham, H. \emph{et al.}
-\href{https://doi.org/10.21105/joss.01686}{Welcome to the {tidyverse}}.
+\href{https://doi.org/10.21105/joss.01686}{{Welcome to the tidyverse}}.
 \emph{Journal of Open Source Software} \textbf{4}, 1686 (2019).}

### 2023-08-08 paper/paper-nature-revised.qmd
final small changes

@@
 As a result, the child node under which Federation Chamber proceedings are nested is named `<maincomm.xscript>` in all XML files prior to 14 August 2012.
-Having developed our first script based on Hansard from recent years, all XPath expressions contain the `<fedchamb.xscript>` specification.
+Having developed our first script based on Hansard from recent years, all XPath expressions for parsing Federation Chamber proceedings contain the `<fedchamb.xscript>` specification.
 To avoid causing issues in our first script which successfully parses about 10 years of Hansard, we created a second script where we replaced all occurrences of `<fedchamb.xscript>` with `<maincomm.xscript>`.
@@
 The challenge with parsing through the `<debate>` element is that every piece of data stored in that element is parsed as a single string, including all `<talk.start>` data, and all nested sub-debate data.
-For example, the data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:
+For example, the `<talker>` data shown in @fig-patternEX would be parsed as a single string preceding the speech content, like so:
 
@@
 This is a period of each sitting day in the Chamber where MPs can ask ministers two types of questions: questions in writing which are written in advance, or questions without notice which are asked verbally in the Chamber and are responded to in real time [@house2021].
-Questions without notice are included directly in the `"chamber.xscript"` child node, with sub-child nodes called `"question"` and `"answer"` to differentiate the two.
-Questions in writing, however, are embedded in their own child node called `"answers.to.questions"` at the end of the XML file.
+Questions without notice are included directly in the `<chamber.xscript>` child node, with sub-child nodes called `<question>` and `<answer>` to differentiate the two.
+Questions in writing, however, are embedded in their own child node called `<answers.to.questions>` at the end of the XML file.
 
-Our approach to parse the `"chamber.xscript"` speeches used in all four scripts meant that all questions without notice content was already parsed in order.
+Our approach to parse the `<chamber.xscript>` speeches used in all four scripts meant that all questions without notice content was already parsed in order.
 For the first two scripts, questions and answers were already separated onto their own rows.
 For the third and fourth scripts, just as we did with the rest of the speech content, we used those patterns of data preceding the text to separate questions and answers.
-Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was to extract all question and answer elements from the `"answers.to.questions"` child node.
+Finally, since questions in writing exist in their own child node we were able to use the same parsing method for all scripts, which was to extract all question and answer elements from the `<answers.to.questions>` child node.
 
@@
 The next step was to merge Question Time contents with all the debate speech.
-Our method of parsing meant that everything was already in order, so we did not have to perform any additional merging.
+As mentioned, our method of parsing meant that everything was already in order, so we did not have to perform any additional merging for questions without notice content.
 For questions in writing, merging this content was also straightforward due to the fact that it is always at the end of Hansard.
@@
 
-Once all interjections, comments and continuations were successfully split onto their own rows using the lists we created, we did one final check for any additional names that were not captured in these lists.
-To do so, we searched for any remaining name matches in speech bodies with general regular expressions and lookarounds, and separated text using those matches when found.
+Once all interjections, comments and continuations were split onto their own rows using the lists we created, we did one final check for any additional names that were not captured in these lists.
+We searched for any remaining name matches in speech bodies with general regular expressions and lookarounds, and separated text using those matches when found.
 
@@
 However, they provide valuable information about the inner-workings and structure of parliamentary events.
-If the focus of the user's research does not require stage directions, then this can be removed by filtering observations in `name` equal to "business start", or "stage direction".
+If the focus of the user's research does not require stage directions, then this can be removed by filtering out observations in `name` equal to "business start" or "stage direction".
 
@@
 
-While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (i.e.
+While we did our best to maximize the completeness of the files in our database as they were processed in the initial four scripts, there were still a number of rows in which details on the person speaking were missing, or the name transcribed for that individual was in a short form (e.g.
 "Mr Abbott" instead of "Abbott, Tony, MP").
@@
 Therefore, we took the first available page number child-node for each debate or sub-debate node to be the one we included in our dataset.
-After summarizing, these topics can be added to the main text by joining, and example code is provided in the README.
+After summarizing, these topics can be added to the main text by joining.
+Example code is provided in the README.
 
@@
 Details on these datasets can be found on the Party Facts datasets documentation page (https://partyfacts.herokuapp.com/documentation/datasets/).
-Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the [Usage Notes](#sec-usage) to follow.
+Details on the usage of `uniqueID` and `partyfacts_id` will be provided in the Usage Notes to follow.
 Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to.

### 2023-08-08 paper/paper-nature-revised.tex
final small changes

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{August 3, 2023}
+\date{August 8, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, enhanced, interior hidden, sharp corners]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, frame hidden, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
 
@@
 prior to 14 August 2012. Having developed our first script based on
-Hansard from recent years, all XPath expressions contain the
+Hansard from recent years, all XPath expressions for parsing Federation
+Chamber proceedings contain the
 \texttt{\textless{}fedchamb.xscript\textgreater{}} specification. To
@@
 string, including all \texttt{\textless{}talk.start\textgreater{}} data,
-and all nested sub-debate data. For example, the data shown in
+and all nested sub-debate data. For example, the
+\texttt{\textless{}talker\textgreater{}} data shown in
 Figure~\ref{fig-patternEX} would be parsed as a single string preceding
@@
 time\textsuperscript{18}. Questions without notice are included directly
-in the \texttt{"chamber.xscript"} child node, with sub-child nodes
-called \texttt{"question"} and \texttt{"answer"} to differentiate the
-two. Questions in writing, however, are embedded in their own child node
-called \texttt{"answers.to.questions"} at the end of the XML file.
-
-Our approach to parse the \texttt{"chamber.xscript"} speeches used in
-all four scripts meant that all questions without notice content was
-already parsed in order. For the first two scripts, questions and
-answers were already separated onto their own rows. For the third and
-fourth scripts, just as we did with the rest of the speech content, we
-used those patterns of data preceding the text to separate questions and
-answers. Finally, since questions in writing exist in their own child
-node we were able to use the same parsing method for all scripts, which
-was to extract all question and answer elements from the
-\texttt{"answers.to.questions"} child node.
+in the \texttt{\textless{}chamber.xscript\textgreater{}} child node,
+with sub-child nodes called \texttt{\textless{}question\textgreater{}}
+and \texttt{\textless{}answer\textgreater{}} to differentiate the two.
+Questions in writing, however, are embedded in their own child node
+called \texttt{\textless{}answers.to.questions\textgreater{}} at the end
+of the XML file.
+
+Our approach to parse the
+\texttt{\textless{}chamber.xscript\textgreater{}} speeches used in all
+four scripts meant that all questions without notice content was already
+parsed in order. For the first two scripts, questions and answers were
+already separated onto their own rows. For the third and fourth scripts,
+just as we did with the rest of the speech content, we used those
+patterns of data preceding the text to separate questions and answers.
+Finally, since questions in writing exist in their own child node we
+were able to use the same parsing method for all scripts, which was to
+extract all question and answer elements from the
+\texttt{\textless{}answers.to.questions\textgreater{}} child node.
 
@@
 The next step was to merge Question Time contents with all the debate
-speech. Our method of parsing meant that everything was already in
-order, so we did not have to perform any additional merging. For
-questions in writing, merging this content was also straightforward due
-to the fact that it is always at the end of Hansard. This means that we
-could bind question in writing rows to the bottom of the main dataframe.
-This approach was used for all four scripts.
+speech. As mentioned, our method of parsing meant that everything was
+already in order, so we did not have to perform any additional merging
+for questions without notice content. For questions in writing, merging
+this content was also straightforward due to the fact that it is always
+at the end of Hansard. This means that we could bind question in writing
+rows to the bottom of the main dataframe. This approach was used for all
+four scripts.
 
@@
 
-Once all interjections, comments and continuations were successfully
-split onto their own rows using the lists we created, we did one final
-check for any additional names that were not captured in these lists. To
-do so, we searched for any remaining name matches in speech bodies with
-general regular expressions and lookarounds, and separated text using
-those matches when found.
+Once all interjections, comments and continuations were split onto their
+own rows using the lists we created, we did one final check for any
+additional names that were not captured in these lists. We searched for
+any remaining name matches in speech bodies with general regular
+expressions and lookarounds, and separated text using those matches when
+found.
 
@@
 the user's research does not require stage directions, then this can be
-removed by filtering observations in \texttt{name} equal to ``business
-start'', or ``stage direction''.
+removed by filtering out observations in \texttt{name} equal to
+``business start'' or ``stage direction''.
 
@@
 missing, or the name transcribed for that individual was in a short form
-(i.e.~``Mr Abbott'' instead of ``Abbott, Tony, MP''). This was a
+(e.g.~``Mr Abbott'' instead of ``Abbott, Tony, MP''). This was a
 particularly frequent occurrence for sitting days where an MP spoke
@@
 sub-debate node to be the one we included in our dataset. After
-summarizing, these topics can be added to the main text by joining, and
-example code is provided in the README.
+summarizing, these topics can be added to the main text by joining.
+Example code is provided in the README.
 
@@
 the usage of \texttt{uniqueID} and \texttt{partyfacts\_id} will be
-provided in the \protect\hyperlink{sec-usage}{Usage Notes} to follow.
-Further, the \texttt{speech\_no} variable allows us to keep track of the
-speech number that each statement and interjection belongs to. Having
-the speech number variable offers an easy way to group statements by
-speech or isolate specific speeches of interest. Lastly, the
-\texttt{order} variable was added to maintain the order of proceedings,
-after all individual statements were separated onto their own rows.
+provided in the Usage Notes to follow. Further, the \texttt{speech\_no}
+variable allows us to keep track of the speech number that each
+statement and interjection belongs to. Having the speech number variable
+offers an easy way to group statements by speech or isolate specific
+speeches of interest. Lastly, the \texttt{order} variable was added to
+maintain the order of proceedings, after all individual statements were
+separated onto their own rows.
 

### 2023-08-10 paper/paper-nature-revised.qmd
final updates

@@
 An international linkage provides a comparison case where domestic issues are different while international ones are common.
-As an example of enabling this linkage we have included PartyFacts IDs in our database.
+As an example of enabling this linkage we have included PartyFacts IDs (https://partyfacts.herokuapp.com) in our database.
 This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].
 
-The Australian House of Representatives 'the House' performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
+The Australian House of Representatives, often referred to as 'the House', performs a number of crucial governmental functions, such as creating new laws and overseeing government expenditure [@australia2018house, ch.
 1].
@@
 To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website.
-For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created (http://historichansard.net/).
+For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created by Tim Sherratt (http://historichansard.net/).
 These data can be navigated by year, parliament, people, and bills.
-To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created (https://github.com/palesl/AustralianHouseOfRepresentatives).
+To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created by Patrick Leslie (https://github.com/palesl/AustralianHouseOfRepresentatives).
 Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol.
@@
 As evident in @fig-xml2, `<talk.start>` nodes are nested within `<interjection>` nodes, meaning that the patterns of data from interjection statements were separated out in the process.
-In other words, our approach to data cleaning in the third and fourth scripts separated out interjections in the process.
 This meant that we did not need to create lists of names and titles for which to search in the text as we did before.
@@
 We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag those rows where "The House divided." was detected in the body variable.
-The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website (https://partyfacts.herokuapp.com).
+The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project website.
 Note that in accordance with the code provided on the Party Facts downloads page (https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov.
@@
 To enhance the usability of our database, we added a `uniqueID` variable to each file.
-This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` [@auspol] and `AustralianElections` R packages (https://github.com/RohanAlexander/AustralianElections).
+This serves as a unique identifier for each speaking MP, and comes from the `uniqueID` variable present within data from both the `AustralianPoliticians` R package, [@auspol] and the `AustralianElections` (https://github.com/RohanAlexander/AustralianElections) R package, which was created by Rohan Alexander.
 By including this variable, one can integrate our data records with those available in these two packages.

### 2023-08-10 paper/paper-nature-revised.tex
final updates

@@
   of Toronto, rohan.alexander@utoronto.ca}}
-\date{August 8, 2023}
+\date{August 10, 2023}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, breakable, enhanced, frame hidden, sharp corners, boxrule=0pt, interior hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
 
@@
 international ones are common. As an example of enabling this linkage we
-have included PartyFacts IDs in our database. This should make it
-possible to link our database with other large parliamentary speech
-collection projects, such as ParlaMint\textsuperscript{4},
-ParlSpeech\textsuperscript{5}, ParlEE\textsuperscript{6}, and
-MAPLE\textsuperscript{7}.
-
-The Australian House of Representatives `the House' performs a number of
-crucial governmental functions, such as creating new laws and overseeing
-government expenditure\textsuperscript{8, ch.~1}. Politicians in the
-House are referred to as Members of Parliament (MPs). The House operates
-under a parallel chamber setup, meaning there are two debate venues
-where proceedings take place: the Chamber, and the Federation Chamber.
+have included PartyFacts IDs (https://partyfacts.herokuapp.com) in our
+database. This should make it possible to link our database with other
+large parliamentary speech collection projects, such as
+ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
+ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.
+
+The Australian House of Representatives, often referred to as `the
+House', performs a number of crucial governmental functions, such as
+creating new laws and overseeing government
+expenditure\textsuperscript{8, ch.~1}. Politicians in the House are
+referred to as Members of Parliament (MPs). The House operates under a
+parallel chamber setup, meaning there are two debate venues where
+proceedings take place: the Chamber, and the Federation Chamber.
 Sittings of the House follow a predefined order of business, regulated
@@
 website. For instance, an online, easy to read database of Hansard from
-1901 to 1980 using the XML files has been created
+1901 to 1980 using the XML files has been created by Tim Sherratt
 (http://historichansard.net/). These data can be navigated by year,
@@
 Handbook more accessible, an \texttt{R} package which includes data on
-all MPs from 1945 to 2019 has been created
+all MPs from 1945 to 2019 has been created by Patrick Leslie
 (https://github.com/palesl/AustralianHouseOfRepresentatives). Further,
@@
 patterns of data from interjection statements were separated out in the
-process. In other words, our approach to data cleaning in the third and
-fourth scripts separated out interjections in the process. This meant
-that we did not need to create lists of names and titles for which to
-search in the text as we did before. However, we used the same list of
-general interjection statements on which to separate as was used in the
-first two scripts. We then did an additional check for statements that
-may have not been separated due to how they were embedded in the XML,
-and separated those out where needed. In particular, while most
-statements were categorized in their own child node and hence captured
-through pattern-based separation, some were not individually
-categorized, and had to be split manually in this step.
+process. This meant that we did not need to create lists of names and
+titles for which to search in the text as we did before. However, we
+used the same list of general interjection statements on which to
+separate as was used in the first two scripts. We then did an additional
+check for statements that may have not been separated due to how they
+were embedded in the XML, and separated those out where needed. In
+particular, while most statements were categorized in their own child
+node and hence captured through pattern-based separation, some were not
+individually categorized, and had to be split manually in this step.
 
@@
 package, and the \texttt{partyfacts\_id} variable was added using code
-and data provided by the Party Facts Project website
-(https://partyfacts.herokuapp.com). Note that in accordance with the
-code provided on the Party Facts downloads page
+and data provided by the Party Facts Project website. Note that in
+accordance with the code provided on the Party Facts downloads page
 (https://partyfacts.herokuapp.com/download/), we used only the core
@@
 speaking MP, and comes from the \texttt{uniqueID} variable present
-within data from both the
-\texttt{AustralianPoliticians}\textsuperscript{9} and
-\texttt{AustralianElections} R packages
-(https://github.com/RohanAlexander/AustralianElections). By including
-this variable, one can integrate our data records with those available
-in these two packages. Similarly, we added the \texttt{partyfacts\_id}
-variable to our data which allows users to link our data to external
-political party data sources with this unique identifier.
+within data from both the \texttt{AustralianPoliticians} R
+package,\textsuperscript{9} and the \texttt{AustralianElections}
+(https://github.com/RohanAlexander/AustralianElections) R package, which
+was created by Rohan Alexander. By including this variable, one can
+integrate our data records with those available in these two packages.
+Similarly, we added the \texttt{partyfacts\_id} variable to our data
+which allows users to link our data to external political party data
+sources with this unique identifier.
 

### 2023-08-10 paper/paper-nature-revised.tex
re-rendered with updated images

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, interior hidden, frame hidden]}{\end{tcolorbox}}\fi
 
